### 2022-01-31 manuscript.tex
Abstract and edits to text. Figure uniform colors and auto creation script

\documentclass[aps,twocolumn]{revtex4-1}

% Maths
\usepackage{bm}
\usepackage{amsmath}

% Text
\usepackage{siunitx}

% Figures
\usepackage{graphicx}
\usepackage{subfig}

% Referencing
\usepackage{cleveref}
\newcommand{\ccite}[1]{ref.~\cite{#1}}
\newcommand{\Ccite}[1]{Ref.~\cite{#1}}
\newcommand{\ccites}[1]{refs.~\cite{#1}}
\newcommand{\Ccites}[1]{Refs.~\cite{#1}}

% Temp
\usepackage{lipsum}
\usepackage{xcolor}
\newcommand{\temp}[1]{{\leavevmode\color{red}#1}}
\newcommand*{\newlinecommand}[2]{%
  \newcommand*{#1}{%
    \begingroup%
    \escapechar=`\\%
    \catcode\endlinechar=\active%
    \csname\string#1\endcsname%
  }%
  \begingroup%
  \escapechar=`\\%
  \lccode`\~=\endlinechar%
  \lowercase{%
    \expandafter\endgroup
    \expandafter\def\csname\string#1\endcsname##1~%
  }{\endgroup#2\space}%
}
\newlinecommand{\topic}{\textbf{#1}}

\begin{document}
\title{Efficient saddle point search - Binary image transistion state search}
\author{Sam Avis}
\author{Jack Panter}
\author{Halim Kusumaatmaja}

\begin{abstract}
  Locating transition states is crucial for investigating minimum energy transition mechanisms, which have been widely investigated for atomistic systems and, more recently, macroscale applications.
  However, macroscale systems in particular pose certain challenges that are largely unaddressed by existing methods.
  We introduce a new double-ended search method, the Binary Image Transition State Search (BITSS), to address these.
  This uses just two states that converge at the transition state, resulting in a faster and more memory-efficient method than existing double-ended methods.
  We demonstate BITSS is able to overcome challenges resulting from adaptive remeshing and short-range potentials, and can even be used for discontinuous energy potentials.
\end{abstract}

\maketitle

%\section{Introduction \& Method}
\topic Transition states provide fundamental insight into the stability and possible reconfiguration of systems in chemistry, condensed matter physics, and engineering.
Historically, the development of computational methods for locating transition states in free or potential energy landscapes has focused significantly upon particulate and atomistic systems.
In these, the energy barrier between a local energy minimum and a transition state informs the probability of the transition occurring within a thermalised population, and ultimately reaction rates and kinetics \temp{[cite]}.
The energy barriers can also be used to characterise the behaviour of molecules and structures with large numbers of stable configurations, which has applications to protein folding \cite{Bryngelson1995,Onuchic1997}, crystalisation and clusters \cite{Wales1998,Wales2012}.

\topic In addition to these microscale applications it is also increasingly being recognised that transition states are useful in mesoscale or macroscale systems.
Here, the minimum energy barriers provide important lower bounds to the energy input required for transitions to occur.
This is essential to capture in, for example, structural engineering applications, where the minimum energy mechanism for structural failure must be known in order to ensure safety \cite{Panter2019,Hutchinson2018}.
Moreover, it is becoming desirable to tailor elastic deformation transitions to enable technologies such as advanced deployable structures \cite{Filipov2015,Zhai2018}, mechanical sensors and actuators, and energy absorption \cite{Shan2015} to name but a few.
Probing minimum energy transition mechanisms are also essential to the development of super liquid-repellent surfaces \cite{Zhang2014,Panter2019b}, and are even finding applications in robotics in efficient locomotion through complex terrain \cite{Othayoth2020}.

\topic Existing transition state search methods generally fall into two categories, single- and double-ended methods.
Single-ended methods are initialised at a single state, typically a minimum in the potential energy landscape, and attempt to identify nearby saddle points.
These methods can converge to a transition state quickly, although are not well suited to identifying specific pathways because a single minimum can be surrounded by many saddle points.
Examples include eigenvector following \cite{Cerjan1981}, the dimer method \cite{Heyden2005,Kastner2008}, and climbing image methods \cite{E2007,Ren2013}.
Double-ended methods, such as the string method \cite{E2002,E2007} and doubly-nudged elastic band (DNEB) \cite{Trygubenko2004}, involve initialising a chain of states between two minima and then minimising the total energy of the chain.
In addition to approximating the transition state, these are useful for obtaining an estimate for the full transition pathway.

\topic Despite this wide variety of existing methods, there are still some important classes of problems particularly relevant to macro-scale applications that have not yet been adequately addressed.
One key problem involves systems that have extremely large numbers of degrees of freedom, such as large particulate systems or discretisations of 3D continuum systems.
In this case, double-ended methods can become computationally expensive, or even prohibitive, owing to the tens of states that are required to accurately approximate the transition state.
An approach to reduce the computational overhead in many macro-scale simulations is adaptive coarse-graining or remeshing. \temp{[cite]}
However, for a transition state search method to utilise this it must be able to deal with changing numbers of degrees of freedom as the method runs.
This is a particular problem for double-ended methods for which each of the states will have a different discretisation.
Further issues arise for systems with short-range contact forces, such as hard-core particles \temp{[cite]} and patchy colloids \temp{[cite]}.
In this case, in many configurations there will exist soft-modes where the landscape is locally flat. \temp{[cite]}
This can cause issues for single-ended search methods that rely only upon local information.
Finally, if short-range interactions are chosen that are discontinuous the gradients will be undefined, in which case typical landscape methods that require continuous, differentiable optimisation functions will not be appropriate.

\topic In this work we introduce a new method, the Binary Image Transition State Search (BITSS), and demonstrate how it addresses each of these challenges.
This method combines aspects of the two traditional categories; it is a double-ended method that uses just two states that converge from two local minima towards a transition state that separates them.
The states, $\bm{x}_1$ and $\bm{x}_2$, are first initialised in different basins of attraction of the local minima.
While these can be set to the minima, this is not a necessary requirement.
Upon application of the BITSS method, the two images are brought closer to the ridge separating the basins of attraction, while also minimising the energy of the pair of images.
In this way, the two images meet at the lowest energy point on the ridge - the transition state.
This is demonstrated for a simple 2D potential with two minima in \cref{fig:toy2d}a.

\begin{figure}[htb]
  \centering
  \includegraphics{fig/toy2d.pdf}
  \caption{
    (a) The trajectories of the two states under the BITSS method for a simple 2D potential with two minima (blue dots).
        The transition state is shown by an red dot, and the minimum energy pathway by the dashed line.
    (b) A snapshot of the BITSS minimisation showing the driving forces on each state due to the energy constraint, $\bm{F}_E$, and distance constraint, $\bm{F}_D$, with $E_1 < E_2$ and $d(\bm{x}_1,\bm{x}_2) > d_i$.
    (c) The final configuration of the BITSS method showing the two states in orange, the transition state in red, and the negative curvature eigenvector, $\bm{\hat{\tau}}$.
  }
  \label{fig:toy2d}
\end{figure}

\topic Two soft constraints are used to achieve the transition state convergence, while preventing either from passing over the dividing ridge.
The former is implemented by constraining the distance between the states and iteratively reducing the target separation, $d_i$, from the initial separation, $d_0$, by a constant factor:
\begin{equation}
  d_{i+1} = (1 - f) d_i.
  \label{eq:diteration}
\end{equation}
We find that a factor of $f = 0.5$ is succesful for most applications, but this can be made smaller to ensure that the states do not slide off the ridge.
The second constraint sets the energies of the two states to be equal.
This ensures neither state can pass over the ridge so long as the distance is not reduced too quickly.
These constraints are implemented using quadratic energy penalty terms, resulting in the following potential for the pair of states,
\begin{multline}
  V_\text{BITSS}(\bm{x}_1, \bm{x}_2) = E_1 + E_2
    + \kappa_e \left( E_1 - E_2 \right) ^2 \\
    + \kappa_d \left( \mathrm{d}(\bm{x}_1, \bm{x}_2) - d_i \right) ^2,
  \label{eq:bitss}
\end{multline}
where $E_1$ and $E_2$ are the single state energies, and $\mathrm{d}(\bm{x}_1, \bm{x}_2)$ is the measure of distance between the two states.
The energy constraint pushes the state with a higher energy down the potential, and the lower energy state up, while the distance constraint pulls them together if their separation is too great, and pushes them apart if they are too close.
These driving forces are demonstrated for the 2D potential in \cref{fig:toy2d}b.

\topic The method is sensitive to the choice of the constraint coefficients, $\kappa_d$ and $\kappa_e$, with optimal values depending upon the specific problem.
Also, as the separation between the states decreases the coefficients will have to change, making them difficult to assign manually.
Consequently, we automate their assignment using information from the system.
They are initially calculated at the start of each minimisation, and regularly recalculated throughout (once per 100 iterations are used in this work).
The coefficients are chosen such that each term in the gradient of \cref{eq:bitss} is of a similar size, providing the following expressions,
\begin{gather}
  \kappa_e = \frac {\alpha} {2 \Delta E},
  \label{eq:ke}
  \\
  \kappa_d = \text{max} \left(
    \frac {\sqrt{|\bm{\nabla} E_1|^2 + |\bm{\nabla} E_2|^2}} {2\sqrt{2} \beta d_i} \; , \;
    \frac{\Delta E}{\beta d_i^2} \right),
  \label{eq:kd}
\end{gather}
where $\alpha$ and $\beta$ are parameters with recommended values of $\alpha = 10$ and $\beta = 0.1$ (see supplementary information).
$\Delta E$ is an estimation for the current energy barrier which is evaluated by linearly interpolating between the two current states.
For systems where the interpolation deviates significantly from the MEP this estimate can be much too large.
In which case, a maximum estimated value for the barrier can be provided, which then decreases proportionally with $d_i$.

\topic In summary, the method involves iteratively performing the following three steps:
\begin{enumerate}
  \item Reduce the target separation using \cref{eq:diteration}.
  \item Compute the constraint coefficients using \cref{eq:ke,eq:kd}.
  \item Minimise the potential, \cref{eq:bitss}, and recompute the coefficients every 100 iterations of the minimisation.
\end{enumerate}
Any minimisation algorithm can be used in step three; in this work the L-BFGS algorithm is chosen, owing to its fast convergence and low memory requirement for large numbers of degrees of freedom \cite{Liu1989}.
Finally, the convergence criteria for the method can be based upon either the separation between the states, or the size of gradient at the estimate for the transition state midway between the two states.

% This is here to prevent it being put on the wrong page
\begin{figure*}[tb]
  \centering
  \includegraphics{fig/speedtest-a.pdf}%
  \includegraphics{fig/speedtest-b.pdf}%
  \includegraphics{fig/speedtest-c.pdf}%
  \caption{
    The rate of convergence to the transition state for (a) a Lennard-Jones seven-particle cluster, (b) cylindrical shell buckling, (c) wetting of a chemically-striped surface.
    Above are the two minimum energy states and the transition state between them.
    Below is shown the convergence to the transition state as a function of the number of gradient calculations using the BITSS (black line) and string methods.
    The string method is repeated with a differing number of images along the string, the number of which is listed in the legend in (c).
  }
  \label{fig:speedtest}
\end{figure*}

\topic The typical trajectory of the two states in the BITSS method is shown in \cref{fig:toy2d}a.
Initially, the lower energy state jumps up to satisfy the equal energy constraint and then moves to reduce the separation as much as possible without increasing it's energy.
Then, the two states begin to converge directly towards one another, before being deflected in the direction of a saddle in the potential.
Consequently, if there are multiple possible pathways between two states, BITSS will be biased towards identifying pathways that are more direct or with lower energy.
As the two states approach the transition state, the path they take begins to closely follow the minimum energy pathway (MEP), which is the path that follows the gradient from the minima and passes through the transition state.
Therefore, the final two states are positioned in the direction of the negative curvature eigenvector, $\bm{\hat{\tau}}$, as shown in \cref{fig:toy2d}c.
So it is also possible to obtain the eigenvector and eigenvalue using BITSS.

\topic Once BITSS has identified the transition state it is possible to find the full MEP.
This is done by tracing the trajectory of downhill minimisations from either side of the transition state, which are provided by the two final states of BITSS.
To ensure this pathway is sufficiently smooth the maximum step size of the minimisation should be restricted.

%\section{Speed Comparison}
\topic As a result of the BITSS method using only two states it has the potential to be significantly faster than chain-of-states approaches which typically use tens of states.
This is tested here by measuring the speed of convergence to the transition state for BITSS in comparison with the string method and DNEB for several representitive examples.
The accuracy of the BITSS method is calculated using the distance between the correct transition state and the average of the two states.
While for the chain-of-states methods, the accuracy is measured as the distance of the transition state from a cubic spline interpolation of the points along the string.
For each method, the accuracy is measured against the number of times the energy and gradient of the system are evaluated.
The results of this are shown in \cref{fig:speedtest} and \temp{SI} for the string method and DNEB respectively.

\topic The first system to be tested is a two-dimensional seven-particle cluster with Lennard-Jones interactions.
The transition begins with the hexagonal cluster and involves two particles shifting to reach a higher energy configuration.

\topic The second system is an elastic cylindrical shell under an applied strain.
This undergoes a transition from an unbuckled state to a singly-dimpled state, which defines the minimum energy required for the cylinder to buckle \cite{Panter2019}.
A 2D triangular mesh is used to model this system, with the following energy function,
\begin{equation}
  E = \sum_i k^S_i (r_i - r^0_i)^2 + \sum_j k^B_j [1 + \text{cos}(\theta_j - \theta^0_j)].
\end{equation}
The first term provides the stretching energy for the system using a sum over all the bonds, where $r_i$ is the length, $r^0_i$ --- the equilibrium length, and $k^S_i$ --- the stretching rigidity of bond $i$.
The second term models the bending energy by representing each pair of adjacent triangles as an elastic hinge.
For hinge $j$, $\theta_j$ is the dihedral angle, $\theta^0_j$ --- the equilibrium angle, and $k^B_j$ --- the bending rigidity.

\topic The final system involves a droplet situated on a chemically striped surface with both hydrophilic and hydrophobic regions.
This has two possible states, with the droplet either upon one hydrophilic stripe, or straddling across two.
This is modelled on a 200x200 2D grid using a phase-field model \cite{Panter2019b}, which has an order parameter, $\phi(\bm{r})$, representing the phase of the liquid ($\phi=-1$ for gas, $\phi=1$ for liquid).
The energy functional has four separate terms,
\begin{equation}
  E[\phi] = E_B + E_I + E_S + E_V.
\end{equation}
The first term, $E_B$, uses a double well potential to set values of $\phi=\pm1$ in the bulk.
The second term then provides the interfacial energy between the liquid and gas by imposing an energy penalty to changes in $\phi$.
$E_S$ is the solid-liquid interaction energy, which sets the contact angles of the hydrophilic and hydrophobic regions to 60\si{\degree} and 110\si{\degree}, respectively.
Finally, $E_V$ constrains the volume of the liquid drop by penalising any variation from 11\% of the total volume of the system.

\topic The results for this test, shown in \cref{fig:speedtest}, demonstrate two main advantages for the BITSS method.
Firstly, the slope illustrates that the rate of convergence is indeed much greater for the BITSS method.
It is matched only by the initial rate of the string method using less than ten images, however these soon slow and are relatively inaccurate.
Secondly, the BITSS method can more accurately approximate the transition state by orders of magnitude, particularly for the wetting example where the string method does not significantly improve upon the initial pathway estimate.
Therefore, unlike the string method, BITSS does not require a second approach to accurately locate the transition state.
Similar results are also found when comparing against against DNEB, which can be seen in the supplementary information.

%\section{Adaptive mesh}
\topic To further increase the speed of the method we can use adaptive remeshing and coarse-graining to lower the resolution of the system in regions with few changing features.
However, this introduces additional complexity to the method.
It must be able to handle both the degrees of freedom changing, and the two states having separate discretisations.
Here we test each of these issues individually.

\topic Firstly, we demonstrate in \cref{fig:adaptivemesh}a that BITSS is indeed able to handle the discretisation changing as the method runs.
For this we use the cylindrical buckling example with the resolution increasing from 40 to 100 triangles around the cylinder.
These changes are performed after the minimisation step in each iteration of the BITSS method.
This demonstrates that BITSS is able to converge to the transition state so long as the remeshing is not so drastic that one state is shifted into the basin of another minima.

\topic For the second test, we investigate how BITSS performs when the two states have different meshes.
The only special consideration needed for this is that the distance measure must take into account the different grids.
This is done here by interpolating one state onto the other grid and computing the Euclidean distance.
Although, for some applications it may be sufficient to use simpler distance measures, such as the difference between average values of the system.
The results for the striped wetting example with two different resolutions (shown in \cref{fig:adaptivemesh}b) demonstates that BITSS is successful.
Notably however, there is a limit to how close the two states can get.
This is because the energy of the transition state is slightly different on each grid, so eventually the energy constraint will fail.
Despite this, the two states are still able to get very close and give a very good approximation to the transition state.
Furthermore, using an adaptive grid model the grids would also be expected to converge, thereby eliminating the issue.

\begin{figure}[tb]
  \centering
  \begin{tabular}[b]{c}
    \includegraphics{fig/changingmesh.pdf}\\
    \includegraphics{fig/differentgrids.pdf}%
  \end{tabular}
  \caption{
    (a) Snapshots of the BITSS method applied to the buckling of a cylinder with a changing mesh.
        The radial displacement relative the unbuckled cylinder is shown, as well as the underlying triangular mesh.
    (b) BITSS applied to the striped wetting example with different resolutions for the two states.
        Each grid cell denotes 50x50 lattice nodes.
        The zoomed axes shows the difference in the fluid interface between the two final states, as well as the approximated transition state (solid black line).
        This is compared to the true transition state found using a high resolution for both states (dashed line).
  }
  \label{fig:adaptivemesh}
\end{figure}

%\section{Zero-curvature modes}
\topic Interaction potentials in many particulate and macroscale systems are short-range, and often limited to contact forces.
Thus, there may be many regions in the potential energy landscape that are locally flat.
Single-ended search methods generally only use local information, and so require specialist treatment to deal with these zero modes.
For example, global translation and rotation in free space require analytic expressions for the translation and rotation vectors, which are known.
However, these single-ended search methods are thwarted by local zero modes.

\topic In \cref{fig:flatdiscontinuous}a we demonstrate the BITSS method applied to a 2D potential with regions containing such zero modes (i \& ii).
We see it is able to successfully converge past these flat regions, even with one very close to the transition state (ii).
In these regions there are no driving forces due to the potential and the energy constraint, which use purely local information about the gradient.
However, the distance constraint continues to pull the states together, preventing them from getting stuck.
When only a single state has a zero-gradient mode then the other is likely to slide down the potential slightly, causing a kink in the pathway (iii).
Although, the two states still remain either side of the dividing ridge and so the result will be unaffected.
Indeed, it may only cause BITSS to fail if the zero-gradient mode is positioned at the transition state in the direction of the pathway.
But in this case there is no single transition state, instead the MEP would have a flat section at the top of its energy profile.

\begin{figure}[tb]
  \centering
  \begin{tabular}[b]{c}
    \includegraphics{fig/zeroeigen.pdf}\\
    \includegraphics{fig/discontinuous.pdf}
  \end{tabular}
  \caption{
    (a) Energy profile of the BITSS pathway on a 2D potential with flat regions.
        The minima and transition state are marked by blue and red dots respectively.
        Points of interest are labelled by i-iii.
        Top inset: A zoomed in view around the transition state.
        Bottom inset: The pathway taken, with the edges of the flat regions marked by dashed lines.
    (b) Disconnectivity graph of the energy landscape for a seven-particle cluster with a discontinuous hard-core pair potential.
    (c) Plot of the discontinuous potential.
        The repulsive section of the usual Lennard-Jones potential is also shown in grey.
  }
  \label{fig:flatdiscontinuous}
\end{figure}

%\section{Gradient-free problems}
\topic In many cases contact forces may be chosen to be infinite to prevent overlap of solid bodies.
This results in the energy landscape becoming discontinuous with regions of undefined gradients.
Alternatively, for some systems the potential energy gradients may be prohibitively expensive to compute, or not available.
In both cases, typical landscapes methods that require continuous, differentiable (often twice-differentiable) optimisation functions will not be appropriate.

\topic However, BITSS can be used for these systems with undefined gradients with just a couple of alterations.
First, the term using gradients in \cref{eq:kd} can be ignored and $\kappa_d$ can instead be calculated using just the second term.
Next we must use a minimiser that does not require a differentiable optimisation function; for this we use simulated annealing \cite{Kirkpatrick1983}.
This has a chance of randomly jumping one state over the dividing barrier, but we can reduce this probability by setting the initial temperature to $T_0 = \frac{\Delta E}{10}$, and the maximum size of random displacements to $d_\text{max} = d(\bm{x}_1, \bm{x}_2) / 100$.

\topic This has been tested using a Lennard-Jones 7-particle cluster with hard cores, resulting in a discontinuous landscape.
Using the gradient-free approach, BITSS is able to successfully find the transition states, allowing us to plot the disconnectivity graph of the system, as shown in \cref{fig:flatdiscontinuous}b.
This is compared with the results for the standard Lennard-Jones cluster in the supplementary information.
It is worth noting that gradient-based approaches are significantly more efficient, so these should be preferred if possible.

%\section{Conclusion}
\topic In conclusion, we have demonstrated a novel method for finding transition states that tackles some problems not currently addressed by existing methods.
The method has advantages over current double-ended methods because it is more efficient, both in terms of memory and computational cost, and does not require an initial estimate for the pathway, useful for systems with non-linear pathways.
Furthermore, we have demonstrated that the method can sucessfully be used with adaptive mesh algorithms, as well as systems with flat or discontinuous energy landscapes.

\bibliographystyle{plain}
\bibliography{../../library.bib}

\end{document}

### 2022-01-31 fig/create_figs.sh

@@ -1,0 +1,10 @@
+#!/bin/bash
+
+figures=('toy2d' 'speedtest' 'changingmesh' 'differentgrids' 'zeroeigen' 'discontinuous')
+
+for fig in ${figures[@]}; do
+  echo "Plotting $fig"
+  cd make_$fig
+  python3 ./plot.py
+  cd ..
+done

### 2022-01-31 fig/make_differentgrids/plot.py

@@ -22,8 +22,8 @@ hs3 = 0.0 # vertical space above arrow box
 zoom_region = [0.595, -0.01, 0.04, 0.08]
 cs1 = 'lightgrey' # hydrophobic
 cs2 = 'k'         # hydrophilic
-cz1 = 'orange'
-cz2 = 'red'
+cz1 = style.c1
+cz2 = style.c2
 
 
 def load_data(data_file):

### 2022-01-31 fig/make_discontinuous/plot.py

@@ -79,7 +79,7 @@ def plot_cluster(x, ax):
 
 
 def plot_potenial(ax):
-    c = 'C1'
+    c = style.c1
     xpad = 0#-2
     ypad = 0
     arrow_len = 0.3

### 2022-01-31 fig/make_speedtest/plot.py

@@ -41,9 +41,11 @@ for subfig in ['a', 'b', 'c']:
 
     ### Plot data
     width = 1/3
-    aspect_ratio = 1 / (1/1.618 + 1/3)
-    fig = lt.figure(width, aspect_ratio)
-    ax = plt.axes((0.21, 0.15, 0.76, 1-aspect_ratio/3-0.16))
+    h1 = 1/1.618 # height of lower axes relative to width
+    h2 = 1/3 # height of upper axes relative to width
+    h = h1 + h2
+    fig = lt.figure(width, h)
+    ax = plt.axes((0.19, 0.13, 0.78, h1/h-0.1))
     fig.text(0, 1, f'({subfig})', va='top', ha='left')
 
     if (subfig == 'a'):
@@ -58,7 +60,7 @@ for subfig in ['a', 'b', 'c']:
 
     # Plot lines
     for i, n in enumerate(string_n):
-        plt.plot(string_calls[i], string_dist[i], lw=1, label=n)
+        plt.plot(string_calls[i], string_dist[i], lw=1, label=n, c=style.colors[i])
     # for i, n in enumerate(dneb_n):
     #    plt.plot(dneb_calls[i], dneb_dist[i], lw=1, label=n)
     plt.plot(bits_calls, bits_dist, c='k', lw=1.5)#, label='BITSS')
@@ -66,7 +68,7 @@ for subfig in ['a', 'b', 'c']:
     plt.semilogy()
     plt.tick_params('both', which='minor')
     plt.xlabel('Gradient evalulations')
-    plt.ylabel('Distance error')
+    plt.ylabel('Distance error', labelpad=-0.5)
     if (subfig == 'a'):
         plt.xlim(0, 1600)
         plt.ylim(bottom=1e-5)
@@ -80,9 +82,10 @@ for subfig in ['a', 'b', 'c']:
         plt.xticks([0,20000,40000])
 
     for i in range(3):
-        plt.axes((0.035+i*0.31, 1-0.31, 0.31, 0.31))
+        tmp_ax = plt.axes((0.035+i*0.31, 1-0.31, 0.31, 0.31))
         img = mim.imread(f'{subfig}{i}.png')
         plt.imshow(img)
-        plt.gca().axis('off')
+        tmp_ax.axis('off')
+        tmp_ax.set_zorder(ax.get_zorder()-1)
     # plt.savefig(f'speedtest-dneb-{subfig}.png')
     lt.savefig(f'../speedtest-{subfig}.pdf', dpi=300)

### 2022-01-31 fig/make_toy2d/plot.py

@@ -18,6 +18,11 @@ ar1 = 0.4
 ar2 = 0.5
 ldx = 0#.008
 
+cbits = style.c1
+cts = style.c2
+cmin = style.c3
+cenergy = style.c3
+cdist = style.c2
 cmap = 'Greys_r'
 mec = 'k'
 ms = 6
@@ -101,12 +106,12 @@ img = mim.imread('potential.png')
 axa.imshow(img, extent=(xlim[0],xlim[1],ylim[0],ylim[1]))
 
 # Minima & TS
-axa.plot(minima[:,0], minima[:,1], 'bo', mec=mec, ms=ms, zorder=99)
-axa.plot(ts[0], ts[1], marker='o', mec=mec, ms=ms, zorder=99, c='orange')
+axa.plot(minima[:,0], minima[:,1], c=cmin, marker='o', mec=mec, ms=ms, ls='none', zorder=99)
+axa.plot(ts[0], ts[1], c=cts, marker='o', mec=mec, ms=ms, zorder=99)
 
 # BITS
-axa.plot(bits[:,0,0], bits[:,0,1], c='r', zorder=2)
-axa.plot(bits[:,1,0], bits[:,1,1], c='r', zorder=2)
+axa.plot(bits[:,0,0], bits[:,0,1], c=cbits, zorder=2)
+axa.plot(bits[:,1,0], bits[:,1,1], c=cbits, zorder=2)
 
 # Pathway
 axa.plot(path[:,0], path[:,1], ls='--', c='k', zorder=1)
@@ -133,24 +138,24 @@ for c in cnt.collections:
 # axb.contour(x, y, e, levels=levels, colors='k', linestyles='solid', linewidths=clw)
 # axb.contour(x, y, e, levels=[e0], colors='k', linestyles='solid', linewidths=1.5*clw)
 
-axb.plot(x1[0], x1[1], 'ro', mec=mec, ms=ms, zorder=99)
-axb.plot(x2[0], x2[1], 'ro', mec=mec, ms=ms, zorder=99)
+axb.plot(x1[0], x1[1], c=cbits, marker='o', mec=mec, ms=ms, zorder=99)
+axb.plot(x2[0], x2[1], c=cbits, marker='o', mec=mec, ms=ms, zorder=99)
 arrow_args = {'units':'xy', 'width':0.018, 'headwidth':4, 'headlength':4, 'headaxislength':3.5, 'scale':2, 'zorder':98}
[…]

### 2022-01-31 fig/make_zeroeigen/plot.py

@@ -22,10 +22,10 @@ y0 = 0.3
 dx = 2.5
 dy = dx * ax_size[1][3] / ax_size[1][2] * aspect
 
-cmin = 'b'
-cpath = 'tab:red'
-cts = 'orange'
-ms = 4
+cpath = style.c1
+cts = style.c2
+cmin = style.c3
+ms = 5
 mec = 'k'
 lw = 1.2
 

### 2022-01-31 fig/style.py

@@ -6,3 +6,29 @@ import pyutils.latexify as lt
 lt.update_width('r4-single')
 plt.rc('font', size=9)
 plt.rc('axes', labelsize=9)
+
+c1 = 'tab:orange'
+c2 = 'tab:red'
+c3 = 'tab:blue'
+colors = [c1, c2, c3]
+
+
+### Make sure this is reloaded by IPython ###
+# exit_register runs at the end of ipython %run or the end of the python interpreter
+from IPython import get_ipython
+ip = get_ipython()
+if (ip == None):
+    from atexit import register as exit_register
+else:
+    def exit_register(fun, *args, **kwargs):
+        """ Decorator that registers at post_execute. After its execution it
+        unregisters itself for subsequent runs. """
+        def callback():
+            fun()
+            ip.events.unregister('post_execute', callback)
+        ip.events.register('post_execute', callback)
+@exit_register
+def reset_rcparams():
+    # Ensure IPython reloads the module
+    import sys
+    del sys.modules['style']

### 2022-02-01 manuscript.tex
Made changes to match PRL guidelines

@@
-\documentclass[aps,twocolumn]{revtex4-1}
+\documentclass[aps,prl,twocolumn,groupedaddress]{revtex4}
 
@@
 \author{Halim Kusumaatmaja}
+\affiliation{Department of Physics, Durham University, South Road, Durham DH1 3LE, UK}
 
@@
 \begin{figure}[htb]
-  \centering
   \includegraphics{fig/toy2d.pdf}
@@
 $\Delta E$ is an estimation for the current energy barrier which is evaluated by linearly interpolating between the two current states.
-For systems where the interpolation deviates significantly from the MEP this estimate can be much too large.
+For systems where the interpolation deviates significantly from the minimum energy pathway this estimate can be much too large.
 In which case, a maximum estimated value for the barrier can be provided, which then decreases proportionally with $d_i$.
@@
 \begin{figure*}[tb]
-  \centering
   \includegraphics{fig/speedtest-a.pdf}%
@@
 Consequently, if there are multiple possible pathways between two states, BITSS will be biased towards identifying pathways that are more direct or with lower energy.
-As the two states approach the transition state, the path they take begins to closely follow the minimum energy pathway (MEP), which is the path that follows the gradient from the minima and passes through the transition state.
+As the two states approach the transition state, the path they take begins to closely follow the minimum energy pathway, which is the path that follows the gradient from the minima and passes through the transition state.
 Therefore, the final two states are positioned in the direction of the negative curvature eigenvector, $\bm{\hat{\tau}}$, as shown in \cref{fig:toy2d}c.
@@
 
-\topic Once BITSS has identified the transition state it is possible to find the full MEP.
+\topic Once BITSS has identified the transition state it is possible to find the full minimum energy pathway.
 This is done by tracing the trajectory of downhill minimisations from either side of the transition state, which are provided by the two final states of BITSS.
@@
 The first term, $E_B$, uses a double well potential to set values of $\phi=\pm1$ in the bulk.
-The second term then provides the interfacial energy between the liquid and gas by imposing an energy penalty to changes in $\phi$.
+The second term then provides the interfacial energy between the liquid and gas by imposing an energy penalty to gradients in $\phi$.
 $E_S$ is the solid-liquid interaction energy, which sets the contact angles of the hydrophilic and hydrophobic regions to 60\si{\degree} and 110\si{\degree}, respectively.
@@
 \begin{figure}[tb]
-  \centering
   \begin{tabular}[b]{c}
@@
 Indeed, it may only cause BITSS to fail if the zero-gradient mode is positioned at the transition state in the direction of the pathway.
-But in this case there is no single transition state, instead the MEP would have a flat section at the top of its energy profile.
+But in this case there is no single transition state, instead the minimum energy pathway would have a flat section at the top of its energy profile.
 
 \begin{figure}[tb]
-  \centering
   \begin{tabular}[b]{c}
@@
 Next we must use a minimiser that does not require a differentiable optimisation function; for this we use simulated annealing \cite{Kirkpatrick1983}.
-This has a chance of randomly jumping one state over the dividing barrier, but we can reduce this probability by setting the initial temperature to $T_0 = \frac{\Delta E}{10}$, and the maximum size of random displacements to $d_\text{max} = d(\bm{x}_1, \bm{x}_2) / 100$.
+This has a chance of randomly jumping one state over the dividing barrier, but we can reduce this probability by setting the initial temperature to $T_0 = \Delta E / 10$, and the maximum size of random displacements to $d_\text{max} = d(\bm{x}_1, \bm{x}_2) / 100$.
 
@@
 
-\bibliographystyle{plain}
+% \bibliographystyle{apsrev4-2}
 \bibliography{../../library.bib}

### 2022-02-07 si/supplementary_information.tex
SI: Constraint coefficients sections done.

\documentclass[aps,prl]{revtex4}

% Maths
\usepackage{bm}
\usepackage{amsmath}
\newcommand{\abs}[1]{\left| #1 \right|}
\newcommand{\grad}[1]{\bm{\nabla} #1}

% Referencing
\usepackage{cleveref}
\renewcommand{\theequation}{S\arabic{equation}}

% Figures
\usepackage{graphicx}

\begin{document}
\title{Supplementary Information}
\maketitle

\section{Constraint coefficients}
The constraint coefficients are chosen to set comparable sizes for each term in the gradient of the BITSS potential,
\begin{equation}
  \grad{E_{tot}} = \sum_{\substack{i=1,2 \\ j\neq i}} \left[ 1 + 2 \kappa_e (E_i - E_j) \right] \grad{E_i} + 2 \kappa_d (d - d_0) \grad{d}.
\end{equation}

To obtain the expression for the energy coefficient we first assume that the separation is fixed, so the distance term can be ignored.
The coefficient must be high enough to prevent one state from being pulled over the ridge, for which the greatest risk occurs when the gradient on one state is much greater than the other, $\abs{\grad{E_2}} \gg \abs{\grad{E_1}}$.
In this case the total gradient is approximated by
\begin{equation}
  \grad{E_{tot}} = \left[ 1 - 2 \kappa_e (E_1 - E_2) \right] \grad{E_2}.
\end{equation}
This will converge when the term in the square brackets is zero, resulting in $\kappa_e = 1 / 2 (E_1 - E_2)$.
To ensure this is large enough we can replace the energy difference with the estimate for the energy barrier, $\Delta E$, and then scale it by a factor, $\alpha$, that is greater than or equal to one,
\begin{equation}
  \kappa_e = \frac {\alpha} {2 \Delta E}.
\end{equation}

The distance coefficient is determined by assuming that the energies are equal and thus the energy constraint can be ignored.
In this case, convergence will occur when $\grad{E_1} + \grad{E_2} = -2 \kappa_d (d - d_0) \grad{d}$.
By comparing the magnitude of the two sides it is possible to obtain an expression for the coefficient in terms of the relative error in the distance, $\beta = (d - d_0) / d_0$.
(Note: The gradient of the distance with respect to a single state has a magnitude of 1, thus $\abs{\grad{d}} = \sqrt{2}$.)
A lower bound on the size of the coefficient is also set using the estimated energy barrier to ensure that the distance constraint is applied even when the gradient is close to zero, such as at the minima.
\begin{equation}
  \kappa_d = \mathrm{max} \! \left(
  \frac {\sqrt{\abs{\grad{E_1}}^2 + \abs{\grad{E_2}}^2}} {2 \sqrt{2} \beta d_0}, \quad
  \frac{\Delta E}{\beta d_0^2} \right).
\end{equation}

In practice, when numerically minimising, the states will jump about slightly which can result in large gradients perpendicular to the optimal movement direction.
To reduce this effect, the size of the gradients in the direction separating the two states are instead calculated:
\begin{equation}
  \abs{\grad{E_i}} \approx \frac {\abs{(\bm{x}_1 - \bm{x}_2) \cdot \grad{E_i}}} {\abs{\bm{x}_1 - \bm{x}_2}}.
\end{equation}

\section{Parameter test}
The constant parameters $\alpha$ and $\beta$ still must be chosen.
To this end we have tested different parameter choices using the seven-particle cluster and cylindrical buckling examples.
\Cref{fig:paramtest} shows which choices lead to convergence and the speed at which they do.
The parameters $\alpha = 10$ and $\beta = 0.1$ are chosen for both converging quickly and being situated far from the regions of non-convergence.
Hence, this choice is unlikely to fail if the boudaries of the regions were to shift under different systems.

\begin{figure} \label{fig:paramtest}
  \includegraphics{fig/paramtest-a.pdf}%
  \includegraphics{fig/paramtest-b.pdf}%
  \caption{
    Speed of convergence of the BITSS method under different choices of parameters for (a) the seven-particle cluster, (b) cylindrical buckling.
    The speed is given by the number of evaluations of the gradient until the two states are separated by less than a thousandth of the initial separation.
    The combinations that do not converge to the transition state are shown in grey. 
    The chosen parameters are marked by a red star.
  }
\end{figure}

\section{Test potentials and gradients}

\section{7 particle cluster comparison}

\end{document}

### 2022-02-07 si/fig/paramtest/plot.py

@@ -1,0 +1,53 @@
+import copy
+import json
+import numpy as np
+from matplotlib import pyplot as plt, cm
+from scipy.ndimage import gaussian_filter
+from pyutils import latexify as lt
+# Get default style for SI
+import sys; sys.path.insert(0, '..')
+import style
+
+subfigs = ['a', 'b']
+systems = ['lj', 'cb']
+levels = [[600, 1000, 2000],
+          [42000, 45000, 50000]]
+label_locs = [[(4.5, 0.1), (10, 0.1), (50,0.19)],
+              [(10, 0.03), (18, 0.13), (180, 0.05)]]
+
+cmap = copy.copy(cm.get_cmap('viridis'))
+cmap.set_bad('lightgrey')
+
+with open('data.json', 'r') as f:
+    data = json.load(f)
+for i, system in enumerate(systems):
+    d = data[system]
+    shape = (len(np.unique(d['alpha'])), -1)
+    alpha = np.reshape(d['alpha'], shape)
+    beta = np.reshape(d['beta'], shape)
+    fc = np.reshape(d['fc'], shape)
+    
+    fig = lt.figure(0.5)
+    fig.text(0, 1, f'({subfigs[i]})', ha='left', va='top')
+    ax = fig.add_axes((0.15, 0.17, 0.78, 0.81))
+    plt.semilogx()
+    plt.semilogy()
+
+    # Colormap
+    plt.pcolormesh(alpha, beta, fc, shading='nearest', cmap=cmap, vmax=np.nanpercentile(fc,90), ec='face', lw=0.1)
+    plt.colorbar(label='function calls')
+
+    # Contours
+    filter1 = gaussian_filter(np.where(np.isnan(fc), 0., fc), 1, truncate=1)
+    filter2 = gaussian_filter(np.where(np.isnan(fc), 0., 1.), 1, truncate=1)
+    filtered = np.where(np.isnan(fc), np.nan, filter1/filter2)
+    contour = plt.contour(alpha, beta, filtered, colors='w', levels=levels[i])
+    plt.clabel(contour, fmt="%d", manual=label_locs[i])
+
+    plt.plot([10], [0.1], marker='*', c='r', zorder=99)
+
+    plt.xlabel(r'$\alpha$')
+    plt.ylabel(r'$\beta$')
+    plt.xticks([0.1, 1, 10, 100, 1000, 10000])
+    plt.minorticks_off()
+    lt.savefig(f'../paramtest-{subfigs[i]}.pdf')

### 2022-02-07 si/fig/style.py

@@ -1,0 +1,34 @@
+#!/usr/bin/env python3
+
+import matplotlib.pyplot as plt
+import pyutils.latexify as lt
+
+lt.update_width('r4')
+plt.rc('font', size=9)
+plt.rc('axes', labelsize=9)
+
+c1 = 'tab:orange'
+c2 = 'tab:red'
+c3 = 'tab:blue'
+colors = [c1, c2, c3]
+
+
+### Make sure this is reloaded by IPython ###
+# exit_register runs at the end of ipython %run or the end of the python interpreter
+from IPython import get_ipython
+ip = get_ipython()
+if (ip == None):
+    from atexit import register as exit_register
+else:
+    def exit_register(fun, *args, **kwargs):
+        """ Decorator that registers at post_execute. After its execution it
+        unregisters itself for subsequent runs. """
+        def callback():
+            fun()
+            ip.events.unregister('post_execute', callback)
+        ip.events.register('post_execute', callback)
+@exit_register
+def reset_rcparams():
+    # Ensure IPython reloads the module
+    import sys
+    del sys.modules['style']

### 2022-02-10 si/supplementary_information.tex
Added SI figures and bar and hinge gradients

@@
 \renewcommand{\theequation}{S\arabic{equation}}
+\renewcommand{\thefigure}{S\arabic{figure}}
 
@@
 The constraint coefficients are chosen to set comparable sizes for each term in the gradient of the BITSS potential,
-\begin{equation}
-  \grad{E_{tot}} = \sum_{\substack{i=1,2 \\ j\neq i}} \left[ 1 + 2 \kappa_e (E_i - E_j) \right] \grad{E_i} + 2 \kappa_d (d - d_0) \grad{d}.
+\begin{equation} \label{eq:gradBITSS}
+  \grad{E_\text{BITSS}} = \sum_{\substack{i=1,2 \\ j\neq i}} \left[ 1 + 2 \kappa_e (E_i - E_j) \right] \grad{E_i} + 2 \kappa_d (d - d_0) \grad{d}.
 \end{equation}
@@
 To this end we have tested different parameter choices using the seven-particle cluster and cylindrical buckling examples.
-\Cref{fig:paramtest} shows which choices lead to convergence and the speed at which they do.
+\Cref{fig:paramtest} shows which choices lead to convergence and the speed at which this occurs.
 The parameters $\alpha = 10$ and $\beta = 0.1$ are chosen for both converging quickly and being situated far from the regions of non-convergence.
-Hence, this choice is unlikely to fail if the boudaries of the regions were to shift under different systems.
+Hence, this choice is unlikely to fail if the boudaries of the regions were to shift for different systems.
 
-\begin{figure} \label{fig:paramtest}
+\begin{figure}
   \includegraphics{fig/paramtest-a.pdf}%
   \includegraphics{fig/paramtest-b.pdf}%
-  \caption{
+  \caption{\label{fig:paramtest}
     Speed of convergence of the BITSS method under different choices of parameters for (a) the seven-particle cluster, (b) cylindrical buckling.
@@
 \section{Test potentials and gradients}
+\begin{figure}
+  \includegraphics{fig/BAHschematic.pdf}
+  \caption{\label{fig:BAHschematic}
+    Schematic of the bar and hinge model showing the relevent parameters for a single hinge element. $h_i$ and $\bm{\hat{n}}_i$ denote the height and unit normal of each triangle respectively.
+  }
+\end{figure}
+To use L-BFGS minisation the gradients of the optimisation function must be known.
+For the BITSS potential this is given by \cref{eq:gradBITSS}, but this still requires knowledge of the gradients of the system under consideration.
+For the cylindrical buckling example we can obtain the gradient by considering each bond and hinge individually.
+Using the schematic in \cref{fig:BAHschematic}, the gradient of the stretching energy of the bond between $\bm{x}_2$ and $\bm{x}_3$ is given by,
+\begin{equation}
+  \frac{\partial E^S}{\partial \bm{x}_2} = - \frac{\partial E^S}{\partial \bm{x}_3} = 
+    2 k^S (r - r^0) (\bm{x_2} - \bm{x_3}).
+\end{equation}
+While the gradients of the bending energy of the hinge are,
+\begin{align}
+  \frac{\partial E^B}{\partial \bm{x}_1} &= k^B \sin(\theta - \theta^0) \frac{\bm{\hat{n}}_a}{h_a}, \\
+  \frac{\partial E^B}{\partial \bm{x}_2} &= - k^B \sin(\theta - \theta^0) \left[\frac{\bm{\hat{n}}_a}{h_a} + \frac{\bm{\hat{n}}_a + \bm{\hat{n}}_b}{r}\right], \\
+  \frac{\partial E^B}{\partial \bm{x}_3} &= - k^B \sin(\theta - \theta^0) \left[\frac{\bm{\hat{n}}_b}{h_b} + \frac{\bm{\hat{n}}_a + \bm{\hat{n}}_b}{r}\right], \\
+  \frac{\partial E^B}{\partial \bm{x}_4} &= k^B \sin(\theta - \theta^0) \frac{\bm{\hat{n}}_b}{h_b}.
+\end{align}
+
+\section{DNEB speedtest}
 

### 2022-02-10 si/fig/create_figs.sh

@@ -1,0 +1,20 @@
+#!/bin/bash
+
+py_figs=('paramtest')
+tex_figs=('BAHschematic')
+
+for fig in ${py_figs[@]}; do
+  echo "Plotting $fig"
+  cd make_$fig
+  python3 ./plot.py
+  cd ..
+done
+
+for fig in ${tex_figs[@]}; do
+  echo "Plotting $fig"
+  pdflatex -interaction=nonstopmode -file-line-error -jobname=$fig make_$fig/plot.tex | \
+    grep -v "[0-9]*/[0-9]*/[0-9]*/[0-9]*:[0-9]*:[0-9]*" | \
+    grep ".*:[0-9]*:\|Warning\|Overfull" --color=always
+  rm $fig.aux
+  rm $fig.log
+done

### 2022-02-15 si/supplementary_information.tex
SI finished

@@
 \newcommand{\abs}[1]{\left| #1 \right|}
-\newcommand{\grad}[1]{\bm{\nabla} #1}
+\newcommand{\grad}{\bm{\nabla}}
+\newcommand{\upDelta}{\mathop{}\!\Delta}
 
@@
 \begin{equation} \label{eq:gradBITSS}
-  \grad{E_\text{BITSS}} = \sum_{\substack{i=1,2 \\ j\neq i}} \left[ 1 + 2 \kappa_e (E_i - E_j) \right] \grad{E_i} + 2 \kappa_d (d - d_0) \grad{d}.
+  \grad E_\text{BITSS} = \sum_{\substack{i=1,2 \\ j\neq i}} \left[ 1 + 2 \kappa_e (E_i - E_j) \right] \grad E_i + 2 \kappa_d (d - d_0) \grad d.
 \end{equation}
@@
 To obtain the expression for the energy coefficient we first assume that the separation is fixed, so the distance term can be ignored.
-The coefficient must be high enough to prevent one state from being pulled over the ridge, for which the greatest risk occurs when the gradient on one state is much greater than the other, $\abs{\grad{E_2}} \gg \abs{\grad{E_1}}$.
+The coefficient must be high enough to prevent one state from being pulled over the ridge, for which the greatest risk occurs when the gradient on one state is much greater than the other, $\abs{\grad E_2} \gg \abs{\grad E_1}$.
 In this case the total gradient is approximated by
 \begin{equation}
-  \grad{E_{tot}} = \left[ 1 - 2 \kappa_e (E_1 - E_2) \right] \grad{E_2}.
+  \grad E_{tot} = \left[ 1 - 2 \kappa_e (E_1 - E_2) \right] \grad E_2.
 \end{equation}
 This will converge when the term in the square brackets is zero, resulting in $\kappa_e = 1 / 2 (E_1 - E_2)$.
-To ensure this is large enough we can replace the energy difference with the estimate for the energy barrier, $\Delta E$, and then scale it by a factor, $\alpha$, that is greater than or equal to one,
+To ensure this is large enough we can replace the energy difference with the estimate for the energy barrier, $\upDelta E$, and then scale it by a factor, $\alpha$, that is greater than or equal to one,
 \begin{equation}
-  \kappa_e = \frac {\alpha} {2 \Delta E}.
+  \kappa_e = \frac {\alpha} {2 \upDelta E}.
 \end{equation}
@@
 The distance coefficient is determined by assuming that the energies are equal and thus the energy constraint can be ignored.
-In this case, convergence will occur when $\grad{E_1} + \grad{E_2} = -2 \kappa_d (d - d_0) \grad{d}$.
+In this case, convergence will occur when $\grad E_1 + \grad E_2 = -2 \kappa_d (d - d_0) \grad d$.
 By comparing the magnitude of the two sides it is possible to obtain an expression for the coefficient in terms of the relative error in the distance, $\beta = (d - d_0) / d_0$.
-(Note: The gradient of the distance with respect to a single state has a magnitude of 1, thus $\abs{\grad{d}} = \sqrt{2}$.)
+(Note: The gradient of the distance with respect to a single state has a magnitude of 1, thus $\abs{\grad d} = \sqrt{2}$.)
 A lower bound on the size of the coefficient is also set using the estimated energy barrier to ensure that the distance constraint is applied even when the gradient is close to zero, such as at the minima.
@@
   \kappa_d = \mathrm{max} \! \left(
-  \frac {\sqrt{\abs{\grad{E_1}}^2 + \abs{\grad{E_2}}^2}} {2 \sqrt{2} \beta d_0}, \quad
-  \frac{\Delta E}{\beta d_0^2} \right).
+  \frac {\sqrt{\abs{\grad E_1}^2 + \abs{\grad E_2}^2}} {2 \sqrt{2} \beta d_0}, \quad
+  \frac{\upDelta E}{\beta d_0^2} \right).
 \end{equation}
 
-In practice, when numerically minimising, the states will jump about slightly which can result in large gradients perpendicular to the optimal movement direction.
-To reduce this effect, the size of the gradients in the direction separating the two states are instead calculated:
-\begin{equation}
-  \abs{\grad{E_i}} \approx \frac {\abs{(\bm{x}_1 - \bm{x}_2) \cdot \grad{E_i}}} {\abs{\bm{x}_1 - \bm{x}_2}}.
-\end{equation}
-
-\section{Parameter test}
-The constant parameters $\alpha$ and $\beta$ still must be chosen.
-To this end we have tested different parameter choices using the seven-particle cluster and cylindrical buckling examples.
-\Cref{fig:paramtest} shows which choices lead to convergence and the speed at which this occurs.
-The parameters $\alpha = 10$ and $\beta = 0.1$ are chosen for both converging quickly and being situated far from the regions of non-convergence.
-Hence, this choice is unlikely to fail if the boudaries of the regions were to shift for different systems.
-
-\begin{figure}
+\begin{figure}[b]
   \includegraphics{fig/paramtest-a.pdf}%
@@
 
+In practice, when numerically minimising, the states will jump about slightly which can result in large gradients perpendicular to the optimal movement direction.
+To reduce this effect, the size of the gradients in the direction separating the two states are instead calculated:
+\begin{equation}
+  \abs{\grad E_i} \approx \frac {\abs{(\bm{x}_1 - \bm{x}_2) \cdot \grad E_i}} {\abs{\bm{x}_1 - \bm{x}_2}}.
+\end{equation}
+
+The constant parameters $\alpha$ and $\beta$ still must be chosen.
+To this end we have tested different parameter choices using the seven-particle cluster and cylindrical buckling examples.
+\Cref{fig:paramtest} shows which choices lead to convergence and the speed at which this occurs.
+The parameters $\alpha = 10$ and $\beta = 0.1$ are chosen for both converging quickly and being situated far from the regions of non-convergence.
+Hence, this choice is unlikely to fail if the boudaries of the regions were to shift for different systems.
+
 \section{Test potentials and gradients}
-\begin{figure}
+To use L-BFGS minisation the gradients of the optimisation function must be known.
+For the BITSS potential this is given by \cref{eq:gradBITSS}, but this also requires the gradients of the system under consideration.
+
+\subsection{Particle cluster}
+For the Lennard-Jones particle cluster the gradient of the potential is found by considering the gradient of the interaction between each pair of particles,
+\begin{equation}
+  \frac{\partial E}{\partial \bm{x}_1} = -\frac{\partial E}{\partial \bm{x}_2} = - \frac{24 \epsilon}{r^2}
+    \left[ 2 \left(\frac{\sigma}{r}\right)^{12} - \left(\frac{\sigma}{r}\right)^6 \right] (\bm{x}_1 - \bm{x}_2),
+\end{equation}
+where $\bm{x}_1$ and $\bm{x}_2$ are the positions of the two particles, $r$ is their separation, $\epsilon$ is the interaction strength, and $\sigma$ is the particle radius.
+
+\subsection{Cylindrical buckling}
+\begin{figure}[htb]
   \includegraphics{fig/BAHschematic.pdf}
@@
 \end{figure}
-To use L-BFGS minisation the gradients of the optimisation function must be known.
-For the BITSS potential this is given by \cref{eq:gradBITSS}, but this still requires knowledge of the gradients of the system under consideration.
 For the cylindrical buckling example we can obtain the gradient by considering each bond and hinge individually.
@@
 
-\section{DNEB speedtest}
+\subsection{Striped wetting}
+The four sections of the phase-field model detailed in \namecref{eq:gradBITSS}~(6) are obtained using the following equations,
+\begin{align}
+  E_B[\phi] &= \sum_i \frac{1}{\epsilon} \left( \frac{{\phi_i}^4}{4} - \frac{{\phi_i}^2}{2} + \frac{1}{4} \right) \upDelta V,\\
+  E_I[\phi] &= \sum_i \frac{\epsilon}{2} \abs{\grad \phi_i}^2 \upDelta V,\\
+  E_S[\phi] &= \sum_j \sqrt{2}\cos\theta_j \left( \frac{{\phi_j}^3}{6} - \frac{\phi_j}{2} - \frac{1}{3} \right) \upDelta S,\\
+  E_V[\phi] &= k_V \left[ \sum_i \frac{\phi_i + 1}{2} \upDelta V - V_0 \right]^2,
+\end{align}
+where the index $i$ includes all of the nodes, while $j$ represents the nodes along the solid surface.
+$\upDelta V$ and $\upDelta S$ are, respectively, the volume and solid surface areas contained by each individual node.
+$\epsilon$ is the liquid-gas interface width, $\theta_j$ --- the contact-angle with the solid surface, and $V_0$ --- the constrained volume of the liquid drop.
+The strength of the volume constraint is parametrised by $k_V$ for which we use a value of $10^4$.
+The gradients of these terms are given by,
+\begin{align}
+  \frac{\partial E_B}{\partial \phi_i} &= \frac{1}{\epsilon} \left( {\phi_i}^3 - \phi_i \right) \upDelta V,\\
+  \frac{\partial E_I}{\partial \phi_i} &= \frac{\epsilon}{2} \left[
+    \frac{\partial \abs{\grad \phi_i}^2}{\partial \phi_i} +
+    \sum_k\frac{\partial \abs{\grad \phi_k}^2}{\partial \phi_i} \right] \upDelta V,\\
+  \frac{\partial E_S}{\partial \phi_j} &= \sqrt{2}\cos\theta_j \left( \frac{{\phi_j}^2}{2} - \frac{1}{2} \right) \upDelta S,\\
+  \frac{\partial E_V}{\partial \phi_i} &= k_V \left[ \sum_{i'} \frac{\phi_{i'} + 1}{2} \upDelta V - V_0 \right] \upDelta V,
+\end{align}
+where index $k$ denotes neighboring nodes at which the evaluation of the gradient uses $\phi_i$.
 
-\section{7 particle cluster comparison}
+\begin{figure}[htb]
+  \includegraphics{fig/DNEBspeedtest.pdf}
+  \caption{\label{fig:DNEBspeedtest}
+    The rate of convergence to the transition state for (a) a Lennard-Jones seven-particle cluster, (b) cylindrical shell buckling, (c) wetting of a chemically-striped surface.
+    Above are the two minimum energy states and the transition state, marked by an asterisk.
+    Below is shown the convergence to the transition state as a function of the number of gradient calculations using BITSS (black line) and DNEB.
+    The DNEB results are repeated with differing numbers of images along the chain, the number of which is listed in the legend in (c).
+  }
+\end{figure}
+
+\begin{figure}[htb]
+  \includegraphics{fig/clusterdgraphs.pdf}
+  \caption{\label{fig:clusterdgraphs}
+    Differences in the disconnectivity graphs for the seven-particle cluster when using the discontinuous potential instead of the standard Lennard-Jones potential.
+The two graphs are horizontally offset for visibility.
+The energies of the transition states are found to be slightly higher when using the discontinuous potential.
+  }
+\end{figure}
 

### 2022-02-15 si/fig/make_DNEBspeedtest/plot.py

@@ -1,0 +1,89 @@
+#!/usr/bin/env python3
+
+import numpy as np
+import pandas as pd
+import matplotlib.pyplot as plt
+import matplotlib.image as mim
+import pyutils.latexify as lt
+# Get default style for si
+import sys; sys.path.insert(0, '..')
+import style
+
+def str_converter(instr):
+    return np.fromstring(instr[1:-1],sep=' ')
+
+y0 = 0.15
+h1 = 0.62/3 # height of lower axes relative to width
+h2 = 1/9 # height of upper axes relative to width
+h = h1 + h2
+fig = lt.figure(1, h)
+
+for isub, subfig in enumerate(['a', 'b', 'c']):
+
+    ### Load data
+    if (subfig == 'a'):
+        file = 'lj_data'
+    elif (subfig == 'b'):
+        file = 'cb_data'
+    elif (subfig == 'c'):
+        file = 'sw_data'
+    df = pd.read_csv(file, converters={'calls':str_converter, 'distance':str_converter})
+
+    bits_data = df[df['method']=='bits']
+    bits_calls = bits_data['calls'][0]
+    bits_dist = bits_data['distance'][0]
+
+    dneb_data = df[df['method']=='dneb']
+    dneb_n = np.array(dneb_data['n'])
+    dneb_calls = np.array(dneb_data['calls'])
+    dneb_dist = np.array(dneb_data['distance'])
+
+
+    ### Plot data
+    x0 = isub / 3
+    ax = plt.axes((x0+0.19/3, y0, 0.26, h1/h-y0+0.03))
+    fig.text(x0, 1, f'({subfig})', va='top', ha='left')
+
+    if (subfig == 'a'):
+        ax.annotate('BITSS', [0.1, 0.08], [0.2, 0.1], xycoords='axes fraction',
+                    arrowprops={'arrowstyle':'-'}, bbox={'pad':0, 'fc':'none', 'ec':'none'})
+        ax.annotate('DNEB', [0.48, 0.29], [0.53, 0.53], xycoords='axes fraction',
+                    arrowprops={'arrowstyle':'-'}, bbox={'pad':0, 'fc':'none', 'ec':'none'})
+        ax.annotate('DNEB', [0.38, 0.42], [0.53, 0.53], xycoords='axes fraction', alpha=0,
[…]

### 2022-02-15 si/fig/make_clusterdgraphs/plot.py

@@ -1,0 +1,135 @@
+#!/usr/bin/env python3
+import glob
+import numpy as np
+import pandas as pd
+import matplotlib.pyplot as plt
+from matplotlib.lines import Line2D
+import networkx as nx
+from pele.utils.disconnectivity_graph import DisconnectivityGraph
+
+import pyutils.latexify as lt
+# Get default style for paper
+import sys; sys.path.insert(0, '..')
+import style
+
+c1 = style.c1
+c2 = 'k'
+
+ndof = 14
+
+class Node:
+    def __init__(self, i, e, x):
+        self.i = i
+        self.energy = e
+        self.x = x
+    def __hash__(self):
+        return self.i
+    def __str__(self):
+        return 'Node '+str(self.i)
+    def __eq__(self, other):
+        return hash(self) == hash(other)
+    def __lt__(self, other):
+        return hash(self) < hash(other)
+
+class TS:
+    def __init__(self, min1, min2, e):
+        self.minimum1 = min1
+        self.minimum2 = min2
+        self.energy = e
+    def __hash__(self):
+        return hash(self.minimum1) ^ hash(self.minimum2)
+    def __str__(self):
+        return 'TS '+str(self.i)
+    def __eq__(self, other):
+        return hash(self) == hash(other)
+    def __lt__(self, other):
+        return hash(self) < hash(other)
+
+
+def load_data(potential):
+    # minima
+    minima = pd.read_csv(f'{potential}-min.data')
+    min_e = np.array(minima['energy'])
+    min_x = minima[[f'x{i}' for i in range(ndof)]].to_numpy()
+    nodes = [Node(i, min_e[i], min_x[i]) for i in range(len(minima))]
+    # TS
+    e_ts = np.loadtxt(f'{potential}-ts.data', usecols=0)
+    pairs = np.loadtxt(f'{potential}-ts.data', usecols=[3,4], dtype=int) - 1
+    ts = [TS(nodes[pair[0]], nodes[pair[1]], e_ts[i]) for i, pair in enumerate(pairs)]
+    return nodes, ts
+
+
+def make_dgraph(nodes, ts):
+    # Generate disconnectivity graph
[…]

### 2022-02-16 manuscript.tex
Jack's suggestions. Intro and conclusion

@@
 \usepackage{graphicx}
-\usepackage{subfig}
 
@@
 \newlinecommand{\topic}{\textbf{#1}}
+% \newlinecommand{\topic}{#1}
 
 \begin{document}
-\title{Efficient saddle point search - Binary image transistion state search}
+\title{Locating saddle points in complex and memory intensive landscapes}
 \author{Sam Avis}
@@
 \begin{abstract}
-  Locating transition states is crucial for investigating minimum energy transition mechanisms, which have been widely investigated for atomistic systems and, more recently, macroscale applications.
-  However, macroscale systems in particular pose certain challenges that are largely unaddressed by existing methods.
-  We introduce a new double-ended search method, the Binary Image Transition State Search (BITSS), to address these.
-  This uses just two states that converge at the transition state, resulting in a faster and more memory-efficient method than existing double-ended methods.
-  We demonstate BITSS is able to overcome challenges resulting from adaptive remeshing and short-range potentials, and can even be used for discontinuous energy potentials.
+  Locating transition states is crucial for investigating transition mechanisms in atomistic systems and, more recently, macroscale applications.
+  However, these pose certain challenges that are largely unaddressed by existing methods.
+  We introduce a new double-ended method, the Binary Image Transition State Search (BITSS), that uses just two states that converge to the transition state, resulting in a faster and more memory-efficient method than current approaches.
+  We demonstate it succesfully overcomes challenges associated with large-scale systems and complex energy landscapes.
 \end{abstract}
@@
 %\section{Introduction \& Method}
-\topic Transition states provide fundamental insight into the stability and possible reconfiguration of systems in chemistry, condensed matter physics, and engineering.
-Historically, the development of computational methods for locating transition states in free or potential energy landscapes has focused significantly upon particulate and atomistic systems.
-In these, the energy barrier between a local energy minimum and a transition state informs the probability of the transition occurring within a thermalised population, and ultimately reaction rates and kinetics \temp{[cite]}.
-The energy barriers can also be used to characterise the behaviour of molecules and structures with large numbers of stable configurations, which has applications to protein folding \cite{Bryngelson1995,Onuchic1997}, crystalisation and clusters \cite{Wales1998,Wales2012}.
+\topic Transition states are central to the description of reconfiguration mechanisms for systems in chemistry, condensed matter physics, and engineering.
+Historically, many computational methods for locating transition states have grown from an atomistic or particulate perspective.
+These have proven to be important tools for understanding, for example, protein folding \cite{Bryngelson1995,Onuchic1997}, biological and industrial catalysis \temp{[cite]}, crystallisation, and cluster formation \cite{Wales1998,Wales2012}.
 
@@
 \topic Existing transition state search methods generally fall into two categories, single- and double-ended methods.
-Single-ended methods are initialised at a single state, typically a minimum in the potential energy landscape, and attempt to identify nearby saddle points.
-These methods can converge to a transition state quickly, although are not well suited to identifying specific pathways because a single minimum can be surrounded by many saddle points.
+Single-ended methods are initialised at a single state and attempt to climb to a nearby saddle point.
 Examples include eigenvector following \cite{Cerjan1981}, the dimer method \cite{Heyden2005,Kastner2008}, and climbing image methods \cite{E2007,Ren2013}.
@@
 
-\topic Despite this wide variety of existing methods, there are still some important classes of problems particularly relevant to macro-scale applications that have not yet been adequately addressed.
-One key problem involves systems that have extremely large numbers of degrees of freedom, such as large particulate systems or discretisations of 3D continuum systems.
-In this case, double-ended methods can become computationally expensive, or even prohibitive, owing to the tens of states that are required to accurately approximate the transition state.
-An approach to reduce the computational overhead in many macro-scale simulations is adaptive coarse-graining or remeshing. \temp{[cite]}
-However, for a transition state search method to utilise this it must be able to deal with changing numbers of degrees of freedom as the method runs.
-This is a particular problem for double-ended methods for which each of the states will have a different discretisation.
-Further issues arise for systems with short-range contact forces, such as hard-core particles \temp{[cite]} and patchy colloids \temp{[cite]}.
-In this case, in many configurations there will exist soft-modes where the landscape is locally flat. \temp{[cite]}
-This can cause issues for single-ended search methods that rely only upon local information.
-Finally, if short-range interactions are chosen that are discontinuous the gradients will be undefined, in which case typical landscape methods that require continuous, differentiable optimisation functions will not be appropriate.
+\topic However, a large range of landscapes prove challenging or impossible to explore via these methods.
+One key problem arises from the push towards larger and more complex systems \temp{[cite]}, resulting in the need to develop algorithms that are more memory and computationally efficient, and can incorporate optimisation strategies such as on-the-fly adaptive remeshing and coarse-graining.
+However, existing transition state methods exhibit inefficiencies that can make complex systems infeasible.
+Single-ended methods are not well suited for identifying specific pathways and can spend a large amount of time searching for undesired transition states.
+While, double-ended methods require a chain of tens of states to gain an accurate approximation, and have issues with remeshing resulting in a different discretisation for each state.
+Other challenges occur for complex landscapes, such as those that are locally flat or discontinous.
+Both of which can be relevent when considering contact forces for macroscopic objects \temp{[cite]}.
+Flat landscapes can pose issues for single-ended search methods that rely only upon local information, and most current methods cannot be used for discontinuous landscapes because they typically require continuous, differentiable optimisation functions.
 
@@
   \includegraphics{fig/toy2d.pdf}
-  \caption{
+  \caption{\label{fig:toy2d}
     (a) The trajectories of the two states under the BITSS method for a simple 2D potential with two minima (blue dots).
@@
   }
-  \label{fig:toy2d}
 \end{figure}
@@
 \topic Two soft constraints are used to achieve the transition state convergence, while preventing either from passing over the dividing ridge.
-The former is implemented by constraining the distance between the states and iteratively reducing the target separation, $d_i$, from the initial separation, $d_0$, by a constant factor:
-\begin{equation}
+The former is implemented by constraining the distance between the states at iteration $i$, and reducing the target separation, $d_i$, from the initial separation, $d_0$, by a constant factor:
+\begin{equation}\label{eq:diteration}
   d_{i+1} = (1 - f) d_i.
-  \label{eq:diteration}
 \end{equation}
@@
 These constraints are implemented using quadratic energy penalty terms, resulting in the following potential for the pair of states,
-\begin{multline}
-  V_\text{BITSS}(\bm{x}_1, \bm{x}_2) = E_1 + E_2
+\begin{multline}\label{eq:bitss}
+  E_\text{BITSS}(\bm{x}_1, \bm{x}_2) = E_1 + E_2
     + \kappa_e \left( E_1 - E_2 \right) ^2 \\
     + \kappa_d \left( \mathrm{d}(\bm{x}_1, \bm{x}_2) - d_i \right) ^2,
-  \label{eq:bitss}
 \end{multline}
@@
 
-\topic The method is sensitive to the choice of the constraint coefficients, $\kappa_d$ and $\kappa_e$, with optimal values depending upon the specific problem.
-Also, as the separation between the states decreases the coefficients will have to change, making them difficult to assign manually.
+\topic To locate the transition state without crossing the ridge, the constraint strengths $\kappa_d$ and $\kappa_e$ are updated as the algorithm proceeds.
 Consequently, we automate their assignment using information from the system.
@@
   \includegraphics{fig/speedtest-c.pdf}%
-  \caption{
+  \caption{\label{fig:speedtest}
     The rate of convergence to the transition state for (a) a Lennard-Jones seven-particle cluster, (b) cylindrical shell buckling, (c) wetting of a chemically-striped surface.
-    Above are the two minimum energy states and the transition state between them.
+    Above are the two minimum energy states and the transition state, marked by an asterisk.
     Below is shown the convergence to the transition state as a function of the number of gradient calculations using the BITSS (black line) and string methods.
@@
   }
-  \label{fig:speedtest}
 \end{figure*}
@@
 \topic The typical trajectory of the two states in the BITSS method is shown in \cref{fig:toy2d}a.
-Initially, the lower energy state jumps up to satisfy the equal energy constraint and then moves to reduce the separation as much as possible without increasing it's energy.
+Initially, the lower energy state jumps up to satisfy the equal energy constraint and then moves to reduce the separation as much as possible without increasing its energy.
 Then, the two states begin to converge directly towards one another, before being deflected in the direction of a saddle in the potential.
@@
 Therefore, the final two states are positioned in the direction of the negative curvature eigenvector, $\bm{\hat{\tau}}$, as shown in \cref{fig:toy2d}c.
-So it is also possible to obtain the eigenvector and eigenvalue using BITSS.
+In this way, BITSS automatically identifies the 'reactive mode' and associated eigenvalue.
 
@@
 For each method, the accuracy is measured against the number of times the energy and gradient of the system are evaluated.
-The results of this are shown in \cref{fig:speedtest} and \temp{SI} for the string method and DNEB respectively.
+The results in comparison with the string method are shown in \cref{fig:speedtest}.
 
@@
 \begin{equation}
-  E = \sum_i k^S_i (r_i - r^0_i)^2 + \sum_j k^B_j [1 + \text{cos}(\theta_j - \theta^0_j)].
+  E = \sum_i k^S_i (r_i - r^0_i)^2 + \sum_j k^B_j [1 + \cos(\theta_j - \theta^0_j)].
 \end{equation}
@@
 The energy functional has four separate terms,
-\begin{equation}
-  E[\phi] = E_B + E_I + E_S + E_V.
+\begin{equation} \label{eq:phasefield}
+  E[\phi] = E_B[\phi] + E_I[\phi] + E_S[\phi] + E_V[\phi].
 \end{equation}
@@
 \begin{figure}[tb]
-  \begin{tabular}[b]{c}
   \includegraphics{fig/changingmesh.pdf}\\
-    \includegraphics{fig/differentgrids.pdf}%
-  \end{tabular}
-  \caption{
+  \includegraphics{fig/differentgrids.pdf}
+  \caption{\label{fig:adaptivemesh}
     (a) Snapshots of the BITSS method applied to the buckling of a cylinder with a changing mesh.
@@
   }
-  \label{fig:adaptivemesh}
 \end{figure}
@@
 Single-ended search methods generally only use local information, and so require specialist treatment to deal with these zero modes.
-For example, global translation and rotation in free space require analytic expressions for the translation and rotation vectors, which are known.
+For example, global translation and rotation in free space require analytic expressions for the translation and rotation vectors, which are known \temp{\cite{Wales2004}}.
 However, these single-ended search methods are thwarted by local zero modes.
@@
 \begin{figure}[tb]
-  \begin{tabular}[b]{c}
   \includegraphics{fig/zeroeigen.pdf}\\
   \includegraphics{fig/discontinuous.pdf}
-  \end{tabular}
-  \caption{
+  \caption{\label{fig:flatdiscontinuous}
     (a) Energy profile of the BITSS pathway on a 2D potential with flat regions.
@@
   }
-  \label{fig:flatdiscontinuous}
 \end{figure}
@@
 Using the gradient-free approach, BITSS is able to successfully find the transition states, allowing us to plot the disconnectivity graph of the system, as shown in \cref{fig:flatdiscontinuous}b.
-This is compared with the results for the standard Lennard-Jones cluster in the supplementary information.
+A comparison with the results for the standard Lennard-Jones cluster is given in the supplementary information.
 It is worth noting that gradient-based approaches are significantly more efficient, so these should be preferred if possible.
@@
 %\section{Conclusion}
-\topic In conclusion, we have demonstrated a novel method for finding transition states that tackles some problems not currently addressed by existing methods.
-The method has advantages over current double-ended methods because it is more efficient, both in terms of memory and computational cost, and does not require an initial estimate for the pathway, useful for systems with non-linear pathways.
-Furthermore, we have demonstrated that the method can sucessfully be used with adaptive mesh algorithms, as well as systems with flat or discontinuous energy landscapes.
+\topic In conclusion, we have demonstrated a novel method for finding transition states that tackles problems not currently addressed by existing methods.
+The method is shown to be more efficient than existing double-ended methods, both in memory and combutational cost, with further reductions possible by utilising adaptive remeshing techniques.
+It can also be adapted to problems with complex energy landscapes, including those with flat or discontinuous regions.
+This method will enable the analysis of energy landscapes for new systems in both particulate and continuum applications, and increase the feasibility of such methods for large-scale, complex systems.
 

### 2022-02-16 fig/make_speedtest/plot.py

@@ -65,6 +65,7 @@ for subfig in ['a', 'b', 'c']:
     #    plt.plot(dneb_calls[i], dneb_dist[i], lw=1, label=n)
     plt.plot(bits_calls, bits_dist, c='k', lw=1.5)#, label='BITSS')
 
+    # Axes
     plt.semilogy()
     plt.tick_params('both', which='minor')
     plt.xlabel('Gradient evalulations')
@@ -73,7 +74,7 @@ for subfig in ['a', 'b', 'c']:
         plt.xlim(0, 1600)
         plt.ylim(bottom=1e-5)
     elif (subfig == 'b'):
-        plt.xlim(0, 60000)
+        plt.xlim(0, 65000)
         plt.ylim(bottom=1e-4)
     elif (subfig == 'c'):
         plt.xlim(0, 50000)
@@ -81,11 +82,15 @@ for subfig in ['a', 'b', 'c']:
         plt.legend(loc='best')
         plt.xticks([0,20000,40000])
 
+    # Snapshots
     for i in range(3):
-        tmp_ax = plt.axes((0.035+i*0.31, 1-0.31, 0.31, 0.31))
+        tmp_ax = plt.axes((0.035+i*0.31, 1-h2/h, 0.31, h2/h))
         img = mim.imread(f'{subfig}{i}.png')
         plt.imshow(img)
         tmp_ax.axis('off')
         tmp_ax.set_zorder(ax.get_zorder()-1)
+        if (i==1):
+            tmp_ax.text(0.25, 1, '*', va='top', ha='center', size='xx-large', transform=tmp_ax.transAxes)
+
     # plt.savefig(f'speedtest-dneb-{subfig}.png')
     lt.savefig(f'../speedtest-{subfig}.pdf', dpi=300)

### 2022-02-16 manuscript.tex
Added bib file

@@
 Historically, many computational methods for locating transition states have grown from an atomistic or particulate perspective.
-These have proven to be important tools for understanding, for example, protein folding \cite{Bryngelson1995,Onuchic1997}, biological and industrial catalysis \temp{[cite]}, crystallisation, and cluster formation \cite{Wales1998,Wales2012}.
+These have proven to be important tools for understanding, for example, protein folding \cite{Bryngelson1995,Onuchic1997}, biological and industrial catalysis \cite{Boehr2006,Kerns2015,Guo2018a}, crystallisation, and cluster formation \cite{Wales1998,Wales2012}.
 
@@
 \topic In conclusion, we have demonstrated a novel method for finding transition states that tackles problems not currently addressed by existing methods.
-The method is shown to be more efficient than existing double-ended methods, both in memory and combutational cost, with further reductions possible by utilising adaptive remeshing techniques.
+The method is shown to be more efficient than existing double-ended methods, both in memory and computational cost, with further reductions possible by utilising adaptive remeshing techniques.
 It can also be adapted to problems with complex energy landscapes, including those with flat or discontinuous regions.
@@
 % \bibliographystyle{apsrev4-2}
-\bibliography{../../library.bib}
+\bibliography{bibexport.bib}
 

### 2022-02-17 manuscript.tex
Made smaller changes suggested by Halim

@@
 \title{Locating saddle points in complex and memory intensive landscapes}
-\author{Sam Avis}
-\author{Jack Panter}
+\title{Binary Image Transition State Search Method}
+\author{Samuel J. Avis}
+\author{Jack R. Panter}
+\email[]{j.r.panter@durham.ac.uk}
 \author{Halim Kusumaatmaja}
+\email[]{halim.kusumaatmaja@durham.ac.uk}
 \affiliation{Department of Physics, Durham University, South Road, Durham DH1 3LE, UK}
@@
 \begin{abstract}
-  Locating transition states is crucial for investigating transition mechanisms in atomistic systems and, more recently, macroscale applications.
-  However, these pose certain challenges that are largely unaddressed by existing methods.
-  We introduce a new double-ended method, the Binary Image Transition State Search (BITSS), that uses just two states that converge to the transition state, resulting in a faster and more memory-efficient method than current approaches.
-  We demonstate it succesfully overcomes challenges associated with large-scale systems and complex energy landscapes.
+  Locating transition states is crucial for investigating transition mechanisms in wide-ranging atomistic systems and, more recently, macroscale systems.
+  Existing methods, however, can struggle in problems with a large number of degrees of freedom, on-the-fly adaptive remeshing and coarse-graining, and energy landscapes that are locally flat or discontinuous.
+  To resolve these challenges, we introduce a new double-ended method, the Binary Image Transition State Search (BITSS).
+  It uses just two states that converge to the transition state, resulting in a flexible, fast, and memory-efficient method.
+  We demonstate its versatility by applying BITSS to three very different classes of problems: Lennard-Jones clusters, shell buckling, and multiphase phase-field models.
 \end{abstract}
@@
 
-\topic In addition to these microscale applications it is also increasingly being recognised that transition states are useful in mesoscale or macroscale systems.
+\topic More recently, it is increasingly being recognised that transition states are useful in mesoscale or macroscale systems.
 Here, the minimum energy barriers provide important lower bounds to the energy input required for transitions to occur.
@@
 One key problem arises from the push towards larger and more complex systems \temp{[cite]}, resulting in the need to develop algorithms that are more memory and computationally efficient, and can incorporate optimisation strategies such as on-the-fly adaptive remeshing and coarse-graining.
-However, existing transition state methods exhibit inefficiencies that can make complex systems infeasible.
+Current double-ended methods require a chain of tens of states to gain an accurate approximation, and have issues with remeshing resulting in a different discretisation for each state.
 Single-ended methods are not well suited for identifying specific pathways and can spend a large amount of time searching for undesired transition states.
-While, double-ended methods require a chain of tens of states to gain an accurate approximation, and have issues with remeshing resulting in a different discretisation for each state.
-Other challenges occur for complex landscapes, such as those that are locally flat or discontinous.
-Both of which can be relevent when considering contact forces for macroscopic objects \temp{[cite]}.
-Flat landscapes can pose issues for single-ended search methods that rely only upon local information, and most current methods cannot be used for discontinuous landscapes because they typically require continuous, differentiable optimisation functions.
+Another major challenge in studying complex energy landscapes relates to the presence of locally flat or discontinous regions.
+Both of which can be relevent when considering contact forces for macroscopic objects \temp{[cite]}, or hard-body interactions in atomistic systems \temp{[cite]}.
+Flat landscapes can pose issues for single-ended search methods that rely only upon local information, and current methods cannot typically be applied to discontinuous landscapes because they require continuous, differentiable optimisation functions.
 
@@
   \caption{\label{fig:speedtest}
-    The rate of convergence to the transition state for (a) a Lennard-Jones seven-particle cluster, (b) cylindrical shell buckling, (c) wetting of a chemically-striped surface.
-    Above are the two minimum energy states and the transition state, marked by an asterisk.
-    Below is shown the convergence to the transition state as a function of the number of gradient calculations using the BITSS (black line) and string methods.
+    The convergence to the transition state as a function of the number of gradient calculations using the BITSS (black line) and string methods for (a) a Lennard-Jones seven-particle cluster, (b) cylindrical shell buckling, (c) wetting of a chemically-striped surface.
     The string method is repeated with a differing number of images along the string, the number of which is listed in the legend in (c).
+    The shown configurations correspond to the two minimum energy states and the transition state, marked by an asterisk.
   }
@@
 \topic As a result of the BITSS method using only two states it has the potential to be significantly faster than chain-of-states approaches which typically use tens of states.
-This is tested here by measuring the speed of convergence to the transition state for BITSS in comparison with the string method and DNEB for several representitive examples.
-The accuracy of the BITSS method is calculated using the distance between the correct transition state and the average of the two states.
-While for the chain-of-states methods, the accuracy is measured as the distance of the transition state from a cubic spline interpolation of the points along the string.
+This is tested here by measuring the speed of convergence to the transition state for BITSS in comparison with the string method and DNEB for several representative examples.
+The accuracy of the BITSS method is calculated using the distance between the correct transition state and the average of the two states, whereas the accuracy for the chain-of-states methods is measured as the distance of the transition state from a cubic spline interpolation of the points along the string.
 For each method, the accuracy is measured against the number of times the energy and gradient of the system are evaluated.
@@
 
-\topic The first system to be tested is a two-dimensional seven-particle cluster with Lennard-Jones interactions.
-The transition begins with the hexagonal cluster and involves two particles shifting to reach a higher energy configuration.
+\topic The first system to be tested is a two-dimensional, seven-particle cluster, with the transition from a hexagonal cluster to a higher energy configuration.
+The interaction between each pair of particles uses the Lennard-Jones potential,
+\begin{equation}
+  E = 4\epsilon \left[ \left(\frac{\sigma}{r}\right)^{12} - \left(\frac{\sigma}{r}\right)^6 \right],
+\end{equation}
+where $r$ is the particle separation, $\epsilon$ is the interaction strength, and $\sigma$ is the particle size.
 
@@
 \end{equation}
-The first term provides the stretching energy for the system using a sum over all the bonds, where $r_i$ is the length, $r^0_i$ --- the equilibrium length, and $k^S_i$ --- the stretching rigidity of bond $i$.
+The first term provides the stretching energy for the system using a sum over all the bonds, where $r_i$ is the length, $r^0_i$ is the equilibrium length, and $k^S_i$ is the stretching rigidity of bond $i$.
 The second term models the bending energy by representing each pair of adjacent triangles as an elastic hinge.
-For hinge $j$, $\theta_j$ is the dihedral angle, $\theta^0_j$ --- the equilibrium angle, and $k^B_j$ --- the bending rigidity.
+For hinge $j$, $\theta_j$ is the dihedral angle, $\theta^0_j$ is the equilibrium angle, and $k^B_j$ is the bending rigidity.
 
@@
 Finally, $E_V$ constrains the volume of the liquid drop by penalising any variation from 11\% of the total volume of the system.
+For further details and the gradients of the potentials see the supplementary information.
 
@@
 These changes are performed after the minimisation step in each iteration of the BITSS method.
-This demonstrates that BITSS is able to converge to the transition state so long as the remeshing is not so drastic that one state is shifted into the basin of another minima.
+This demonstrates that BITSS is able to converge to the transition state so long as the remeshing does not effectively change the landscape.
 
@@
 This is done here by interpolating one state onto the other grid and computing the Euclidean distance.
-Although, for some applications it may be sufficient to use simpler distance measures, such as the difference between average values of the system.
+However, for some applications it may be sufficient to use simpler distance measures, such as the difference between average values of the system.
 The results for the striped wetting example with two different resolutions (shown in \cref{fig:adaptivemesh}b) demonstates that BITSS is successful.
@@
 However, the distance constraint continues to pull the states together, preventing them from getting stuck.
-When only a single state has a zero-gradient mode then the other is likely to slide down the potential slightly, causing a kink in the pathway (iii).
-Although, the two states still remain either side of the dividing ridge and so the result will be unaffected.
-Indeed, it may only cause BITSS to fail if the zero-gradient mode is positioned at the transition state in the direction of the pathway.
-But in this case there is no single transition state, instead the minimum energy pathway would have a flat section at the top of its energy profile.
+When only a single state has a zero-gradient mode then the other is likely to slide down the potential slightly (iii), but the two states still remain either side of the dividing ridge and so the result will be unaffected.
+Indeed, a zero-gradient mode may only cause BITSS to fail if it is positioned at the transition state in the direction of the pathway.
+In this case there would be no single transition state, instead the minimum energy pathway would have a flat section at the top of its energy profile.
 
@@
     (a) Energy profile of the BITSS pathway on a 2D potential with flat regions.
-        The minima and transition state are marked by blue and red dots respectively.
-        Points of interest are labelled by i-iii.
+        The blue and red dots denote the minima and transition state, respectively.
+        Points of interest are labelled by i--iii (see text).
         Top inset: A zoomed in view around the transition state.
@@
     (c) Plot of the discontinuous potential.
-        The repulsive section of the usual Lennard-Jones potential is also shown in grey.
+        The repulsive section of the standard Lennard-Jones potential is also shown in grey.
   }
@@
 In both cases, typical landscapes methods that require continuous, differentiable (often twice-differentiable) optimisation functions will not be appropriate.
-
-\topic However, BITSS can be used for these systems with undefined gradients with just a couple of alterations.
+However, BITSS can be used for these systems with undefined gradients with just a couple of alterations.
 First, the term using gradients in \cref{eq:kd} can be ignored and $\kappa_d$ can instead be calculated using just the second term.
@@
 
+\appendix
+\section{}
+
+\begin{acknowledgments}
+  S.~J.~A. is supported by a studentship from the Engineering and Physical Sciences Research Council (Grant No. EP/R513039/1).
+  H.~K. and J.~P. acknowledge funding from the Engineering and Physical Sciences Research Council (Grant No. EP/V034154/1).
+\end{acknowledgments}
+
 % \bibliographystyle{apsrev4-2}

### 2022-02-17 fig/make_speedtest/make_lj.py

@@ -3,7 +3,6 @@
 import numpy as np
 from matplotlib import pyplot as plt
 import json
-import latexipy as lp
 
 sigma = 1
 n_particle = 7
@@ -26,6 +25,9 @@ lj[2,:,1] -= lj[2,5,1]
 width = np.max(lj[:,:,0])+rad - (np.min(lj[:,:,0])-rad)
 height = np.max(lj[:,:,1])+rad - (np.min(lj[:,:,1])-rad)
 
+# Rearrange
+lj = lj[:,[5,2,3,4,0,6,1]]
+
 
 ### Plot
 for i_state in np.arange(0, len(lj)):
@@ -33,6 +35,7 @@ for i_state in np.arange(0, len(lj)):
     plt.axes((0,0,1,1))
     for i_part in range(n_particle):
         circle = plt.Circle(lj[i_state,i_part], rad, alpha=1, fc=col, ec='none', lw=3)
+        plt.text(lj[i_state,i_part,0], lj[i_state,i_part,1], i_part, ha='center', va='center_baseline', size=60)
         plt.gca().add_artist(circle)
 
     xlim = (np.max(lj[i_state,:,0]) + np.min(lj[i_state,:,0]))/2 + np.array([-width/2, width/2])
@@ -41,4 +44,4 @@ for i_state in np.arange(0, len(lj)):
     plt.ylim(ylim)
     plt.gca().axis('off')
     plt.gca().set_aspect('equal')
-    plt.savefig(f'lj{i_state}.png')
+    plt.savefig(f'a{i_state}.png')

### 2022-02-21 manuscript.tex
Condensed shorter sections suggested by Halim

@@
 Historically, many computational methods for locating transition states have grown from an atomistic or particulate perspective.
-These have proven to be important tools for understanding, for example, protein folding \cite{Bryngelson1995,Onuchic1997}, biological and industrial catalysis \cite{Boehr2006,Kerns2015,Guo2018a}, crystallisation, and cluster formation \cite{Wales1998,Wales2012}.
+These have proven to be important tools for understanding, for example, protein folding \cite{Bryngelson1995,Onuchic1997}, biological and industrial catalysis \cite{Boehr2006,Kerns2015,Guo2018a}, quantum tunneling \cite{Richardson2016,Vaillant2019}, crystallisation, and cluster formation \cite{Wales1998,Wales2012}.
 
@@
 Here, the minimum energy barriers provide important lower bounds to the energy input required for transitions to occur.
-This is essential to capture in, for example, structural engineering applications, where the minimum energy mechanism for structural failure must be known in order to ensure safety \cite{Panter2019,Hutchinson2018}.
+This has been used to understand failure in structural engineering applications \cite{Panter2019,Hutchinson2018}, for the development of super liquid-repellent surfaces \cite{Zhang2014,Panter2019b}, and investigating locomotion through complex terrain for robotics \cite{Othayoth2020}.
 Moreover, it is becoming desirable to tailor elastic deformation transitions to enable technologies such as advanced deployable structures \cite{Filipov2015,Zhai2018}, mechanical sensors and actuators, and energy absorption \cite{Shan2015} to name but a few.
-Probing minimum energy transition mechanisms are also essential to the development of super liquid-repellent surfaces \cite{Zhang2014,Panter2019b}, and are even finding applications in robotics in efficient locomotion through complex terrain \cite{Othayoth2020}.
 
@@
 Both of which can be relevent when considering contact forces for macroscopic objects \temp{[cite]}, or hard-body interactions in atomistic systems \temp{[cite]}.
-Flat landscapes can pose issues for single-ended search methods that rely only upon local information, and current methods cannot typically be applied to discontinuous landscapes because they require continuous, differentiable optimisation functions.
+Flat zero-modes in the landscape pose issues for single-ended search methods that rely only upon local information.
+Specialist treatment can sometimes be used such as in the case of global rotation and translation \temp{\cite{Wales2004}}, but they are thwarted by local zero-modes.
+Meanwhile, current methods cannot typically be applied in the case of discontinuous potentials, or where the gradient is prohibitively expensive to compute, because they require continuous, differentiable optimisation functions.
 
@@
 This is tested here by measuring the speed of convergence to the transition state for BITSS in comparison with the string method and DNEB for several representative examples.
-The accuracy of the BITSS method is calculated using the distance between the correct transition state and the average of the two states, whereas the accuracy for the chain-of-states methods is measured as the distance of the transition state from a cubic spline interpolation of the points along the string.
-For each method, the accuracy is measured against the number of times the energy and gradient of the system are evaluated.
-The results in comparison with the string method are shown in \cref{fig:speedtest}.
 
@@
 
+\topic Convergence is measured using the distance from the transition state as a function of number of evaluations to the gradient of the system's potential.
+The transition state is compared to the average of the two states for BITSS, whereas for the chain-of-states methods, the closest point on a cubic spline is used.
+
 \topic The results for this test, shown in \cref{fig:speedtest}, demonstrate two main advantages for the BITSS method.
@@
 %\section{Adaptive mesh}
-\topic To further increase the speed of the method we can use adaptive remeshing and coarse-graining to lower the resolution of the system in regions with few changing features.
-However, this introduces additional complexity to the method.
-It must be able to handle both the degrees of freedom changing, and the two states having separate discretisations.
-Here we test each of these issues individually.
+\topic Adaptive remeshing and coarse-graining are widely used techniques that we can utilise to further increase the efficiency of BITSS.
+These techniques cause issues for double-ended methods because the coupled states may end up with different discretisations.
+However, in BITSS the only direct coupling is in the distance measure, $\mathrm{d}(\bm{x}_1,\bm{x}_2)$, so it is relatively easy to adapt.
+Here we demonstrate the use of adaptive remeshing by splitting it into two issues that we will consider separately.
 
-\topic Firstly, we demonstrate in \cref{fig:adaptivemesh}a that BITSS is indeed able to handle the discretisation changing as the method runs.
+\topic Firstly, we show in \cref{fig:adaptivemesh}a that BITSS is able to handle the discretisation changing as the method runs.
 For this we use the cylindrical buckling example with the resolution increasing from 40 to 100 triangles around the cylinder.
 These changes are performed after the minimisation step in each iteration of the BITSS method.
-This demonstrates that BITSS is able to converge to the transition state so long as the remeshing does not effectively change the landscape.
+This demonstrates that BITSS is able to converge to the transition state so long as the remeshing does not significantly change the landscape.
 
-\topic For the second test, we investigate how BITSS performs when the two states have different meshes.
-The only special consideration needed for this is that the distance measure must take into account the different grids.
-This is done here by interpolating one state onto the other grid and computing the Euclidean distance.
-However, for some applications it may be sufficient to use simpler distance measures, such as the difference between average values of the system.
-The results for the striped wetting example with two different resolutions (shown in \cref{fig:adaptivemesh}b) demonstates that BITSS is successful.
-Notably however, there is a limit to how close the two states can get.
-This is because the energy of the transition state is slightly different on each grid, so eventually the energy constraint will fail.
-Despite this, the two states are still able to get very close and give a very good approximation to the transition state.
-Furthermore, using an adaptive grid model the grids would also be expected to converge, thereby eliminating the issue.
+\topic In the second test, \cref{fig:adaptivemesh}b, we demonstrate the use of different meshes for the two states in the striped wetting example.
+In this case, the distance measure is adapted by interpolating one state onto the other mesh and computing the Euclidean distance.
+However, for some applications a simpler measure may be sufficient, such as the difference between average values of the system.
+Using this approach BITSS is able to get very close to the transition state, but there is now a limit because the energy of the transition state is different on each grid, so the energy constraint will eventually fail.
+However, this is less of an issue for true adaptive methods, because the two meshes would also be expected to converge.
 
@@
         The zoomed axes shows the difference in the fluid interface between the two final states, as well as the approximated transition state (solid black line).
-        This is compared to the true transition state found using a high resolution for both states (dashed line).
+        This is compared to the transition state found using a high resolution (dashed line).
   }
@@
 %\section{Zero-curvature modes}
-\topic Interaction potentials in many particulate and macroscale systems are short-range, and often limited to contact forces.
-Thus, there may be many regions in the potential energy landscape that are locally flat.
-Single-ended search methods generally only use local information, and so require specialist treatment to deal with these zero modes.
-For example, global translation and rotation in free space require analytic expressions for the translation and rotation vectors, which are known \temp{\cite{Wales2004}}.
-However, these single-ended search methods are thwarted by local zero modes.
-
-\topic In \cref{fig:flatdiscontinuous}a we demonstrate the BITSS method applied to a 2D potential with regions containing such zero modes (i \& ii).
+\topic The final challenges we will address are those related to complex landscapes.
+The first of which being the presence of flat regions in the landscape.
+\Cref{fig:flatdiscontinuous}a shows BITSS applied to a 2D landscape with two such regions (i \& ii) that are flat in the $x$-direction.
 We see it is able to successfully converge past these flat regions, even with one very close to the transition state (ii).
@@
 However, the distance constraint continues to pull the states together, preventing them from getting stuck.
-When only a single state has a zero-gradient mode then the other is likely to slide down the potential slightly (iii), but the two states still remain either side of the dividing ridge and so the result will be unaffected.
+When only a single state has a zero-gradient mode then the other is likely to slide down the potential slightly (iii), but the two states still remain either side of the dividing ridge and so the result is unaffected.
 Indeed, a zero-gradient mode may only cause BITSS to fail if it is positioned at the transition state in the direction of the pathway.
@@
 %\section{Gradient-free problems}
-\topic In many cases contact forces may be chosen to be infinite to prevent overlap of solid bodies.
-This results in the energy landscape becoming discontinuous with regions of undefined gradients.
-Alternatively, for some systems the potential energy gradients may be prohibitively expensive to compute, or not available.
-In both cases, typical landscapes methods that require continuous, differentiable (often twice-differentiable) optimisation functions will not be appropriate.
-However, BITSS can be used for these systems with undefined gradients with just a couple of alterations.
+\topic Finally we investigate the application of BITSS to systems with undefined gradients, such as when the landscape is discontinuous.
+In this case a couple of alterations to the method must be made.
 First, the term using gradients in \cref{eq:kd} can be ignored and $\kappa_d$ can instead be calculated using just the second term.
@@
 This has a chance of randomly jumping one state over the dividing barrier, but we can reduce this probability by setting the initial temperature to $T_0 = \Delta E / 10$, and the maximum size of random displacements to $d_\text{max} = d(\bm{x}_1, \bm{x}_2) / 100$.
-
-\topic This has been tested using a Lennard-Jones 7-particle cluster with hard cores, resulting in a discontinuous landscape.
-Using the gradient-free approach, BITSS is able to successfully find the transition states, allowing us to plot the disconnectivity graph of the system, as shown in \cref{fig:flatdiscontinuous}b.
+This has been tested using a Lennard-Jones 7-particle cluster with hard cores, resulting in a discontinuous landscape.
+Using the gradient-free approach, BITSS is able to successfully find the transition states, allowing us to plot the disconnectivity graph of the system, shown in \cref{fig:flatdiscontinuous}b.
 A comparison with the results for the standard Lennard-Jones cluster is given in the supplementary information.
-It is worth noting that gradient-based approaches are significantly more efficient, so these should be preferred if possible.
+It is worth noting, however, that a gradient-based approach is significantly more efficient, and so should be preferred if possible.
 

### 2022-02-23 manuscript.tex
Method section condensed. Under word limit

@@
 
-\topic In this work we introduce a new method, the Binary Image Transition State Search (BITSS), and demonstrate how it addresses each of these challenges.
-This method combines aspects of the two traditional categories; it is a double-ended method that uses just two states that converge from two local minima towards a transition state that separates them.
-The states, $\bm{x}_1$ and $\bm{x}_2$, are first initialised in different basins of attraction of the local minima.
-While these can be set to the minima, this is not a necessary requirement.
-Upon application of the BITSS method, the two images are brought closer to the ridge separating the basins of attraction, while also minimising the energy of the pair of images.
-In this way, the two images meet at the lowest energy point on the ridge - the transition state.
-This is demonstrated for a simple 2D potential with two minima in \cref{fig:toy2d}a.
-
 \begin{figure}[htb]
@@
         The transition state is shown by an red dot, and the minimum energy pathway by the dashed line.
-    (b) A snapshot of the BITSS minimisation showing the driving forces on each state due to the energy constraint, $\bm{F}_E$, and distance constraint, $\bm{F}_D$, with $E_1 < E_2$ and $d(\bm{x}_1,\bm{x}_2) > d_i$.
+    (b) A snapshot of the BITSS minimisation showing the driving forces on each state due to the energy constraint, $\bm{F}_E$, and distance constraint, $\bm{F}_D$, with $E_1 < E_2$ and $\mathrm{d}(\bm{x}_1,\bm{x}_2) < d_i$.
     (c) The final configuration of the BITSS method showing the two states in orange, the transition state in red, and the negative curvature eigenvector, $\bm{\hat{\tau}}$.
@@
 
-\topic Two soft constraints are used to achieve the transition state convergence, while preventing either from passing over the dividing ridge.
-The former is implemented by constraining the distance between the states at iteration $i$, and reducing the target separation, $d_i$, from the initial separation, $d_0$, by a constant factor:
+\topic In this work we introduce a new method, the Binary Image Transition State Search (BITSS).
+This is a double-ended method that uses two states that converge toward a transition state from either side, therefore combining aspects of the two traditional transition state search categories.
+We will demonstrate how it addresses each of the above challenges using a range of different applications.
+
+%\section{Method}
+\topic The method begins by first initialising the states, $\bm{x}_1$ and $\bm{x}_2$, in the basins of attraction of different local minima.
+These can be set to the minima, but this is not a necessary requirement.
+The BITSS method then causes these states to meet at the lowest point on the ridge between the basins of attraction - the transision state.
+This is done by minimising their energy while constraining their separation and incrementally reducing it, such that at iteration $i$ it is given by
 \begin{equation}\label{eq:diteration}
-  d_{i+1} = (1 - f) d_i.
+  d_i = (1 - f) d_{i-1},
 \end{equation}
-We find that a factor of $f = 0.5$ is succesful for most applications, but this can be made smaller to ensure that the states do not slide off the ridge.
-The second constraint sets the energies of the two states to be equal.
-This ensures neither state can pass over the ridge so long as the distance is not reduced too quickly.
-These constraints are implemented using quadratic energy penalty terms, resulting in the following potential for the pair of states,
+with $d_0$ as the separation between the initial states.
+A factor of $f = 0.5$ is succesful for most applications, but this can be made smaller to ensure that the states do not slide off the ridge.
+A secondary constraint that sets the energies of the two states equal is also used to ensure that neither state is pulled over the ridge.
+
+\topic Using this approach, the typical trajectories of the states are demonstrated for a simple 2D potential in \cref{fig:toy2d}a.
+Initially, the lower energy state jumps up to satisfy the equal energy constraint and then moves to minimise the separation without increasing its energy.
+Then, the two states converge directly towards one another, before being deflected towards the saddle in the ridge.
+Consequently, if there are multiple possible pathways between two states, BITSS will be biased towards identifying those that are more direct or with lower energy.
+Furthermore, the final two states are positioned either side of the transition state in the direction of the negative curvature eigenvector, $\bm{\hat{\tau}}$ (\cref{fig:toy2d}c).
+So, BITSS automatically identifies the `reactive mode' and associated eigenvalue in addition to the transition state.
+
+\topic The two constraints are implemented using energy penalty terms, which, if the constraints are not met, result in driving forces on the two states, such as in \cref{fig:toy2d}b.
+The total energy of the pair of states is therefore given by,
 \begin{multline}\label{eq:bitss}
@@
 \end{multline}
-where $E_1$ and $E_2$ are the single state energies, and $\mathrm{d}(\bm{x}_1, \bm{x}_2)$ is the measure of distance between the two states.
-The energy constraint pushes the state with a higher energy down the potential, and the lower energy state up, while the distance constraint pulls them together if their separation is too great, and pushes them apart if they are too close.
-These driving forces are demonstrated for the 2D potential in \cref{fig:toy2d}b.
+where $E_1$ and $E_2$ are the single state energies, $\kappa_e$ and $\kappa_d$ parametrise the strengths of the energy and distance constraints, and $\mathrm{d}(\bm{x}_1, \bm{x}_2)$ is the measure of distance between the two states.
+In this work the L-BFGS algorithm is chosen to minimise the energy, owing to its fast convergence and low memory requirement for large numbers of degrees of freedom \cite{Liu1989}.
+However, any other minimisation method can be used instead.
 
-\topic To locate the transition state without crossing the ridge, the constraint strengths $\kappa_d$ and $\kappa_e$ are updated as the algorithm proceeds.
-Consequently, we automate their assignment using information from the system.
+\topic To ensure that the transition state is located successfully, the constraint strengths $\kappa_d$ and $\kappa_e$ are updated as the algorithm proceeds using information from the system.
 They are initially calculated at the start of each minimisation, and regularly recalculated throughout (once per 100 iterations are used in this work).
-The coefficients are chosen such that each term in the gradient of \cref{eq:bitss} is of a similar size, providing the following expressions,
+They are set using the following equations such that each term in the gradient of \cref{eq:bitss} is of a similar size,
 \begin{gather}
@@
   \\
-  \kappa_d = \text{max} \left(
+  \kappa_d = \max \left(
     \frac {\sqrt{|\bm{\nabla} E_1|^2 + |\bm{\nabla} E_2|^2}} {2\sqrt{2} \beta d_i} \; , \;
@@
 where $\alpha$ and $\beta$ are parameters with recommended values of $\alpha = 10$ and $\beta = 0.1$ (see supplementary information).
-$\Delta E$ is an estimation for the current energy barrier which is evaluated by linearly interpolating between the two current states.
-For systems where the interpolation deviates significantly from the minimum energy pathway this estimate can be much too large.
-In which case, a maximum estimated value for the barrier can be provided, which then decreases proportionally with $d_i$.
+Here, $\Delta E$ is an estimation for the current energy barrier evaluated by linearly interpolating between the two states.
+For systems where the interpolation deviates significantly from the pathway the estimate can be too large.
+In which case, a maximum estimated value can be provided, which then decreases proportionally with $d_i$.
 
@@
 \end{enumerate}
-Any minimisation algorithm can be used in step three; in this work the L-BFGS algorithm is chosen, owing to its fast convergence and low memory requirement for large numbers of degrees of freedom \cite{Liu1989}.
-Finally, the convergence criteria for the method can be based upon either the separation between the states, or the size of gradient at the estimate for the transition state midway between the two states.
+This process is completed once a convergence criteria is reached that can be based upon either the separation between the states, or the size of gradient at the midpoint between the two states.
 
-% This is here to prevent it being put on the wrong page
+\topic Once BITSS has identified the transition state it is possible to find the full minimum energy pathway.
+This is done by tracing the trajectory of downhill minimisations from the two final states either side of the transition state.
+
+%\section{Speed Comparison}
 \begin{figure*}[tb]
@@
 \end{figure*}
-
-\topic The typical trajectory of the two states in the BITSS method is shown in \cref{fig:toy2d}a.
-Initially, the lower energy state jumps up to satisfy the equal energy constraint and then moves to reduce the separation as much as possible without increasing its energy.
-Then, the two states begin to converge directly towards one another, before being deflected in the direction of a saddle in the potential.
-Consequently, if there are multiple possible pathways between two states, BITSS will be biased towards identifying pathways that are more direct or with lower energy.
-As the two states approach the transition state, the path they take begins to closely follow the minimum energy pathway, which is the path that follows the gradient from the minima and passes through the transition state.
-Therefore, the final two states are positioned in the direction of the negative curvature eigenvector, $\bm{\hat{\tau}}$, as shown in \cref{fig:toy2d}c.
-In this way, BITSS automatically identifies the 'reactive mode' and associated eigenvalue.
-
-\topic Once BITSS has identified the transition state it is possible to find the full minimum energy pathway.
-This is done by tracing the trajectory of downhill minimisations from either side of the transition state, which are provided by the two final states of BITSS.
-To ensure this pathway is sufficiently smooth the maximum step size of the minimisation should be restricted.
-
-%\section{Speed Comparison}
 \topic As a result of the BITSS method using only two states it has the potential to be significantly faster than chain-of-states approaches which typically use tens of states.

### 2022-02-23 fig/make_speedtest/plot.py
Updated labels of speedtest figures

@@ -69,7 +69,7 @@ for subfig in ['a', 'b', 'c']:
     plt.semilogy()
     plt.tick_params('both', which='minor')
     plt.xlabel('Gradient evalulations')
-    plt.ylabel('Distance error', labelpad=-0.5)
+    plt.ylabel('Distance error / $d_0$', labelpad=-0.2)
     if (subfig == 'a'):
         plt.xlim(0, 1600)
         plt.ylim(bottom=1e-5)

### 2022-02-23 si/fig/make_DNEBspeedtest/plot.py

@@ -63,7 +63,7 @@ for isub, subfig in enumerate(['a', 'b', 'c']):
     plt.semilogy()
     plt.tick_params('both', which='minor')
     plt.xlabel('Gradient evalulations')
-    plt.ylabel('Distance error', labelpad=-0.5)
+    plt.ylabel('Distance error / $d_0$', labelpad=-0.2)
     if (subfig == 'a'):
         plt.xlim(0, 1600)
         plt.ylim(bottom=1e-5)

### 2022-02-23 si/supplementary_information.tex
Made Jack's suggested changes to SI.

@@
 \begin{document}
-\title{Supplementary Information}
+\title{Binary Image Transition State Search \\ Supplementary Information}
+\author{Samuel J. Avis}
+\author{Jack R. Panter}
+% \email[]{j.r.panter@durham.ac.uk}
+\author{Halim Kusumaatmaja}
+% \email[]{halim.kusumaatmaja@durham.ac.uk}
+\affiliation{Department of Physics, Durham University, South Road, Durham DH1 3LE, UK}
 \maketitle
@@
 
-To obtain the expression for the energy coefficient we first assume that the separation is fixed, so the distance term can be ignored.
-The coefficient must be high enough to prevent one state from being pulled over the ridge, for which the greatest risk occurs when the gradient on one state is much greater than the other, $\abs{\grad E_2} \gg \abs{\grad E_1}$.
+To obtain the expression for the energy coefficient, $\kappa_e$, we first assume that the separation is fixed, so the distance term can be ignored.
+The coefficient $\kappa_e$ must be high enough to prevent one state from being pulled over the ridge, for which the greatest risk occurs when the gradient on one state is much greater than the other, $\abs{\grad E_2} \gg \abs{\grad E_1}$.
 In this case the total gradient is approximated by
@@
 \end{equation}
-This will converge when the term in the square brackets is zero, resulting in $\kappa_e = 1 / 2 (E_1 - E_2)$.
-To ensure this is large enough we can replace the energy difference with the estimate for the energy barrier, $\upDelta E$, and then scale it by a factor, $\alpha$, that is greater than or equal to one,
+This will converge when the term in the square brackets is zero, resulting in $E_1 - E_2 = 1 / 2 \kappa_e$.
+This energy difference should be less than current energy barrier, so we can substitute it with $\upDelta E / \alpha$, where $\upDelta E$ is the energy barrier estimate and $\alpha$ is a constant greater than one.
+Leaving us with the expression
 \begin{equation}
@@
 In this case, convergence will occur when $\grad E_1 + \grad E_2 = -2 \kappa_d (d - d_0) \grad d$.
-By comparing the magnitude of the two sides it is possible to obtain an expression for the coefficient in terms of the relative error in the distance, $\beta = (d - d_0) / d_0$.
-(Note: The gradient of the distance with respect to a single state has a magnitude of 1, thus $\abs{\grad d} = \sqrt{2}$.)
-A lower bound on the size of the coefficient is also set using the estimated energy barrier to ensure that the distance constraint is applied even when the gradient is close to zero, such as at the minima.
+It is then possible to find the value of $\kappa_d$ for which the magnitude of each side of this equation is equal for a desired relative error in the distance, $\beta = (d - d_0) / d_0$.
+(Note: The gradient of the distance with respect to a single state has a magnitude of 1, thus the magnitude of the gradient for the pair of states is $\abs{\grad d} = \sqrt{1^2+1^2} = \sqrt{2}$.)
+A lower bound on the size of the coefficient is also set using the estimated energy barrier to ensure that the distance constraint is applied even when the gradient is close to zero, such as when the states are initialised at the minima.
 \begin{equation}
@@
 The parameters $\alpha = 10$ and $\beta = 0.1$ are chosen for both converging quickly and being situated far from the regions of non-convergence.
-Hence, this choice is unlikely to fail if the boudaries of the regions were to shift for different systems.
+Hence, this choice is likely to still succeed even if the boudaries of the regions were to shift under different systems.
+However, the user is able to choose values optimised for their specific system should they wish.
 
@@
 For the cylindrical buckling example we can obtain the gradient by considering each bond and hinge individually.
-Using the schematic in \cref{fig:BAHschematic}, the gradient of the stretching energy of the bond between $\bm{x}_2$ and $\bm{x}_3$ is given by,
+Using the variables shown in the schematic in \cref{fig:BAHschematic}, the gradient of the stretching energy of the bond between $\bm{x}_2$ and $\bm{x}_3$, with equilibrium length $r^0$ and stretching rigidity $k^S$, is given by,
 \begin{equation}
@@
 \end{equation}
-While the gradients of the bending energy of the hinge are,
+While the gradients of the bending energy of the hinge, with equilibium angle $\theta^0$ and bending rigidity $k^B$, are,
 \begin{align}

### 2022-02-24 manuscript.tex
Updated labels of speedtest figures
Jack's edits to manuscript

@@
-\documentclass[aps,prl,twocolumn,groupedaddress]{revtex4}
+\documentclass[aps,prl,twocolumn,groupedaddress]{revtex4-2}
 
@@
 The BITSS method then causes these states to meet at the lowest point on the ridge between the basins of attraction - the transision state.
-This is done by minimising their energy while constraining their separation and incrementally reducing it, such that at iteration $i$ it is given by
+This is done by minimising the energy of the pair while constraining their separation.
+The separation $d_i$ is incrementally reduced, such that at iteration $i$,
 \begin{equation}\label{eq:diteration}
@@
 \end{enumerate}
-This process is completed once a convergence criteria is reached that can be based upon either the separation between the states, or the size of gradient at the midpoint between the two states.
+This process is completed once a convergence criterion is reached that can be based upon either the separation between the states, or the size of gradient at the midpoint between the two states.
 
@@
 These techniques cause issues for double-ended methods because the coupled states may end up with different discretisations.
-However, in BITSS the only direct coupling is in the distance measure, $\mathrm{d}(\bm{x}_1,\bm{x}_2)$, so it is relatively easy to adapt.
-Here we demonstrate the use of adaptive remeshing by splitting it into two issues that we will consider separately.
+However, in BITSS the only direct coupling is in the distance measure, $\mathrm{d}(\bm{x}_1,\bm{x}_2)$, which is relatively easy to adapt.
+Here we demonstrate the use of adaptive remeshing by considering two separate issues.
 
@@
 However, for some applications a simpler measure may be sufficient, such as the difference between average values of the system.
-Using this approach BITSS is able to get very close to the transition state, but there is now a limit because the energy of the transition state is different on each grid, so the energy constraint will eventually fail.
-However, this is less of an issue for true adaptive methods, because the two meshes would also be expected to converge.
+Using this approach, BITSS is able to closely approach the transition state.
+The convergence precision is now limited by the transition state energy differing slightly on each grid, but this effect is reduced when using an adaptive method or a higher resolution.
 
@@
 \topic The final challenges we will address are those related to complex landscapes.
-The first of which being the presence of flat regions in the landscape.
+The first is the presence of flat regions in the landscape.
 \Cref{fig:flatdiscontinuous}a shows BITSS applied to a 2D landscape with two such regions (i \& ii) that are flat in the $x$-direction.
-We see it is able to successfully converge past these flat regions, even with one very close to the transition state (ii).
+We see BITSS is able to successfully converge past these flat regions, even with one very close to the transition state (ii).
 In these regions there are no driving forces due to the potential and the energy constraint, which use purely local information about the gradient.
@@
 When only a single state has a zero-gradient mode then the other is likely to slide down the potential slightly (iii), but the two states still remain either side of the dividing ridge and so the result is unaffected.
-Indeed, a zero-gradient mode may only cause BITSS to fail if it is positioned at the transition state in the direction of the pathway.
-In this case there would be no single transition state, instead the minimum energy pathway would have a flat section at the top of its energy profile.
+\temp{Indeed, the only circumstance under which a zero-mode could cause BITSS to fail is if it is positioned at the transition state in the direction of the pathway.
+In this case there is no single transition state, instead the minimum energy pathway would have a flat section at the top of its energy profile.}
 
@@
   S.~J.~A. is supported by a studentship from the Engineering and Physical Sciences Research Council (Grant No. EP/R513039/1).
-  H.~K. and J.~P. acknowledge funding from the Engineering and Physical Sciences Research Council (Grant No. EP/V034154/1).
+  H.~K. and J.~R.~P. acknowledge funding from the Engineering and Physical Sciences Research Council (Grant No. EP/V034154/1).
 \end{acknowledgments}
 
-% \bibliographystyle{apsrev4-2}
+\bibliographystyle{apsrev4-2}
 \bibliography{bibexport.bib}

### 2022-02-24 manuscript.tex
Made Halim's edits to SI

@@
-\documentclass[aps,prl,twocolumn,groupedaddress]{revtex4-2}
+\documentclass[aps,prl,twocolumn,10pt,groupedaddress]{revtex4-2}
 
@@
 \usepackage{cleveref}
+\Crefname{figure}{Fig.}{Figs.}
 \newcommand{\ccite}[1]{ref.~\cite{#1}}
@@
   \caption{\label{fig:speedtest}
-    The convergence to the transition state as a function of the number of gradient calculations using the BITSS (black line) and string methods for (a) a Lennard-Jones seven-particle cluster, (b) cylindrical shell buckling, (c) wetting of a chemically-striped surface.
+    The convergence to the transition state as a function of the number of gradient calculations using the BITSS (black line) and string methods for (a) a Lennard-Jones seven-particle cluster, (b) cylindrical shell buckling, and (c) wetting of a chemically-striped surface.
     The string method is repeated with a differing number of images along the string, the number of which is listed in the legend in (c).

### 2022-02-24 si/supplementary_information.tex
Made Halim's edits to SI

@@
-\documentclass[aps,prl]{revtex4}
+\documentclass[aps,physrev,10pt]{revtex4-2}
 
@@
 \usepackage{cleveref}
+\Crefname{figure}{Fig.}{Figs.}
 \renewcommand{\theequation}{S\arabic{equation}}
@@
 \usepackage{graphicx}
+\usepackage{placeins}
 
@@
 \author{Jack R. Panter}
-% \email[]{j.r.panter@durham.ac.uk}
+\email[]{j.r.panter@durham.ac.uk}
 \author{Halim Kusumaatmaja}
-% \email[]{halim.kusumaatmaja@durham.ac.uk}
+\email[]{halim.kusumaatmaja@durham.ac.uk}
 \affiliation{Department of Physics, Durham University, South Road, Durham DH1 3LE, UK}
@@
 
-\section{Constraint coefficients}
+\section{Optimising the constraint coefficients}
 The constraint coefficients are chosen to set comparable sizes for each term in the gradient of the BITSS potential,
 \begin{equation} \label{eq:gradBITSS}
-  \grad E_\text{BITSS} = \sum_{\substack{i=1,2 \\ j\neq i}} \left[ 1 + 2 \kappa_e (E_i - E_j) \right] \grad E_i + 2 \kappa_d (d - d_0) \grad d.
+  \grad E_\text{BITSS} = \sum_{\substack{i=1,2 \\ j\neq i}} \left[ 1 + 2 \kappa_e (E_i - E_j) \right] \grad E_i + 2 \kappa_d (d - d_i) \grad d.
 \end{equation}
-
 To obtain the expression for the energy coefficient, $\kappa_e$, we first assume that the separation is fixed, so the distance term can be ignored.
@@
 \begin{equation}
-  \grad E_{tot} = \left[ 1 - 2 \kappa_e (E_1 - E_2) \right] \grad E_2.
+  \grad E_\text{BITSS} = \left[ 1 - 2 \kappa_e (E_1 - E_2) \right] \grad E_2.
 \end{equation}
-This will converge when the term in the square brackets is zero, resulting in $E_1 - E_2 = 1 / 2 \kappa_e$.
-This energy difference should be less than current energy barrier, so we can substitute it with $\upDelta E / \alpha$, where $\upDelta E$ is the energy barrier estimate and $\alpha$ is a constant greater than one.
-Leaving us with the expression
+Therefore, when not at a transition state or a minima in the landscape ($\abs{\grad E_2} \neq 0$) convergence will occur when the term in the square brackets is zero, resulting in $E_1 - E_2 = 1 / 2 \kappa_e$.
+This energy difference should be less than current energy barrier, so we can substitute it with $\upDelta E / \alpha$, where $\upDelta E$ is the energy barrier estimate described in the main paper and $\alpha$ is a constant greater than one.
+This leaves us with the expression,
 \begin{equation}
@@
 The distance coefficient is determined by assuming that the energies are equal and thus the energy constraint can be ignored.
-In this case, convergence will occur when $\grad E_1 + \grad E_2 = -2 \kappa_d (d - d_0) \grad d$.
-It is then possible to find the value of $\kappa_d$ for which the magnitude of each side of this equation is equal for a desired relative error in the distance, $\beta = (d - d_0) / d_0$.
+In this case, convergence will occur when $\grad E_1 + \grad E_2 = -2 \kappa_d (d - d_i) \grad d$.
+It is then possible to find the value of $\kappa_d$ for which the magnitude of each side of this equation is equal for a desired relative error in the distance, $\beta = (d - d_i) / d_i$,
+\begin{equation}
+  \kappa_d = \frac {\sqrt{\abs{\grad E_1}^2 + \abs{\grad E_2}^2}} {2 \sqrt{2} \beta d_i}.
+\end{equation}
 (Note: The gradient of the distance with respect to a single state has a magnitude of 1, thus the magnitude of the gradient for the pair of states is $\abs{\grad d} = \sqrt{1^2+1^2} = \sqrt{2}$.)
-A lower bound on the size of the coefficient is also set using the estimated energy barrier to ensure that the distance constraint is applied even when the gradient is close to zero, such as when the states are initialised at the minima.
+To ensure that the coefficient is not too small if the gradient is close to zero, such as when the states are initialised at the minima, a lower bound is set by replacing $\abs{\grad E_1}$ and $\abs{\grad E_2}$ with $2 \upDelta E / d_i$.
+Giving the expression,
 \begin{equation}
   \kappa_d = \mathrm{max} \! \left(
-  \frac {\sqrt{\abs{\grad E_1}^2 + \abs{\grad E_2}^2}} {2 \sqrt{2} \beta d_0}, \quad
-  \frac{\upDelta E}{\beta d_0^2} \right).
+  \frac {\sqrt{\abs{\grad E_1}^2 + \abs{\grad E_2}^2}} {2 \sqrt{2} \beta d_i}, \quad
+  \frac{\upDelta E}{\beta d_i^2} \right).
 \end{equation}
 
-\begin{figure}[b]
+In practice, when numerically minimising, the states will jump about slightly which can result in large gradients perpendicular to the optimal movement direction.
+To reduce this effect, the gradients are projected in the direction of the separation between the two states:
+\begin{equation}
+  \abs{\grad E_n} \approx \frac {\abs{(\bm{x}_1 - \bm{x}_2) \cdot \grad E_n}} {\abs{\bm{x}_1 - \bm{x}_2}}.
+\end{equation}
+
+\begin{figure}[htb]
   \includegraphics{fig/paramtest-a.pdf}%
@@
   \caption{\label{fig:paramtest}
-    Speed of convergence of the BITSS method under different choices of parameters for (a) the seven-particle cluster, (b) cylindrical buckling.
+    Speed of convergence of the BITSS method under different choices of parameters for (a) the seven-particle cluster, and (b) cylindrical buckling.
     The speed is given by the number of evaluations of the gradient until the two states are separated by less than a thousandth of the initial separation.
@@
 
-In practice, when numerically minimising, the states will jump about slightly which can result in large gradients perpendicular to the optimal movement direction.
-To reduce this effect, the size of the gradients in the direction separating the two states are instead calculated:
-\begin{equation}
-  \abs{\grad E_i} \approx \frac {\abs{(\bm{x}_1 - \bm{x}_2) \cdot \grad E_i}} {\abs{\bm{x}_1 - \bm{x}_2}}.
-\end{equation}
-
 The constant parameters $\alpha$ and $\beta$ still must be chosen.
@@
 \Cref{fig:paramtest} shows which choices lead to convergence and the speed at which this occurs.
-The parameters $\alpha = 10$ and $\beta = 0.1$ are chosen for both converging quickly and being situated far from the regions of non-convergence.
+The parameters $\alpha = 10$ and $\beta = 0.1$ are chosen for both converging quickly and being situated far from the regions of non-convergence in both test cases.
 Hence, this choice is likely to still succeed even if the boudaries of the regions were to shift under different systems.
@@
 
+\FloatBarrier
 \section{Test potentials and gradients}
@@
 \end{equation}
-While the gradients of the bending energy of the hinge, with equilibium angle $\theta^0$ and bending rigidity $k^B$, are,
+The gradients of the bending energy of the hinge, with equilibium angle $\theta^0$ and bending rigidity $k^B$, are,
 \begin{align}
@@
 \subsection{Striped wetting}
-The four sections of the phase-field model detailed in \namecref{eq:gradBITSS}~(6) are obtained using the following equations,
+The four sections of the phase-field model detailed in \namecref{eq:gradBITSS}~(7) are obtained using the following equations,
 \begin{align}
@@
 $\upDelta V$ and $\upDelta S$ are, respectively, the volume and solid surface areas contained by each individual node.
-$\epsilon$ is the liquid-gas interface width, $\theta_j$ --- the contact-angle with the solid surface, and $V_0$ --- the constrained volume of the liquid drop.
+$\epsilon$ is the liquid-gas interface width, $\theta_j$ is the contact-angle with the solid surface, and $V_0$ is the constrained volume of the liquid drop.
 The strength of the volume constraint is parametrised by $k_V$ for which we use a value of $10^4$.
@@
 
+\newpage
+\section{Additional results: DNEB speed comparison}
+\Cref{fig:DNEBspeedtest} shows the results for the speed test in comparison with DNEB.
+Much the same as the string method, the slope of BITSS is greater than DNEB with 10 or 20 states, indicating a faster convergence.
+Furthermore, with the exception of the seven-particle cluster, DNEB is also much less accurate at approximating the transition state, even with a large number of images.
+So it will require a secondary method to accurately locate the transition state, while BITSS does not.
+
 \begin{figure}[htb]
@@
   \caption{\label{fig:DNEBspeedtest}
-    The rate of convergence to the transition state for (a) a Lennard-Jones seven-particle cluster, (b) cylindrical shell buckling, (c) wetting of a chemically-striped surface.
-    Above are the two minimum energy states and the transition state, marked by an asterisk.
-    Below is shown the convergence to the transition state as a function of the number of gradient calculations using BITSS (black line) and DNEB.
-    The DNEB results are repeated with differing numbers of images along the chain, the number of which is listed in the legend in (c).
+    The convergence to the transition state as a function of the number of gradient calculations using the BITSS (black line) and DNEB for (a) a Lennard-Jones seven-particle cluster, (b) cylindrical shell buckling, and (c) wetting of a chemically-striped surface.
+    The string method is repeated with a differing number of images along the string, the number of which is listed in the legend in (c).
+    The shown configurations correspond to the two minimum energy states and the transition state, marked by an asterisk.
   }
 \end{figure}
+
+\section{Additional results: Seven-particle cluster comparison}
+\Cref{fig:clusterdgraphs} shows the comparison between the energies of the minima and transition states for the seven-particle cluster.
+Notably the energies of the minima are largely unchanged, but the energies of the transition states are found to be slightly higher when using the discontinuous potential.
+This indicates that the particles in the Lennard-Jones cluster cut the corner slightly as they transition, whereas this is not possible using the discontinuous potential, resulting in higher energies.
 
@@
     The two graphs are horizontally offset for visibility.
-The energies of the transition states are found to be slightly higher when using the discontinuous potential.
   }

### 2022-02-24 manuscript.tex
Added exascale computing citations

@@
 \topic However, a large range of landscapes prove challenging or impossible to explore via these methods.
-One key problem arises from the push towards larger and more complex systems \temp{[cite]}, resulting in the need to develop algorithms that are more memory and computationally efficient, and can incorporate optimisation strategies such as on-the-fly adaptive remeshing and coarse-graining.
+One key problem arises from the push towards larger and more complex systems \cite{Trefethen2013,Shalf2020,Alexander2020}, resulting in the need to develop algorithms that are more memory and computationally efficient, and can incorporate optimisation strategies such as on-the-fly adaptive remeshing and coarse-graining.
 Current double-ended methods require a chain of tens of states to gain an accurate approximation, and have issues with remeshing resulting in a different discretisation for each state.

### 2022-03-04 manuscript.tex
SI interpolation section added. Removed zeroeigen failure discussion

@@
 Flat zero-modes in the landscape pose issues for single-ended search methods that rely only upon local information.
-Specialist treatment can sometimes be used such as in the case of global rotation and translation \temp{\cite{Wales2004}}, but they are thwarted by local zero-modes.
+Specialist treatment can sometimes be used such as in the case of global rotation and translation \cite{Page1988}, but they are thwarted by local zero-modes.
 Meanwhile, current methods cannot typically be applied in the case of discontinuous potentials, or where the gradient is prohibitively expensive to compute, because they require continuous, differentiable optimisation functions.
@@
 When only a single state has a zero-gradient mode then the other is likely to slide down the potential slightly (iii), but the two states still remain either side of the dividing ridge and so the result is unaffected.
-\temp{Indeed, the only circumstance under which a zero-mode could cause BITSS to fail is if it is positioned at the transition state in the direction of the pathway.
-In this case there is no single transition state, instead the minimum energy pathway would have a flat section at the top of its energy profile.}
 

### 2022-03-04 si/supplementary_information.tex
SI interpolation section added. Removed zeroeigen failure discussion

@@
 
-\newpage
+\section{Details for the adaptive discretisation tests}
+Here we provide the details for the interpolations and mapping involved in the two examples demonstrating the feasibility of using an adaptive discretisation method.
+For the cylindrical buckling example with a changing mesh, the resolution is refined each time the separation between the two states is halved. 
+This involves the number of triangles around the circumference of the cylinder increasing along the sequence, $40 \rightarrow 60 \rightarrow 80 \rightarrow 100$.
+The positions of the nodes on the new grid, $\{\bm{n}_i\}$, are determined by linear interpolating from the previous grid $\{\bm{p}_i\}$, using the positions of the unbuckled meshes, $\{\bm{n'}_i\}$ and $\{\bm{p'}_i\}$.
+For each node of the new grid, $\bm{n'}_i$, the triangle that contains it is first identified, which we will denote $\{\bm{p'}_1,\bm{p'}_2,\bm{p'}_3\}$, and the barycentric coordinates of the point are computed, $\{\lambda_1,\lambda_2,\lambda_3\}$.
+The new position is then given by $\bm{n}_i = \lambda_1 \bm{p}_1 + \lambda_2 \bm{p}_2 + \lambda_3 \bm{p}_3$.
+
+In the example with different resolutions for the two states, the distance is obtained by mapping the phase field from the higher resolution grid to the low resolution grid, and then using the 2-norm.
+Because a square grid is used with a resolution ratio of two, the mapping involves averaging each 2x2 block to a single point.
+Finally, the gradient with respect to each point must be mapped back to the higher-resolution grid, which is done by assigning a quarter of each component back to its the original four points.
+
 \section{Additional results: DNEB speed comparison}
@@
 
+\newpage
 \section{Additional results: Seven-particle cluster comparison}

### 2022-03-06 manuscript.tex
Combined subfigures

@@
 \Crefname{figure}{Fig.}{Figs.}
-\newcommand{\ccite}[1]{ref.~\cite{#1}}
-\newcommand{\Ccite}[1]{Ref.~\cite{#1}}
-\newcommand{\ccites}[1]{refs.~\cite{#1}}
-\newcommand{\Ccites}[1]{Refs.~\cite{#1}}
 
 % Temp
-\usepackage{lipsum}
-\usepackage{xcolor}
-\newcommand{\temp}[1]{{\leavevmode\color{red}#1}}
 \newcommand*{\newlinecommand}[2]{%
@@
 Another major challenge in studying complex energy landscapes relates to the presence of locally flat or discontinous regions.
-Both of which can be relevent when considering contact forces for macroscopic objects \temp{[cite]}, or hard-body interactions in atomistic systems \temp{[cite]}.
+Both of which can be relevent when considering contact forces for macroscopic objects [cite], or hard-body interactions in atomistic systems [cite].
 Flat zero-modes in the landscape pose issues for single-ended search methods that rely only upon local information.
@@
 \begin{figure*}[tb]
-  \includegraphics{fig/speedtest-a.pdf}%
-  \includegraphics{fig/speedtest-b.pdf}%
-  \includegraphics{fig/speedtest-c.pdf}%
+  \includegraphics{fig/speedtest.pdf}
   \caption{\label{fig:speedtest}
@@
 \begin{figure}[tb]
-  \includegraphics{fig/changingmesh.pdf}\\
-  \includegraphics{fig/differentgrids.pdf}
+  \includegraphics{fig/adaptivemesh.pdf}
   \caption{\label{fig:adaptivemesh}
@@
 \begin{figure}[tb]
-  \includegraphics{fig/zeroeigen.pdf}\\
-  \includegraphics{fig/discontinuous.pdf}
+  \includegraphics{fig/flatdiscontinuous.pdf}
   \caption{\label{fig:flatdiscontinuous}

### 2022-03-06 fig/create_figs.sh

@@ -1,6 +1,6 @@
 #!/bin/bash
 
-figures=('toy2d' 'speedtest' 'changingmesh' 'differentgrids' 'zeroeigen' 'discontinuous')
+figures=('toy2d' 'speedtest' 'adaptivemesh' 'flatdiscontinuous')
 
 for fig in ${figures[@]}; do
   echo "Plotting $fig"

### 2022-03-06 fig/make_adaptivemesh/plot.py

@@ -1,0 +1,274 @@
+#!/usr/bin/env python3
+import numpy as np
+import matplotlib as mpl
+import matplotlib.pyplot as plt
+import matplotlib.tri as mtri
+import json
+import pyutils.latexify as lt
+# Get default style for paper
+import sys; sys.path.insert(0, '..')
+import style
+
+def plot_cb(fig, y0, htot):
+    # Figure parameters
+    w1 = 0.24
+    h1 = 0.45
+    w2 = 0.2
+    h2 = 0.2
+    w3 = 0.025
+    h3 = 0.325
+    h4 = 0.05
+    wspace1 = 0.02
+    wspace3 = 0.08
+    hspace2 = 0.03
+    hspace4 = 0.04
+    zoom_region = [-30, 30, -30, 30]
+    indicator_region = [185, 455, 140, 140]
+
+    # Plot parameters
+    cmap = 'RdBu_r'
+    lw = 0.1
+    lalpha = 0.3
+
+    h = (1 - y0) * htot
+    hspace1 = (h - h1) / 2
+    hspace3 = (h - h4 - h3) / 2
+    wspace2 = (1 - w1 - 3*w2 - w3 - wspace1 - wspace3) / 2
+
+    def load_data(data_file):
+        def set_region(tri, disp):
+            def in_region(x, y):
+                return (x>zoom_region[0]) & (x<zoom_region[1]) & (y>zoom_region[2]) & (y<zoom_region[3])
+            node_mask = ~in_region(tri.x, tri.y)
+            tri_mask = np.all(node_mask[tri.triangles], axis=1)
+            tri.set_mask(tri_mask)
+            # disp_mask = np.full(disp.shape, True)
+            # disp_mask[:,tri.triangles[~tri_mask]] = False
+        with open(data_file) as f:
+            data = json.load(f)
+        disp1 = data['d1']
+        disp2 = data['d2']
+        disp3 = data['d3']
+        tri1 = mtri.Triangulation(data['x1'], data['y1'], data['t1'])
+        tri2 = mtri.Triangulation(data['x2'], data['y2'], data['t2'])
+        tri3 = mtri.Triangulation(data['x3'], data['y3'], data['t3'])
+        set_region(tri1, disp1)
+        set_region(tri2, disp2)
+        set_region(tri3, disp3)
[…]

### 2022-03-06 fig/make_changingmesh/plot.py

@@ -1,145 +1,0 @@
-#!/usr/bin/env python3
-import numpy as np
-import matplotlib as mpl
-import matplotlib.pyplot as plt
-import matplotlib.tri as mtri
-import json
-import pyutils.latexify as lt
-# Get default style for paper
-import sys; sys.path.insert(0, '..')
-import style
-
-# Figure parameters
-ar = 0.5
-w1 = 0.24
-h1 = 0.9
-w2 = 0.2
-h2 = 0.4
-w3 = 0.025
-h3 = 0.65
-h4 = 0.13
-wspace1 = 0.02
-wspace3 = 0.08
-hspace4 = 0.04
-
-region = [-30, 30, -30, 30]
-indicator_region = [185, 455, 140, 140]
-
-# Plot parameters
-cmap = 'RdBu_r'
-lw = 0.1
-lalpha = 0.3
-
-
-def set_region(tri, disp):
-    def in_region(x, y):
-        return (x>region[0]) & (x<region[1]) & (y>region[2]) & (y<region[3])
-    node_mask = ~in_region(tri.x, tri.y)
-    tri_mask = np.all(node_mask[tri.triangles], axis=1)
-    tri.set_mask(tri_mask)
-    # disp_mask = np.full(disp.shape, True)
-    # disp_mask[:,tri.triangles[~tri_mask]] = False
-
-
-def load_data(data_file):
-    with open(data_file) as f:
-        data = json.load(f)
-    disp1 = data['d1']
-    disp2 = data['d2']
-    disp3 = data['d3']
-    tri1 = mtri.Triangulation(data['x1'], data['y1'], data['t1'])
-    tri2 = mtri.Triangulation(data['x2'], data['y2'], data['t2'])
-    tri3 = mtri.Triangulation(data['x3'], data['y3'], data['t3'])
-    set_region(tri1, disp1)
-    set_region(tri2, disp2)
-    set_region(tri3, disp3)
-    return tri1, disp1, tri2, disp2, tri3, disp3
-
-
-def create_axes():
-    wspace2 = (1 - w1 - 3*w2 - w3 - wspace1 - wspace3) / 2
-    hspace2 = (1 - h4 - 2*h2)
-    hspace3 = (1 - h4 - h3) / 2
-    xax1 = w1 + wspace1
-    xax2 = xax1 + w2 + wspace2
-    xax3 = xax2 + w2 + wspace2
-    yax1 = 1 - h2
[…]

### 2022-03-06 fig/make_differentgrids/plot.py

@@ -1,148 +1,0 @@
-#!/usr/bin/env python3
-
-import numpy as np
-import matplotlib.pyplot as plt
-import pyutils.latexify as lt
-import json
-# Get default style for paper
-import sys; sys.path.insert(0, '..')
-import style
-
-# Layout parameters with width=1
-w1 = 0.24 # width of state boxes
-h1 = 0.135 # height of state boxes
-w2 = 0.13 # width of zoom box
-h3 = 0.05 # height of arrow box
-ws0 = 0.09 # horizontal space left of state boxes
-ws1 = 0.02 # horizontal space between state boxes
-ws2 = 0.03 # horizontal space left of zoom box
-hs1 = 0.02 # vertical space between state boxes
-hs3 = 0.0 # vertical space above arrow box
-
-zoom_region = [0.595, -0.01, 0.04, 0.08]
-cs1 = 'lightgrey' # hydrophobic
-cs2 = 'k'         # hydrophilic
-cz1 = style.c1
-cz2 = style.c2
-
-
-def load_data(data_file):
-    with open(data_file) as f:
-        data = json.load(f)
-    x11 = np.reshape(data['state11'], [200,201])[:,1:]
-    x12 = np.reshape(data['state12'], [400,401])[:,1:]
-    x21 = np.reshape(data['state21'], [200,201])[:,1:]
-    x22 = np.reshape(data['state22'], [400,401])[:,1:]
-    x31 = np.reshape(data['state31'], [200,201])[:,1:]
-    x32 = np.reshape(data['state32'], [400,401])[:,1:]
-    ts = np.reshape(data['ts'], [400,401])[:,1:]
-    return x11, x12, x21, x22, x31, x32, ts
-
-
-def fig_layout():
-    # Parameters
-    h2 = w1 * zoom_region[3] / zoom_region[2]
-    w3 = 3*w1 + 2*ws1
-    h = 2*h1 + h3 + hs1 + hs3
-    xa = ws0
-    xb = xa + w1 + ws1
-    xc = xb + w1 + ws1
-    xd = 0.999 - w2
-    ya = (h3 + hs3) / h
-    yb = 0.999 - h1/h
-    yc = ya + 0.5*(1 - ya - h2/h)
-    # Axes
-    fig = lt.figure(1, h)
[…]

### 2022-03-06 fig/make_discontinuous/plot.py

@@ -1,145 +1,0 @@
-#!/usr/bin/env python3
-import glob
-import numpy as np
-import pandas as pd
-import matplotlib.pyplot as plt
-import networkx as nx
-from pele.utils.disconnectivity_graph import DisconnectivityGraph
-
-import pyutils.latexify as lt
-# Get default style for paper
-import sys; sys.path.insert(0, '..')
-import style
-
-ndof = 14
-
-class Node:
-    def __init__(self, i, e, x):
-        self.i = i
-        self.energy = e
-        self.x = x
-    def __hash__(self):
-        return self.i
-    def __str__(self):
-        return 'Node '+str(self.i)
-    def __eq__(self, other):
-        return hash(self) == hash(other)
-    def __lt__(self, other):
-        return hash(self) < hash(other)
-
-class TS:
-    def __init__(self, min1, min2, e):
-        self.minimum1 = min1
-        self.minimum2 = min2
-        self.energy = e
-    def __hash__(self):
-        return hash(self.minimum1) ^ hash(self.minimum2)
-    def __str__(self):
-        return 'TS '+str(self.i)
-    def __eq__(self, other):
-        return hash(self) == hash(other)
-    def __lt__(self, other):
-        return hash(self) < hash(other)
-
-
-def load_data():
-    # minima
-    minima = pd.read_csv('min.data')
-    min_e = np.array(minima['energy'])
-    min_x = minima[[f'x{i}' for i in range(ndof)]].to_numpy()
-    nodes = [Node(i, min_e[i], min_x[i]) for i in range(len(minima))]
-    # TS
-    e_ts = np.loadtxt('ts.data', usecols=0)
-    pairs = np.loadtxt('ts.data', usecols=[3,4], dtype=int) - 1
-    ts = [TS(nodes[pair[0]], nodes[pair[1]], e_ts[i]) for i, pair in enumerate(pairs)]
-    return nodes, ts
-
-
-def make_dgraph(nodes, ts):
-    # Generate disconnectivity graph
-    g = nx.Graph()
-    g.add_nodes_from(nodes)
[…]

### 2022-03-06 fig/make_flatdiscontinuous/plot.py

@@ -1,0 +1,290 @@
+#!/usr/bin/env python3
+import glob
+import numpy as np
+import pandas as pd
+import matplotlib.pyplot as plt
+import matplotlib.image as mim
+import networkx as nx
+from pele.utils.disconnectivity_graph import DisconnectivityGraph
+
+import pyutils.latexify as lt
+# Get default style for paper
+import sys; sys.path.insert(0, '..')
+import style
+
+
+def plot_flat(fig, hsize):
+    ### Plot parameters
+    ax_size = np.array([[0.15, 0.2, 0.83, 0.78],
+                        [0.42, 0.25, 0.48, 0.38]])
+    axin_bounds = np.array([[0.675, 0.8], [-2,-1.45]])
+    axin_scale = 50
+
+    y0 = 0.3
+    dx = 2.5
+
+    cpath = style.c1
+    cts = style.c2
+    cmin = style.c3
+    ms = 5
+    mec = 'k'
+    lw = 1.2
+
+    ax_size[:,1] = ax_size[:,1] * hsize[1] + hsize[0]
+    ax_size[:,3] = ax_size[:,3] * hsize[1]
+    dy = dx * ax_size[1,3] / ax_size[1,2]
+
+    ### Potential parameters
+    cut1 = -0.5
+    cut2 = 0.3
+    w = 0.5
+    peaks = [[-3., -1.414, 0., 1., 1.],
+             [-2., 1.414, 0., 1., 1.],
+             [-1., 0.07, 1.06, 1., 1.]]
+
+    def energy(x, y):
+        def adjust_x(x):
+            x = np.array(x)
+            reg1 = x < (cut1-w)
+            reg2 = np.logical_and(x>(cut1-w), x<cut1)
+            reg3 = x > (cut2+w)
+            reg4 = np.logical_and(x<(cut2+w), x>cut2)
+            xp = x.copy()
+            xp[reg1] = x[reg1] + w
+            xp[reg2] = cut1
+            xp[reg3] = x[reg3] - w
+            xp[reg4] = cut2
+            return xp
+        xp = adjust_x(x)
+        e = np.zeros_like(x)
+        for peak in peaks:
+            e += peak[0] * np.exp( -((xp-peak[1])/peak[3])**2 - ((y-peak[2])/peak[4])**2 )
+        return e
+
+    def make_potential():
+        xlim = (-dx, dx)
+        ylim = (y0-dy, y0+dy)
[…]

### 2022-03-06 fig/make_speedtest/plot.py

@@ -13,7 +13,13 @@ lt.update_width('r4-double')
 def str_converter(instr):
     return np.fromstring(instr[1:-1],sep=' ')
 
-for subfig in ['a', 'b', 'c']:
+y0 = 0.15
+h1 = 0.62/3 # height of lower axes relative to width
+h2 = 1/9 # height of upper axes relative to width
+h = h1 + h2
+fig = lt.figure(1, h)
+
+for isub, subfig in enumerate(['a', 'b', 'c']):
 
     ### Load data
     if (subfig == 'a'):
@@ -40,13 +46,9 @@ for subfig in ['a', 'b', 'c']:
 
 
     ### Plot data
-    width = 1/3
-    h1 = 1/1.618 # height of lower axes relative to width
-    h2 = 1/3 # height of upper axes relative to width
-    h = h1 + h2
-    fig = lt.figure(width, h)
-    ax = plt.axes((0.19, 0.13, 0.78, h1/h-0.1))
-    fig.text(0, 1, f'({subfig})', va='top', ha='left')
+    x0 = isub / 3
+    ax = plt.axes((x0+0.19/3, y0, 0.26, h1/h-y0+0.03))
+    fig.text(x0, 1, f'({subfig})', va='top', ha='left')
 
     if (subfig == 'a'):
         ax.annotate('BITSS', [0.1, 0.08], [0.2, 0.1], xycoords='axes fraction',
@@ -84,7 +86,7 @@ for subfig in ['a', 'b', 'c']:
 
     # Snapshots
     for i in range(3):
-        tmp_ax = plt.axes((0.035+i*0.31, 1-h2/h, 0.31, h2/h))
+        tmp_ax = plt.axes((x0+(0.035+i*0.31)/3, 1-h2/h, 0.1, h2/h))
         img = mim.imread(f'{subfig}{i}.png')
         plt.imshow(img)
         tmp_ax.axis('off')
@@ -92,5 +94,4 @@ for subfig in ['a', 'b', 'c']:
         if (i==1):
             tmp_ax.text(0.25, 1, '*', va='top', ha='center', size='xx-large', transform=tmp_ax.transAxes)
 
-    # plt.savefig(f'speedtest-dneb-{subfig}.png')
-    lt.savefig(f'../speedtest-{subfig}.pdf', dpi=300)
+lt.savefig(f'../speedtest.pdf', dpi=300)

### 2022-03-06 fig/make_zeroeigen/plot.py

@@ -1,172 +1,0 @@
-#!/usr/bin/env python3
-import numpy as np
-import matplotlib as mpl
-import matplotlib.pyplot as plt
-import matplotlib.image as mim
-import pandas as pd
-import pyutils.latexify as lt
-from mpl_toolkits.axes_grid1.inset_locator import mark_inset
-# Get default style for paper
-import sys; sys.path.insert(0, '..')
-import style
-
-### Plot parameters
-aspect = 0.5
-ax_size = [[0.15, 0.2, 0.83, 0.78],
-           [0.42, 0.25, 0.48, 0.38]]
-# axin_size = [0.05, 0.53, 0.2, 0.4]
-axin_bounds = np.array([[0.675, 0.8], [-2,-1.45]])
-axin_scale = 50
-
-y0 = 0.3
-dx = 2.5
-dy = dx * ax_size[1][3] / ax_size[1][2] * aspect
-
-cpath = style.c1
-cts = style.c2
-cmin = style.c3
-ms = 5
-mec = 'k'
-lw = 1.2
-
-
-### Potential parameters
-cut1 = -0.5
-cut2 = 0.3
-w = 0.5
-peaks = [[-3., -1.414, 0., 1., 1.],
-         [-2., 1.414, 0., 1., 1.],
-         [-1., 0.07, 1.06, 1., 1.]]
-
-
-def energy(x, y):
-    def adjust_x(x):
-        x = np.array(x)
-        reg1 = x < (cut1-w)
-        reg2 = np.logical_and(x>(cut1-w), x<cut1)
-        reg3 = x > (cut2+w)
-        reg4 = np.logical_and(x<(cut2+w), x>cut2)
-        xp = x.copy()
-        xp[reg1] = x[reg1] + w
-        xp[reg2] = cut1
-        xp[reg3] = x[reg3] - w
-        xp[reg4] = cut2
-        return xp
-    xp = adjust_x(x)
-    e = np.zeros_like(x)
-    for peak in peaks:
-        e += peak[0] * np.exp( -((xp-peak[1])/peak[3])**2 - ((y-peak[2])/peak[4])**2 )
-    return e
-
-
-### Make potential
-def make_potential():
-    xlim = (-dx, dx)
-    ylim = (y0-dy, y0+dy)
-    x, y = np.mgrid[xlim[0]:xlim[1]:100j, ylim[0]:ylim[1]:100j]
-    e = energy(x, y)
-
[…]

### 2022-03-06 si/fig/make_DNEBspeedtest/plot.py

@@ -86,4 +86,4 @@ for isub, subfig in enumerate(['a', 'b', 'c']):
         if (i==1):
             tmp_ax.text(0.25, 1, '*', va='top', ha='center', size='xx-large', transform=tmp_ax.transAxes)
 
-    lt.savefig(f'../DNEBspeedtest.pdf', dpi=300)
+lt.savefig(f'../DNEBspeedtest.pdf', dpi=300)

### 2022-03-10 manuscript.tex
Halim's edits to manuscript. Removed topic lines.

@@
 \usepackage{siunitx}
+\usepackage{enumitem}
 
@@
 \Crefname{figure}{Fig.}{Figs.}
-
-% Temp
-\newcommand*{\newlinecommand}[2]{%
-  \newcommand*{#1}{%
-    \begingroup%
-    \escapechar=`\\%
-    \catcode\endlinechar=\active%
-    \csname\string#1\endcsname%
-  }%
-  \begingroup%
-  \escapechar=`\\%
-  \lccode`\~=\endlinechar%
-  \lowercase{%
-    \expandafter\endgroup
-    \expandafter\def\csname\string#1\endcsname##1~%
-  }{\endgroup#2\space}%
-}
-\newlinecommand{\topic}{\textbf{#1}}
-% \newlinecommand{\topic}{#1}
 
@@
 \begin{abstract}
-  Locating transition states is crucial for investigating transition mechanisms in wide-ranging atomistic systems and, more recently, macroscale systems.
+  Locating transition states is crucial for investigating transition mechanisms in wide-ranging, from atomistic tomacroscale systems.
   Existing methods, however, can struggle in problems with a large number of degrees of freedom, on-the-fly adaptive remeshing and coarse-graining, and energy landscapes that are locally flat or discontinuous.
@@
 %\section{Introduction \& Method}
-\topic Transition states are central to the description of reconfiguration mechanisms for systems in chemistry, condensed matter physics, and engineering.
+Transition states are central to the description of reconfiguration mechanisms for systems in chemistry, condensed matter physics, and engineering.
 Historically, many computational methods for locating transition states have grown from an atomistic or particulate perspective.
-These have proven to be important tools for understanding, for example, protein folding \cite{Bryngelson1995,Onuchic1997}, biological and industrial catalysis \cite{Boehr2006,Kerns2015,Guo2018a}, quantum tunneling \cite{Richardson2016,Vaillant2019}, crystallisation, and cluster formation \cite{Wales1998,Wales2012}.
+These have proven to be important tools for understanding, for example, protein folding \cite{Bryngelson1995,Onuchic1997}, biological and industrial catalysis \cite{Boehr2006,Kerns2015,Guo2018a}, quantum tunneling \cite{Richardson2016,Vaillant2019}, crystallisation [cite], and cluster formation \cite{Wales1998,Wales2012}.
 
-\topic More recently, it is increasingly being recognised that transition states are useful in mesoscale or macroscale systems.
+More recently, it is increasingly being recognised that transition states are useful in mesoscale or macroscale systems.
 Here, the minimum energy barriers provide important lower bounds to the energy input required for transitions to occur.
 This has been used to understand failure in structural engineering applications \cite{Panter2019,Hutchinson2018}, for the development of super liquid-repellent surfaces \cite{Zhang2014,Panter2019b}, and investigating locomotion through complex terrain for robotics \cite{Othayoth2020}.
-Moreover, it is becoming desirable to tailor elastic deformation transitions to enable technologies such as advanced deployable structures \cite{Filipov2015,Zhai2018}, mechanical sensors and actuators, and energy absorption \cite{Shan2015} to name but a few.
+Moreover, it is becoming desirable to tailor elastic deformation transitions to enable technologies such as advanced deployable structures \cite{Filipov2015,Zhai2018}, mechanical sensors and actuators [cite], and energy absorption \cite{Shan2015} to name but a few.
 
-\topic Existing transition state search methods generally fall into two categories, single- and double-ended methods.
+Existing transition state search methods generally fall into two categories, single- and double-ended methods.
 Single-ended methods are initialised at a single state and attempt to climb to a nearby saddle point.
@@
 
-\topic However, a large range of landscapes prove challenging or impossible to explore via these methods.
+However, a large range of landscapes prove challenging or impossible to explore via these methods.
 One key problem arises from the push towards larger and more complex systems \cite{Trefethen2013,Shalf2020,Alexander2020}, resulting in the need to develop algorithms that are more memory and computationally efficient, and can incorporate optimisation strategies such as on-the-fly adaptive remeshing and coarse-graining.
-Current double-ended methods require a chain of tens of states to gain an accurate approximation, and have issues with remeshing resulting in a different discretisation for each state.
+Current double-ended methods require a chain of tens of states to gain an accurate approximation, and have issues with remeshing resulting in a different number of degrees of freedom for each state.
 Single-ended methods are not well suited for identifying specific pathways and can spend a large amount of time searching for undesired transition states.
@@
 
-\topic In this work we introduce a new method, the Binary Image Transition State Search (BITSS).
+In this work we introduce a new method, the Binary Image Transition State Search (BITSS).
 This is a double-ended method that uses two states that converge toward a transition state from either side, therefore combining aspects of the two traditional transition state search categories.
@@
 %\section{Method}
-\topic The method begins by first initialising the states, $\bm{x}_1$ and $\bm{x}_2$, in the basins of attraction of different local minima.
+The method begins by first initialising the states, $\bm{x}_1$ and $\bm{x}_2$, in the basins of attraction of different local minima.
 These can be set to the minima, but this is not a necessary requirement.
-The BITSS method then causes these states to meet at the lowest point on the ridge between the basins of attraction - the transision state.
+The BITSS method then leads these states to meet at the lowest point on the ridge between the basins of attraction - the transition state.
 This is done by minimising the energy of the pair while constraining their separation.
@@
 \end{equation}
-with $d_0$ as the separation between the initial states.
+with $d_0$ the separation between the initial states.
 A factor of $f = 0.5$ is succesful for most applications, but this can be made smaller to ensure that the states do not slide off the ridge.
@@
 
-\topic Using this approach, the typical trajectories of the states are demonstrated for a simple 2D potential in \cref{fig:toy2d}a.
-Initially, the lower energy state jumps up to satisfy the equal energy constraint and then moves to minimise the separation without increasing its energy.
-Then, the two states converge directly towards one another, before being deflected towards the saddle in the ridge.
-Consequently, if there are multiple possible pathways between two states, BITSS will be biased towards identifying those that are more direct or with lower energy.
-Furthermore, the final two states are positioned either side of the transition state in the direction of the negative curvature eigenvector, $\bm{\hat{\tau}}$ (\cref{fig:toy2d}c).
-So, BITSS automatically identifies the `reactive mode' and associated eigenvalue in addition to the transition state.
-
-\topic The two constraints are implemented using energy penalty terms, which, if the constraints are not met, result in driving forces on the two states, such as in \cref{fig:toy2d}b.
+The two constraints are implemented using energy penalty terms, which, if the constraints are not met, result in driving forces on the two states, such as in \cref{fig:toy2d}b.
 The total energy of the pair of states is therefore given by,
@@
 
-\topic To ensure that the transition state is located successfully, the constraint strengths $\kappa_d$ and $\kappa_e$ are updated as the algorithm proceeds using information from the system.
+Using this approach, the typical trajectories of the states are demonstrated for a simple 2D potential in \cref{fig:toy2d}a.
+Initially, the lower energy state jumps up to satisfy the equal energy constraint and then moves to minimise the separation without increasing its energy.
+Then, the two states converge directly towards one another, before being deflected towards the saddle in the ridge.
+Consequently, if there are multiple possible pathways between two states, BITSS will be biased towards identifying those that are more direct or with lower energy.
+Furthermore, the final two states are positioned either side of the transition state in the direction of the negative curvature eigenvector, $\bm{\hat{\tau}}$ (\cref{fig:toy2d}c).
+So, BITSS automatically identifies the `reactive mode' and associated eigenvalue in addition to the transition state.
+
+To ensure that the transition state is located successfully, the constraint strengths $\kappa_d$ and $\kappa_e$ are updated as the algorithm proceeds using information from the system.
 They are initially calculated at the start of each minimisation, and regularly recalculated throughout (once per 100 iterations are used in this work).
@@
 For systems where the interpolation deviates significantly from the pathway the estimate can be too large.
-In which case, a maximum estimated value can be provided, which then decreases proportionally with $d_i$.
+In this case, a maximum estimated value can be provided, which then decreases proportionally with $d_i$.
 
-\topic In summary, the method involves iteratively performing the following three steps:
-\begin{enumerate}
+In summary, the method involves iteratively performing the following three steps:
+\begin{enumerate}[noitemsep,nolistsep]
   \item Reduce the target separation using \cref{eq:diteration}.
@@
 This process is completed once a convergence criterion is reached that can be based upon either the separation between the states, or the size of gradient at the midpoint between the two states.
-
-\topic Once BITSS has identified the transition state it is possible to find the full minimum energy pathway.
+Once BITSS has identified the transition state it is possible to find the full minimum energy pathway.
 This is done by tracing the trajectory of downhill minimisations from the two final states either side of the transition state.
@@
 \end{figure*}
-\topic As a result of the BITSS method using only two states it has the potential to be significantly faster than chain-of-states approaches which typically use tens of states.
+As a result of the BITSS method using only two states it has the potential to be significantly faster than chain-of-states approaches which typically use tens of states.
 This is tested here by measuring the speed of convergence to the transition state for BITSS in comparison with the string method and DNEB for several representative examples.
 
-\topic The first system to be tested is a two-dimensional, seven-particle cluster, with the transition from a hexagonal cluster to a higher energy configuration.
+The first system to be tested is a two-dimensional, seven-particle cluster, with the transition from a hexagonal cluster to a higher energy configuration.
 The interaction between each pair of particles uses the Lennard-Jones potential,
@@
 
-\topic The second system is an elastic cylindrical shell under an applied strain.
+The second system is an elastic cylindrical shell under an applied strain.
 This undergoes a transition from an unbuckled state to a singly-dimpled state, which defines the minimum energy required for the cylinder to buckle \cite{Panter2019}.
-A 2D triangular mesh is used to model this system, with the following energy function,
+A 2D triangular mesh with 35400 degrees of freedom is used to model this system, with the following energy function,
 \begin{equation}
@@
 
-\topic The final system involves a droplet situated on a chemically striped surface with both hydrophilic and hydrophobic regions.
+The final system involves a droplet situated on a chemically striped surface with both hydrophilic and hydrophobic regions.
 This has two possible states, with the droplet either upon one hydrophilic stripe, or straddling across two.
@@
 $E_S$ is the solid-liquid interaction energy, which sets the contact angles of the hydrophilic and hydrophobic regions to 60\si{\degree} and 110\si{\degree}, respectively.
-Finally, $E_V$ constrains the volume of the liquid drop by penalising any variation from 11\% of the total volume of the system.
+Finally, $E_V$ constrains the volume of the liquid drop by penalising any variation from the target volume.
 For further details and the gradients of the potentials see the supplementary information.
 
-\topic Convergence is measured using the distance from the transition state as a function of number of evaluations to the gradient of the system's potential.
+Convergence is measured using the distance from the transition state as a function of number of evaluations to the gradient of the system's potential.
 The transition state is compared to the average of the two states for BITSS, whereas for the chain-of-states methods, the closest point on a cubic spline is used.
 
-\topic The results for this test, shown in \cref{fig:speedtest}, demonstrate two main advantages for the BITSS method.
+The results for this test, shown in \cref{fig:speedtest}, demonstrate two main advantages for the BITSS method.
 Firstly, the slope illustrates that the rate of convergence is indeed much greater for the BITSS method.
@@
 %\section{Adaptive mesh}
-\topic Adaptive remeshing and coarse-graining are widely used techniques that we can utilise to further increase the efficiency of BITSS.
-These techniques cause issues for double-ended methods because the coupled states may end up with different discretisations.
+Adaptive remeshing and coarse-graining are widely used techniques that we can utilise to further increase the efficiency of BITSS.
+These techniques cause issues for existing double-ended methods because the coupled states may end up with different degrees of freedom.
 However, in BITSS the only direct coupling is in the distance measure, $\mathrm{d}(\bm{x}_1,\bm{x}_2)$, which is relatively easy to adapt.
@@
 
-\topic Firstly, we show in \cref{fig:adaptivemesh}a that BITSS is able to handle the discretisation changing as the method runs.
+Firstly, we show in \cref{fig:adaptivemesh}a that BITSS is able to handle the discretisation changing as the method runs.
 For this we use the cylindrical buckling example with the resolution increasing from 40 to 100 triangles around the cylinder.
@@
 
-\topic In the second test, \cref{fig:adaptivemesh}b, we demonstrate the use of different meshes for the two states in the striped wetting example.
+In the second test, \cref{fig:adaptivemesh}b, we demonstrate the use of different meshes for the two states in the striped wetting example.
 In this case, the distance measure is adapted by interpolating one state onto the other mesh and computing the Euclidean distance.
@@
 %\section{Zero-curvature modes}
-\topic The final challenges we will address are those related to complex landscapes.
+The final challenges we will address are those related to complex landscapes.
 The first is the presence of flat regions in the landscape.
@@
     (a) Energy profile of the BITSS pathway on a 2D potential with flat regions.
-        The blue and red dots denote the minima and transition state, respectively.
+        Blue and red dots denote the minima and transition state, respectively.
         Points of interest are labelled by i--iii (see text).
@@
 %\section{Gradient-free problems}
-\topic Finally we investigate the application of BITSS to systems with undefined gradients, such as when the landscape is discontinuous.
+Finally, we investigate the application of BITSS to systems with undefined gradients, such as when the landscape is discontinuous.
 In this case a couple of alterations to the method must be made.
-First, the term using gradients in \cref{eq:kd} can be ignored and $\kappa_d$ can instead be calculated using just the second term.
+First, the gradients in \cref{eq:kd} are ill-defined, so $\kappa_d$ can be calculated using just the second term in the equation.
 Next we must use a minimiser that does not require a differentiable optimisation function; for this we use simulated annealing \cite{Kirkpatrick1983}.
-This has a chance of randomly jumping one state over the dividing barrier, but we can reduce this probability by setting the initial temperature to $T_0 = \Delta E / 10$, and the maximum size of random displacements to $d_\text{max} = d(\bm{x}_1, \bm{x}_2) / 100$.
+This has a chance of randomly jumping one state over the dividing barrier, but we can reduce this probability by limiting the initial temparature and maximum random displacement.
+We typically employ $T_0 = \Delta E / 10$, and $d_\text{max} = d(\bm{x}_1, \bm{x}_2) / 100$.
 This has been tested using a Lennard-Jones 7-particle cluster with hard cores, resulting in a discontinuous landscape.
@@
 %\section{Conclusion}
-\topic In conclusion, we have demonstrated a novel method for finding transition states that tackles problems not currently addressed by existing methods.
+In conclusion, we have demonstrated a novel method for finding transition states that tackles problems not currently addressed by existing methods.
 The method is shown to be more efficient than existing double-ended methods, both in memory and computational cost, with further reductions possible by utilising adaptive remeshing techniques.
@@
 \begin{acknowledgments}
-  S.~J.~A. is supported by a studentship from the Engineering and Physical Sciences Research Council (Grant No. EP/R513039/1).
-  H.~K. and J.~R.~P. acknowledge funding from the Engineering and Physical Sciences Research Council (Grant No. EP/V034154/1).
+  S.~J.~A. is supported by a studentship from the Engineering and Physical Sciences Research Council [EP/R513039/1].
+  H.~K. and J.~R.~P. acknowledge funding from the Engineering and Physical Sciences Research Council [EP/V034154/1].
 \end{acknowledgments}
@@
 \bibliographystyle{apsrev4-2}
-\bibliography{bibexport.bib}
+% \bibliography{bibexport.bib}
+\bibliography{../../library.bib}
 

### 2022-03-14 si/supplementary_information.tex
Combined subfigures
Halim's edits to SI

@@
 \end{equation}
-Therefore, when not at a transition state or a minima in the landscape ($\abs{\grad E_2} \neq 0$) convergence will occur when the term in the square brackets is zero, resulting in $E_1 - E_2 = 1 / 2 \kappa_e$.
+Therefore, when not at a transition state or a minimum in the landscape ($\abs{\grad E_2} \neq 0$) convergence will occur when the term in the square brackets is zero, resulting in $E_1 - E_2 = 1 / 2 \kappa_e$.
 This energy difference should be less than current energy barrier, so we can substitute it with $\upDelta E / \alpha$, where $\upDelta E$ is the energy barrier estimate described in the main paper and $\alpha$ is a constant greater than one.
@@
 To ensure that the coefficient is not too small if the gradient is close to zero, such as when the states are initialised at the minima, a lower bound is set by replacing $\abs{\grad E_1}$ and $\abs{\grad E_2}$ with $2 \upDelta E / d_i$.
-Giving the expression,
+This gives the expression,
 \begin{equation}
@@
 The constant parameters $\alpha$ and $\beta$ still must be chosen.
-To this end we have tested different parameter choices using the seven-particle cluster and cylindrical buckling examples.
+To this end we have tested different parameter choices using the seven-particle cluster and cylindrical buckling examples, with fractional separation decreases per BITSS step of $f=0.5$ and $f=0.4$, respectively.
 \Cref{fig:paramtest} shows which choices lead to convergence and the speed at which this occurs.
@@
 
-\FloatBarrier
 \section{Test potentials and gradients}
@@
 
+\newpage
 \section{Details for the adaptive discretisation tests}
@@
 
-In the example with different resolutions for the two states, the distance is obtained by mapping the phase field from the higher resolution grid to the low resolution grid, and then using the 2-norm.
-Because a square grid is used with a resolution ratio of two, the mapping involves averaging each 2x2 block to a single point.
-Finally, the gradient with respect to each point must be mapped back to the higher-resolution grid, which is done by assigning a quarter of each component back to its the original four points.
+In the example with different resolutions for the two states, the distance is obtained by first mapping the phase field from the higher resolution grid, $\{\phi_{k,l} | k,l \in \{0,1,\cdots,399\}\}$, to the low resolution grid, $\{\phi'_{i,j} | i,j \in \{0,1,\cdots,199\}$.
+Because a square grid is used with a resolution ratio of two, the mapping involves averaging each 2x2 block to a single point:
+\begin{equation}
+  \phi'_{i,j} = \frac{1}{4} \left( \phi_{2i,2j} + \phi_{2i+1,2j} + \phi_{2i,2j+1} + \phi_{2i+1,2j+1} \right)
+\end{equation}
+Then the separation from the other state, $\{\widetilde{\phi}_{i,j}\}$ is computed using the 2-norm,
+\begin{equation}
+  d = \sqrt{\sum_{i,j} \left( \phi'_{i,j} - \widetilde{\phi}_{i,j} \right)^2}.
+\end{equation}
+Finally, the gradient of the distance with respect to each point must be mapped back to the higher-resolution grid, which is done by assigning a quarter of each component back to its the original four points:
+\begin{equation}
+  \frac{\partial d}{\partial \phi_{k,l}} =
+    \frac{\partial \phi'_{i,j}}{\partial \phi_{k,l}} \frac{\partial d}{\partial \phi'_{i,j}} =
+    \frac{1}{4} \frac{\partial d}{\partial \phi'_{i,j}} =
+    \frac{1}{4} \frac{\phi'_{i,j} - \widetilde{\phi}_{i,j}}{d},
+\end{equation}
+where $k \in \{2i, 2i+1\}$, and $l \in \{2j, 2j+1\}$.
 
@@
 \Cref{fig:DNEBspeedtest} shows the results for the speed test in comparison with DNEB.
-Much the same as the string method, the slope of BITSS is greater than DNEB with 10 or 20 states, indicating a faster convergence.
+Similar to the results for the string method, the slope of BITSS is greater than DNEB with 10 or 20 states, indicating a faster convergence.
 Furthermore, with the exception of the seven-particle cluster, DNEB is also much less accurate at approximating the transition state, even with a large number of images.
@@
     The convergence to the transition state as a function of the number of gradient calculations using the BITSS (black line) and DNEB for (a) a Lennard-Jones seven-particle cluster, (b) cylindrical shell buckling, and (c) wetting of a chemically-striped surface.
-    The string method is repeated with a differing number of images along the string, the number of which is listed in the legend in (c).
+    DNEB is repeated with a differing number of images along the chain, the number of which is listed in the legend in (c).
     The shown configurations correspond to the two minimum energy states and the transition state, marked by an asterisk.

### 2022-03-14 manuscript.tex
Added remaining references and new and high-impact references

@@
 Historically, many computational methods for locating transition states have grown from an atomistic or particulate perspective.
-These have proven to be important tools for understanding, for example, protein folding \cite{Bryngelson1995,Onuchic1997}, biological and industrial catalysis \cite{Boehr2006,Kerns2015,Guo2018a}, quantum tunneling \cite{Richardson2016,Vaillant2019}, crystallisation [cite], and cluster formation \cite{Wales1998,Wales2012}.
+These have proven to be important tools for understanding, for example, protein folding \cite{Bryngelson1995,Onuchic1997}, biological and industrial catalysis \cite{Boehr2006,Kerns2015,Guo2018a}, quantum tunneling \cite{Richardson2016,Vaillant2019}, crystallisation \cite{Richard2018}, and cluster formation \cite{Wales1998,Wales2012}.
 
@@
 This has been used to understand failure in structural engineering applications \cite{Panter2019,Hutchinson2018}, for the development of super liquid-repellent surfaces \cite{Zhang2014,Panter2019b}, and investigating locomotion through complex terrain for robotics \cite{Othayoth2020}.
-Moreover, it is becoming desirable to tailor elastic deformation transitions to enable technologies such as advanced deployable structures \cite{Filipov2015,Zhai2018}, mechanical sensors and actuators [cite], and energy absorption \cite{Shan2015} to name but a few.
+Moreover, it is becoming desirable to tailor elastic deformation transitions to enable technologies such as advanced deployable structures \cite{Filipov2015,Zhai2018}, mechanical sensors and actuators \cite{Bertoldi2017,Truby2016,Chi2022,Bonfanti2020}, and energy absorbers \cite{Shan2015,Giri2021} to name but a few.
 
@@
 Another major challenge in studying complex energy landscapes relates to the presence of locally flat or discontinous regions.
-Both of which can be relevent when considering contact forces for macroscopic objects [cite], or hard-body interactions in atomistic systems [cite].
+Both of which can be relevent when considering patchy \cite{McMullen2018,Nguemaha2018,Chen2018b} and hard-body \cite{Richard2018,Santra2018} interactions in atomistic systems, or collision constraints for macroscopic objects \cite{Wriggers2006}.
 Flat zero-modes in the landscape pose issues for single-ended search methods that rely only upon local information.
@@
 This is a double-ended method that uses two states that converge toward a transition state from either side, therefore combining aspects of the two traditional transition state search categories.
-We will demonstrate how it addresses each of the above challenges using a range of different applications.
+We demonstrate how it addresses each of the above challenges using a range of different applications.
 
@@
 \begin{acknowledgments}
-  S.~J.~A. is supported by a studentship from the Engineering and Physical Sciences Research Council [EP/R513039/1].
-  H.~K. and J.~R.~P. acknowledge funding from the Engineering and Physical Sciences Research Council [EP/V034154/1].
+  S.~J.~A. is supported by a studentship from the Engineering and Physical Sciences Research Council [Grant No. EP/R513039/1].
+  H.~K. and J.~R.~P. acknowledge funding from the Engineering and Physical Sciences Research Council [Grant No. EP/V034154/1].
 \end{acknowledgments}
@@
 \bibliographystyle{apsrev4-2}
-% \bibliography{bibexport.bib}
-\bibliography{../../library.bib}
+\bibliography{bibexport.bib}
+% \bibliography{../../library.bib}
 

### 2022-03-14 si/fig/make_paramtest/plot.py
Updated paramtest

@@ -11,9 +11,9 @@ import style
 subfigs = ['a', 'b']
 systems = ['lj', 'cb']
 levels = [[600, 1000, 2000],
-          [42000, 45000, 50000]]
-label_locs = [[(4.5, 0.1), (10, 0.1), (50,0.19)],
-              [(10, 0.03), (18, 0.13), (180, 0.05)]]
+          [57000, 60000, 65000]]
+label_locs = [[(10, 0.01), (20, 0.003), (50,0.0003)],
+              [(20, 0.01), (5.6, 0.13), (100, 0.2)]]
 
 cmap = copy.copy(cm.get_cmap('viridis'))
 cmap.set_bad('lightgrey')

### 2022-03-15 manuscript.tex
Inserted citations into manuscript. Added SI footnote.

@@
 \end{gather}
-where $\alpha$ and $\beta$ are parameters with recommended values of $\alpha = 10$ and $\beta = 0.1$ (see supplementary information).
+where $\alpha$ and $\beta$ are parameters with recommended values of $\alpha = 10$ and $\beta = 0.1$ (see supplementary information \footnote{See Supplemental Material at [URL] for derivations of the constraint coefficients, extra details for the example systems, results for the speed test against DNEB, and a comparison of the discontinuous energy landscape with the standard Lennard-Jones cluster}).
 Here, $\Delta E$ is an estimation for the current energy barrier evaluated by linearly interpolating between the two states.
@@
 Finally, $E_V$ constrains the volume of the liquid drop by penalising any variation from the target volume.
-For further details and the gradients of the potentials see the supplementary information.
+For further details and the gradients of the potentials see the supplementary information \cite{Note1}.
 
@@
 Therefore, unlike the string method, BITSS does not require a second approach to accurately locate the transition state.
-Similar results are also found when comparing against against DNEB, which can be seen in the supplementary information.
+Similar results are also found when comparing against against DNEB, which can be seen in the supplementary information \cite{Note1}.
 
@@
 Using the gradient-free approach, BITSS is able to successfully find the transition states, allowing us to plot the disconnectivity graph of the system, shown in \cref{fig:flatdiscontinuous}b.
-A comparison with the results for the standard Lennard-Jones cluster is given in the supplementary information.
+A comparison with the results for the standard Lennard-Jones cluster is given in the supplementary information \cite{Note1}.
 It is worth noting, however, that a gradient-based approach is significantly more efficient, and so should be preferred if possible.
@@
 
-\bibliographystyle{apsrev4-2}
-\bibliography{bibexport.bib}
+% \bibliographystyle{apsrev4-2}
+% \bibliography{bibexport.bib}
 % \bibliography{../../library.bib}
 
+% start bib
+\begin{thebibliography}{42}%
+\makeatletter
+\providecommand \@ifxundefined [1]{%
+ \@ifx{#1\undefined}
+}%
+\providecommand \@ifnum [1]{%
+ \ifnum #1\expandafter \@firstoftwo
+ \else \expandafter \@secondoftwo
+ \fi
+}%
+\providecommand \@ifx [1]{%
+ \ifx #1\expandafter \@firstoftwo
+ \else \expandafter \@secondoftwo
+ \fi
+}%
+\providecommand \natexlab [1]{#1}%
+\providecommand \enquote  [1]{``#1''}%
+\providecommand \bibnamefont  [1]{#1}%
+\providecommand \bibfnamefont [1]{#1}%
+\providecommand \citenamefont [1]{#1}%
+\providecommand \href@noop [0]{\@secondoftwo}%
+\providecommand \href [0]{\begingroup \@sanitize@url \@href}%
+\providecommand \@href[1]{\@@startlink{#1}\@@href}%
+\providecommand \@@href[1]{\endgroup#1\@@endlink}%
+\providecommand \@sanitize@url [0]{\catcode `\\12\catcode `\$12\catcode
+  `\&12\catcode `\#12\catcode `\^12\catcode `\_12\catcode `\%12\relax}%
+\providecommand \@@startlink[1]{}%
+\providecommand \@@endlink[0]{}%
+\providecommand \url  [0]{\begingroup\@sanitize@url \@url }%
+\providecommand \@url [1]{\endgroup\@href {#1}{\urlprefix }}%
+\providecommand \urlprefix  [0]{URL }%
+\providecommand \Eprint [0]{\href }%
+\providecommand \doibase [0]{https://doi.org/}%
+\providecommand \selectlanguage [0]{\@gobble}%
+\providecommand \bibinfo  [0]{\@secondoftwo}%
+\providecommand \bibfield  [0]{\@secondoftwo}%
+\providecommand \translation [1]{[#1]}%
+\providecommand \BibitemOpen [0]{}%
+\providecommand \bibitemStop [0]{}%
+\providecommand \bibitemNoStop [0]{.\EOS\space}%
+\providecommand \EOS [0]{\spacefactor3000\relax}%
+\providecommand \BibitemShut  [1]{\csname bibitem#1\endcsname}%
+\let\auto@bib@innerbib\@empty
+\bibitem [{\citenamefont {Bryngelson}\ \emph {et~al.}(1995)\citenamefont
+  {Bryngelson}, \citenamefont {Onuchic}, \citenamefont {Socci},\ and\
+  \citenamefont {Wolynes}}]{Bryngelson1995}%
+  \BibitemOpen
+  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {J.~D.}\ \bibnamefont
+  {Bryngelson}}, \bibinfo {author} {\bibfnamefont {J.~N.}\ \bibnamefont
+  {Onuchic}}, \bibinfo {author} {\bibfnamefont {N.~D.}\ \bibnamefont {Socci}},\
+  and\ \bibinfo {author} {\bibfnamefont {P.~G.}\ \bibnamefont {Wolynes}},\
+  }\href {https://doi.org/10.1002/prot.340210302} {\bibfield  {journal}
+  {\bibinfo  {journal} {Proteins: Structure, Function, and Bioinformatics}\
+  }\textbf {\bibinfo {volume} {21}},\ \bibinfo {pages} {167} (\bibinfo {year}
+  {1995})}\BibitemShut {NoStop}%
+\bibitem [{\citenamefont {Onuchic}\ \emph {et~al.}(1997)\citenamefont
+  {Onuchic}, \citenamefont {Luthey-Schulten},\ and\ \citenamefont
+  {Wolynes}}]{Onuchic1997}%
+  \BibitemOpen
+  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {J.~N.}\ \bibnamefont
+  {Onuchic}}, \bibinfo {author} {\bibfnamefont {Z.}~\bibnamefont
+  {Luthey-Schulten}},\ and\ \bibinfo {author} {\bibfnamefont {P.~G.}\
+  \bibnamefont {Wolynes}},\ }\href
+  {https://doi.org/10.1146/annurev.physchem.48.1.545} {\bibfield  {journal}
+  {\bibinfo  {journal} {Annual Review of Physical Chemistry}\ }\textbf
+  {\bibinfo {volume} {48}},\ \bibinfo {pages} {545} (\bibinfo {year}
+  {1997})}\BibitemShut {NoStop}%
+\bibitem [{\citenamefont {Boehr}\ \emph {et~al.}(2006)\citenamefont {Boehr},
+  \citenamefont {McElheny}, \citenamefont {Dyson},\ and\ \citenamefont
+  {Wrightt}}]{Boehr2006}%
+  \BibitemOpen
+  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {D.~D.}\ \bibnamefont
+  {Boehr}}, \bibinfo {author} {\bibfnamefont {D.}~\bibnamefont {McElheny}},
+  \bibinfo {author} {\bibfnamefont {H.~J.}\ \bibnamefont {Dyson}},\ and\
+  \bibinfo {author} {\bibfnamefont {P.~E.}\ \bibnamefont {Wrightt}},\ }\href
+  {https://doi.org/10.1126/science.1130258} {\bibfield  {journal} {\bibinfo
+  {journal} {Science}\ }\textbf {\bibinfo {volume} {313}},\ \bibinfo {pages}
+  {1638} (\bibinfo {year} {2006})}\BibitemShut {NoStop}%
+\bibitem [{\citenamefont {Kerns}\ \emph {et~al.}(2015)\citenamefont {Kerns},
+  \citenamefont {Agafonov}, \citenamefont {Cho}, \citenamefont {Pontiggia},
+  \citenamefont {Otten}, \citenamefont {Pachov}, \citenamefont {Kutter},
+  \citenamefont {Phung}, \citenamefont {Murphy}, \citenamefont {Thai},
+  \citenamefont {Alber}, \citenamefont {Hagan},\ and\ \citenamefont
+  {Kern}}]{Kerns2015}%
+  \BibitemOpen
+  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {S.~J.}\ \bibnamefont
+  {Kerns}}, \bibinfo {author} {\bibfnamefont {R.~V.}\ \bibnamefont {Agafonov}},
+  \bibinfo {author} {\bibfnamefont {Y.~J.}\ \bibnamefont {Cho}}, \bibinfo
+  {author} {\bibfnamefont {F.}~\bibnamefont {Pontiggia}}, \bibinfo {author}
+  {\bibfnamefont {R.}~\bibnamefont {Otten}}, \bibinfo {author} {\bibfnamefont
+  {D.~V.}\ \bibnamefont {Pachov}}, \bibinfo {author} {\bibfnamefont
+  {S.}~\bibnamefont {Kutter}}, \bibinfo {author} {\bibfnamefont {L.~A.}\
+  \bibnamefont {Phung}}, \bibinfo {author} {\bibfnamefont {P.~N.}\ \bibnamefont
+  {Murphy}}, \bibinfo {author} {\bibfnamefont {V.}~\bibnamefont {Thai}},
+  \bibinfo {author} {\bibfnamefont {T.}~\bibnamefont {Alber}}, \bibinfo
+  {author} {\bibfnamefont {M.~F.}\ \bibnamefont {Hagan}},\ and\ \bibinfo
+  {author} {\bibfnamefont {D.}~\bibnamefont {Kern}},\ }\href
+  {https://doi.org/10.1038/nsmb.2941} {\bibfield  {journal} {\bibinfo
+  {journal} {Nature Structural and Molecular Biology}\ }\textbf {\bibinfo
+  {volume} {22}},\ \bibinfo {pages} {124} (\bibinfo {year} {2015})}\BibitemShut
+  {NoStop}%
+\bibitem [{\citenamefont {Guo}\ \emph {et~al.}(2018)\citenamefont {Guo},
+  \citenamefont {Wang}, \citenamefont {Wang}, \citenamefont {Wang},\ and\
+  \citenamefont {Hu}}]{Guo2018a}%
+  \BibitemOpen
+  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {C.}~\bibnamefont
+  {Guo}}, \bibinfo {author} {\bibfnamefont {Z.}~\bibnamefont {Wang}}, \bibinfo
+  {author} {\bibfnamefont {D.}~\bibnamefont {Wang}}, \bibinfo {author}
+  {\bibfnamefont {H.~F.}\ \bibnamefont {Wang}},\ and\ \bibinfo {author}
+  {\bibfnamefont {P.}~\bibnamefont {Hu}},\ }\href
+  {https://doi.org/10.1021/acs.jpcc.8b06782} {\bibfield  {journal} {\bibinfo
+  {journal} {Journal of Physical Chemistry C}\ }\textbf {\bibinfo {volume}
+  {122}},\ \bibinfo {pages} {21478} (\bibinfo {year} {2018})}\BibitemShut
+  {NoStop}%
+\bibitem [{\citenamefont {Richardson}\ \emph {et~al.}(2016)\citenamefont
+  {Richardson}, \citenamefont {P{\'{e}}rez}, \citenamefont {Lobsiger},
+  \citenamefont {Reid}, \citenamefont {Temelso}, \citenamefont {Shields},
+  \citenamefont {Kisiel}, \citenamefont {Wales}, \citenamefont {Pate},\ and\
+  \citenamefont {Althorpe}}]{Richardson2016}%
+  \BibitemOpen
+  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {J.~O.}\ \bibnamefont
+  {Richardson}}, \bibinfo {author} {\bibfnamefont {C.}~\bibnamefont
+  {P{\'{e}}rez}}, \bibinfo {author} {\bibfnamefont {S.}~\bibnamefont
+  {Lobsiger}}, \bibinfo {author} {\bibfnamefont {A.~A.}\ \bibnamefont {Reid}},
+  \bibinfo {author} {\bibfnamefont {B.}~\bibnamefont {Temelso}}, \bibinfo
+  {author} {\bibfnamefont {G.~C.}\ \bibnamefont {Shields}}, \bibinfo {author}
+  {\bibfnamefont {Z.}~\bibnamefont {Kisiel}}, \bibinfo {author} {\bibfnamefont
+  {D.~J.}\ \bibnamefont {Wales}}, \bibinfo {author} {\bibfnamefont {B.~H.}\
+  \bibnamefont {Pate}},\ and\ \bibinfo {author} {\bibfnamefont {S.~C.}\
+  \bibnamefont {Althorpe}},\ }\href@noop {} {\bibfield  {journal} {\bibinfo
+  {journal} {Science}\ }\textbf {\bibinfo {volume} {351}},\ \bibinfo {pages}
+  {1310} (\bibinfo {year} {2016})}\BibitemShut {NoStop}%
+\bibitem [{\citenamefont {Vaillant}\ \emph {et~al.}(2019)\citenamefont
+  {Vaillant}, \citenamefont {Althorpe},\ and\ \citenamefont
+  {Wales}}]{Vaillant2019}%
+  \BibitemOpen
+  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {C.~L.}\ \bibnamefont
+  {Vaillant}}, \bibinfo {author} {\bibfnamefont {S.~C.}\ \bibnamefont
+  {Althorpe}},\ and\ \bibinfo {author} {\bibfnamefont {D.~J.}\ \bibnamefont
+  {Wales}},\ }\href {https://doi.org/10.1021/acs.jctc.8b00675} {\bibfield
+  {journal} {\bibinfo  {journal} {Journal of Chemical Theory and Computation}\
+  }\textbf {\bibinfo {volume} {15}},\ \bibinfo {pages} {33} (\bibinfo {year}
+  {2019})}\BibitemShut {NoStop}%
+\bibitem [{\citenamefont {Richard}\ and\ \citenamefont
+  {Speck}(2018)}]{Richard2018}%
+  \BibitemOpen
+  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {D.}~\bibnamefont
+  {Richard}}\ and\ \bibinfo {author} {\bibfnamefont {T.}~\bibnamefont
+  {Speck}},\ }\href {https://doi.org/10.1063/1.5016277} {\bibfield  {journal}
+  {\bibinfo  {journal} {The Journal of Chemical Physics}\ }\textbf {\bibinfo
+  {volume} {148}},\ \bibinfo {pages} {124110} (\bibinfo {year}
+  {2018})}\BibitemShut {NoStop}%
+\bibitem [{\citenamefont {Wales}\ \emph {et~al.}(1998)\citenamefont {Wales},
+  \citenamefont {Miller},\ and\ \citenamefont {Walsh}}]{Wales1998}%
+  \BibitemOpen
+  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {D.~J.}\ \bibnamefont
+  {Wales}}, \bibinfo {author} {\bibfnamefont {M.~A.}\ \bibnamefont {Miller}},\
+  and\ \bibinfo {author} {\bibfnamefont {T.~R.}\ \bibnamefont {Walsh}},\ }\href
+  {https://doi.org/10.1038/29487} {\bibfield  {journal} {\bibinfo  {journal}
+  {Nature}\ }\textbf {\bibinfo {volume} {394}},\ \bibinfo {pages} {758}
+  (\bibinfo {year} {1998})}\BibitemShut {NoStop}%
+\bibitem [{\citenamefont {Wales}(2012)}]{Wales2012}%
+  \BibitemOpen
+  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {D.~J.}\ \bibnamefont
+  {Wales}},\ }\href {https://doi.org/10.1098/rsta.2011.0208} {\bibfield
+  {journal} {\bibinfo  {journal} {Philosophical Transactions of the Royal
+  Society A: Mathematical, Physical and Engineering Sciences}\ }\textbf
+  {\bibinfo {volume} {370}},\ \bibinfo {pages} {2877} (\bibinfo {year}
+  {2012})}\BibitemShut {NoStop}%
+\bibitem [{\citenamefont {Panter}\ \emph
+  {et~al.}(2019{\natexlab{a}})\citenamefont {Panter}, \citenamefont {Chen},
+  \citenamefont {Zhang},\ and\ \citenamefont {Kusumaatmaja}}]{Panter2019}%
+  \BibitemOpen
+  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {J.~R.}\ \bibnamefont
+  {Panter}}, \bibinfo {author} {\bibfnamefont {J.}~\bibnamefont {Chen}},
+  \bibinfo {author} {\bibfnamefont {T.}~\bibnamefont {Zhang}},\ and\ \bibinfo
+  {author} {\bibfnamefont {H.}~\bibnamefont {Kusumaatmaja}},\ }\href
+  {https://doi.org/10.1038/s42005-019-0251-4} {\bibfield  {journal} {\bibinfo
+  {journal} {Communications Physics}\ }\textbf {\bibinfo {volume} {2}},\
+  \bibinfo {pages} {151} (\bibinfo {year} {2019}{\natexlab{a}})}\BibitemShut
+  {NoStop}%
+\bibitem [{\citenamefont {Hutchinson}\ and\ \citenamefont
+  {Thompson}(2018)}]{Hutchinson2018}%
+  \BibitemOpen
+  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {J.~W.}\ \bibnamefont
+  {Hutchinson}}\ and\ \bibinfo {author} {\bibfnamefont {J.~M.~T.}\ \bibnamefont
+  {Thompson}},\ }\href {https://doi.org/10.1016/j.ijsolstr.2018.01.030}
+  {\bibfield  {journal} {\bibinfo  {journal} {International Journal of Solids
+  and Structures}\ }\textbf {\bibinfo {volume} {148-149}},\ \bibinfo {pages}
+  {157} (\bibinfo {year} {2018})}\BibitemShut {NoStop}%
+\bibitem [{\citenamefont {Zhang}\ and\ \citenamefont {Ren}(2014)}]{Zhang2014}%
+  \BibitemOpen
+  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {Y.}~\bibnamefont
+  {Zhang}}\ and\ \bibinfo {author} {\bibfnamefont {W.}~\bibnamefont {Ren}},\
+  }\href {https://doi.org/10.1063/1.4904947} {\bibfield  {journal} {\bibinfo
+  {journal} {The Journal of Chemical Physics}\ }\textbf {\bibinfo {volume}
+  {141}},\ \bibinfo {pages} {244705} (\bibinfo {year} {2014})}\BibitemShut
+  {NoStop}%
+\bibitem [{\citenamefont {Panter}\ \emph
+  {et~al.}(2019{\natexlab{b}})\citenamefont {Panter}, \citenamefont {Gizaw},\
+  and\ \citenamefont {Kusumaatmaja}}]{Panter2019b}%
+  \BibitemOpen
+  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {J.~R.}\ \bibnamefont
+  {Panter}}, \bibinfo {author} {\bibfnamefont {Y.}~\bibnamefont {Gizaw}},\ and\
+  \bibinfo {author} {\bibfnamefont {H.}~\bibnamefont {Kusumaatmaja}},\ }\href
+  {https://doi.org/10.1126/sciadv.aav7328} {\bibfield  {journal} {\bibinfo
+  {journal} {Science Advances}\ }\textbf {\bibinfo {volume} {5}},\ \bibinfo
+  {pages} {eaav7328} (\bibinfo {year} {2019}{\natexlab{b}})}\BibitemShut
+  {NoStop}%
+\bibitem [{\citenamefont {Othayoth}\ \emph {et~al.}(2020)\citenamefont
+  {Othayoth}, \citenamefont {Thoms},\ and\ \citenamefont {Li}}]{Othayoth2020}%
+  \BibitemOpen
+  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {R.}~\bibnamefont
+  {Othayoth}}, \bibinfo {author} {\bibfnamefont {G.}~\bibnamefont {Thoms}},\
+  and\ \bibinfo {author} {\bibfnamefont {C.}~\bibnamefont {Li}},\ }\href
+  {https://doi.org/10.1073/pnas.1918297117} {\bibfield  {journal} {\bibinfo
+  {journal} {Proceedings of the National Academy of Sciences}\ }\textbf
+  {\bibinfo {volume} {117}},\ \bibinfo {pages} {14987} (\bibinfo {year}
+  {2020})}\BibitemShut {NoStop}%
+\bibitem [{\citenamefont {Filipov}\ \emph {et~al.}(2015)\citenamefont
+  {Filipov}, \citenamefont {Tachi}, \citenamefont {Paulino},\ and\
+  \citenamefont {Weitz}}]{Filipov2015}%
+  \BibitemOpen
+  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {E.~T.}\ \bibnamefont
+  {Filipov}}, \bibinfo {author} {\bibfnamefont {T.}~\bibnamefont {Tachi}},
+  \bibinfo {author} {\bibfnamefont {G.~H.}\ \bibnamefont {Paulino}},\ and\
+  \bibinfo {author} {\bibfnamefont {D.~A.}\ \bibnamefont {Weitz}},\ }\href
+  {https://doi.org/10.1073/pnas.1509465112} {\bibfield  {journal} {\bibinfo
+  {journal} {Proceedings of the National Academy of Sciences of the United
+  States of America}\ }\textbf {\bibinfo {volume} {112}},\ \bibinfo {pages}
+  {12321} (\bibinfo {year} {2015})}\BibitemShut {NoStop}%
+\bibitem [{\citenamefont {Zhai}\ \emph {et~al.}(2018)\citenamefont {Zhai},
+  \citenamefont {Wang},\ and\ \citenamefont {Jiang}}]{Zhai2018}%
+  \BibitemOpen
+  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {Z.}~\bibnamefont
+  {Zhai}}, \bibinfo {author} {\bibfnamefont {Y.}~\bibnamefont {Wang}},\ and\
+  \bibinfo {author} {\bibfnamefont {H.}~\bibnamefont {Jiang}},\ }\href
+  {https://doi.org/10.1073/pnas.1720171115} {\bibfield  {journal} {\bibinfo
+  {journal} {Proceedings of the National Academy of Sciences of the United
+  States of America}\ }\textbf {\bibinfo {volume} {115}},\ \bibinfo {pages}
+  {2032} (\bibinfo {year} {2018})}\BibitemShut {NoStop}%
+\bibitem [{\citenamefont {Bertoldi}\ \emph {et~al.}(2017)\citenamefont
+  {Bertoldi}, \citenamefont {Vitelli}, \citenamefont {Christensen},\ and\
+  \citenamefont {{Van Hecke}}}]{Bertoldi2017}%
+  \BibitemOpen
+  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {K.}~\bibnamefont
+  {Bertoldi}}, \bibinfo {author} {\bibfnamefont {V.}~\bibnamefont {Vitelli}},
+  \bibinfo {author} {\bibfnamefont {J.}~\bibnamefont {Christensen}},\ and\
+  \bibinfo {author} {\bibfnamefont {M.}~\bibnamefont {{Van Hecke}}},\ }\href
+  {https://doi.org/10.1038/natrevmats.2017.66} {\bibfield  {journal} {\bibinfo
+  {journal} {Nature Reviews Materials}\ }\textbf {\bibinfo {volume} {2}},\
+  \bibinfo {pages} {17066} (\bibinfo {year} {2017})}\BibitemShut {NoStop}%
+\bibitem [{\citenamefont {Truby}\ and\ \citenamefont
+  {Lewis}(2016)}]{Truby2016}%
+  \BibitemOpen
+  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {R.~L.}\ \bibnamefont
+  {Truby}}\ and\ \bibinfo {author} {\bibfnamefont {J.~A.}\ \bibnamefont
+  {Lewis}},\ }\href {https://doi.org/10.1038/nature21003} {\bibfield  {journal}
+  {\bibinfo  {journal} {Nature}\ }\textbf {\bibinfo {volume} {540}},\ \bibinfo
+  {pages} {371} (\bibinfo {year} {2016})}\BibitemShut {NoStop}%
+\bibitem [{\citenamefont {Chi}\ \emph {et~al.}(2022)\citenamefont {Chi},
+  \citenamefont {Li}, \citenamefont {Zhao}, \citenamefont {Hong}, \citenamefont
+  {Tang},\ and\ \citenamefont {Yin}}]{Chi2022}%
+  \BibitemOpen
+  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {Y.}~\bibnamefont
+  {Chi}}, \bibinfo {author} {\bibfnamefont {Y.}~\bibnamefont {Li}}, \bibinfo
+  {author} {\bibfnamefont {Y.}~\bibnamefont {Zhao}}, \bibinfo {author}
+  {\bibfnamefont {Y.}~\bibnamefont {Hong}}, \bibinfo {author} {\bibfnamefont
+  {Y.}~\bibnamefont {Tang}},\ and\ \bibinfo {author} {\bibfnamefont
+  {J.}~\bibnamefont {Yin}},\ }\bibfield  {journal} {\bibinfo  {journal}
+  {Advanced Materials}\ }\href {https://doi.org/10.1002/adma.202110384}
+  {10.1002/adma.202110384} (\bibinfo {year} {2022})\BibitemShut {NoStop}%
+\bibitem [{\citenamefont {Bonfanti}\ \emph {et~al.}(2020)\citenamefont
+  {Bonfanti}, \citenamefont {Guerra}, \citenamefont {Font-Clos}, \citenamefont
+  {Rayneau-Kirkhope},\ and\ \citenamefont {Zapperi}}]{Bonfanti2020}%
+  \BibitemOpen
+  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {S.}~\bibnamefont
+  {Bonfanti}}, \bibinfo {author} {\bibfnamefont {R.}~\bibnamefont {Guerra}},
+  \bibinfo {author} {\bibfnamefont {F.}~\bibnamefont {Font-Clos}}, \bibinfo
+  {author} {\bibfnamefont {D.}~\bibnamefont {Rayneau-Kirkhope}},\ and\ \bibinfo
+  {author} {\bibfnamefont {S.}~\bibnamefont {Zapperi}},\ }\href
+  {https://doi.org/10.1038/s41467-020-17947-2} {\bibfield  {journal} {\bibinfo
+  {journal} {Nature Communications}\ }\textbf {\bibinfo {volume} {11}},\
+  \bibinfo {pages} {4162} (\bibinfo {year} {2020})}\BibitemShut {NoStop}%
+\bibitem [{\citenamefont {Shan}\ \emph {et~al.}(2015)\citenamefont {Shan},
+  \citenamefont {Kang}, \citenamefont {Raney}, \citenamefont {Wang},
+  \citenamefont {Fang}, \citenamefont {Candido}, \citenamefont {Lewis},\ and\
+  \citenamefont {Bertoldi}}]{Shan2015}%
+  \BibitemOpen
+  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {S.}~\bibnamefont
+  {Shan}}, \bibinfo {author} {\bibfnamefont {S.~H.}\ \bibnamefont {Kang}},
+  \bibinfo {author} {\bibfnamefont {J.~R.}\ \bibnamefont {Raney}}, \bibinfo
+  {author} {\bibfnamefont {P.}~\bibnamefont {Wang}}, \bibinfo {author}
+  {\bibfnamefont {L.}~\bibnamefont {Fang}}, \bibinfo {author} {\bibfnamefont
+  {F.}~\bibnamefont {Candido}}, \bibinfo {author} {\bibfnamefont {J.~A.}\
+  \bibnamefont {Lewis}},\ and\ \bibinfo {author} {\bibfnamefont
+  {K.}~\bibnamefont {Bertoldi}},\ }\href
+  {https://doi.org/10.1002/adma.201501708} {\bibfield  {journal} {\bibinfo
+  {journal} {Advanced Materials}\ }\textbf {\bibinfo {volume} {27}},\ \bibinfo
+  {pages} {4296} (\bibinfo {year} {2015})}\BibitemShut {NoStop}%
+\bibitem [{\citenamefont {Giri}\ and\ \citenamefont {Mailen}(2021)}]{Giri2021}%
+  \BibitemOpen
+  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {T.~R.}\ \bibnamefont
+  {Giri}}\ and\ \bibinfo {author} {\bibfnamefont {R.}~\bibnamefont {Mailen}},\
+  }\href {https://doi.org/10.1016/j.ijmecsci.2021.106541} {\bibfield  {journal}
+  {\bibinfo  {journal} {International Journal of Mechanical Sciences}\ }\textbf
+  {\bibinfo {volume} {204}},\ \bibinfo {pages} {106541} (\bibinfo {year}
+  {2021})}\BibitemShut {NoStop}%
+\bibitem [{\citenamefont {Cerjan}\ and\ \citenamefont
+  {Miller}(1981)}]{Cerjan1981}%
+  \BibitemOpen
+  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {C.~J.}\ \bibnamefont
+  {Cerjan}}\ and\ \bibinfo {author} {\bibfnamefont {W.~H.}\ \bibnamefont
+  {Miller}},\ }\href {https://doi.org/10.1063/1.442352} {\bibfield  {journal}
+  {\bibinfo  {journal} {The Journal of Chemical Physics}\ }\textbf {\bibinfo
+  {volume} {75}},\ \bibinfo {pages} {2800} (\bibinfo {year}
+  {1981})}\BibitemShut {NoStop}%
+\bibitem [{\citenamefont {Heyden}\ \emph {et~al.}(2005)\citenamefont {Heyden},
+  \citenamefont {Bell},\ and\ \citenamefont {Keil}}]{Heyden2005}%
+  \BibitemOpen
+  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {A.}~\bibnamefont
+  {Heyden}}, \bibinfo {author} {\bibfnamefont {A.~T.}\ \bibnamefont {Bell}},\
+  and\ \bibinfo {author} {\bibfnamefont {F.~J.}\ \bibnamefont {Keil}},\ }\href
+  {https://doi.org/10.1063/1.2104507} {\bibfield  {journal} {\bibinfo
+  {journal} {Journal of Chemical Physics}\ }\textbf {\bibinfo {volume} {123}},\
+  \bibinfo {pages} {224101} (\bibinfo {year} {2005})}\BibitemShut {NoStop}%
+\bibitem [{\citenamefont {K{\"{a}}stner}\ and\ \citenamefont
+  {Sherwood}(2008)}]{Kastner2008}%
+  \BibitemOpen
+  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {J.}~\bibnamefont
+  {K{\"{a}}stner}}\ and\ \bibinfo {author} {\bibfnamefont {P.}~\bibnamefont
+  {Sherwood}},\ }\href {https://doi.org/10.1063/1.2815812} {\bibfield
+  {journal} {\bibinfo  {journal} {Journal of Chemical Physics}\ }\textbf
+  {\bibinfo {volume} {128}},\ \bibinfo {pages} {014106} (\bibinfo {year}
+  {2008})}\BibitemShut {NoStop}%
+\bibitem [{\citenamefont {E}\ \emph {et~al.}(2007)\citenamefont {E},
+  \citenamefont {Ren},\ and\ \citenamefont {Vanden-Eijnden}}]{E2007}%
+  \BibitemOpen
+  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {W.}~\bibnamefont {E}},
+  \bibinfo {author} {\bibfnamefont {W.}~\bibnamefont {Ren}},\ and\ \bibinfo
+  {author} {\bibfnamefont {E.}~\bibnamefont {Vanden-Eijnden}},\ }\href
+  {https://doi.org/10.1063/1.2720838} {\bibfield  {journal} {\bibinfo
+  {journal} {The Journal of Chemical Physics}\ }\textbf {\bibinfo {volume}
+  {126}},\ \bibinfo {pages} {164103} (\bibinfo {year} {2007})}\BibitemShut
+  {NoStop}%
+\bibitem [{\citenamefont {Ren}\ and\ \citenamefont
+  {Vanden-Eijnden}(2013)}]{Ren2013}%
+  \BibitemOpen
+  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {W.}~\bibnamefont
+  {Ren}}\ and\ \bibinfo {author} {\bibfnamefont {E.}~\bibnamefont
+  {Vanden-Eijnden}},\ }\href {https://doi.org/10.1063/1.4798344} {\bibfield
+  {journal} {\bibinfo  {journal} {Journal of Chemical Physics}\ }\textbf
+  {\bibinfo {volume} {138}},\ \bibinfo {pages} {134105} (\bibinfo {year}
+  {2013})}\BibitemShut {NoStop}%
+\bibitem [{\citenamefont {E}\ \emph {et~al.}(2002)\citenamefont {E},
+  \citenamefont {Ren},\ and\ \citenamefont {Vanden-Eijnden}}]{E2002}%
+  \BibitemOpen
+  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {W.}~\bibnamefont {E}},
+  \bibinfo {author} {\bibfnamefont {W.}~\bibnamefont {Ren}},\ and\ \bibinfo
+  {author} {\bibfnamefont {E.}~\bibnamefont {Vanden-Eijnden}},\ }\href
+  {https://doi.org/10.1103/PhysRevB.66.052301} {\bibfield  {journal} {\bibinfo
+  {journal} {Physical Review B}\ }\textbf {\bibinfo {volume} {66}},\ \bibinfo
+  {pages} {052301} (\bibinfo {year} {2002})}\BibitemShut {NoStop}%
+\bibitem [{\citenamefont {Trygubenko}\ and\ \citenamefont
+  {Wales}(2004)}]{Trygubenko2004}%
+  \BibitemOpen
+  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {S.~A.}\ \bibnamefont
+  {Trygubenko}}\ and\ \bibinfo {author} {\bibfnamefont {D.~J.}\ \bibnamefont
+  {Wales}},\ }\href {https://doi.org/10.1063/1.1636455} {\bibfield  {journal}
+  {\bibinfo  {journal} {Journal of Chemical Physics}\ }\textbf {\bibinfo
+  {volume} {120}},\ \bibinfo {pages} {2082} (\bibinfo {year}
+  {2004})}\BibitemShut {NoStop}%
+\bibitem [{\citenamefont {Trefethen}\ and\ \citenamefont
+  {Thiyagalingam}(2013)}]{Trefethen2013}%
+  \BibitemOpen
+  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {A.~E.}\ \bibnamefont
+  {Trefethen}}\ and\ \bibinfo {author} {\bibfnamefont {J.}~\bibnamefont
+  {Thiyagalingam}},\ }\href {https://doi.org/10.1016/j.jocs.2013.01.005}
+  {\bibfield  {journal} {\bibinfo  {journal} {Journal of Computational
+  Science}\ }\textbf {\bibinfo {volume} {4}},\ \bibinfo {pages} {444} (\bibinfo
+  {year} {2013})}\BibitemShut {NoStop}%
+\bibitem [{\citenamefont {Shalf}(2020)}]{Shalf2020}%
+  \BibitemOpen
+  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {J.}~\bibnamefont
+  {Shalf}},\ }\href {https://doi.org/10.1098/rsta.2019.0061} {\bibfield
+  {journal} {\bibinfo  {journal} {Philosophical Transactions Royal Society}\
+  }\textbf {\bibinfo {volume} {378}},\ \bibinfo {pages} {20190061} (\bibinfo
+  {year} {2020})}\BibitemShut {NoStop}%
+\bibitem [{\citenamefont {Alexander}\ \emph {et~al.}(2020)\citenamefont
+  {Alexander}, \citenamefont {Almgren}, \citenamefont {Bell}, \citenamefont
+  {Bhattacharjee}, \citenamefont {Chen}, \citenamefont {Colella}, \citenamefont
+  {Daniel}, \citenamefont {DeSlippe}, \citenamefont {Diachin}, \citenamefont
+  {Draeger}, \citenamefont {Dubey}, \citenamefont {Dunning}, \citenamefont
+  {Evans}, \citenamefont {Foster}, \citenamefont {Francois}, \citenamefont
+  {Germann}, \citenamefont {Gordon}, \citenamefont {Habib}, \citenamefont
+  {Halappanavar}, \citenamefont {Hamilton}, \citenamefont {Hart}, \citenamefont
+  {Huang}, \citenamefont {Hungerford}, \citenamefont {Kasen}, \citenamefont
+  {Kent}, \citenamefont {Kolev}, \citenamefont {Kothe}, \citenamefont
+  {Kronfeld}, \citenamefont {Luo}, \citenamefont {Mackenzie}, \citenamefont
+  {McCallen}, \citenamefont {Messer}, \citenamefont {Mniszewski}, \citenamefont
+  {Oehmen}, \citenamefont {Perazzo}, \citenamefont {Perez}, \citenamefont
+  {Richards}, \citenamefont {Rider}, \citenamefont {Rieben}, \citenamefont
+  {Roche}, \citenamefont {Siegel}, \citenamefont {Sprague}, \citenamefont
+  {Steefel}, \citenamefont {Stevens}, \citenamefont {Syamlal}, \citenamefont
+  {Taylor}, \citenamefont {Turner}, \citenamefont {Vay}, \citenamefont {Voter},
+  \citenamefont {Windus},\ and\ \citenamefont {Yelick}}]{Alexander2020}%
+  \BibitemOpen
+  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {F.}~\bibnamefont
+  {Alexander}}, \bibinfo {author} {\bibfnamefont {A.}~\bibnamefont {Almgren}},
+  \bibinfo {author} {\bibfnamefont {J.}~\bibnamefont {Bell}}, \bibinfo {author}
+  {\bibfnamefont {A.}~\bibnamefont {Bhattacharjee}}, \bibinfo {author}
+  {\bibfnamefont {J.}~\bibnamefont {Chen}}, \bibinfo {author} {\bibfnamefont
+  {P.}~\bibnamefont {Colella}}, \bibinfo {author} {\bibfnamefont
+  {D.}~\bibnamefont {Daniel}}, \bibinfo {author} {\bibfnamefont
+  {J.}~\bibnamefont {DeSlippe}}, \bibinfo {author} {\bibfnamefont
+  {L.}~\bibnamefont {Diachin}}, \bibinfo {author} {\bibfnamefont
+  {E.}~\bibnamefont {Draeger}}, \bibinfo {author} {\bibfnamefont
+  {A.}~\bibnamefont {Dubey}}, \bibinfo {author} {\bibfnamefont
+  {T.}~\bibnamefont {Dunning}}, \bibinfo {author} {\bibfnamefont
+  {T.}~\bibnamefont {Evans}}, \bibinfo {author} {\bibfnamefont
+  {I.}~\bibnamefont {Foster}}, \bibinfo {author} {\bibfnamefont
+  {M.}~\bibnamefont {Francois}}, \bibinfo {author} {\bibfnamefont
+  {T.}~\bibnamefont {Germann}}, \bibinfo {author} {\bibfnamefont
+  {M.}~\bibnamefont {Gordon}}, \bibinfo {author} {\bibfnamefont
+  {S.}~\bibnamefont {Habib}}, \bibinfo {author} {\bibfnamefont
+  {M.}~\bibnamefont {Halappanavar}}, \bibinfo {author} {\bibfnamefont
+  {S.}~\bibnamefont {Hamilton}}, \bibinfo {author} {\bibfnamefont
+  {W.}~\bibnamefont {Hart}}, \bibinfo {author} {\bibfnamefont {Z.}~\bibnamefont
+  {Huang}}, \bibinfo {author} {\bibfnamefont {A.}~\bibnamefont {Hungerford}},
+  \bibinfo {author} {\bibfnamefont {D.}~\bibnamefont {Kasen}}, \bibinfo
+  {author} {\bibfnamefont {P.~R.}\ \bibnamefont {Kent}}, \bibinfo {author}
+  {\bibfnamefont {T.}~\bibnamefont {Kolev}}, \bibinfo {author} {\bibfnamefont
+  {D.~B.}\ \bibnamefont {Kothe}}, \bibinfo {author} {\bibfnamefont
+  {A.}~\bibnamefont {Kronfeld}}, \bibinfo {author} {\bibfnamefont
+  {Y.}~\bibnamefont {Luo}}, \bibinfo {author} {\bibfnamefont {P.}~\bibnamefont
+  {Mackenzie}}, \bibinfo {author} {\bibfnamefont {D.}~\bibnamefont {McCallen}},
+  \bibinfo {author} {\bibfnamefont {B.}~\bibnamefont {Messer}}, \bibinfo
+  {author} {\bibfnamefont {S.}~\bibnamefont {Mniszewski}}, \bibinfo {author}
+  {\bibfnamefont {C.}~\bibnamefont {Oehmen}}, \bibinfo {author} {\bibfnamefont
+  {A.}~\bibnamefont {Perazzo}}, \bibinfo {author} {\bibfnamefont
+  {D.}~\bibnamefont {Perez}}, \bibinfo {author} {\bibfnamefont
+  {D.}~\bibnamefont {Richards}}, \bibinfo {author} {\bibfnamefont {W.~J.}\
+  \bibnamefont {Rider}}, \bibinfo {author} {\bibfnamefont {R.}~\bibnamefont
+  {Rieben}}, \bibinfo {author} {\bibfnamefont {K.}~\bibnamefont {Roche}},
+  \bibinfo {author} {\bibfnamefont {A.}~\bibnamefont {Siegel}}, \bibinfo
+  {author} {\bibfnamefont {M.}~\bibnamefont {Sprague}}, \bibinfo {author}
+  {\bibfnamefont {C.}~\bibnamefont {Steefel}}, \bibinfo {author} {\bibfnamefont
+  {R.}~\bibnamefont {Stevens}}, \bibinfo {author} {\bibfnamefont
+  {M.}~\bibnamefont {Syamlal}}, \bibinfo {author} {\bibfnamefont
+  {M.}~\bibnamefont {Taylor}}, \bibinfo {author} {\bibfnamefont
+  {J.}~\bibnamefont {Turner}}, \bibinfo {author} {\bibfnamefont {J.~L.}\
+  \bibnamefont {Vay}}, \bibinfo {author} {\bibfnamefont {A.~F.}\ \bibnamefont
+  {Voter}}, \bibinfo {author} {\bibfnamefont {T.~L.}\ \bibnamefont {Windus}},\
+  and\ \bibinfo {author} {\bibfnamefont {K.}~\bibnamefont {Yelick}},\ }\href
+  {https://doi.org/10.1098/rsta.2019.0056} {\bibfield  {journal} {\bibinfo
+  {journal} {Philosophical Transactions of the Royal Society A}\ }\textbf
+  {\bibinfo {volume} {378}},\ \bibinfo {pages} {20190056} (\bibinfo {year}
+  {2020})}\BibitemShut {NoStop}%
+\bibitem [{\citenamefont {McMullen}\ \emph {et~al.}(2018)\citenamefont
+  {McMullen}, \citenamefont {Holmes-Cerfon}, \citenamefont {Sciortino},
+  \citenamefont {Grosberg},\ and\ \citenamefont {Brujic}}]{McMullen2018}%
+  \BibitemOpen
+  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {A.}~\bibnamefont
+  {McMullen}}, \bibinfo {author} {\bibfnamefont {M.}~\bibnamefont
+  {Holmes-Cerfon}}, \bibinfo {author} {\bibfnamefont {F.}~\bibnamefont
+  {Sciortino}}, \bibinfo {author} {\bibfnamefont {A.~Y.}\ \bibnamefont
+  {Grosberg}},\ and\ \bibinfo {author} {\bibfnamefont {J.}~\bibnamefont
+  {Brujic}},\ }\href {https://doi.org/10.1103/PhysRevLett.121.138002}
+  {\bibfield  {journal} {\bibinfo  {journal} {Physical Review Letters}\
+  }\textbf {\bibinfo {volume} {121}},\ \bibinfo {pages} {138002} (\bibinfo
+  {year} {2018})}\BibitemShut {NoStop}%
+\bibitem [{\citenamefont {Nguemaha}\ and\ \citenamefont
+  {Zhou}(2018)}]{Nguemaha2018}%
+  \BibitemOpen
+  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {V.}~\bibnamefont
+  {Nguemaha}}\ and\ \bibinfo {author} {\bibfnamefont {H.~X.}\ \bibnamefont
+  {Zhou}},\ }\href {https://doi.org/10.1038/s41598-018-25132-1} {\bibfield
+  {journal} {\bibinfo  {journal} {Scientific Reports}\ }\textbf {\bibinfo
+  {volume} {8}},\ \bibinfo {pages} {1} (\bibinfo {year} {2018})}\BibitemShut
+  {NoStop}%
+\bibitem [{\citenamefont {Chen}\ \emph {et~al.}(2018)\citenamefont {Chen},
+  \citenamefont {Zhang},\ and\ \citenamefont {Torquato}}]{Chen2018b}%
+  \BibitemOpen
+  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {D.}~\bibnamefont
+  {Chen}}, \bibinfo {author} {\bibfnamefont {G.}~\bibnamefont {Zhang}},\ and\
+  \bibinfo {author} {\bibfnamefont {S.}~\bibnamefont {Torquato}},\ }\href
+  {https://doi.org/10.1021/acs.jpcb.8b05627} {\bibfield  {journal} {\bibinfo
+  {journal} {Journal of Physical Chemistry B}\ }\textbf {\bibinfo {volume}
+  {122}},\ \bibinfo {pages} {8462} (\bibinfo {year} {2018})}\BibitemShut
+  {NoStop}%
+\bibitem [{\citenamefont {Santra}\ \emph {et~al.}(2018)\citenamefont {Santra},
+  \citenamefont {Singh},\ and\ \citenamefont {Bagchi}}]{Santra2018}%
+  \BibitemOpen
+  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {M.}~\bibnamefont
+  {Santra}}, \bibinfo {author} {\bibfnamefont {R.~S.}\ \bibnamefont {Singh}},\
+  and\ \bibinfo {author} {\bibfnamefont {B.}~\bibnamefont {Bagchi}},\ }\href
+  {https://doi.org/10.1103/PhysRevE.98.032606} {\bibfield  {journal} {\bibinfo
+  {journal} {Physical Review E}\ }\textbf {\bibinfo {volume} {98}},\ \bibinfo
+  {pages} {1} (\bibinfo {year} {2018})}\BibitemShut {NoStop}%
+\bibitem [{\citenamefont {Wriggers}(2006)}]{Wriggers2006}%
+  \BibitemOpen
+  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {P.}~\bibnamefont
+  {Wriggers}},\ }\href {https://doi.org/10.1007/978-3-540-32609-0} {\emph
+  {\bibinfo {title} {{Computational Contact Mechanics}}}}\ (\bibinfo
+  {publisher} {Springer Berlin Heidelberg},\ \bibinfo {address} {Berlin,
+  Heidelberg},\ \bibinfo {year} {2006})\BibitemShut {NoStop}%
+\bibitem [{\citenamefont {Page}\ and\ \citenamefont {McIver}(1988)}]{Page1988}%
+  \BibitemOpen
+  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {M.}~\bibnamefont
+  {Page}}\ and\ \bibinfo {author} {\bibfnamefont {J.~W.}\ \bibnamefont
+  {McIver}},\ }\href {https://doi.org/10.1063/1.454172} {\bibfield  {journal}
+  {\bibinfo  {journal} {The Journal of Chemical Physics}\ }\textbf {\bibinfo
+  {volume} {88}},\ \bibinfo {pages} {922} (\bibinfo {year} {1988})}\BibitemShut
+  {NoStop}%
+\bibitem [{\citenamefont {Liu}\ and\ \citenamefont {Nocedal}(1989)}]{Liu1989}%
+  \BibitemOpen
+  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {D.~C.}\ \bibnamefont
+  {Liu}}\ and\ \bibinfo {author} {\bibfnamefont {J.}~\bibnamefont {Nocedal}},\
+  }\href@noop {} {\bibfield  {journal} {\bibinfo  {journal} {Mathematical
+  Programming}\ }\textbf {\bibinfo {volume} {45}},\ \bibinfo {pages} {503}
+  (\bibinfo {year} {1989})}\BibitemShut {NoStop}%
+\bibitem [{Note1()}]{Note1}%
+  \BibitemOpen
+  \bibinfo {note} {See Supplemental Material at [URL] for derivations of the
+  constraint coefficients, extra details for the example systems, results for
+  the speed test against DNEB, and a comparison of the discontinuous energy
+  landscape with the standard Lennard-Jones cluster}\BibitemShut {NoStop}%
+\bibitem [{\citenamefont {Kirkpatrick}\ \emph {et~al.}(1983)\citenamefont
+  {Kirkpatrick}, \citenamefont {Gelatt},\ and\ \citenamefont
+  {Vecchi}}]{Kirkpatrick1983}%
+  \BibitemOpen
+  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {S.}~\bibnamefont
+  {Kirkpatrick}}, \bibinfo {author} {\bibfnamefont {C.~D.}\ \bibnamefont
+  {Gelatt}},\ and\ \bibinfo {author} {\bibfnamefont {M.~P.}\ \bibnamefont
+  {Vecchi}},\ }\href {https://doi.org/10.1126/science.220.4598.671} {\bibfield
+  {journal} {\bibinfo  {journal} {Science}\ }\textbf {\bibinfo {volume}
+  {220}},\ \bibinfo {pages} {671} (\bibinfo {year} {1983})}\BibitemShut
+  {NoStop}%
+\end{thebibliography}%
+% end bib
+
 \end{document}

### 2022-03-15 export_bib.sh

@@ -1,0 +1,19 @@
+#!/bin/bash
+
+AUXFILE="${1%.tex}.aux"
+if [ ! -f "$1" ]; then
+  echo "File not found"
+  exit 1
+elif [ ! -f "$AUXFILE" ]; then
+  echo "AUX file does not exist. Run bibtex on file."
+  exit 1
+fi
+
+bibexport -ns $AUXFILE
+# Remove empty lines, abstract, url, etc
+sed -i '/^\s*$/d' bibexport.bib
+remove_fields=('abstract' 'url' 'issn' 'isbn' 'annote' 'month')
+for field in "${remove_fields[@]}"; do
+  sed -i "/^\s*$field =.*},$/d" bibexport.bib
+  sed -i "/^\s*$field =\s*{/,/},$/d" bibexport.bib
+done

### 2022-03-15 insert_bib.sh

@@ -1,0 +1,22 @@
+#!/bin/bash
+
+start_tag='% start bib'
+end_tag='% end bib'
+
+BBLFILE="${1%.tex}.bbl"
+if [ ! -f "$1" ]; then
+  echo "File not found"
+  exit 1
+elif [ ! -f "$BBLFILE" ]; then
+  echo "BBL file does not exist. Run bibtex on file."
+  exit 1
+fi
+
+# Remove commented lines
+sed -i "/^%/d" $BBLFILE
+
+# Delete between two tags
+sed -i "/${start_tag}/,/${end_tag}/{//!d}" $1
+
+# Paste bibliography between two tags
+sed -i "/${start_tag}/r $BBLFILE" $1

### 2022-03-15 manuscript.tex
Smaller changes

@@
 
+\usepackage{color,soul}
+
 \begin{document}
@@
 \begin{abstract}
-  Locating transition states is crucial for investigating transition mechanisms in wide-ranging, from atomistic tomacroscale systems.
+  Locating transition states is crucial for investigating transition mechanisms in wide-ranging phenomena, from atomistic to macroscale systems.
   Existing methods, however, can struggle in problems with a large number of degrees of freedom, on-the-fly adaptive remeshing and coarse-graining, and energy landscapes that are locally flat or discontinuous.
@@
 However, a large range of landscapes prove challenging or impossible to explore via these methods.
-One key problem arises from the push towards larger and more complex systems \cite{Trefethen2013,Shalf2020,Alexander2020}, resulting in the need to develop algorithms that are more memory and computationally efficient, and can incorporate optimisation strategies such as on-the-fly adaptive remeshing and coarse-graining.
+One key problem arises from the push towards larger and more complex systems \cite{Trefethen2013,Shalf2020,Alexander2020}, resulting in the need to develop algorithms that are more memory and computationally efficient, and can incorporate advanced optimisation strategies such as on-the-fly adaptive remeshing and coarse-graining.
 Current double-ended methods require a chain of tens of states to gain an accurate approximation, and have issues with remeshing resulting in a different number of degrees of freedom for each state.
@@
 Another major challenge in studying complex energy landscapes relates to the presence of locally flat or discontinous regions.
-Both of which can be relevent when considering patchy \cite{McMullen2018,Nguemaha2018,Chen2018b} and hard-body \cite{Richard2018,Santra2018} interactions in atomistic systems, or collision constraints for macroscopic objects \cite{Wriggers2006}.
+\hl{Such as} when considering patchy \cite{McMullen2018,Nguemaha2018,Chen2018b} and hard-body \cite{Richard2018,Santra2018} interactions in atomistic systems, or collision constraints for macroscopic objects \cite{Wriggers2006}.
 Flat zero-modes in the landscape pose issues for single-ended search methods that rely only upon local information.
@@
   \caption{\label{fig:toy2d}
-    (a) The trajectories of the two states under the BITSS method for a simple 2D potential with two minima (blue dots).
-        The transition state is shown by an red dot, and the minimum energy pathway by the dashed line.
+    (a) The trajectories of the two states under the BITSS method (orange line) for a simple 2D potential with two minima (blue dots).
+        The transition state is shown by a red dot, and the minimum energy pathway by the dashed line.
     (b) A snapshot of the BITSS minimisation showing the driving forces on each state due to the energy constraint, $\bm{F}_E$, and distance constraint, $\bm{F}_D$, with $E_1 < E_2$ and $\mathrm{d}(\bm{x}_1,\bm{x}_2) < d_i$.
@@
 This is done by minimising the energy of the pair while constraining their separation.
-The separation $d_i$ is incrementally reduced, such that at iteration $i$,
+The separation constraint $d_i$ is incrementally reduced, such that at iteration $i$,
 \begin{equation}\label{eq:diteration}
@@
 The two constraints are implemented using energy penalty terms, which, if the constraints are not met, result in driving forces on the two states, such as in \cref{fig:toy2d}b.
-The total energy of the pair of states is therefore given by,
+The total energy of the pair of states is therefore given by
 \begin{multline}\label{eq:bitss}
@@
 \end{gather}
-where $\alpha$ and $\beta$ are parameters with recommended values of $\alpha = 10$ and $\beta = 0.1$ (see supplementary information \footnote{See Supplemental Material at [URL] for derivations of the constraint coefficients, extra details for the example systems, results for the speed test against DNEB, and a comparison of the discontinuous energy landscape with the standard Lennard-Jones cluster}).
+where $\alpha$ and $\beta$ are parameters with recommended values of $\alpha = 10$ and $\beta = 0.1$ (see supplementary information \footnote{\hl{See Supplemental Material at [URL] for derivations of the constraint coefficients, extra details for the example systems, results for the speed test against DNEB, and a comparison of the discontinuous energy landscape with the standard Lennard-Jones cluster}}).
 Here, $\Delta E$ is an estimation for the current energy barrier evaluated by linearly interpolating between the two states.
@@
 This process is completed once a convergence criterion is reached that can be based upon either the separation between the states, or the size of gradient at the midpoint between the two states.
-Once BITSS has identified the transition state it is possible to find the full minimum energy pathway.
+Once BITSS has identified the transition state, it is possible to find the full minimum energy pathway.
 This is done by tracing the trajectory of downhill minimisations from the two final states either side of the transition state.
@@
 
-Firstly, we show in \cref{fig:adaptivemesh}a that BITSS is able to handle the discretisation changing as the method runs.
+Firstly, we show in \cref{fig:adaptivemesh}a that BITSS is able to handle the discretisation adapting as the method runs \hl{(changing number of degrees of freedom)}.
 For this we use the cylindrical buckling example with the resolution increasing from 40 to 100 triangles around the cylinder.
 These changes are performed after the minimisation step in each iteration of the BITSS method.
-This demonstrates that BITSS is able to converge to the transition state so long as the remeshing does not significantly change the landscape.
+This demonstrates that BITSS is able to converge to the transition state so long as the remeshing does not change the energy landscape of interest.
 
@@
   \BibitemOpen
-  \bibinfo {note} {See Supplemental Material at [URL] for derivations of the
-  constraint coefficients, extra details for the example systems, results for
-  the speed test against DNEB, and a comparison of the discontinuous energy
-  landscape with the standard Lennard-Jones cluster}\BibitemShut {NoStop}%
+  \bibinfo {note} {\protect \texthl {See Supplemental Material at [URL] for
+  derivations of the constraint coefficients, extra details for the example
+  systems, results for the speed test against DNEB, and a comparison of the
+  discontinuous energy landscape with the standard Lennard-Jones
+  cluster}}\BibitemShut {NoStop}%
 \bibitem [{\citenamefont {Kirkpatrick}\ \emph {et~al.}(1983)\citenamefont

### 2022-03-15 si/supplementary_information.tex
Smaller changes

@@
 To obtain the expression for the energy coefficient, $\kappa_e$, we first assume that the separation is fixed, so the distance term can be ignored.
-The coefficient $\kappa_e$ must be high enough to prevent one state from being pulled over the ridge, for which the greatest risk occurs when the gradient on one state is much greater than the other, $\abs{\grad E_2} \gg \abs{\grad E_1}$.
+The coefficient $\kappa_e$ must be high enough to prevent one state from being pulled over the ridge, for which the greatest risk occurs when the gradient on one state is much greater than the other, e.g.
+$\abs{\grad E_2} \gg \abs{\grad E_1}$.
 In this case the total gradient is approximated by
@@
 This involves the number of triangles around the circumference of the cylinder increasing along the sequence, $40 \rightarrow 60 \rightarrow 80 \rightarrow 100$.
-The positions of the nodes on the new grid, $\{\bm{n}_i\}$, are determined by linear interpolating from the previous grid $\{\bm{p}_i\}$, using the positions of the unbuckled meshes, $\{\bm{n'}_i\}$ and $\{\bm{p'}_i\}$.
+The positions of the nodes on the new grid, $\{\bm{n}_i\}$, are determined by linear interpolation from the previous grid $\{\bm{p}_i\}$, using the positions of the unbuckled meshes, $\{\bm{n'}_i\}$ and $\{\bm{p'}_i\}$.
 For each node of the new grid, $\bm{n'}_i$, the triangle that contains it is first identified, which we will denote $\{\bm{p'}_1,\bm{p'}_2,\bm{p'}_3\}$, and the barycentric coordinates of the point are computed, $\{\lambda_1,\lambda_2,\lambda_3\}$.
@@
 
-In the example with different resolutions for the two states, the distance is obtained by first mapping the phase field from the higher resolution grid, $\{\phi_{k,l} | k,l \in \{0,1,\cdots,399\}\}$, to the low resolution grid, $\{\phi'_{i,j} | i,j \in \{0,1,\cdots,199\}$.
+In the example with different resolutions for the two states, the distance is obtained by first mapping the phase field from the higher resolution grid, $\{\phi_{k,l} | k,l \in \{0,1,\cdots,399\}\}$, to the low resolution grid, $\{\phi'_{i,j} | i,j \in \{0,1,\cdots,199\}\}$.
 Because a square grid is used with a resolution ratio of two, the mapping involves averaging each 2x2 block to a single point:
@@
 
+\newpage
 \section{Additional results: DNEB speed comparison}
@@
 
-\newpage
 \section{Additional results: Seven-particle cluster comparison}

### 2022-03-15 fig/make_flatdiscontinuous/plot.py

@@ -263,6 +263,7 @@ def plot_discontinuous(fig, hsize):
     
     dg = make_dgraph(nodes, ts)
     dg.plot(axes=ax, linewidth=1)
+    ax.tick_params(which='both', direction='in')
     # Plot clusters on dgraph
     ybot, ytop = ax.get_ylim()
     dy = (ytop - ybot) / 4

### 2022-03-15 manuscript.tex
Added discussion of multiple TS path. Renamed energy barrier estimate

@@
 
-\usepackage{color,soul}
-
 \begin{document}
-\title{Locating saddle points in complex and memory intensive landscapes}
 \title{Binary Image Transition State Search Method}
@@
 Another major challenge in studying complex energy landscapes relates to the presence of locally flat or discontinous regions.
-\hl{Such as} when considering patchy \cite{McMullen2018,Nguemaha2018,Chen2018b} and hard-body \cite{Richard2018,Santra2018} interactions in atomistic systems, or collision constraints for macroscopic objects \cite{Wriggers2006}.
+Such as when considering patchy \cite{McMullen2018,Nguemaha2018,Chen2018b} and hard-body \cite{Richard2018,Santra2018} interactions in atomistic systems, or collision constraints for macroscopic objects \cite{Wriggers2006}.
 Flat zero-modes in the landscape pose issues for single-ended search methods that rely only upon local information.
@@
 The BITSS method then leads these states to meet at the lowest point on the ridge between the basins of attraction - the transition state.
-This is done by minimising the energy of the pair while constraining their separation.
+This is done by minimising the energy of the pair while constraining their separation and energy difference.
 The separation constraint $d_i$ is incrementally reduced, such that at iteration $i$,
@@
 A factor of $f = 0.5$ is succesful for most applications, but this can be made smaller to ensure that the states do not slide off the ridge.
-A secondary constraint that sets the energies of the two states equal is also used to ensure that neither state is pulled over the ridge.
+The secondary constraint sets the energies of the two states equal to ensure that neither state is pulled over the ridge.
 
@@
 \begin{gather}
-  \kappa_e = \frac {\alpha} {2 \Delta E},
+  \kappa_e = \frac {\alpha} {2 E_B},
   \label{eq:ke}
@@
     \frac {\sqrt{|\bm{\nabla} E_1|^2 + |\bm{\nabla} E_2|^2}} {2\sqrt{2} \beta d_i} \; , \;
-    \frac{\Delta E}{\beta d_i^2} \right),
+    \frac{E_B}{\beta d_i^2} \right),
   \label{eq:kd}
 \end{gather}
-where $\alpha$ and $\beta$ are parameters with recommended values of $\alpha = 10$ and $\beta = 0.1$ (see supplementary information \footnote{\hl{See Supplemental Material at [URL] for derivations of the constraint coefficients, extra details for the example systems, results for the speed test against DNEB, and a comparison of the discontinuous energy landscape with the standard Lennard-Jones cluster}}).
-Here, $\Delta E$ is an estimation for the current energy barrier evaluated by linearly interpolating between the two states.
-For systems where the interpolation deviates significantly from the pathway the estimate can be too large.
-In this case, a maximum estimated value can be provided, which then decreases proportionally with $d_i$.
+where $\bm{\nabla} E_1$ and $\bm{\nabla} E_2$ are the gradients of the energies two states, and $\alpha$ and $\beta$ are parameters with recommended values of $\alpha = 10$ and $\beta = 0.1$ (see supplementary information \footnote{See Supplemental Material at [URL] for derivations of the constraint coefficients, extra details for the example systems, results for the speed test against DNEB, and a comparison of the discontinuous energy landscape with the standard Lennard-Jones cluster}).
+Here, $E_B$ is an estimation for the current energy barrier; evaluated using the difference between the highest energy along a linear interpolation between the two states and the average energy of the two states.
 
@@
 This process is completed once a convergence criterion is reached that can be based upon either the separation between the states, or the size of gradient at the midpoint between the two states.
+
 Once BITSS has identified the transition state, it is possible to find the full minimum energy pathway.
 This is done by tracing the trajectory of downhill minimisations from the two final states either side of the transition state.
+In the case where there is a chain of transition states between the two starting minima, BITSS will identify the transition state with the highest energy.
+If, instead, all of transition states or the full pathway are desired, BITSS can be continually repeated from one of the minima downhill from the located transition state and one of the initial minima until the desired minima are connected.
+However, chain-of-states methods are likely more efficient for this as they compute the entire pathway at once.
 
@@
 \begin{equation} \label{eq:phasefield}
-  E[\phi] = E_B[\phi] + E_I[\phi] + E_S[\phi] + E_V[\phi].
+  E[\phi] = E^B[\phi] + E^I[\phi] + E^S[\phi] + E^V[\phi].
 \end{equation}
-The first term, $E_B$, uses a double well potential to set values of $\phi=\pm1$ in the bulk.
+The first term, $E^B$, uses a double well potential to set values of $\phi=\pm1$ in the bulk.
 The second term then provides the interfacial energy between the liquid and gas by imposing an energy penalty to gradients in $\phi$.
-$E_S$ is the solid-liquid interaction energy, which sets the contact angles of the hydrophilic and hydrophobic regions to 60\si{\degree} and 110\si{\degree}, respectively.
-Finally, $E_V$ constrains the volume of the liquid drop by penalising any variation from the target volume.
+$E^S$ is the solid-liquid interaction energy, which sets the contact angles of the hydrophilic and hydrophobic regions to 60\si{\degree} and 110\si{\degree}, respectively.
+Finally, $E^V$ constrains the volume of the liquid drop by penalising any variation from the target volume.
 For further details and the gradients of the potentials see the supplementary information \cite{Note1}.
@@
 %\section{Adaptive mesh}
-Adaptive remeshing and coarse-graining are widely used techniques that we can utilise to further increase the efficiency of BITSS.
-These techniques cause issues for existing double-ended methods because the coupled states may end up with different degrees of freedom.
-However, in BITSS the only direct coupling is in the distance measure, $\mathrm{d}(\bm{x}_1,\bm{x}_2)$, which is relatively easy to adapt.
-Here we demonstrate the use of adaptive remeshing by considering two separate issues.
-
-Firstly, we show in \cref{fig:adaptivemesh}a that BITSS is able to handle the discretisation adapting as the method runs \hl{(changing number of degrees of freedom)}.
-For this we use the cylindrical buckling example with the resolution increasing from 40 to 100 triangles around the cylinder.
-These changes are performed after the minimisation step in each iteration of the BITSS method.
-This demonstrates that BITSS is able to converge to the transition state so long as the remeshing does not change the energy landscape of interest.
-
-In the second test, \cref{fig:adaptivemesh}b, we demonstrate the use of different meshes for the two states in the striped wetting example.
-In this case, the distance measure is adapted by interpolating one state onto the other mesh and computing the Euclidean distance.
-However, for some applications a simpler measure may be sufficient, such as the difference between average values of the system.
-Using this approach, BITSS is able to closely approach the transition state.
-The convergence precision is now limited by the transition state energy differing slightly on each grid, but this effect is reduced when using an adaptive method or a higher resolution.
-
 \begin{figure}[tb]
@@
 
+Adaptive remeshing and coarse-graining are widely used techniques that we can utilise to further increase the efficiency of BITSS.
+These techniques cause issues for existing double-ended methods because the coupled states may end up with different degrees of freedom.
+However, in BITSS the only direct coupling is in the distance measure, $\mathrm{d}(\bm{x}_1,\bm{x}_2)$, which is relatively easy to adapt.
+Here we demonstrate the use of adaptive remeshing by considering two separate issues.
+
+Firstly, we show in \cref{fig:adaptivemesh}a that BITSS is able to handle the discretisation adapting as the method runs (changing number of degrees of freedom).
+For this we use the cylindrical buckling example with the resolution increasing from 40 to 100 triangles around the cylinder.
+These changes are performed after the minimisation step in each iteration of the BITSS method.
+This demonstrates that BITSS is able to converge to the transition state so long as the remeshing does not change the energy landscape of interest.
+
+In the second test, \cref{fig:adaptivemesh}b, we demonstrate the use of different meshes for the two states in the striped wetting example.
+In this case, the distance measure is adapted by interpolating one state onto the other mesh and computing the Euclidean distance.
+However, for some applications a simpler measure may be sufficient, such as the difference between average values of the system.
+Using this approach, BITSS is able to closely approach the transition state.
+The convergence precision is now limited by the transition state energy differing slightly on each grid, but this effect is reduced when using an adaptive method or a higher resolution.
+
 %\section{Zero-curvature modes}
-The final challenges we will address are those related to complex landscapes.
-The first is the presence of flat regions in the landscape.
-\Cref{fig:flatdiscontinuous}a shows BITSS applied to a 2D landscape with two such regions (i \& ii) that are flat in the $x$-direction.
-We see BITSS is able to successfully converge past these flat regions, even with one very close to the transition state (ii).
-In these regions there are no driving forces due to the potential and the energy constraint, which use purely local information about the gradient.
-However, the distance constraint continues to pull the states together, preventing them from getting stuck.
-When only a single state has a zero-gradient mode then the other is likely to slide down the potential slightly (iii), but the two states still remain either side of the dividing ridge and so the result is unaffected.
-
 \begin{figure}[tb]
@@
 
+The final challenges we will address are those related to complex landscapes.
+The first is the presence of flat regions in the landscape.
+\Cref{fig:flatdiscontinuous}a shows BITSS applied to a 2D landscape with two such regions (i \& ii) that are flat in the $x$-direction.
+We see BITSS is able to successfully converge past these flat regions, even with one very close to the transition state (ii).
+In these regions there are no driving forces due to the potential and the energy constraint, which use purely local information about the gradient.
+However, the distance constraint continues to pull the states together, preventing them from getting stuck.
+When only a single state has a zero-gradient mode then the other is likely to slide down the potential slightly (iii), but the two states still remain either side of the dividing ridge and so the result is unaffected.
+
 %\section{Gradient-free problems}
@@
 This has a chance of randomly jumping one state over the dividing barrier, but we can reduce this probability by limiting the initial temparature and maximum random displacement.
-We typically employ $T_0 = \Delta E / 10$, and $d_\text{max} = d(\bm{x}_1, \bm{x}_2) / 100$.
+We typically employ $T_0 = E_B / 10$, and $d_\text{max} = d(\bm{x}_1, \bm{x}_2) / 100$.
 This has been tested using a Lennard-Jones 7-particle cluster with hard cores, resulting in a discontinuous landscape.
@@
   \BibitemOpen
-  \bibinfo {note} {\protect \texthl {See Supplemental Material at [URL] for
-  derivations of the constraint coefficients, extra details for the example
-  systems, results for the speed test against DNEB, and a comparison of the
-  discontinuous energy landscape with the standard Lennard-Jones
-  cluster}}\BibitemShut {NoStop}%
+  \bibinfo {note} {See Supplemental Material at [URL] for derivations of the
+  constraint coefficients, extra details for the example systems, results for
+  the speed test against DNEB, and a comparison of the discontinuous energy
+  landscape with the standard Lennard-Jones cluster}\BibitemShut {NoStop}%
 \bibitem [{\citenamefont {Kirkpatrick}\ \emph {et~al.}(1983)\citenamefont

### 2022-03-15 si/supplementary_information.tex
Added discussion of multiple TS path. Renamed energy barrier estimate

@@
 Therefore, when not at a transition state or a minimum in the landscape ($\abs{\grad E_2} \neq 0$) convergence will occur when the term in the square brackets is zero, resulting in $E_1 - E_2 = 1 / 2 \kappa_e$.
-This energy difference should be less than current energy barrier, so we can substitute it with $\upDelta E / \alpha$, where $\upDelta E$ is the energy barrier estimate described in the main paper and $\alpha$ is a constant greater than one.
+This energy difference should be less than current energy barrier, so we can substitute it with $E_B / \alpha$, where $E_B$ is the energy barrier estimate described in the main paper and $\alpha$ is a constant greater than one.
 This leaves us with the expression,
 \begin{equation}
-  \kappa_e = \frac {\alpha} {2 \upDelta E}.
+  \kappa_e = \frac {\alpha} {2 E_B}.
 \end{equation}
@@
 (Note: The gradient of the distance with respect to a single state has a magnitude of 1, thus the magnitude of the gradient for the pair of states is $\abs{\grad d} = \sqrt{1^2+1^2} = \sqrt{2}$.)
-To ensure that the coefficient is not too small if the gradient is close to zero, such as when the states are initialised at the minima, a lower bound is set by replacing $\abs{\grad E_1}$ and $\abs{\grad E_2}$ with $2 \upDelta E / d_i$.
+To ensure that the coefficient is not too small if the gradient is close to zero, such as when the states are initialised at the minima, a lower bound is set by replacing $\abs{\grad E_1}$ and $\abs{\grad E_2}$ with $2 E_B / d_i$.
 This gives the expression,
@@
   \frac {\sqrt{\abs{\grad E_1}^2 + \abs{\grad E_2}^2}} {2 \sqrt{2} \beta d_i}, \quad
-  \frac{\upDelta E}{\beta d_i^2} \right).
+  \frac{E_B}{\beta d_i^2} \right).
 \end{equation}
@@
 \begin{align}
-  E_B[\phi] &= \sum_i \frac{1}{\epsilon} \left( \frac{{\phi_i}^4}{4} - \frac{{\phi_i}^2}{2} + \frac{1}{4} \right) \upDelta V,\\
-  E_I[\phi] &= \sum_i \frac{\epsilon}{2} \abs{\grad \phi_i}^2 \upDelta V,\\
-  E_S[\phi] &= \sum_j \sqrt{2}\cos\theta_j \left( \frac{{\phi_j}^3}{6} - \frac{\phi_j}{2} - \frac{1}{3} \right) \upDelta S,\\
-  E_V[\phi] &= k_V \left[ \sum_i \frac{\phi_i + 1}{2} \upDelta V - V_0 \right]^2,
+  E^B[\phi] &= \sum_i \frac{1}{\epsilon} \left( \frac{{\phi_i}^4}{4} - \frac{{\phi_i}^2}{2} + \frac{1}{4} \right) \upDelta V,\\
+  E^I[\phi] &= \sum_i \frac{\epsilon}{2} \abs{\grad \phi_i}^2 \upDelta V,\\
+  E^S[\phi] &= \sum_j \sqrt{2}\cos\theta_j \left( \frac{{\phi_j}^3}{6} - \frac{\phi_j}{2} - \frac{1}{3} \right) \upDelta S,\\
+  E^V[\phi] &= k_V \left[ \sum_i \frac{\phi_i + 1}{2} \upDelta V - V_0 \right]^2,
 \end{align}
@@
 \begin{align}
-  \frac{\partial E_B}{\partial \phi_i} &= \frac{1}{\epsilon} \left( {\phi_i}^3 - \phi_i \right) \upDelta V,\\
-  \frac{\partial E_I}{\partial \phi_i} &= \frac{\epsilon}{2} \left[
+  \frac{\partial E^B}{\partial \phi_i} &= \frac{1}{\epsilon} \left( {\phi_i}^3 - \phi_i \right) \upDelta V,\\
+  \frac{\partial E^I}{\partial \phi_i} &= \frac{\epsilon}{2} \left[
     \frac{\partial \abs{\grad \phi_i}^2}{\partial \phi_i} +
     \sum_k\frac{\partial \abs{\grad \phi_k}^2}{\partial \phi_i} \right] \upDelta V,\\
-  \frac{\partial E_S}{\partial \phi_j} &= \sqrt{2}\cos\theta_j \left( \frac{{\phi_j}^2}{2} - \frac{1}{2} \right) \upDelta S,\\
-  \frac{\partial E_V}{\partial \phi_i} &= k_V \left[ \sum_{i'} \frac{\phi_{i'} + 1}{2} \upDelta V - V_0 \right] \upDelta V,
+  \frac{\partial E^S}{\partial \phi_j} &= \sqrt{2}\cos\theta_j \left( \frac{{\phi_j}^2}{2} - \frac{1}{2} \right) \upDelta S,\\
+  \frac{\partial E^V}{\partial \phi_i} &= k_V \left[ \sum_{i'} \frac{\phi_{i'} + 1}{2} \upDelta V - V_0 \right] \upDelta V,
 \end{align}

### 2022-03-15 insert_bib.sh
Updated insert_bib script

@@ -1,22 +1,35 @@
 #!/bin/bash
 
-start_tag='% start bib'
-end_tag='% end bib'
+start_tag='%% start bib'
+mid_tag='%% mid bib'
+end_tag='%% end bib'
 
 BBLFILE="${1%.tex}.bbl"
+AUXFILE="${1%.tex}.aux"
 if [ ! -f "$1" ]; then
-  echo "File not found"
-  exit 1
-elif [ ! -f "$BBLFILE" ]; then
-  echo "BBL file does not exist. Run bibtex on file."
+  echo "Error: File not found."
   exit 1
 fi
 
-# Remove commented lines
+# Use bibtex to generate aux file
+sed -i "/$start_tag/,/$mid_tag/ {//b; /$start_tag/b; s/^%\s*//}" $1 # Uncomment
+sed -i "/$mid_tag/,/$end_tag/ {//b; /$mid_tag/b; /^%/b; s/^/% /}" $1 # Comment
+latex -interaction=batchmode "$1" > /dev/null 2>&1
+sed -i "/$start_tag/,/$mid_tag/ {//b; /$start_tag/b; s/^/% /}" $1 # Comment
+sed -i "/$mid_tag/,/$end_tag/ {//b; /$mid_tag/b; s/^%\s*//}" $1 # Uncomment
+if [ ! -f "$AUXFILE" ]; then
+  echo "Error: Failure generating aux file."
+  exit 1
+fi
+
+# Generate bbl file
+bibtex -terse "$AUXFILE"
+if [ ! -f "$BBLFILE" ]; then
+  echo "Error: Failure generating bbl file."
+  exit 1
+fi
 sed -i "/^%/d" $BBLFILE
 
-# Delete between two tags
-sed -i "/${start_tag}/,/${end_tag}/{//!d}" $1
-
-# Paste bibliography between two tags
-sed -i "/${start_tag}/r $BBLFILE" $1
+# Paste bibliography into tex file
+sed -i "/${mid_tag}/,/${end_tag}/{//!d}" $1
+sed -i "/${mid_tag}/r $BBLFILE" $1

### 2022-03-16 manuscript.tex
Updated insert_bib script
Small edits

@@
 One key problem arises from the push towards larger and more complex systems \cite{Trefethen2013,Shalf2020,Alexander2020}, resulting in the need to develop algorithms that are more memory and computationally efficient, and can incorporate advanced optimisation strategies such as on-the-fly adaptive remeshing and coarse-graining.
-Current double-ended methods require a chain of tens of states to gain an accurate approximation, and have issues with remeshing resulting in a different number of degrees of freedom for each state.
+Current double-ended methods require a chain of tens of states to gain an accurate approximation, and have issues with remeshing due to the different number of degrees of freedom for each state.
 Single-ended methods are not well suited for identifying specific pathways and can spend a large amount of time searching for undesired transition states.
@@
 These can be set to the minima, but this is not a necessary requirement.
-The BITSS method then leads these states to meet at the lowest point on the ridge between the basins of attraction - the transition state.
+The BITSS method then leads these states to meet at the lowest point on the ridge between the basins of attraction - the transition state, as shown in \cref{fig:toy2d}a.
 This is done by minimising the energy of the pair while constraining their separation and energy difference.
@@
 To ensure that the transition state is located successfully, the constraint strengths $\kappa_d$ and $\kappa_e$ are updated as the algorithm proceeds using information from the system.
-They are initially calculated at the start of each minimisation, and regularly recalculated throughout (once per 100 iterations are used in this work).
+They are initially calculated at the start of each minimisation, and regularly recalculated throughout (once per 100 iterations is used in this work).
 They are set using the following equations such that each term in the gradient of \cref{eq:bitss} is of a similar size,
@@
   \item Compute the constraint coefficients using \cref{eq:ke,eq:kd}.
-  \item Minimise the potential, \cref{eq:bitss}, and recompute the coefficients every 100 iterations of the minimisation.
+  \item Minimise the potential, \cref{eq:bitss}, and recompute the coefficients regularly throughout the minimisation.
 \end{enumerate}
@@
 This is done by tracing the trajectory of downhill minimisations from the two final states either side of the transition state.
-In the case where there is a chain of transition states between the two starting minima, BITSS will identify the transition state with the highest energy.
-If, instead, all of transition states or the full pathway are desired, BITSS can be continually repeated from one of the minima downhill from the located transition state and one of the initial minima until the desired minima are connected.
-However, chain-of-states methods are likely more efficient for this as they compute the entire pathway at once.
+In the case where there is a chain of transition states between the two starting minima, BITSS will identify the transition state with the highest energy in the chain.
+If, instead, all of transition states or the full pathway are desired, BITSS can be continually repeated from one of the minima downhill from the located transition state and one of the initial minima until the desired minima are piecewise connected.
 
@@
 
+%% start bib
 % \bibliographystyle{apsrev4-2}
 % \bibliography{bibexport.bib}
-% \bibliography{../../library.bib}
-
-% start bib
+% %\bibliography{../../library.bib}
+%% mid bib
 \begin{thebibliography}{42}%
@@
 \end{thebibliography}%
-% end bib
+%% end bib
 

### 2022-03-16 si/supplementary_information.tex
Small edits

@@
 For the cylindrical buckling example with a changing mesh, the resolution is refined each time the separation between the two states is halved. 
-This involves the number of triangles around the circumference of the cylinder increasing along the sequence, $40 \rightarrow 60 \rightarrow 80 \rightarrow 100$.
+This involves the number of triangles around the circumference of the cylinder increasing along the sequence: $40 \rightarrow 60 \rightarrow 80 \rightarrow 100$; with the number of degrees of freedom increasing by: $1760 \rightarrow 3960 \rightarrow 7040 \rightarrow 11000$.
 The positions of the nodes on the new grid, $\{\bm{n}_i\}$, are determined by linear interpolation from the previous grid $\{\bm{p}_i\}$, using the positions of the unbuckled meshes, $\{\bm{n'}_i\}$ and $\{\bm{p'}_i\}$.
@@
 
-In the example with different resolutions for the two states, the distance is obtained by first mapping the phase field from the higher resolution grid, $\{\phi_{k,l} | k,l \in \{0,1,\cdots,399\}\}$, to the low resolution grid, $\{\phi'_{i,j} | i,j \in \{0,1,\cdots,199\}\}$.
+In the wetting example with different resolutions for the two states, the distance is obtained by first mapping the phase field from the higher resolution grid, $\{\phi_{k,l} | k,l \in \{0,1,\cdots,399\}\}$, to the low resolution grid, $\{\phi'_{i,j} | i,j \in \{0,1,\cdots,199\}\}$.
 Because a square grid is used with a resolution ratio of two, the mapping involves averaging each 2x2 block to a single point:

### 2022-03-16 fig/make_adaptivemesh/plot.py
Added information about where data comes from.

@@ -9,6 +9,9 @@ import pyutils.latexify as lt
 import sys; sys.path.insert(0, '..')
 import style
 
+# Cylindrical buckling data generated by energyLandscapes/bits_test/changing_mesh/zoom2d.py
+# Striped wetting data generated by energyLandscapes/bits_test/different_meshes/send_data.py
+
 def plot_cb(fig, y0, htot):
     # Figure parameters
     w1 = 0.24

### 2022-03-16 fig/make_flatdiscontinuous/plot.py

@@ -12,6 +12,8 @@ import pyutils.latexify as lt
 import sys; sys.path.insert(0, '..')
 import style
 
+# Flat data generated by energyLandscapes/bits_test/zeroeigen2d/view.py
+# Discontinuous data from energyLandscapes/bits_test/discontinuous-lj7/network/dgraph/{min,ts}.data
 
 def plot_flat(fig, hsize):
     ### Plot parameters

### 2022-03-16 fig/make_speedtest/plot.py

@@ -10,6 +10,8 @@ import sys; sys.path.insert(0, '..')
 import style
 lt.update_width('r4-double')
 
+# Data generated by energyLandscapes/bits_test/speed_test/{system}/view_convergence.py
+
 def str_converter(instr):
     return np.fromstring(instr[1:-1],sep=' ')
 

### 2022-03-16 fig/make_toy2d/plot.py

@@ -11,6 +11,8 @@ from mpl_toolkits.axes_grid1.inset_locator import mark_inset
 import sys; sys.path.insert(0, '..')
 import style
 
+# Data generated using energyLandscapes/bits_test/2peaks/view.py
+
 ### Plot parameters
 dt = 0.06
 de = 0.02

### 2022-03-17 manuscript.tex
Added citations

@@
 \usepackage{graphicx}
+\graphicspath{{fig/}}
 
@@
 Here, the minimum energy barriers provide important lower bounds to the energy input required for transitions to occur.
-This has been used to understand failure in structural engineering applications \cite{Panter2019,Hutchinson2018}, for the development of super liquid-repellent surfaces \cite{Zhang2014,Panter2019b}, and investigating locomotion through complex terrain for robotics \cite{Othayoth2020}.
+This has been used to understand failure in structural engineering applications \cite{Panter2019,Hutchinson2018}, for the development of super liquid-repellent surfaces \cite{Zhang2014,Panter2019b,Amabili2017}, and investigating locomotion through complex terrain for robotics \cite{Othayoth2020}.
 Moreover, it is becoming desirable to tailor elastic deformation transitions to enable technologies such as advanced deployable structures \cite{Filipov2015,Zhai2018}, mechanical sensors and actuators \cite{Bertoldi2017,Truby2016,Chi2022,Bonfanti2020}, and energy absorbers \cite{Shan2015,Giri2021} to name but a few.
@@
 Single-ended methods are initialised at a single state and attempt to climb to a nearby saddle point.
-Examples include eigenvector following \cite{Cerjan1981}, the dimer method \cite{Heyden2005,Kastner2008}, and climbing image methods \cite{E2007,Ren2013}.
+Examples include eigenvector following \cite{Cerjan1981}, the dimer method \cite{Heyden2005,Kastner2008,Zhang2016}, and climbing image methods \cite{E2007,Ren2013}.
 Double-ended methods, such as the string method \cite{E2002,E2007} and doubly-nudged elastic band (DNEB) \cite{Trygubenko2004}, involve initialising a chain of states between two minima and then minimising the total energy of the chain.
-In addition to approximating the transition state, these are useful for obtaining an estimate for the full transition pathway.
+The initial chain must use an appropriate interpolation, which can sometimes be complicated to produce \cite{Wales2012a}.
+In addition to approximating the transition state, these double-ended methods also provide an estimate for the full transition pathway.
 
@@
 Single-ended methods are not well suited for identifying specific pathways and can spend a large amount of time searching for undesired transition states.
-Another major challenge in studying complex energy landscapes relates to the presence of locally flat or discontinous regions.
-Such as when considering patchy \cite{McMullen2018,Nguemaha2018,Chen2018b} and hard-body \cite{Richard2018,Santra2018} interactions in atomistic systems, or collision constraints for macroscopic objects \cite{Wriggers2006}.
+Another major challenge in studying complex energy landscapes relates to the presence of locally flat or discontinous regions, such as when considering patchy \cite{McMullen2018,Nguemaha2018,Chen2018b} and hard-body \cite{Richard2018,Santra2018} interactions in atomistic simulations, systems of polymer chains \cite{Mokkonen2016}, or collision constraints for macroscopic objects \cite{Wriggers2006}.
 Flat zero-modes in the landscape pose issues for single-ended search methods that rely only upon local information.
@@
 \begin{figure}[htb]
-  \includegraphics{fig/toy2d.pdf}
+  \includegraphics{toy2d.pdf}
   \caption{\label{fig:toy2d}
@@
 This is a double-ended method that uses two states that converge toward a transition state from either side, therefore combining aspects of the two traditional transition state search categories.
-We demonstrate how it addresses each of the above challenges using a range of different applications.
+This has the advantage of not requiring an initial interpolation, unlike other double-ended methods.
+Using a range of different applications, we will demonstrate how BITSS addresses each of the above challenges.
 
@@
 \end{gather}
-where $\bm{\nabla} E_1$ and $\bm{\nabla} E_2$ are the gradients of the energies two states, and $\alpha$ and $\beta$ are parameters with recommended values of $\alpha = 10$ and $\beta = 0.1$ (see supplementary information \footnote{See Supplemental Material at [URL] for derivations of the constraint coefficients, extra details for the example systems, results for the speed test against DNEB, and a comparison of the discontinuous energy landscape with the standard Lennard-Jones cluster}).
+where $\bm{\nabla} E_1$ and $\bm{\nabla} E_2$ are the gradients of the energies of the two states, and $\alpha$ and $\beta$ are parameters with recommended values of $\alpha = 10$ and $\beta = 0.1$ (see supplementary information \footnote{See Supplemental Material at [URL] for derivations of the constraint coefficients, extra details for the example systems, results for the speed test against DNEB, and a comparison of the discontinuous energy landscape with the standard Lennard-Jones cluster}).
 Here, $E_B$ is an estimation for the current energy barrier; evaluated using the difference between the highest energy along a linear interpolation between the two states and the average energy of the two states.
@@
 \begin{figure*}[tb]
-  \includegraphics{fig/speedtest.pdf}
+  \includegraphics{speedtest.pdf}
   \caption{\label{fig:speedtest}
@@
 \begin{figure}[tb]
-  \includegraphics{fig/adaptivemesh.pdf}
+  \includegraphics{adaptivemesh.pdf}
   \caption{\label{fig:adaptivemesh}
@@
 \begin{figure}[tb]
-  \includegraphics{fig/flatdiscontinuous.pdf}
+  \includegraphics{flatdiscontinuous.pdf}
   \caption{\label{fig:flatdiscontinuous}
@@
 %% mid bib
-\begin{thebibliography}{42}%
+\begin{thebibliography}{46}%
 \makeatletter
@@
   {NoStop}%
+\bibitem [{\citenamefont {Amabili}\ \emph {et~al.}(2017)\citenamefont
+  {Amabili}, \citenamefont {Giacomello}, \citenamefont {Meloni},\ and\
+  \citenamefont {Casciola}}]{Amabili2017}%
+  \BibitemOpen
+  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {M.}~\bibnamefont
+  {Amabili}}, \bibinfo {author} {\bibfnamefont {A.}~\bibnamefont {Giacomello}},
+  \bibinfo {author} {\bibfnamefont {S.}~\bibnamefont {Meloni}},\ and\ \bibinfo
+  {author} {\bibfnamefont {C.~M.}\ \bibnamefont {Casciola}},\ }\href
+  {https://doi.org/10.1103/PhysRevFluids.2.034202} {\bibfield  {journal}
+  {\bibinfo  {journal} {Physical Review Fluids}\ }\textbf {\bibinfo {volume}
+  {2}},\ \bibinfo {pages} {034202} (\bibinfo {year} {2017})}\BibitemShut
+  {NoStop}%
 \bibitem [{\citenamefont {Othayoth}\ \emph {et~al.}(2020)\citenamefont
@@
   {2008})}\BibitemShut {NoStop}%
+\bibitem [{\citenamefont {Zhang}\ \emph {et~al.}(2016)\citenamefont {Zhang},
+  \citenamefont {Du},\ and\ \citenamefont {Zheng}}]{Zhang2016}%
+  \BibitemOpen
+  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {L.}~\bibnamefont
+  {Zhang}}, \bibinfo {author} {\bibfnamefont {Q.}~\bibnamefont {Du}},\ and\
+  \bibinfo {author} {\bibfnamefont {Z.}~\bibnamefont {Zheng}},\ }\href
+  {https://doi.org/10.1137/140972676} {\bibfield  {journal} {\bibinfo
+  {journal} {SIAM Journal on Scientific Computing}\ }\textbf {\bibinfo {volume}
+  {38}},\ \bibinfo {pages} {A528} (\bibinfo {year} {2016})}\BibitemShut
+  {NoStop}%
 \bibitem [{\citenamefont {E}\ \emph {et~al.}(2007)\citenamefont {E},
@@
   {2004})}\BibitemShut {NoStop}%
+\bibitem [{\citenamefont {Wales}\ and\ \citenamefont
+  {Carr}(2012)}]{Wales2012a}%
+  \BibitemOpen
+  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {D.~J.}\ \bibnamefont
+  {Wales}}\ and\ \bibinfo {author} {\bibfnamefont {J.~M.}\ \bibnamefont
+  {Carr}},\ }\href {https://doi.org/10.1021/ct3004832} {\bibfield  {journal}
+  {\bibinfo  {journal} {Journal of Chemical Theory and Computation}\ }\textbf
+  {\bibinfo {volume} {8}},\ \bibinfo {pages} {5020} (\bibinfo {year}
+  {2012})}\BibitemShut {NoStop}%
 \bibitem [{\citenamefont {Trefethen}\ and\ \citenamefont
@@
   {journal} {Physical Review E}\ }\textbf {\bibinfo {volume} {98}},\ \bibinfo
-  {pages} {1} (\bibinfo {year} {2018})}\BibitemShut {NoStop}%
+  {pages} {032606} (\bibinfo {year} {2018})}\BibitemShut {NoStop}%
+\bibitem [{\citenamefont {M{\"{o}}kk{\"{o}}nen}\ \emph
+  {et~al.}(2016)\citenamefont {M{\"{o}}kk{\"{o}}nen}, \citenamefont
+  {Ala-Nissila},\ and\ \citenamefont {J{\'{o}}nsson}}]{Mokkonen2016}%
+  \BibitemOpen
+  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {H.}~\bibnamefont
+  {M{\"{o}}kk{\"{o}}nen}}, \bibinfo {author} {\bibfnamefont {T.}~\bibnamefont
+  {Ala-Nissila}},\ and\ \bibinfo {author} {\bibfnamefont {H.}~\bibnamefont
+  {J{\'{o}}nsson}},\ }\href {https://doi.org/10.1063/1.4962167} {\bibfield
+  {journal} {\bibinfo  {journal} {The Journal of Chemical Physics}\ }\textbf
+  {\bibinfo {volume} {145}},\ \bibinfo {pages} {094901} (\bibinfo {year}
+  {2016})}\BibitemShut {NoStop}%
 \bibitem [{\citenamefont {Wriggers}(2006)}]{Wriggers2006}%

### 2022-03-17 manuscript.tex
Final edits before submission

@@
   To resolve these challenges, we introduce a new double-ended method, the Binary Image Transition State Search (BITSS).
-  It uses just two states that converge to the transition state, resulting in a flexible, fast, and memory-efficient method.
+  It uses just two states that converge to the transition state, resulting in a fast, flexible, and memory-efficient method.
   We demonstate its versatility by applying BITSS to three very different classes of problems: Lennard-Jones clusters, shell buckling, and multiphase phase-field models.
@@
 Double-ended methods, such as the string method \cite{E2002,E2007} and doubly-nudged elastic band (DNEB) \cite{Trygubenko2004}, involve initialising a chain of states between two minima and then minimising the total energy of the chain.
-The initial chain must use an appropriate interpolation, which can sometimes be complicated to produce \cite{Wales2012a}.
-In addition to approximating the transition state, these double-ended methods also provide an estimate for the full transition pathway.
+An appropriate interpolation must be used for the initialisation, which can be challenging to produce \cite{Wales2012a}.
+These double-ended methods also provide an estimate for the full transition pathway in addition to approximating the transition state.
 
@@
 Specialist treatment can sometimes be used such as in the case of global rotation and translation \cite{Page1988}, but they are thwarted by local zero-modes.
-Meanwhile, current methods cannot typically be applied in the case of discontinuous potentials, or where the gradient is prohibitively expensive to compute, because they require continuous, differentiable optimisation functions.
+Meanwhile, current methods cannot typically be applied in the case of discontinuous potentials, or where the gradient is prohibitively expensive to compute, because continuous, differentiable optimisation functions are required.
 
@@
 
-In this work we introduce a new method, the Binary Image Transition State Search (BITSS).
-This is a double-ended method that uses two states that converge toward a transition state from either side, therefore combining aspects of the two traditional transition state search categories.
-This has the advantage of not requiring an initial interpolation, unlike other double-ended methods.
-Using a range of different applications, we will demonstrate how BITSS addresses each of the above challenges.
+In this work we introduce a new method, the Binary Image Transition State Search (BITSS), and using a range of different applications, we will demonstrate how BITSS addresses each of the above challenges.
+BITSS is a double-ended method that uses just two states that converge toward a transition state from either side, therefore combining aspects of the two traditional transition state search categories.
+Importantly, unlike other double-ended methods, BITSS does not require any initial interpolation.
 
@@
         Each grid cell denotes 50x50 lattice nodes.
-        The zoomed axes shows the difference in the fluid interface between the two final states, as well as the approximated transition state (solid black line).
+        The zoomed axis shows the difference in the fluid interface between the two final states, as well as the approximated transition state (solid black line).
         This is compared to the transition state found using a high resolution (dashed line).
@@
 Using this approach, BITSS is able to closely approach the transition state.
-The convergence precision is now limited by the transition state energy differing slightly on each grid, but this effect is reduced when using an adaptive method or a higher resolution.
+The precision of this convergence is now limited by the transition state energy differing slightly on each grid, but this effect will be reduced when using an adaptive method or a higher resolution.
 

### 2022-03-30 fig/make_flatdiscontinuous/plot.py
Added lj cluster dgraph to main paper figure

@@ -167,6 +167,8 @@ def plot_discontinuous(fig, hsize):
     h1 = 0.9
     h2 = 0.7
     y2 = 0.2
+    c1 = style.c1
+    c2 = 'dimgrey'
     
     class Node:
         def __init__(self, i, e, x):
@@ -196,15 +198,15 @@ def plot_discontinuous(fig, hsize):
         def __lt__(self, other):
             return hash(self) < hash(other)
     
-    def load_data():
+    def load_data(potential):
         # minima
-        minima = pd.read_csv('discont_min.data')
+        minima = pd.read_csv(f'{potential}-min.data')
         min_e = np.array(minima['energy'])
         min_x = minima[[f'x{i}' for i in range(14)]].to_numpy()
         nodes = [Node(i, min_e[i], min_x[i]) for i in range(len(minima))]
         # TS
-        e_ts = np.loadtxt('discont_ts.data', usecols=0)
-        pairs = np.loadtxt('discont_ts.data', usecols=[3,4], dtype=int) - 1
+        e_ts = np.loadtxt(f'{potential}-ts.data', usecols=0)
+        pairs = np.loadtxt(f'{potential}-ts.data', usecols=[3,4], dtype=int) - 1
         ts = [TS(nodes[pair[0]], nodes[pair[1]], e_ts[i]) for i, pair in enumerate(pairs)]
         return nodes, ts
 
@@ -223,9 +225,16 @@ def plot_discontinuous(fig, hsize):
         g.add_nodes_from(nodes)
         for t in ts:
             g.add_edge(t.minimum1, t.minimum2, ts=t)
-        dg = DisconnectivityGraph(g, Emax=-10.5)
+        dg = DisconnectivityGraph(g, Emax=-10.5, order_by_value=lambda m: -m.i)
         dg.calculate()
         return dg
+
+    def offset_graph(dg, offset):
+        def recursive_offset(tree):
+            tree.data['x'] += offset
+            for subtree in tree.get_branches():
+                recursive_offset(subtree)
+        recursive_offset(dg.tree_graph)
     
     def plot_cluster(x, ax):
         rad = 1.1225 / 2
@@ -249,10 +258,10 @@ def plot_discontinuous(fig, hsize):
[…]

### 2022-03-30 fig/make_speedtest/plot.py
Added DNEB to main paper speedtest

@@ -15,10 +15,12 @@ lt.update_width('r4-double')
 def str_converter(instr):
     return np.fromstring(instr[1:-1],sep=' ')
 
-y0 = 0.15
-h1 = 0.62/3 # height of lower axes relative to width
+hd11 = 0.045
+hd12 = 0.01
+hd2 = -0.01
+h1 = 0.4/3 # height of lower axes relative to width
 h2 = 1/9 # height of upper axes relative to width
-h = h1 + h2
+h = hd11 + hd12 + hd2 + 2*h1 + h2
 fig = lt.figure(1, h)
 
 for isub, subfig in enumerate(['a', 'b', 'c']):
@@ -48,43 +50,64 @@ for isub, subfig in enumerate(['a', 'b', 'c']):
 
 
     ### Plot data
-    x0 = isub / 3
-    ax = plt.axes((x0+0.19/3, y0, 0.26, h1/h-y0+0.03))
+    x0 = isub/3
+    xd0 = 0.055
+    w1 = 1/3-0.005 - xd0
+    if (isub == 0):
+        x0 = x0 + 0.01
+        w1 = w1 - 0.01
+    ax1 = plt.axes((x0+xd0, hd11/h, w1, h1/h))
+    ax2 = plt.axes((x0+xd0, (hd11+h1+hd12)/h, w1, h1/h), sharex=ax1, sharey=ax1)
     fig.text(x0, 1, f'({subfig})', va='top', ha='left')
-
-    if (subfig == 'a'):
-        ax.annotate('BITSS', [0.1, 0.08], [0.2, 0.1], xycoords='axes fraction',
-                    arrowprops={'arrowstyle':'-'}, bbox={'pad':0, 'fc':'none', 'ec':'none'})
-        ax.annotate('String', [0.37, 0.35], [0.51, 0.48], xycoords='axes fraction',
-                    arrowprops={'arrowstyle':'-'}, bbox={'pad':0, 'fc':'none', 'ec':'none'})
-        ax.annotate('String', [0.4, 0.455], [0.51, 0.48], xycoords='axes fraction', alpha=0,
-                    arrowprops={'arrowstyle':'-'}, bbox={'pad':0, 'fc':'none', 'ec':'none'})
-        ax.annotate('String', [0.4, 0.595], [0.51, 0.48], xycoords='axes fraction', alpha=0,
[…]

### 2022-03-30 manuscript.tex
Updated captions of figures

@@
-\documentclass[aps,prl,twocolumn,10pt,groupedaddress]{revtex4-2}
+\documentclass[twocolumn,10pt]{revtex4-2}
 
@@
 
-%\section{Introduction \& Method}
+\section{Introduction}
 Transition states are central to the description of reconfiguration mechanisms for systems in chemistry, condensed matter physics, and engineering.
@@
 
-%\section{Method}
+\section{Method}
 The method begins by first initialising the states, $\bm{x}_1$ and $\bm{x}_2$, in the basins of attraction of different local minima.
@@
 
-%\section{Speed Comparison}
+\section{Results}
+\subsection{Speed Comparison}
 \begin{figure*}[tb]
@@
   \caption{\label{fig:speedtest}
-    The convergence to the transition state as a function of the number of gradient calculations using the BITSS (black line) and string methods for (a) a Lennard-Jones seven-particle cluster, (b) cylindrical shell buckling, and (c) wetting of a chemically-striped surface.
-    The string method is repeated with a differing number of images along the string, the number of which is listed in the legend in (c).
-    The shown configurations correspond to the two minimum energy states and the transition state, marked by an asterisk.
+    Comparisons between BITSS, DNEB, and the string method in the convergence to the transition state as a function of the number of calculations of the energy gradient.
+    Three test systems are used: (a) a Lennard-Jones seven-particle cluster, (b) cylindrical shell buckling, and (c) wetting of a chemically-striped surface.
+    The configurations shown correspond to the two minimum energy states and the transition state, marked by an asterisk.
+    The string method and DNEB are repeated with a differing number of images, as listed in the legend in (c).
   }
@@
 
-%\section{Adaptive mesh}
+\subsection{Adaptive discretisation}
 \begin{figure}[tb]
@@
 
-%\section{Zero-curvature modes}
+\subsection{Locally flat landscapes}
 \begin{figure}[tb]
@@
         Bottom inset: The pathway taken, with the edges of the flat regions marked by dashed lines.
-    (b) Disconnectivity graph of the energy landscape for a seven-particle cluster with a discontinuous hard-core pair potential.
+    (b) Disconnectivity graph of the energy landscape for a seven-particle cluster with a discontinuous hard-core pair potential (orange), and a standard Lennard-Jones potnetial (gray).
+        The two graphs are offset for visibility.
     (c) Plot of the discontinuous potential.
@@
 
-%\section{Gradient-free problems}
+\subsection{Undefined gradients}
 Finally, we investigate the application of BITSS to systems with undefined gradients, such as when the landscape is discontinuous.
@@
 
-%\section{Conclusion}
+\section{Conclusion}
 In conclusion, we have demonstrated a novel method for finding transition states that tackles problems not currently addressed by existing methods.
@@
 \appendix
-\section{}
 

### 2022-03-30 fig/style.py

@@ -10,7 +10,7 @@ plt.rc('axes', labelsize=9)
 c1 = 'tab:orange'
 c2 = 'tab:red'
 c3 = 'tab:blue'
-colors = [c1, c2, c3]
+colors = [c2, c1, c3]
 
 
 ### Make sure this is reloaded by IPython ###

### 2022-03-30 manuscript.tex
started updating methods

@@
 
-\section{Method}
+\section{Results and discussion}
+\subsection{BITSS method in a nutshell}
 The method begins by first initialising the states, $\bm{x}_1$ and $\bm{x}_2$, in the basins of attraction of different local minima.
@@
 
-The two constraints are implemented using energy penalty terms, which, if the constraints are not met, result in driving forces on the two states, such as in \cref{fig:toy2d}b.
+The two constraints are implemented using energy penalty terms, which result in driving forces on the two states if the constraints are not met, such as in \cref{fig:toy2d}b.
 The total energy of the pair of states is therefore given by
@@
 
+In summary, the method involves iteratively performing the following three steps:
+\begin{enumerate}[noitemsep,nolistsep]
+  \item Reduce the target separation using \cref{eq:diteration}.
+  \item Compute the constraint coefficients using \cref{eq:ke,eq:kd}.
+  \item Minimise the potential given by \cref{eq:bitss}, and recompute the coefficients at regular intervals.
+\end{enumerate}
+This process is completed once a suitable convergence criterion is reached.
+This can either be based upon the separation between the states, or the size of gradient at the midpoint between the states.
+
 Using this approach, the typical trajectories of the states are demonstrated for a simple 2D potential in \cref{fig:toy2d}a.
@@
 
-To ensure that the transition state is located successfully, the constraint strengths $\kappa_d$ and $\kappa_e$ are updated as the algorithm proceeds using information from the system.
-They are initially calculated at the start of each minimisation, and regularly recalculated throughout (once per 100 iterations is used in this work).
-They are set using the following equations such that each term in the gradient of \cref{eq:bitss} is of a similar size,
-\begin{gather}
-  \kappa_e = \frac {\alpha} {2 E_B},
-  \label{eq:ke}
-  \\
-  \kappa_d = \max \left(
-    \frac {\sqrt{|\bm{\nabla} E_1|^2 + |\bm{\nabla} E_2|^2}} {2\sqrt{2} \beta d_i} \; , \;
-    \frac{E_B}{\beta d_i^2} \right),
-  \label{eq:kd}
-\end{gather}
-where $\bm{\nabla} E_1$ and $\bm{\nabla} E_2$ are the gradients of the energies of the two states, and $\alpha$ and $\beta$ are parameters with recommended values of $\alpha = 10$ and $\beta = 0.1$ (see supplementary information \footnote{See Supplemental Material at [URL] for derivations of the constraint coefficients, extra details for the example systems, results for the speed test against DNEB, and a comparison of the discontinuous energy landscape with the standard Lennard-Jones cluster}).
-Here, $E_B$ is an estimation for the current energy barrier; evaluated using the difference between the highest energy along a linear interpolation between the two states and the average energy of the two states.
-
-In summary, the method involves iteratively performing the following three steps:
-\begin{enumerate}[noitemsep,nolistsep]
-  \item Reduce the target separation using \cref{eq:diteration}.
-  \item Compute the constraint coefficients using \cref{eq:ke,eq:kd}.
-  \item Minimise the potential, \cref{eq:bitss}, and recompute the coefficients regularly throughout the minimisation.
-\end{enumerate}
-This process is completed once a convergence criterion is reached that can be based upon either the separation between the states, or the size of gradient at the midpoint between the two states.
-
 Once BITSS has identified the transition state, it is possible to find the full minimum energy pathway.
@@
 
-\section{Results}
 \subsection{Speed Comparison}
@@
 Therefore, unlike the string method, BITSS does not require a second approach to accurately locate the transition state.
-Similar results are also found when comparing against against DNEB, which can be seen in the supplementary information \cite{Note1}.
 
@@
 
-\subsection{Locally flat landscapes}
+\subsection{Complex landscapes}
 \begin{figure}[tb]
@@
 
-\subsection{Undefined gradients}
 Finally, we investigate the application of BITSS to systems with undefined gradients, such as when the landscape is discontinuous.
@@
 This method will enable the analysis of energy landscapes for new systems in both particulate and continuum applications, and increase the feasibility of such methods for large-scale, complex systems.
+
+\section{Methods}
+\subsection{BITSS: Target distance}
+
+\subsection{BITSS: Total potential}
+
+\subsection{BITSS: Constraint coefficients}
+To ensure that the transition state is located successfully, the constraint strengths $\kappa_d$ and $\kappa_e$ are updated as the algorithm proceeds using information from the system.
+They are initially calculated at the start of each minimisation, and regularly recalculated throughout (once per 100 iterations is used in this work).
+They are set using the following equations such that each term in the gradient of \cref{eq:bitss} is of a similar size,
+\begin{gather}
+  \kappa_e = \frac {\alpha} {2 E_B},
+  \label{eq:ke}
+  \\
+  \kappa_d = \max \left(
+    \frac {\sqrt{|\bm{\nabla} E_1|^2 + |\bm{\nabla} E_2|^2}} {2\sqrt{2} \beta d_i} \; , \;
+    \frac{E_B}{\beta d_i^2} \right),
+  \label{eq:kd}
+\end{gather}
+where $\bm{\nabla} E_1$ and $\bm{\nabla} E_2$ are the gradients of the energies of the two states, and $\alpha$ and $\beta$ are parameters with recommended values of $\alpha = 10$ and $\beta = 0.1$ (see supplementary information \footnote{See Supplemental Material at [URL] for derivations of the constraint coefficients, and extra details for the example systems}).
+Here, $E_B$ is an estimation for the current energy barrier; evaluated using the difference between the highest energy along a linear interpolation between the two states and the average energy of the two states.
+
+\subsection{BITSS: Changes for undefined gradients}
+
+\subsection{Adaptive discretisation test details}
+
+\subsection{Particle cluster system}
+
+\subsection{Cylindrical buckling system}
+
+\subsection{Striped wetting system}
 

### 2022-03-31 manuscript.tex
Moved main BITSS method to methods section

@@
 \usepackage{amsmath}
+\newcommand{\abs}[1]{\left| #1 \right|}
+\newcommand{\grad}{\bm{\nabla}}
+\newcommand{\upDelta}{\mathop{}\!\Delta}
 
@@
 These can be set to the minima, but this is not a necessary requirement.
-The BITSS method then leads these states to meet at the lowest point on the ridge between the basins of attraction - the transition state, as shown in \cref{fig:toy2d}a.
-This is done by minimising the energy of the pair while constraining their separation and energy difference.
-The separation constraint $d_i$ is incrementally reduced, such that at iteration $i$,
-\begin{equation}\label{eq:diteration}
-  d_i = (1 - f) d_{i-1},
-\end{equation}
-with $d_0$ the separation between the initial states.
-A factor of $f = 0.5$ is succesful for most applications, but this can be made smaller to ensure that the states do not slide off the ridge.
-The secondary constraint sets the energies of the two states equal to ensure that neither state is pulled over the ridge.
-
-The two constraints are implemented using energy penalty terms, which result in driving forces on the two states if the constraints are not met, such as in \cref{fig:toy2d}b.
-The total energy of the pair of states is therefore given by
-\begin{multline}\label{eq:bitss}
-  E_\text{BITSS}(\bm{x}_1, \bm{x}_2) = E_1 + E_2
-    + \kappa_e \left( E_1 - E_2 \right) ^2 \\
-    + \kappa_d \left( \mathrm{d}(\bm{x}_1, \bm{x}_2) - d_i \right) ^2,
-\end{multline}
-where $E_1$ and $E_2$ are the single state energies, $\kappa_e$ and $\kappa_d$ parametrise the strengths of the energy and distance constraints, and $\mathrm{d}(\bm{x}_1, \bm{x}_2)$ is the measure of distance between the two states.
-In this work the L-BFGS algorithm is chosen to minimise the energy, owing to its fast convergence and low memory requirement for large numbers of degrees of freedom \cite{Liu1989}.
-However, any other minimisation method can be used instead.
+The energies of these two states are then minimised, while constraining their separation, which is iteratively reduced to zero.
+This results in the two states meeting at the lowest point on the ridge between the two basin of attraction - the transition state.
+To ensure that neither state is pulled over the ridge, a secondary constraint enforces equal energies for the two states.
+These two constraints are implemented using energy penalty terms, which result in driving forces on the two states if the constraints are not met, such as in \cref{fig:toy2d}b.
 
@@
 \begin{enumerate}[noitemsep,nolistsep]
-  \item Reduce the target separation using \cref{eq:diteration}.
-  \item Compute the constraint coefficients using \cref{eq:ke,eq:kd}.
-  \item Minimise the potential given by \cref{eq:bitss}, and recompute the coefficients at regular intervals.
+  \item Reduce the constrained separation.
+  \item Compute the constraint coefficients.
+  \item Minimise the potential of the pair of states, including energy penalty terms, while recomputing the coefficients at regular intervals.
 \end{enumerate}
+See the methods section for further details of each step.
 This process is completed once a suitable convergence criterion is reached.
@@
 This is tested here by measuring the speed of convergence to the transition state for BITSS in comparison with the string method and DNEB for several representative examples.
-
-The first system to be tested is a two-dimensional, seven-particle cluster, with the transition from a hexagonal cluster to a higher energy configuration.
-The interaction between each pair of particles uses the Lennard-Jones potential,
-\begin{equation}
-  E = 4\epsilon \left[ \left(\frac{\sigma}{r}\right)^{12} - \left(\frac{\sigma}{r}\right)^6 \right],
-\end{equation}
-where $r$ is the particle separation, $\epsilon$ is the interaction strength, and $\sigma$ is the particle size.
-
-The second system is an elastic cylindrical shell under an applied strain.
+The first is a two-dimensional, seven-particle cluster, with a transition from a hexagonal cluster to a higher energy configuration.
+The second system is an elastic cylindrical shell with an applied axial strain.
 This undergoes a transition from an unbuckled state to a singly-dimpled state, which defines the minimum energy required for the cylinder to buckle \cite{Panter2019}.
-A 2D triangular mesh with 35400 degrees of freedom is used to model this system, with the following energy function,
-\begin{equation}
-  E = \sum_i k^S_i (r_i - r^0_i)^2 + \sum_j k^B_j [1 + \cos(\theta_j - \theta^0_j)].
-\end{equation}
-The first term provides the stretching energy for the system using a sum over all the bonds, where $r_i$ is the length, $r^0_i$ is the equilibrium length, and $k^S_i$ is the stretching rigidity of bond $i$.
-The second term models the bending energy by representing each pair of adjacent triangles as an elastic hinge.
-For hinge $j$, $\theta_j$ is the dihedral angle, $\theta^0_j$ is the equilibrium angle, and $k^B_j$ is the bending rigidity.
-
 The final system involves a droplet situated on a chemically striped surface with both hydrophilic and hydrophobic regions.
 This has two possible states, with the droplet either upon one hydrophilic stripe, or straddling across two.
-This is modelled on a 200x200 2D grid using a phase-field model \cite{Panter2019b}, which has an order parameter, $\phi(\bm{r})$, representing the phase of the liquid ($\phi=-1$ for gas, $\phi=1$ for liquid).
-The energy functional has four separate terms,
-\begin{equation} \label{eq:phasefield}
-  E[\phi] = E^B[\phi] + E^I[\phi] + E^S[\phi] + E^V[\phi].
-\end{equation}
-The first term, $E^B$, uses a double well potential to set values of $\phi=\pm1$ in the bulk.
-The second term then provides the interfacial energy between the liquid and gas by imposing an energy penalty to gradients in $\phi$.
-$E^S$ is the solid-liquid interaction energy, which sets the contact angles of the hydrophilic and hydrophobic regions to 60\si{\degree} and 110\si{\degree}, respectively.
-Finally, $E^V$ constrains the volume of the liquid drop by penalising any variation from the target volume.
-For further details and the gradients of the potentials see the supplementary information \cite{Note1}.
+The details about how these systems are modelled are included in the methods section.
 
-Convergence is measured using the distance from the transition state as a function of number of evaluations to the gradient of the system's potential.
-The transition state is compared to the average of the two states for BITSS, whereas for the chain-of-states methods, the closest point on a cubic spline is used.
+Convergence is measured using the distance from the transition state.
+For BITSS, the average of the two states is used for this, whereas for the chain-of-states methods, the closest point on a cubic spline interpolation is used.
+The speed of this convergence is evaluated through comparison with the number of calculations of the potential gradient for a single state.
 
@@
 Secondly, the BITSS method can more accurately approximate the transition state by orders of magnitude, particularly for the wetting example where the string method does not significantly improve upon the initial pathway estimate.
-Therefore, unlike the string method, BITSS does not require a second approach to accurately locate the transition state.
+Therefore, unlike these other double-ended methods, BITSS does not require a second approach to accurately locate the transition state.
 
@@
 \section{Methods}
-\subsection{BITSS: Target distance}
+\subsection{BITSS: Distance constraint}
+The value of the separation constraint is incrementally reduced such that, at iteration $i$, it is given by
+\begin{equation}\label{eq:diteration}
+  d_i = (1 - f) d_{i-1},
+\end{equation}
+with $d_0$ the separation between the two initial states.
+This fractional reduction ensures that as the two states approach the transition state they are not likely to undergo a sudden jump that will send them into the opposite basin.
+A factor of $f = 0.5$ is succesful for most applications, but this can be made smaller to ensure that the states do not slide off the ridge.
 
 \subsection{BITSS: Total potential}
+The total energy of the pair of states, including energy penalty terms for the constraints, is given by
+\begin{multline}\label{eq:bitss}
+  E_\text{BITSS}(\bm{x}_1, \bm{x}_2) = E_1 + E_2
+    + \kappa_e \left( E_1 - E_2 \right) ^2 \\
+    + \kappa_d \left( \mathrm{d}(\bm{x}_1, \bm{x}_2) - d_i \right) ^2,
+\end{multline}
+where $E_1$ and $E_2$ are the single state energies, $\kappa_e$ and $\kappa_d$ parametrise the strengths of the energy and distance constraints, and $\mathrm{d}(\bm{x}_1, \bm{x}_2)$ is the measure of distance between the two states.
+In this work the L-BFGS algorithm is chosen to minimise this energy, owing to its fast convergence and low memory requirement for large numbers of degrees of freedom \cite{Liu1989}.
+However, any other minimisation method can be used instead.
 
@@
   \kappa_d = \max \left(
-    \frac {\sqrt{|\bm{\nabla} E_1|^2 + |\bm{\nabla} E_2|^2}} {2\sqrt{2} \beta d_i} \; , \;
+    \frac {\sqrt{\abs{\grad E_1}^2 + \abs{\grad E_2}^2}} {2\sqrt{2} \beta d_i} \; , \;
     \frac{E_B}{\beta d_i^2} \right),
@@
 \end{gather}
-where $\bm{\nabla} E_1$ and $\bm{\nabla} E_2$ are the gradients of the energies of the two states, and $\alpha$ and $\beta$ are parameters with recommended values of $\alpha = 10$ and $\beta = 0.1$ (see supplementary information \footnote{See Supplemental Material at [URL] for derivations of the constraint coefficients, and extra details for the example systems}).
+where $\grad E_1$ and $\grad E_2$ are the gradients of the energies of the two states, and $\alpha$ and $\beta$ are parameters with recommended values of $\alpha = 10$ and $\beta = 0.1$ (see supplementary information \footnote{See Supplemental Material at [URL] for derivations of the constraint coefficients, and extra details for the example systems}).
 Here, $E_B$ is an estimation for the current energy barrier; evaluated using the difference between the highest energy along a linear interpolation between the two states and the average energy of the two states.
+
+In practice, when numerically minimising, the states will jump about slightly which can result in large gradients perpendicular to the optimal movement direction.
+To reduce this effect, the gradients used in \cref{eq:kd} are projected in the direction of the separation between the two states:
+\begin{equation}
+  \abs{\grad E_n} \approx \frac {\abs{(\bm{x}_1 - \bm{x}_2) \cdot \grad E_n}} {\abs{\bm{x}_1 - \bm{x}_2}}.
+\end{equation}
 
@@
 \subsection{Adaptive discretisation test details}
+Here we provide the details for the interpolations and mapping involved in the two examples demonstrating the feasibility of using an adaptive discretisation method.
+In the examples demonstrating the feasibility of using adaptive 
+For the cylindrical buckling example with a changing mesh, the resolution is refined each time the separation between the two states is halved. 
+This involves the number of triangles around the circumference of the cylinder increasing along the sequence: $40 \rightarrow 60 \rightarrow 80 \rightarrow 100$; with the number of degrees of freedom increasing by: $1760 \rightarrow 3960 \rightarrow 7040 \rightarrow 11000$.
+The positions of the nodes on the new grid, $\{\bm{n}_i\}$, are determined by linear interpolation from the previous grid $\{\bm{p}_i\}$, using the positions of the unbuckled meshes, $\{\bm{n'}_i\}$ and $\{\bm{p'}_i\}$.
+For each node of the new grid, $\bm{n'}_i$, the triangle that contains it is first identified, which we will denote $\{\bm{p'}_1,\bm{p'}_2,\bm{p'}_3\}$, and the barycentric coordinates of the point are computed, $\{\lambda_1,\lambda_2,\lambda_3\}$.
+The new position is then given by $\bm{n}_i = \lambda_1 \bm{p}_1 + \lambda_2 \bm{p}_2 + \lambda_3 \bm{p}_3$.
+
+In the wetting example with different resolutions for the two states, the distance is obtained by first mapping the phase field from the higher resolution grid, $\{\phi_{k,l} | k,l \in \{0,1,\cdots,399\}\}$, to the low resolution grid, $\{\phi'_{i,j} | i,j \in \{0,1,\cdots,199\}\}$.
+Because a square grid is used with a resolution ratio of two, the mapping involves averaging each 2x2 block to a single point:
+\begin{equation}
+  \phi'_{i,j} = \frac{1}{4} \left( \phi_{2i,2j} + \phi_{2i+1,2j} + \phi_{2i,2j+1} + \phi_{2i+1,2j+1} \right)
+\end{equation}
+Then the separation from the other state, $\{\widetilde{\phi}_{i,j}\}$ is computed using the 2-norm,
+\begin{equation}
+  d = \sqrt{\sum_{i,j} \left( \phi'_{i,j} - \widetilde{\phi}_{i,j} \right)^2}.
+\end{equation}
+Finally, the gradient of the distance with respect to each point must be mapped back to the higher-resolution grid, which is done by assigning a quarter of each component back to its the original four points:
+\begin{equation}
+  \frac{\partial d}{\partial \phi_{k,l}} =
+    \frac{\partial \phi'_{i,j}}{\partial \phi_{k,l}} \frac{\partial d}{\partial \phi'_{i,j}} =
+    \frac{1}{4} \frac{\partial d}{\partial \phi'_{i,j}} =
+    \frac{1}{4} \frac{\phi'_{i,j} - \widetilde{\phi}_{i,j}}{d},
+\end{equation}
+where $k \in \{2i, 2i+1\}$, and $l \in \{2j, 2j+1\}$.
 
 \subsection{Particle cluster system}
+The interaction between each pair of particles uses the Lennard-Jones potential,
+\begin{equation}
+  E = 4\epsilon \left[ \left(\frac{\sigma}{r}\right)^{12} - \left(\frac{\sigma}{r}\right)^6 \right],
+\end{equation}
+where $r$ is the particle separation, $\epsilon$ is the interaction strength, and $\sigma$ is the particle size.
 
 \subsection{Cylindrical buckling system}
+A 2D triangular mesh with 35400 degrees of freedom is used to model this system, with the following energy function,
+\begin{equation}
+  E = \sum_i k^S_i (r_i - r^0_i)^2 + \sum_j k^B_j [1 + \cos(\theta_j - \theta^0_j)].
+\end{equation}
+The first term provides the stretching energy for the system using a sum over all the bonds, where $r_i$ is the length, $r^0_i$ is the equilibrium length, and $k^S_i$ is the stretching rigidity of bond $i$.
+The second term models the bending energy by representing each pair of adjacent triangles as an elastic hinge.
+For hinge $j$, $\theta_j$ is the dihedral angle, $\theta^0_j$ is the equilibrium angle, and $k^B_j$ is the bending rigidity.
 
 \subsection{Striped wetting system}
+This is modelled on a 200x200 2D grid using a phase-field model \cite{Panter2019b}, which has an order parameter, $\phi(\bm{r})$, representing the phase of the liquid ($\phi=-1$ for gas, $\phi=1$ for liquid).
+The energy functional has four separate terms,
+\begin{equation} \label{eq:phasefield}
+  E[\phi] = E^B[\phi] + E^I[\phi] + E^S[\phi] + E^V[\phi].
+\end{equation}
+The first term, $E^B$, uses a double well potential to set values of $\phi=\pm1$ in the bulk.
+The second term then provides the interfacial energy between the liquid and gas by imposing an energy penalty to gradients in $\phi$.
+$E^S$ is the solid-liquid interaction energy, which sets the contact angles of the hydrophilic and hydrophobic regions to 60\si{\degree} and 110\si{\degree}, respectively.
+Finally, $E^V$ constrains the volume of the liquid drop by penalising any variation from the target volume.
+For further details and the gradients of the potentials see the supplementary information \cite{Note1}.
 

### 2022-03-31 si/supplementary_information.tex
Moved main BITSS method to methods section

--- 2022-03-15 si/supplementary_information.tex
@@
   \frac{E_B}{\beta d_i^2} \right).
-\end{equation}
-
-In practice, when numerically minimising, the states will jump about slightly which can result in large gradients perpendicular to the optimal movement direction.
-To reduce this effect, the gradients are projected in the direction of the separation between the two states:
-\begin{equation}
-  \abs{\grad E_n} \approx \frac {\abs{(\bm{x}_1 - \bm{x}_2) \cdot \grad E_n}} {\abs{\bm{x}_1 - \bm{x}_2}}.
 \end{equation}
@@
 \newpage
-\section{Details for the adaptive discretisation tests}
-Here we provide the details for the interpolations and mapping involved in the two examples demonstrating the feasibility of using an adaptive discretisation method.
-For the cylindrical buckling example with a changing mesh, the resolution is refined each time the separation between the two states is halved. 
-This involves the number of triangles around the circumference of the cylinder increasing along the sequence, $40 \rightarrow 60 \rightarrow 80 \rightarrow 100$.
-The positions of the nodes on the new grid, $\{\bm{n}_i\}$, are determined by linear interpolation from the previous grid $\{\bm{p}_i\}$, using the positions of the unbuckled meshes, $\{\bm{n'}_i\}$ and $\{\bm{p'}_i\}$.
-For each node of the new grid, $\bm{n'}_i$, the triangle that contains it is first identified, which we will denote $\{\bm{p'}_1,\bm{p'}_2,\bm{p'}_3\}$, and the barycentric coordinates of the point are computed, $\{\lambda_1,\lambda_2,\lambda_3\}$.
-The new position is then given by $\bm{n}_i = \lambda_1 \bm{p}_1 + \lambda_2 \bm{p}_2 + \lambda_3 \bm{p}_3$.
-
-In the example with different resolutions for the two states, the distance is obtained by first mapping the phase field from the higher resolution grid, $\{\phi_{k,l} | k,l \in \{0,1,\cdots,399\}\}$, to the low resolution grid, $\{\phi'_{i,j} | i,j \in \{0,1,\cdots,199\}\}$.
-Because a square grid is used with a resolution ratio of two, the mapping involves averaging each 2x2 block to a single point:
-\begin{equation}
-  \phi'_{i,j} = \frac{1}{4} \left( \phi_{2i,2j} + \phi_{2i+1,2j} + \phi_{2i,2j+1} + \phi_{2i+1,2j+1} \right)
-\end{equation}
-Then the separation from the other state, $\{\widetilde{\phi}_{i,j}\}$ is computed using the 2-norm,
-\begin{equation}
-  d = \sqrt{\sum_{i,j} \left( \phi'_{i,j} - \widetilde{\phi}_{i,j} \right)^2}.
-\end{equation}
-Finally, the gradient of the distance with respect to each point must be mapped back to the higher-resolution grid, which is done by assigning a quarter of each component back to its the original four points:
-\begin{equation}
-  \frac{\partial d}{\partial \phi_{k,l}} =
-    \frac{\partial \phi'_{i,j}}{\partial \phi_{k,l}} \frac{\partial d}{\partial \phi'_{i,j}} =
-    \frac{1}{4} \frac{\partial d}{\partial \phi'_{i,j}} =
-    \frac{1}{4} \frac{\phi'_{i,j} - \widetilde{\phi}_{i,j}}{d},
-\end{equation}
-where $k \in \{2i, 2i+1\}$, and $l \in \{2j, 2j+1\}$.
-
-\newpage
-\section{Additional results: DNEB speed comparison}
-\Cref{fig:DNEBspeedtest} shows the results for the speed test in comparison with DNEB.
-Similar to the results for the string method, the slope of BITSS is greater than DNEB with 10 or 20 states, indicating a faster convergence.
-Furthermore, with the exception of the seven-particle cluster, DNEB is also much less accurate at approximating the transition state, even with a large number of images.
-So it will require a secondary method to accurately locate the transition state, while BITSS does not.
-
-\begin{figure}[htb]
-  \includegraphics{fig/DNEBspeedtest.pdf}
-  \caption{\label{fig:DNEBspeedtest}
-    The convergence to the transition state as a function of the number of gradient calculations using the BITSS (black line) and DNEB for (a) a Lennard-Jones seven-particle cluster, (b) cylindrical shell buckling, and (c) wetting of a chemically-striped surface.
-    DNEB is repeated with a differing number of images along the chain, the number of which is listed in the legend in (c).
-    The shown configurations correspond to the two minimum energy states and the transition state, marked by an asterisk.
-  }
-\end{figure}
 

### 2022-03-31 manuscript.tex
Moved discontinuous details to methods. Added discussion of discontinuous landscape

@@
 Finally, we investigate the application of BITSS to systems with undefined gradients, such as when the landscape is discontinuous.
-In this case a couple of alterations to the method must be made.
-First, the gradients in \cref{eq:kd} are ill-defined, so $\kappa_d$ can be calculated using just the second term in the equation.
-Next we must use a minimiser that does not require a differentiable optimisation function; for this we use simulated annealing \cite{Kirkpatrick1983}.
-This has a chance of randomly jumping one state over the dividing barrier, but we can reduce this probability by limiting the initial temparature and maximum random displacement.
-We typically employ $T_0 = E_B / 10$, and $d_\text{max} = d(\bm{x}_1, \bm{x}_2) / 100$.
+A couple of changes are necessary to account for this, as detailed in the methods section.
 This has been tested using a Lennard-Jones 7-particle cluster with hard cores, resulting in a discontinuous landscape.
 Using the gradient-free approach, BITSS is able to successfully find the transition states, allowing us to plot the disconnectivity graph of the system, shown in \cref{fig:flatdiscontinuous}b.
-A comparison with the results for the standard Lennard-Jones cluster is given in the supplementary information \cite{Note1}.
-It is worth noting, however, that a gradient-based approach is significantly more efficient, and so should be preferred if possible.
+Compared with the results for the standard Lennard-Jones cluster, the energies of the minima are largely unchanged, but the energies of the transition states are found to be slightly higher.
+This indicates that the particles in the Lennard-Jones cluster cut the corner slightly as they transition, whereas this is not possible using the discontinuous potential, resulting in higher energies.
+Despite this gradient-free method being feasible, it is worth noting that a gradient-based approach is significantly more efficient, and so should be preferred if possible.
 
@@
 \subsection{BITSS: Changes for undefined gradients}
+A couple of alterations to the method must be made to account for situations where the gradients are unknown.
+First, the gradients in \cref{eq:kd} are ill-defined.
+Instead, $\kappa_d$ can be calculated using just the second term in the equation.
+Secondly, L-BFGS can no longer be used because it requires knowledge of the gradients.
+We must instead use a minimiser that does not require a differentiable optimisation function, for which we use simulated annealing \cite{Kirkpatrick1983}.
+This has a chance of randomly jumping one state over the dividing barrier, but we can reduce this probability by limiting the initial temparature and maximum random displacement.
+We typically employ $T_0 = E_B / 10$, and $d_\text{max} = d(\bm{x}_1, \bm{x}_2) / 100$.
 

### 2022-03-31 si/supplementary_information.tex
Moved discontinuous details to methods. Added discussion of discontinuous landscape

@@
 
-\newpage
-
-\section{Additional results: Seven-particle cluster comparison}
-\Cref{fig:clusterdgraphs} shows the comparison between the energies of the minima and transition states for the seven-particle cluster.
-Notably the energies of the minima are largely unchanged, but the energies of the transition states are found to be slightly higher when using the discontinuous potential.
-This indicates that the particles in the Lennard-Jones cluster cut the corner slightly as they transition, whereas this is not possible using the discontinuous potential, resulting in higher energies.
-
-\begin{figure}[htb]
-  \includegraphics{fig/clusterdgraphs.pdf}
-  \caption{\label{fig:clusterdgraphs}
-    Differences in the disconnectivity graphs for the seven-particle cluster when using the discontinuous potential instead of the standard Lennard-Jones potential.
-    The two graphs are horizontally offset for visibility.
-  }
-\end{figure}
-
 \end{document}

### 2022-03-31 fig/make_BAHschematic/plot.tex
Moved example system details to methods

\documentclass{standalone}
\usepackage{bm}
\usepackage{tikz}
\usetikzlibrary{calc}
\usetikzlibrary{angles,quotes}

\begin{document}
\begin{tikzpicture}[x=2cm, y=2cm, z={(0.25,-0.433)}, >=latex]
  % Nodes
  \node[label=$\bm{x}_1$] (x1) at (0, 0, 0) {};
  \node[label=$\bm{x}_2$] (x2) at (1, 0.5, -0.5) {};
  \node[label=below:$\bm{x}_3$] (x3) at (1, 0.5, 0.5) {};
  \node[label=$\bm{x}_4$] (x4) at (2, 0, -0.1) {};
  \fill (x1) circle (5pt);
  \fill (x2) circle (5pt);
  \fill (x3) circle (5pt);
  \fill (x4) circle (5pt);

  % Bonds
  \draw[thick] (x1) -- (x2);
  \draw[thick] (x1) -- (x3);
  \draw[thick] (x2) -- (x3);
  \draw[thick] (x2) -- (x4);
  \draw[thick] (x3) -- (x4);

  % Heights
  \coordinate (x23) at ($(x2)!0.5!(x3)$);
  \draw[<->,blue,very thick] (x23) -- node[label={[fill=white,inner sep=0pt,rounded corners=4pt,shift={(0.3,-0.15)}]$h_a$}] {} (x1);
  \draw[<->,blue,very thick] (x23) -- node[label={[fill=white,inner sep=0pt,rounded corners=4pt,shift={(-0.1,-0.22)}]$h_b$}] {} (x4);

  % Bond length
  \draw[<->,red,very thick] (x2) -- node[above right,fill=white,inner sep=1pt,rounded corners=4pt] {$r$} (x3);

  % Normals
  \coordinate (na0) at ($0.33*(x1)+0.33*(x2)+0.33*(x3)$);
  \coordinate (nb0) at ($0.33*(x2)+0.33*(x3)+0.33*(x4)$);
  \coordinate (na1) at ($ (na0)!1!-90:(x1) $);
  \coordinate (nb1) at ($ (nb0)!1!90:(x4) $);
  \draw[->,purple,very thick] (na0) -- (na1) node[left] {$\bm{\hat{n}}_a$};
  \draw[->,purple,very thick] (nb0) -- (nb1) node[right] {$\bm{\hat{n}}_b$};

  % Angle
  \pic [draw,"$\theta$"{shift=(18:0.4)},orange,very thick,angle radius=1.3cm,angle eccentricity=1.15] {angle = x1--x23--x4};
\end{tikzpicture}
\end{document}

### 2022-03-31 manuscript.tex
Moved example system details to methods

@@
 This has two possible states, with the droplet either upon one hydrophilic stripe, or straddling across two.
-The details about how these systems are modelled are included in the methods section.
+These systems have 14, 35400, and 40000 degrees of freedom, respectively.
+Details about how they are modelled are included in the methods section.
 
@@
 \subsection{Particle cluster system}
-The interaction between each pair of particles uses the Lennard-Jones potential,
-\begin{equation}
-  E = 4\epsilon \left[ \left(\frac{\sigma}{r}\right)^{12} - \left(\frac{\sigma}{r}\right)^6 \right],
-\end{equation}
-where $r$ is the particle separation, $\epsilon$ is the interaction strength, and $\sigma$ is the particle size.
+In the particle cluster example system, the Lennard-Jones potential is used for the interaction between each pair of particles.
+Therefore, the potential and its gradient for each pair of particles are
+\begin{gather}
+  E = 4\epsilon \left[ \left(\frac{\sigma}{r}\right)^{12} - \left(\frac{\sigma}{r}\right)^6 \right], \\
+  \frac{\partial E}{\partial \bm{x}_1} = -\frac{\partial E}{\partial \bm{x}_2} =
+    \frac{24 \epsilon (\bm{x}_2 - \bm{x}_1)}{r^2} \left[ 2 \left(\frac{\sigma}{r}\right)^{12} - \left(\frac{\sigma}{r}\right)^6 \right],
+\end{gather}
+where $\bm{x}_1$ and $\bm{x}_2$ are the positions of the two particles, $r$ is their separation, $\epsilon$ is the interaction strength, and $\sigma$ is the particle radius.
 
 \subsection{Cylindrical buckling system}
-A 2D triangular mesh with 35400 degrees of freedom is used to model this system, with the following energy function,
+A 2D triangular mesh is used to model the cylindrical buckling system, with the ends of the cylinder fixed in place to apply an axial compression of 0.14\%.
+The energy of the system is evaluated by treating all bonds in the mesh as an elastic spring to obtain the stretching energy, and all pairs of adjacent triangles to be connected by elastic hinges, providing the bending energy.
 \begin{equation}
@@
 \end{equation}
-The first term provides the stretching energy for the system using a sum over all the bonds, where $r_i$ is the length, $r^0_i$ is the equilibrium length, and $k^S_i$ is the stretching rigidity of bond $i$.
-The second term models the bending energy by representing each pair of adjacent triangles as an elastic hinge.
-For hinge $j$, $\theta_j$ is the dihedral angle, $\theta^0_j$ is the equilibrium angle, and $k^B_j$ is the bending rigidity.
+The first term is the stretching energy, where $r_i$ is the length, $r^0_i$ is the equilibrium length, and $k^S_i$ is the stretching rigidity of bond $i$.
+The second term provides the bending energy, where $\theta_j$ is the dihedral angle, $\theta^0_j$ is the equilibrium angle, and $k^B_j$ is the bending rigidity of hinge $j$.
+
+\begin{figure}[htb]
+  \includegraphics{fig/BAHschematic.pdf}
+  \caption{\label{fig:BAHschematic}
+    Schematic of the bar and hinge model showing the relevent parameters for a single hinge element. $h_i$ and $\bm{\hat{n}}_i$ denote the height and unit normal of each triangle respectively.
+  }
+\end{figure}
+The gradient of the energy can be obtained by individually considering the stretching and bending energies of a single bond and hinge.
+For simplicity we will ignore the index for the bond and hinge.
+Using the variables shown in the schematic in \cref{fig:BAHschematic}, the gradient of the stretching energy of the bond between $\bm{x}_2$ and $\bm{x}_3$ is given by,
+\begin{equation}
+  \frac{\partial E^S}{\partial \bm{x}_2} = - \frac{\partial E^S}{\partial \bm{x}_3} = 
+    2 k^S (r - r^0) (\bm{x_2} - \bm{x_3}).
+\end{equation}
+The gradients of the bending energy of the hinge are,
+\begin{align}
+  \frac{\partial E^B}{\partial \bm{x}_1} &= k^B \sin(\theta - \theta^0) \frac{\bm{\hat{n}}_a}{h_a}, \\
+  \frac{\partial E^B}{\partial \bm{x}_2} &= - k^B \sin(\theta - \theta^0) \left[\frac{\bm{\hat{n}}_a}{h_a} + \frac{\bm{\hat{n}}_a + \bm{\hat{n}}_b}{r}\right], \\
+  \frac{\partial E^B}{\partial \bm{x}_3} &= - k^B \sin(\theta - \theta^0) \left[\frac{\bm{\hat{n}}_b}{h_b} + \frac{\bm{\hat{n}}_a + \bm{\hat{n}}_b}{r}\right], \\
+  \frac{\partial E^B}{\partial \bm{x}_4} &= k^B \sin(\theta - \theta^0) \frac{\bm{\hat{n}}_b}{h_b}.
+\end{align}
 
 \subsection{Striped wetting system}
-This is modelled on a 200x200 2D grid using a phase-field model \cite{Panter2019b}, which has an order parameter, $\phi(\bm{r})$, representing the phase of the liquid ($\phi=-1$ for gas, $\phi=1$ for liquid).
+The  is modelled on a 200x200 2D grid using a phase-field model \cite{Panter2019b}, which has an order parameter, $\phi(\bm{r})$, representing the phase of the liquid ($\phi=-1$ for gas, $\phi=1$ for liquid).
 The energy functional has four separate terms,
@@
 Finally, $E^V$ constrains the volume of the liquid drop by penalising any variation from the target volume.
-For further details and the gradients of the potentials see the supplementary information \cite{Note1}.
+
+These four sections of the phase-field model are obtained using the following equations,
+\begin{align}
+  E^B[\phi] &= \sum_i \frac{1}{\epsilon} \left( \frac{{\phi_i}^4}{4} - \frac{{\phi_i}^2}{2} + \frac{1}{4} \right) \upDelta V,\\
+  E^I[\phi] &= \sum_i \frac{\epsilon}{2} \abs{\grad \phi_i}^2 \upDelta V,\\
+  E^S[\phi] &= \sum_j \sqrt{2}\cos\theta_j \left( \frac{{\phi_j}^3}{6} - \frac{\phi_j}{2} - \frac{1}{3} \right) \upDelta S,\\
+  E^V[\phi] &= k_V \left[ \sum_i \frac{\phi_i + 1}{2} \upDelta V - V_0 \right]^2,
+\end{align}
+where the index $i$ includes all of the nodes, while $j$ represents the nodes along the solid surface.
+$\upDelta V$ and $\upDelta S$ are, respectively, the volume and solid surface areas contained by each individual node.
+$\epsilon$ is the liquid-gas interface width, $\theta_j$ is the contact-angle with the solid surface, and $V_0$ is the constrained volume of the liquid drop.
+The strength of the volume constraint is parametrised by $k_V$ for which we use a value of $10^4$.
+The gradients of these terms are given by,
+\begin{align}
+  \frac{\partial E^B}{\partial \phi_i} &= \frac{1}{\epsilon} \left( {\phi_i}^3 - \phi_i \right) \upDelta V,\\
+  \frac{\partial E^I}{\partial \phi_i} &= \frac{\epsilon}{2} \left[
+    \frac{\partial \abs{\grad \phi_i}^2}{\partial \phi_i} +
+    \sum_k\frac{\partial \abs{\grad \phi_k}^2}{\partial \phi_i} \right] \upDelta V,\\
+  \frac{\partial E^S}{\partial \phi_j} &= \sqrt{2}\cos\theta_j \left( \frac{{\phi_j}^2}{2} - \frac{1}{2} \right) \upDelta S,\\
+  \frac{\partial E^V}{\partial \phi_i} &= k_V \left[ \sum_{i'} \frac{\phi_{i'} + 1}{2} \upDelta V - V_0 \right] \upDelta V,
+\end{align}
+where index $k$ denotes neighboring nodes at which the evaluation of the gradient uses $\phi_i$.
 

### 2022-03-31 si/supplementary_information.tex
Moved example system details to methods

@@
 
-\section{Test potentials and gradients}
-To use L-BFGS minisation the gradients of the optimisation function must be known.
-For the BITSS potential this is given by \cref{eq:gradBITSS}, but this also requires the gradients of the system under consideration.
-
-\subsection{Particle cluster}
-For the Lennard-Jones particle cluster the gradient of the potential is found by considering the gradient of the interaction between each pair of particles,
-\begin{equation}
-  \frac{\partial E}{\partial \bm{x}_1} = -\frac{\partial E}{\partial \bm{x}_2} = - \frac{24 \epsilon}{r^2}
-    \left[ 2 \left(\frac{\sigma}{r}\right)^{12} - \left(\frac{\sigma}{r}\right)^6 \right] (\bm{x}_1 - \bm{x}_2),
-\end{equation}
-where $\bm{x}_1$ and $\bm{x}_2$ are the positions of the two particles, $r$ is their separation, $\epsilon$ is the interaction strength, and $\sigma$ is the particle radius.
-
-\subsection{Cylindrical buckling}
-\begin{figure}[htb]
-  \includegraphics{fig/BAHschematic.pdf}
-  \caption{\label{fig:BAHschematic}
-    Schematic of the bar and hinge model showing the relevent parameters for a single hinge element. $h_i$ and $\bm{\hat{n}}_i$ denote the height and unit normal of each triangle respectively.
-  }
-\end{figure}
-For the cylindrical buckling example we can obtain the gradient by considering each bond and hinge individually.
-Using the variables shown in the schematic in \cref{fig:BAHschematic}, the gradient of the stretching energy of the bond between $\bm{x}_2$ and $\bm{x}_3$, with equilibrium length $r^0$ and stretching rigidity $k^S$, is given by,
-\begin{equation}
-  \frac{\partial E^S}{\partial \bm{x}_2} = - \frac{\partial E^S}{\partial \bm{x}_3} = 
-    2 k^S (r - r^0) (\bm{x_2} - \bm{x_3}).
-\end{equation}
-The gradients of the bending energy of the hinge, with equilibium angle $\theta^0$ and bending rigidity $k^B$, are,
-\begin{align}
-  \frac{\partial E^B}{\partial \bm{x}_1} &= k^B \sin(\theta - \theta^0) \frac{\bm{\hat{n}}_a}{h_a}, \\
-  \frac{\partial E^B}{\partial \bm{x}_2} &= - k^B \sin(\theta - \theta^0) \left[\frac{\bm{\hat{n}}_a}{h_a} + \frac{\bm{\hat{n}}_a + \bm{\hat{n}}_b}{r}\right], \\
-  \frac{\partial E^B}{\partial \bm{x}_3} &= - k^B \sin(\theta - \theta^0) \left[\frac{\bm{\hat{n}}_b}{h_b} + \frac{\bm{\hat{n}}_a + \bm{\hat{n}}_b}{r}\right], \\
-  \frac{\partial E^B}{\partial \bm{x}_4} &= k^B \sin(\theta - \theta^0) \frac{\bm{\hat{n}}_b}{h_b}.
-\end{align}
-
-\subsection{Striped wetting}
-The four sections of the phase-field model detailed in \namecref{eq:gradBITSS}~(7) are obtained using the following equations,
-\begin{align}
-  E^B[\phi] &= \sum_i \frac{1}{\epsilon} \left( \frac{{\phi_i}^4}{4} - \frac{{\phi_i}^2}{2} + \frac{1}{4} \right) \upDelta V,\\
-  E^I[\phi] &= \sum_i \frac{\epsilon}{2} \abs{\grad \phi_i}^2 \upDelta V,\\
-  E^S[\phi] &= \sum_j \sqrt{2}\cos\theta_j \left( \frac{{\phi_j}^3}{6} - \frac{\phi_j}{2} - \frac{1}{3} \right) \upDelta S,\\
-  E^V[\phi] &= k_V \left[ \sum_i \frac{\phi_i + 1}{2} \upDelta V - V_0 \right]^2,
-\end{align}
-where the index $i$ includes all of the nodes, while $j$ represents the nodes along the solid surface.
-$\upDelta V$ and $\upDelta S$ are, respectively, the volume and solid surface areas contained by each individual node.
-$\epsilon$ is the liquid-gas interface width, $\theta_j$ is the contact-angle with the solid surface, and $V_0$ is the constrained volume of the liquid drop.
-The strength of the volume constraint is parametrised by $k_V$ for which we use a value of $10^4$.
-The gradients of these terms are given by,
-\begin{align}
-  \frac{\partial E^B}{\partial \phi_i} &= \frac{1}{\epsilon} \left( {\phi_i}^3 - \phi_i \right) \upDelta V,\\
-  \frac{\partial E^I}{\partial \phi_i} &= \frac{\epsilon}{2} \left[
-    \frac{\partial \abs{\grad \phi_i}^2}{\partial \phi_i} +
-    \sum_k\frac{\partial \abs{\grad \phi_k}^2}{\partial \phi_i} \right] \upDelta V,\\
-  \frac{\partial E^S}{\partial \phi_j} &= \sqrt{2}\cos\theta_j \left( \frac{{\phi_j}^2}{2} - \frac{1}{2} \right) \upDelta S,\\
-  \frac{\partial E^V}{\partial \phi_i} &= k_V \left[ \sum_{i'} \frac{\phi_{i'} + 1}{2} \upDelta V - V_0 \right] \upDelta V,
-\end{align}
-where index $k$ denotes neighboring nodes at which the evaluation of the gradient uses $\phi_i$.
-
 \end{document}

### 2022-03-31 fig/create_figs.sh

@@ -1,10 +1,20 @@
 #!/bin/bash
 
-figures=('toy2d' 'speedtest' 'adaptivemesh' 'flatdiscontinuous')
+py_figs=('toy2d' 'speedtest' 'adaptivemesh' 'flatdiscontinuous')
+tex_figs=('BAHschematic')
 
-for fig in ${figures[@]}; do
+for fig in ${py_figs[@]}; do
   echo "Plotting $fig"
   cd make_$fig
   python3 ./plot.py
   cd ..
+done
+
+for fig in ${tex_figs[@]}; do
+  echo "Plotting $fig"
+  pdflatex -interaction=nonstopmode -file-line-error -jobname=$fig make_$fig/plot.tex | \
+    grep -v "[0-9]*/[0-9]*/[0-9]*/[0-9]*:[0-9]*:[0-9]*" | \
+    grep ".*:[0-9]*:\|Warning\|Overfull" --color=always
+  rm $fig.aux
+  rm $fig.log
 done

### 2022-03-31 manuscript.tex
Removed SI footnote

@@
 \end{gather}
-where $\grad E_1$ and $\grad E_2$ are the gradients of the energies of the two states, and $\alpha$ and $\beta$ are parameters with recommended values of $\alpha = 10$ and $\beta = 0.1$ (see supplementary information \footnote{See Supplemental Material at [URL] for derivations of the constraint coefficients, and extra details for the example systems}).
+where $\grad E_1$ and $\grad E_2$ are the gradients of the energies of the two states, and $\alpha$ and $\beta$ are parameters with recommended values of $\alpha = 10$ and $\beta = 0.1$ (see supplementary information).
 Here, $E_B$ is an estimation for the current energy barrier; evaluated using the difference between the highest energy along a linear interpolation between the two states and the average energy of the two states.
@@
 % \bibliography{bibexport.bib}
-% %\bibliography{../../library.bib}
+% % \bibliography{../../library.bib}
 %% mid bib
-\begin{thebibliography}{46}%
+\begin{thebibliography}{45}%
 \makeatletter
@@
   (\bibinfo {year} {1989})}\BibitemShut {NoStop}%
-\bibitem [{Note1()}]{Note1}%
-  \BibitemOpen
-  \bibinfo {note} {See Supplemental Material at [URL] for derivations of the
-  constraint coefficients, extra details for the example systems, results for
-  the speed test against DNEB, and a comparison of the discontinuous energy
-  landscape with the standard Lennard-Jones cluster}\BibitemShut {NoStop}%
 \bibitem [{\citenamefont {Kirkpatrick}\ \emph {et~al.}(1983)\citenamefont

### 2022-03-31 export_bib.sh

@@ -1,5 +1,7 @@
 #!/bin/bash
 
+# Extract bibliography into separate bib file
+
 AUXFILE="${1%.tex}.aux"
 if [ ! -f "$1" ]; then
   echo "File not found"
@@ -9,7 +11,8 @@ elif [ ! -f "$AUXFILE" ]; then
   exit 1
 fi
 
-bibexport -ns $AUXFILE
+# bibexport -ns $AUXFILE
+bibexport $AUXFILE
 # Remove empty lines, abstract, url, etc
 sed -i '/^\s*$/d' bibexport.bib
 remove_fields=('abstract' 'url' 'issn' 'isbn' 'annote' 'month')

### 2022-04-12 manuscript.tex
Put distance and pair energy in results. Made Jack's changes.

@@
 \begin{document}
-\title{Binary Image Transition State Search Method}
+\title{A Binary-Image Transition State Search Method}
 \author{Samuel J. Avis}
@@
   Existing methods, however, can struggle in problems with a large number of degrees of freedom, on-the-fly adaptive remeshing and coarse-graining, and energy landscapes that are locally flat or discontinuous.
-  To resolve these challenges, we introduce a new double-ended method, the Binary Image Transition State Search (BITSS).
+  To resolve these challenges, we introduce a new double-ended method, the Binary-Image Transition State Search (BITSS).
   It uses just two states that converge to the transition state, resulting in a fast, flexible, and memory-efficient method.
@@
 
+In this work we introduce a new method, the Binary-Image Transition State Search (BITSS), and using a range of different applications, we will demonstrate how BITSS addresses each of the above challenges.
+BITSS is a double-ended method that uses just two states that converge toward a transition state from either side, therefore combining aspects of the two traditional transition state search categories.
+Importantly, unlike other double-ended methods, BITSS does not require any initial interpolation.
+
+\section{Results and discussion}
+\subsection{BITSS method in a nutshell}
+
 \begin{figure}[htb]
@@
 
-In this work we introduce a new method, the Binary Image Transition State Search (BITSS), and using a range of different applications, we will demonstrate how BITSS addresses each of the above challenges.
-BITSS is a double-ended method that uses just two states that converge toward a transition state from either side, therefore combining aspects of the two traditional transition state search categories.
-Importantly, unlike other double-ended methods, BITSS does not require any initial interpolation.
+The method begins by first initialising the states, $\bm{x}_1$ and $\bm{x}_2$, in the basins of attraction of different local minima, such as the two blue spots in the 2d example potential in \cref{fig:toy2d}a.
+These can be set to the minima, but this is not a necessary requirement.
+The energies of these two states are then minimised, while constraining their separation.
+This is iteratively reduced to zero, such that, at iteration $i$, their separation is
+\begin{equation}\label{eq:diteration}
+  d_i = (1 - f) d_{i-1}.
+\end{equation}
+With $d_0$ as the separation between the two initial states.
+A reduction factor of $f = 0.5$ is succesful for most applications, but this can be made smaller to ensure that the states do not slide off the ridge between the two basin of attraction.
+To further ensure that neither state is pulled over the ridge, a secondary constraint enforces equal energies for the two states.
+Using this strategy, the two states will meet at the lowest point on the ridge - the transition state.
 
-\section{Results and discussion}
-\subsection{BITSS method in a nutshell}
-The method begins by first initialising the states, $\bm{x}_1$ and $\bm{x}_2$, in the basins of attraction of different local minima.
-These can be set to the minima, but this is not a necessary requirement.
-The energies of these two states are then minimised, while constraining their separation, which is iteratively reduced to zero.
-This results in the two states meeting at the lowest point on the ridge between the two basin of attraction - the transition state.
-To ensure that neither state is pulled over the ridge, a secondary constraint enforces equal energies for the two states.
-These two constraints are implemented using energy penalty terms, which result in driving forces on the two states if the constraints are not met, such as in \cref{fig:toy2d}b.
+The two constraints are implemented using energy penalty terms, which result in driving forces on the two states if the constraints are not met, such as in \cref{fig:toy2d}b.
+Including these energy penalty terms gives the following total energy for the pair of states,
+\begin{multline}\label{eq:bitss}
+  E_\text{BITSS}(\bm{x}_1, \bm{x}_2) = E_1 + E_2
+    + \kappa_e \left( E_1 - E_2 \right) ^2 \\
+    + \kappa_d \left( \mathrm{d}(\bm{x}_1, \bm{x}_2) - d_i \right) ^2,
+\end{multline}
+where $E_1$ and $E_2$ are the single state energies, $\kappa_e$ and $\kappa_d$ parametrise the strengths of the energy and distance constraints, and $\mathrm{d}(\bm{x}_1, \bm{x}_2)$ is the measure of distance between the two states.
+In this work the L-BFGS algorithm is chosen to minimise this energy, owing to its fast convergence and low memory requirement for large numbers of degrees of freedom \cite{Liu1989}.
+However, any other minimisation method can be used instead.
 
@@
 \begin{enumerate}[noitemsep,nolistsep]
-  \item Reduce the constrained separation.
+  \item Reduce the constrained separation, according to \cref{eq:diteration}.
   \item Compute the constraint coefficients.
-  \item Minimise the potential of the pair of states, including energy penalty terms, while recomputing the coefficients at regular intervals.
+  \item Minimise the potential of the pair of states, \cref{eq:bitss}, while recomputing the coefficients at regular intervals.
 \end{enumerate}
-See the methods section for further details of each step.
+For details about computing the constraint coefficients see the methods section.
 This process is completed once a suitable convergence criterion is reached.
-This can either be based upon the separation between the states, or the size of gradient at the midpoint between the states.
+This can either be based upon the separation between the states, or the size of gradient at the midpoint between them.
 
@@
 
-Once BITSS has identified the transition state, it is possible to find the full minimum energy pathway.
-This is done by tracing the trajectory of downhill minimisations from the two final states either side of the transition state.
+Once BITSS has identified the transition state, it is possible to find the full minimum energy pathway by tracing the trajectory of downhill minimisations from the two final states, either side of the transition state.
 In the case where there is a chain of transition states between the two starting minima, BITSS will identify the transition state with the highest energy in the chain.
-If, instead, all of transition states or the full pathway are desired, BITSS can be continually repeated from one of the minima downhill from the located transition state and one of the initial minima until the desired minima are piecewise connected.
+If all of transition states or the full pathway are desired instead, BITSS can be continually repeated from one of the minima downhill from the located transition state and one of the initial minima until the initial minima are piecewise connected by a full pathway.
 
@@
 This has two possible states, with the droplet either upon one hydrophilic stripe, or straddling across two.
-These systems have 14, 35400, and 40000 degrees of freedom, respectively.
-Details about how they are modelled are included in the methods section.
+Each of these are modelled using very different systems with \num{14}, \num{35400}, and \num{40000} degrees of freedom, respectively.
+The details about how they are modelled are included in the methods section.
 
@@
 
-Firstly, we show in \cref{fig:adaptivemesh}a that BITSS is able to handle the discretisation adapting as the method runs (changing number of degrees of freedom).
-For this we use the cylindrical buckling example with the resolution increasing from 40 to 100 triangles around the cylinder.
-These changes are performed after the minimisation step in each iteration of the BITSS method.
-This demonstrates that BITSS is able to converge to the transition state so long as the remeshing does not change the energy landscape of interest.
+Firstly, we show in \cref{fig:adaptivemesh}a that BITSS is able to handle the discretisation adapting, and the number of degrees of freedom changing, as the method runs.
+For this we use the cylindrical buckling example with the resolution increasing from 40 to 100 triangles around the cylinder, corresponding to an increase from \num{1760} to \num{11000} degrees of freedom.
+This demonstrates that BITSS is able to converge to the transition state so long as the remeshing is not so significant as to shift a state into the basin of attraction of the other minima.
 
-In the second test, \cref{fig:adaptivemesh}b, we demonstrate the use of different meshes for the two states in the striped wetting example.
+In the second test, shown in \cref{fig:adaptivemesh}b, we demonstrate the use of different meshes for the two states in the striped wetting example.
 In this case, the distance measure is adapted by interpolating one state onto the other mesh and computing the Euclidean distance.
@@
 
-The final challenges we will address are those related to complex landscapes.
+The final challenges we will address are those related to complex landscapes that prove challenging for previous algorithms.
 The first is the presence of flat regions in the landscape.
@@
 Finally, we investigate the application of BITSS to systems with undefined gradients, such as when the landscape is discontinuous.
-A couple of changes are necessary to account for this, as detailed in the methods section.
+To account for this, the equations for the coefficients must be adapted to not depend upon the gradients, and a gradient-free minimiser (simulated annealing) is used.
+These changes are detailed in the methods section.
 This has been tested using a Lennard-Jones 7-particle cluster with hard cores, resulting in a discontinuous landscape.
@@
 In conclusion, we have demonstrated a novel method for finding transition states that tackles problems not currently addressed by existing methods.
-The method is shown to be more efficient than existing double-ended methods, both in memory and computational cost, with further reductions possible by utilising adaptive remeshing techniques.
+The method is shown to be more efficient than existing double-ended methods, both in memory and computational cost, and we have demonstrated that it is possible to utilise adaptive remeshing techniques to further reduce the computational cost.
 It can also be adapted to problems with complex energy landscapes, including those with flat or discontinuous regions.
@@
 \section{Methods}
-\subsection{BITSS: Distance constraint}
-The value of the separation constraint is incrementally reduced such that, at iteration $i$, it is given by
-\begin{equation}\label{eq:diteration}
-  d_i = (1 - f) d_{i-1},
-\end{equation}
-with $d_0$ the separation between the two initial states.
-This fractional reduction ensures that as the two states approach the transition state they are not likely to undergo a sudden jump that will send them into the opposite basin.
-A factor of $f = 0.5$ is succesful for most applications, but this can be made smaller to ensure that the states do not slide off the ridge.
-
-\subsection{BITSS: Total potential}
-The total energy of the pair of states, including energy penalty terms for the constraints, is given by
-\begin{multline}\label{eq:bitss}
-  E_\text{BITSS}(\bm{x}_1, \bm{x}_2) = E_1 + E_2
-    + \kappa_e \left( E_1 - E_2 \right) ^2 \\
-    + \kappa_d \left( \mathrm{d}(\bm{x}_1, \bm{x}_2) - d_i \right) ^2,
-\end{multline}
-where $E_1$ and $E_2$ are the single state energies, $\kappa_e$ and $\kappa_d$ parametrise the strengths of the energy and distance constraints, and $\mathrm{d}(\bm{x}_1, \bm{x}_2)$ is the measure of distance between the two states.
-In this work the L-BFGS algorithm is chosen to minimise this energy, owing to its fast convergence and low memory requirement for large numbers of degrees of freedom \cite{Liu1989}.
-However, any other minimisation method can be used instead.
-
 \subsection{BITSS: Constraint coefficients}
@@
 Here we provide the details for the interpolations and mapping involved in the two examples demonstrating the feasibility of using an adaptive discretisation method.
-In the examples demonstrating the feasibility of using adaptive 
-For the cylindrical buckling example with a changing mesh, the resolution is refined each time the separation between the two states is halved. 
+For the cylindrical buckling example with a changing mesh, the resolution is refined each time the separation between the two states has halved, and is performed at the end of each iteration of the BITSS method.
 This involves the number of triangles around the circumference of the cylinder increasing along the sequence: $40 \rightarrow 60 \rightarrow 80 \rightarrow 100$; with the number of degrees of freedom increasing by: $1760 \rightarrow 3960 \rightarrow 7040 \rightarrow 11000$.

### 2022-04-13 manuscript.tex
Jack's changes

@@
 \begin{document}
-\title{A Binary-Image Transition State Search Method}
+\title{A fast and memory-efficient transition state search method for complex energy landscapes}
 \author{Samuel J. Avis}
@@
 Historically, many computational methods for locating transition states have grown from an atomistic or particulate perspective.
-These have proven to be important tools for understanding, for example, protein folding \cite{Bryngelson1995,Onuchic1997}, biological and industrial catalysis \cite{Boehr2006,Kerns2015,Guo2018a}, quantum tunneling \cite{Richardson2016,Vaillant2019}, crystallisation \cite{Richard2018}, and cluster formation \cite{Wales1998,Wales2012}.
+These have proven to be important tools for understanding, for example, protein folding \cite{Bryngelson1995,Onuchic1997}, biological and industrial catalysis \cite{Boehr2006,Kerns2015,Guo2018a}, quantum tunnelling \cite{Richardson2016,Vaillant2019}, crystallisation \cite{Richard2018}, and cluster formation \cite{Wales1998,Wales2012}.
 
@@
 Single-ended methods are not well suited for identifying specific pathways and can spend a large amount of time searching for undesired transition states.
-Another major challenge in studying complex energy landscapes relates to the presence of locally flat or discontinous regions, such as when considering patchy \cite{McMullen2018,Nguemaha2018,Chen2018b} and hard-body \cite{Richard2018,Santra2018} interactions in atomistic simulations, systems of polymer chains \cite{Mokkonen2016}, or collision constraints for macroscopic objects \cite{Wriggers2006}.
+Another major challenge in studying complex energy landscapes relates to the presence of locally flat or discontinuous regions, such as when considering patchy \cite{McMullen2018,Nguemaha2018,Chen2018b} and hard-body \cite{Richard2018,Santra2018} interactions in atomistic simulations, systems of polymer chains \cite{Mokkonen2016}, or collision constraints for macroscopic objects \cite{Wriggers2006}.
 Flat zero-modes in the landscape pose issues for single-ended search methods that rely only upon local information.
@@
 With $d_0$ as the separation between the two initial states.
-A reduction factor of $f = 0.5$ is succesful for most applications, but this can be made smaller to ensure that the states do not slide off the ridge between the two basin of attraction.
+A reduction factor of $f = 0.5$ is successful for most applications, but this can be made smaller to ensure that the states do not slide off the ridge between the two basin of attraction.
 To further ensure that neither state is pulled over the ridge, a secondary constraint enforces equal energies for the two states.
@@
 where $E_1$ and $E_2$ are the single state energies, $\kappa_e$ and $\kappa_d$ parametrise the strengths of the energy and distance constraints, and $\mathrm{d}(\bm{x}_1, \bm{x}_2)$ is the measure of distance between the two states.
+
 In this work the L-BFGS algorithm is chosen to minimise this energy, owing to its fast convergence and low memory requirement for large numbers of degrees of freedom \cite{Liu1989}.
 However, any other minimisation method can be used instead.
+
+To ensure that the transition state is located successfully, the constraint strengths $\kappa_d$ and $\kappa_e$ are updated as the algorithm proceeds using information from the system.
+They are initially calculated at the start of each minimisation, and regularly recalculated throughout (once per 100 iterations is used in this work).
+They are set using the following equations such that each term in the gradient of \cref{eq:bitss} is of a similar size,
+\begin{gather}
+  \kappa_e = \frac {\alpha} {2 E_B},
+  \label{eq:ke}
+  \\
+  \kappa_d = \max \left(
+    \frac {\sqrt{\abs{\grad E_1}^2 + \abs{\grad E_2}^2}} {2\sqrt{2} \beta d_i} \; , \;
+    \frac{E_B}{\beta d_i^2} \right),
+  \label{eq:kd}
+\end{gather}
+where $\grad E_1$ and $\grad E_2$ are the gradients of the energies of the two states, and $\alpha$ and $\beta$ are parameters with recommended values of $\alpha = 10$ and $\beta = 0.1$ (see supplementary information).
+Here, $E_B$ is an estimation for the current energy barrier; evaluated using the difference between the highest energy along a linear interpolation between the two states and the average energy of the two states.
+
+In practice, when numerically minimising, the states will jump about slightly which can result in large gradients perpendicular to the optimal movement direction.
+To reduce this effect, the gradients used in \cref{eq:kd} are projected in the direction of the separation between the two states:
+\begin{equation}
+  \abs{\grad E_n} \approx \frac {\abs{(\bm{x}_1 - \bm{x}_2) \cdot \grad E_n}} {\abs{\bm{x}_1 - \bm{x}_2}}.
+\end{equation}
 
@@
 \end{figure*}
-As a result of the BITSS method using only two states it has the potential to be significantly faster than chain-of-states approaches which typically use tens of states.
-This is tested here by measuring the speed of convergence to the transition state for BITSS in comparison with the string method and DNEB for several representative examples.
-The first is a two-dimensional, seven-particle cluster, with a transition from a hexagonal cluster to a higher energy configuration.
-The second system is an elastic cylindrical shell with an applied axial strain.
-This undergoes a transition from an unbuckled state to a singly-dimpled state, which defines the minimum energy required for the cylinder to buckle \cite{Panter2019}.
+
+As a result of the BITSS method using only two states, it has the potential to be significantly faster than chain-of-states approaches which typically use tens of states.
+This is tested here by measuring the speed of convergence to the transition state for BITSS in comparison with the string method and DNEB for three diverse systems, exhibiting a broad range of energy landscapes.
+Details of each are presented in the methods section.
+
+The first system is a two-dimensional, seven-particle cluster, interacting via a Lennard-Jones pair potential.
+This is a frequently used test system for studying transition rates \cite{Wales2002,Passerone2001}.
+Here, the \num{14} degrees of freedom are the particle coordinates.
+The characteristic transition shown in \cref{fig:speedtest}a sees a particle rearrangement between two close-packed clusters.
+
+The second system is an elastic cylindrical shell, modelled by a triangulated mesh of nodes, which interact via extensional and angular springs.
+The \num{35400} degrees of freedom are the node coordinates in three-dimensional space.
+The characteristic transition in \cref{fig:speedtest}b shows the formation of a stable dimple from an initially unbuckled cylinder.
+This transition is essential to capture to predict mechanical failure under strain \cite{Panter2019,Virot2017}.
+
 The final system involves a droplet situated on a chemically striped surface with both hydrophilic and hydrophobic regions.
-This has two possible states, with the droplet either upon one hydrophilic stripe, or straddling across two.
-Each of these are modelled using very different systems with \num{14}, \num{35400}, and \num{40000} degrees of freedom, respectively.
-The details about how they are modelled are included in the methods section.
+Droplet transitions on patterned surfaces are vital to understand as powerful bio-inspired liquid manipulation strategies  \cite{Kusumaatmaja2006,Brown2016}.
+In the example shown in \cref{fig:speedtest}c, a droplet transitions from two hydrophilic patches to one patch.
+Here, the system is represented by a diffuse-interface model, in which the \num{40000} degrees of freedom are the local fluid compositions at each site of the discretised domain.
 
@@
 \section{Conclusion}
-In conclusion, we have demonstrated a novel method for finding transition states that tackles problems not currently addressed by existing methods.
-The method is shown to be more efficient than existing double-ended methods, both in memory and computational cost, and we have demonstrated that it is possible to utilise adaptive remeshing techniques to further reduce the computational cost.
-It can also be adapted to problems with complex energy landscapes, including those with flat or discontinuous regions.
-This method will enable the analysis of energy landscapes for new systems in both particulate and continuum applications, and increase the feasibility of such methods for large-scale, complex systems.
+Overall, we have developed the binary image transition state search (BITSS) algorithm for the efficient location of transition states in traditionally challenging landscapes.
+Principally, the demonstrated speed and memory-efficiency will be key as we move towards simulating systems with increasingly large numbers of degrees of freedom, such as in large biomolecules, or with increasingly fine resolution, such as in finite element domains.
+
+A second source of efficiency in the BITSS method comes from the ability to adaptively change the degrees of freedom as the algorithm proceeds.
+We demonstrated how transition states could be found by both increasing the resolution upon convergence, and coupling systems with different discretisations.
+The ease of coupling two copies of a system and adaptive remeshing, now leads to the possibility of incorporating BITSS into existing optimisation methods, such as surface evolver or finite element analysis software, to provide important energy barrier functionality.
+
+Finally, we showed how BITSS can be used to survey discontinuous energy landscapes, demonstrated for a system of attractive hard-core particles.
+This opens up possibilities for studying a broad range of systems previously out of reach of conventional landscape methods, but where transition information is valuable.
+These include systems with very short range interactions or contact forces, such as in colloidal clusters, wrinkling and buckling of elastic materials, or locomotion and environmental interaction in robotics.
+
+The distance metric between the two BITSS images proves interesting to analyse further in the future.
+One question that emerges is whether transition states can be located by coupling two images through a small number of collective properties, rather than the total distance between all degrees of freedom in the system.
+A second question is that for landscapes with multiple pathways between states, how can the distance metric be biased to access transition states different from the most direct one?
+Overall, these will enable BITSS to access even more challenging landscapes, and those not yet amenable to traditional landscape exploration techniques.
 
 \section{Methods}
-\subsection{BITSS: Constraint coefficients}
-To ensure that the transition state is located successfully, the constraint strengths $\kappa_d$ and $\kappa_e$ are updated as the algorithm proceeds using information from the system.
-They are initially calculated at the start of each minimisation, and regularly recalculated throughout (once per 100 iterations is used in this work).
-They are set using the following equations such that each term in the gradient of \cref{eq:bitss} is of a similar size,
-\begin{gather}
-  \kappa_e = \frac {\alpha} {2 E_B},
-  \label{eq:ke}
-  \\
-  \kappa_d = \max \left(
-    \frac {\sqrt{\abs{\grad E_1}^2 + \abs{\grad E_2}^2}} {2\sqrt{2} \beta d_i} \; , \;
-    \frac{E_B}{\beta d_i^2} \right),
-  \label{eq:kd}
-\end{gather}
-where $\grad E_1$ and $\grad E_2$ are the gradients of the energies of the two states, and $\alpha$ and $\beta$ are parameters with recommended values of $\alpha = 10$ and $\beta = 0.1$ (see supplementary information).
-Here, $E_B$ is an estimation for the current energy barrier; evaluated using the difference between the highest energy along a linear interpolation between the two states and the average energy of the two states.
-
-In practice, when numerically minimising, the states will jump about slightly which can result in large gradients perpendicular to the optimal movement direction.
-To reduce this effect, the gradients used in \cref{eq:kd} are projected in the direction of the separation between the two states:
-\begin{equation}
-  \abs{\grad E_n} \approx \frac {\abs{(\bm{x}_1 - \bm{x}_2) \cdot \grad E_n}} {\abs{\bm{x}_1 - \bm{x}_2}}.
-\end{equation}
 
@@
 %% mid bib
-\begin{thebibliography}{45}%
+\begin{thebibliography}{50}%
 \makeatletter
@@
   (\bibinfo {year} {1989})}\BibitemShut {NoStop}%
+\bibitem [{\citenamefont {Wales}(2002)}]{Wales2002}%
+  \BibitemOpen
+  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {D.~J.}\ \bibnamefont
+  {Wales}},\ }\href {https://doi.org/10.1080/00268970210162691} {\bibfield
+  {journal} {\bibinfo  {journal} {Molecular Physics}\ }\textbf {\bibinfo
+  {volume} {100}},\ \bibinfo {pages} {3285} (\bibinfo {year}
+  {2002})}\BibitemShut {NoStop}%
+\bibitem [{\citenamefont {Passerone}\ and\ \citenamefont
+  {Parrinello}(2001)}]{Passerone2001}%
+  \BibitemOpen
+  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {D.}~\bibnamefont
+  {Passerone}}\ and\ \bibinfo {author} {\bibfnamefont {M.}~\bibnamefont
+  {Parrinello}},\ }\href {https://doi.org/10.1103/PhysRevLett.87.108302}
+  {\bibfield  {journal} {\bibinfo  {journal} {Physical Review Letters}\
+  }\textbf {\bibinfo {volume} {87}},\ \bibinfo {pages} {108302} (\bibinfo
+  {year} {2001})}\BibitemShut {NoStop}%
+\bibitem [{\citenamefont {Virot}\ \emph {et~al.}(2017)\citenamefont {Virot},
+  \citenamefont {Kreilos}, \citenamefont {Schneider},\ and\ \citenamefont
+  {Rubinstein}}]{Virot2017}%
+  \BibitemOpen
+  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {E.}~\bibnamefont
+  {Virot}}, \bibinfo {author} {\bibfnamefont {T.}~\bibnamefont {Kreilos}},
+  \bibinfo {author} {\bibfnamefont {T.~M.}\ \bibnamefont {Schneider}},\ and\
+  \bibinfo {author} {\bibfnamefont {S.~M.}\ \bibnamefont {Rubinstein}},\ }\href
+  {https://doi.org/10.1103/PhysRevLett.119.224101} {\bibfield  {journal}
+  {\bibinfo  {journal} {Physical Review Letters}\ }\textbf {\bibinfo {volume}
+  {119}},\ \bibinfo {pages} {224101} (\bibinfo {year} {2017})}\BibitemShut
+  {NoStop}%
+\bibitem [{\citenamefont {Kusumaatmaja}\ \emph {et~al.}(2006)\citenamefont
+  {Kusumaatmaja}, \citenamefont {L{\'{e}}opold{\`{e}}s}, \citenamefont
+  {Dupuis},\ and\ \citenamefont {Yeomans}}]{Kusumaatmaja2006}%
+  \BibitemOpen
+  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {H.}~\bibnamefont
+  {Kusumaatmaja}}, \bibinfo {author} {\bibfnamefont {J.}~\bibnamefont
+  {L{\'{e}}opold{\`{e}}s}}, \bibinfo {author} {\bibfnamefont {A.}~\bibnamefont
+  {Dupuis}},\ and\ \bibinfo {author} {\bibfnamefont {J.~M.}\ \bibnamefont
+  {Yeomans}},\ }\href {https://doi.org/10.1209/epl/i2005-10452-0} {\bibfield
+  {journal} {\bibinfo  {journal} {Europhysics Letters}\ }\textbf {\bibinfo
+  {volume} {73}},\ \bibinfo {pages} {740} (\bibinfo {year} {2006})}\BibitemShut
+  {NoStop}%
+\bibitem [{\citenamefont {Brown}\ and\ \citenamefont
+  {Bhushan}(2016)}]{Brown2016}%
+  \BibitemOpen
+  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {P.~S.}\ \bibnamefont
+  {Brown}}\ and\ \bibinfo {author} {\bibfnamefont {B.}~\bibnamefont
+  {Bhushan}},\ }\href {https://doi.org/10.1098/rsta.2016.0135} {\bibfield
+  {journal} {\bibinfo  {journal} {Philosophical Transactions of the Royal
+  Society A}\ }\textbf {\bibinfo {volume} {374}},\ \bibinfo {pages} {20160135}
+  (\bibinfo {year} {2016})}\BibitemShut {NoStop}%
 \bibitem [{\citenamefont {Kirkpatrick}\ \emph {et~al.}(1983)\citenamefont

### 2022-04-14 manuscript.tex
Halim's changes

@@
-\documentclass[twocolumn,10pt]{revtex4-2}
+\documentclass[twocolumn,10pt]{revtex4}
 
@@
 BITSS is a double-ended method that uses just two states that converge toward a transition state from either side, therefore combining aspects of the two traditional transition state search categories.
-Importantly, unlike other double-ended methods, BITSS does not require any initial interpolation.
+In addition, unlike other double-ended methods, BITSS does not require any initial interpolation.
 
 \section{Results and discussion}
-\subsection{BITSS method in a nutshell}
-
+\subsection{BITSS method}
 \begin{figure}[htb]
@@
 
-The method begins by first initialising the states, $\bm{x}_1$ and $\bm{x}_2$, in the basins of attraction of different local minima, such as the two blue spots in the 2d example potential in \cref{fig:toy2d}a.
+The method begins by first initialising the states, $\bm{x}_1$ and $\bm{x}_2$, in the basins of attraction of different local minima, such as the two blue spots in the 2d potential in \cref{fig:toy2d}a.
 These can be set to the minima, but this is not a necessary requirement.
@@
 With $d_0$ as the separation between the two initial states.
-A reduction factor of $f = 0.5$ is successful for most applications, but this can be made smaller to ensure that the states do not slide off the ridge between the two basin of attraction.
+A reduction factor of $f = 0.5$ is successful for most applications, but this can be made smaller to ensure that the states do not slide off the ridge between the two basins of attraction.
+Different metrics may be used to compute the distance.
+%######
 To further ensure that neither state is pulled over the ridge, a secondary constraint enforces equal energies for the two states.
@@
 The two constraints are implemented using energy penalty terms, which result in driving forces on the two states if the constraints are not met, such as in \cref{fig:toy2d}b.
-Including these energy penalty terms gives the following total energy for the pair of states,
+Including these energy penalty terms gives the total BITSS energy for the pair of states,
 \begin{multline}\label{eq:bitss}
@@
   \item Reduce the constrained separation, according to \cref{eq:diteration}.
-  \item Compute the constraint coefficients.
-  \item Minimise the potential of the pair of states, \cref{eq:bitss}, while recomputing the coefficients at regular intervals.
+  \item Minimise the potential of the pair of states, \cref{eq:bitss}.
+  \item Recompute the constraint coefficients, $\kappa_e$ and $\kappa_d$, at regular intervals using \cref{eq:ke,eq:kd}.
 \end{enumerate}
-For details about computing the constraint coefficients see the methods section.
 This process is completed once a suitable convergence criterion is reached.
@@
 Firstly, the slope illustrates that the rate of convergence is indeed much greater for the BITSS method.
-It is matched only by the initial rate of the string method using less than ten images, however these soon slow and are relatively inaccurate.
-Secondly, the BITSS method can more accurately approximate the transition state by orders of magnitude, particularly for the wetting example where the string method does not significantly improve upon the initial pathway estimate.
+It is matched only by the initial rates of DNEB and the string method using fewer than ten images, however these soon slow and are relatively inaccurate.
+Secondly, the BITSS method can more accurately approximate the transition state by orders of magnitude, particularly for the wetting example where the other methods do not significantly improve upon the initial pathway estimate.
 Therefore, unlike these other double-ended methods, BITSS does not require a second approach to accurately locate the transition state.
@@
 \subsection{Adaptive discretisation}
+\label{sec:adaptive}
 \begin{figure}[tb]
@@
 A couple of alterations to the method must be made to account for situations where the gradients are unknown.
-First, the gradients in \cref{eq:kd} are ill-defined.
-Instead, $\kappa_d$ can be calculated using just the second term in the equation.
+First, the calculation of $\kappa_d$ in \cref{eq:kd} must be adapted to avoid the use of gradients.
+This can be done by simply removing the first term and just using the second term in the equation.
 Secondly, L-BFGS can no longer be used because it requires knowledge of the gradients.
@@
 \begin{equation}
-  \phi'_{i,j} = \frac{1}{4} \left( \phi_{2i,2j} + \phi_{2i+1,2j} + \phi_{2i,2j+1} + \phi_{2i+1,2j+1} \right)
+  \phi'_{i,j} = \frac{1}{4} \left( \phi_{2i,2j} + \phi_{2i+1,2j} + \phi_{2i,2j+1} + \phi_{2i+1,2j+1} \right).
 \end{equation}
-Then the separation from the other state, $\{\widetilde{\phi}_{i,j}\}$ is computed using the 2-norm,
+Then the separation from the other state, $\{\widetilde{\phi}_{i,j}\}$, is computed using the 2-norm,
 \begin{equation}
@@
 
-\subsection{Particle cluster system}
+\subsection{Energy and gradient expressions for the example systems}
+\subsubsection{Particle cluster system}
 In the particle cluster example system, the Lennard-Jones potential is used for the interaction between each pair of particles.
@@
 
-\subsection{Cylindrical buckling system}
+\subsubsection{Cylindrical buckling system}
 A 2D triangular mesh is used to model the cylindrical buckling system, with the ends of the cylinder fixed in place to apply an axial compression of 0.14\%.
 The energy of the system is evaluated by treating all bonds in the mesh as an elastic spring to obtain the stretching energy, and all pairs of adjacent triangles to be connected by elastic hinges, providing the bending energy.
+Their expressions are given by
 \begin{equation}
@@
 The gradient of the energy can be obtained by individually considering the stretching and bending energies of a single bond and hinge.
-For simplicity we will ignore the index for the bond and hinge.
+For simplicity, we will ignore the index for the bond and hinge.
 Using the variables shown in the schematic in \cref{fig:BAHschematic}, the gradient of the stretching energy of the bond between $\bm{x}_2$ and $\bm{x}_3$ is given by,
@@
 \end{equation}
-The gradients of the bending energy of the hinge are,
+The gradients of the bending energy of the hinge are
 \begin{align}
@@
 
-\subsection{Striped wetting system}
-The  is modelled on a 200x200 2D grid using a phase-field model \cite{Panter2019b}, which has an order parameter, $\phi(\bm{r})$, representing the phase of the liquid ($\phi=-1$ for gas, $\phi=1$ for liquid).
+\subsubsection{Striped wetting system}
+This modelled on a 200x200 2D grid (and 400x400 in \cref{sec:adaptive}) using a phase-field model \cite{Panter2019b}, which has an order parameter, $\phi(\bm{r})$, representing the phase of the liquid ($\phi=-1$ for gas, $\phi=1$ for liquid).
 The energy functional has four separate terms,
@@
 $\upDelta V$ and $\upDelta S$ are, respectively, the volume and solid surface areas contained by each individual node.
-$\epsilon$ is the liquid-gas interface width, $\theta_j$ is the contact-angle with the solid surface, and $V_0$ is the constrained volume of the liquid drop.
+$\epsilon$ is the liquid-gas interface width (set to 2.5 lattice units), $\theta_j$ is the contact-angle with the solid surface, and $V_0$ is the constrained volume of the liquid drop.
 The strength of the volume constraint is parametrised by $k_V$ for which we use a value of $10^4$.
@@
 \appendix
-
+\section*{}
 \begin{acknowledgments}
@@
 %% start bib
-% \bibliographystyle{apsrev4-2}
 % \bibliography{bibexport.bib}
 % % \bibliography{../../library.bib}
+% % \bibliographystyle{apsrev4}
 %% mid bib
-\begin{thebibliography}{50}%
-\makeatletter
-\providecommand \@ifxundefined [1]{%
- \@ifx{#1\undefined}
-}%
-\providecommand \@ifnum [1]{%
- \ifnum #1\expandafter \@firstoftwo
- \else \expandafter \@secondoftwo
- \fi
-}%
-\providecommand \@ifx [1]{%
- \ifx #1\expandafter \@firstoftwo
- \else \expandafter \@secondoftwo
- \fi
-}%
-\providecommand \natexlab [1]{#1}%
-\providecommand \enquote  [1]{``#1''}%
-\providecommand \bibnamefont  [1]{#1}%
-\providecommand \bibfnamefont [1]{#1}%
-\providecommand \citenamefont [1]{#1}%
-\providecommand \href@noop [0]{\@secondoftwo}%
-\providecommand \href [0]{\begingroup \@sanitize@url \@href}%
-\providecommand \@href[1]{\@@startlink{#1}\@@href}%
-\providecommand \@@href[1]{\endgroup#1\@@endlink}%
-\providecommand \@sanitize@url [0]{\catcode `\\12\catcode `\$12\catcode
-  `\&12\catcode `\#12\catcode `\^12\catcode `\_12\catcode `\%12\relax}%
-\providecommand \@@startlink[1]{}%
-\providecommand \@@endlink[0]{}%
-\providecommand \url  [0]{\begingroup\@sanitize@url \@url }%
-\providecommand \@url [1]{\endgroup\@href {#1}{\urlprefix }}%
-\providecommand \urlprefix  [0]{URL }%
-\providecommand \Eprint [0]{\href }%
-\providecommand \doibase [0]{https://doi.org/}%
-\providecommand \selectlanguage [0]{\@gobble}%
-\providecommand \bibinfo  [0]{\@secondoftwo}%
-\providecommand \bibfield  [0]{\@secondoftwo}%
-\providecommand \translation [1]{[#1]}%
-\providecommand \BibitemOpen [0]{}%
-\providecommand \bibitemStop [0]{}%
-\providecommand \bibitemNoStop [0]{.\EOS\space}%
-\providecommand \EOS [0]{\spacefactor3000\relax}%
-\providecommand \BibitemShut  [1]{\csname bibitem#1\endcsname}%
-\let\auto@bib@innerbib\@empty
-\bibitem [{\citenamefont {Bryngelson}\ \emph {et~al.}(1995)\citenamefont
-  {Bryngelson}, \citenamefont {Onuchic}, \citenamefont {Socci},\ and\
-  \citenamefont {Wolynes}}]{Bryngelson1995}%
-  \BibitemOpen
-  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {J.~D.}\ \bibnamefont
-  {Bryngelson}}, \bibinfo {author} {\bibfnamefont {J.~N.}\ \bibnamefont
-  {Onuchic}}, \bibinfo {author} {\bibfnamefont {N.~D.}\ \bibnamefont {Socci}},\
-  and\ \bibinfo {author} {\bibfnamefont {P.~G.}\ \bibnamefont {Wolynes}},\
-  }\href {https://doi.org/10.1002/prot.340210302} {\bibfield  {journal}
-  {\bibinfo  {journal} {Proteins: Structure, Function, and Bioinformatics}\
-  }\textbf {\bibinfo {volume} {21}},\ \bibinfo {pages} {167} (\bibinfo {year}
-  {1995})}\BibitemShut {NoStop}%
-\bibitem [{\citenamefont {Onuchic}\ \emph {et~al.}(1997)\citenamefont
-  {Onuchic}, \citenamefont {Luthey-Schulten},\ and\ \citenamefont
-  {Wolynes}}]{Onuchic1997}%
-  \BibitemOpen
-  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {J.~N.}\ \bibnamefont
-  {Onuchic}}, \bibinfo {author} {\bibfnamefont {Z.}~\bibnamefont
-  {Luthey-Schulten}},\ and\ \bibinfo {author} {\bibfnamefont {P.~G.}\
-  \bibnamefont {Wolynes}},\ }\href
-  {https://doi.org/10.1146/annurev.physchem.48.1.545} {\bibfield  {journal}
-  {\bibinfo  {journal} {Annual Review of Physical Chemistry}\ }\textbf
-  {\bibinfo {volume} {48}},\ \bibinfo {pages} {545} (\bibinfo {year}
-  {1997})}\BibitemShut {NoStop}%
-\bibitem [{\citenamefont {Boehr}\ \emph {et~al.}(2006)\citenamefont {Boehr},
-  \citenamefont {McElheny}, \citenamefont {Dyson},\ and\ \citenamefont
-  {Wrightt}}]{Boehr2006}%
-  \BibitemOpen
-  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {D.~D.}\ \bibnamefont
-  {Boehr}}, \bibinfo {author} {\bibfnamefont {D.}~\bibnamefont {McElheny}},
-  \bibinfo {author} {\bibfnamefont {H.~J.}\ \bibnamefont {Dyson}},\ and\
-  \bibinfo {author} {\bibfnamefont {P.~E.}\ \bibnamefont {Wrightt}},\ }\href
-  {https://doi.org/10.1126/science.1130258} {\bibfield  {journal} {\bibinfo
-  {journal} {Science}\ }\textbf {\bibinfo {volume} {313}},\ \bibinfo {pages}
-  {1638} (\bibinfo {year} {2006})}\BibitemShut {NoStop}%
-\bibitem [{\citenamefont {Kerns}\ \emph {et~al.}(2015)\citenamefont {Kerns},
-  \citenamefont {Agafonov}, \citenamefont {Cho}, \citenamefont {Pontiggia},
-  \citenamefont {Otten}, \citenamefont {Pachov}, \citenamefont {Kutter},
-  \citenamefont {Phung}, \citenamefont {Murphy}, \citenamefont {Thai},
-  \citenamefont {Alber}, \citenamefont {Hagan},\ and\ \citenamefont
-  {Kern}}]{Kerns2015}%
-  \BibitemOpen
-  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {S.~J.}\ \bibnamefont
-  {Kerns}}, \bibinfo {author} {\bibfnamefont {R.~V.}\ \bibnamefont {Agafonov}},
-  \bibinfo {author} {\bibfnamefont {Y.~J.}\ \bibnamefont {Cho}}, \bibinfo
-  {author} {\bibfnamefont {F.}~\bibnamefont {Pontiggia}}, \bibinfo {author}
-  {\bibfnamefont {R.}~\bibnamefont {Otten}}, \bibinfo {author} {\bibfnamefont
-  {D.~V.}\ \bibnamefont {Pachov}}, \bibinfo {author} {\bibfnamefont
-  {S.}~\bibnamefont {Kutter}}, \bibinfo {author} {\bibfnamefont {L.~A.}\
-  \bibnamefont {Phung}}, \bibinfo {author} {\bibfnamefont {P.~N.}\ \bibnamefont
-  {Murphy}}, \bibinfo {author} {\bibfnamefont {V.}~\bibnamefont {Thai}},
-  \bibinfo {author} {\bibfnamefont {T.}~\bibnamefont {Alber}}, \bibinfo
-  {author} {\bibfnamefont {M.~F.}\ \bibnamefont {Hagan}},\ and\ \bibinfo
-  {author} {\bibfnamefont {D.}~\bibnamefont {Kern}},\ }\href
-  {https://doi.org/10.1038/nsmb.2941} {\bibfield  {journal} {\bibinfo
-  {journal} {Nature Structural and Molecular Biology}\ }\textbf {\bibinfo
-  {volume} {22}},\ \bibinfo {pages} {124} (\bibinfo {year} {2015})}\BibitemShut
-  {NoStop}%
-\bibitem [{\citenamefont {Guo}\ \emph {et~al.}(2018)\citenamefont {Guo},
-  \citenamefont {Wang}, \citenamefont {Wang}, \citenamefont {Wang},\ and\
-  \citenamefont {Hu}}]{Guo2018a}%
-  \BibitemOpen
-  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {C.}~\bibnamefont
-  {Guo}}, \bibinfo {author} {\bibfnamefont {Z.}~\bibnamefont {Wang}}, \bibinfo
-  {author} {\bibfnamefont {D.}~\bibnamefont {Wang}}, \bibinfo {author}
-  {\bibfnamefont {H.~F.}\ \bibnamefont {Wang}},\ and\ \bibinfo {author}
-  {\bibfnamefont {P.}~\bibnamefont {Hu}},\ }\href
-  {https://doi.org/10.1021/acs.jpcc.8b06782} {\bibfield  {journal} {\bibinfo
-  {journal} {Journal of Physical Chemistry C}\ }\textbf {\bibinfo {volume}
-  {122}},\ \bibinfo {pages} {21478} (\bibinfo {year} {2018})}\BibitemShut
-  {NoStop}%
-\bibitem [{\citenamefont {Richardson}\ \emph {et~al.}(2016)\citenamefont
-  {Richardson}, \citenamefont {P{\'{e}}rez}, \citenamefont {Lobsiger},
-  \citenamefont {Reid}, \citenamefont {Temelso}, \citenamefont {Shields},
-  \citenamefont {Kisiel}, \citenamefont {Wales}, \citenamefont {Pate},\ and\
-  \citenamefont {Althorpe}}]{Richardson2016}%
-  \BibitemOpen
-  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {J.~O.}\ \bibnamefont
-  {Richardson}}, \bibinfo {author} {\bibfnamefont {C.}~\bibnamefont
-  {P{\'{e}}rez}}, \bibinfo {author} {\bibfnamefont {S.}~\bibnamefont
-  {Lobsiger}}, \bibinfo {author} {\bibfnamefont {A.~A.}\ \bibnamefont {Reid}},
-  \bibinfo {author} {\bibfnamefont {B.}~\bibnamefont {Temelso}}, \bibinfo
-  {author} {\bibfnamefont {G.~C.}\ \bibnamefont {Shields}}, \bibinfo {author}
-  {\bibfnamefont {Z.}~\bibnamefont {Kisiel}}, \bibinfo {author} {\bibfnamefont
-  {D.~J.}\ \bibnamefont {Wales}}, \bibinfo {author} {\bibfnamefont {B.~H.}\
-  \bibnamefont {Pate}},\ and\ \bibinfo {author} {\bibfnamefont {S.~C.}\
-  \bibnamefont {Althorpe}},\ }\href@noop {} {\bibfield  {journal} {\bibinfo
-  {journal} {Science}\ }\textbf {\bibinfo {volume} {351}},\ \bibinfo {pages}
-  {1310} (\bibinfo {year} {2016})}\BibitemShut {NoStop}%
-\bibitem [{\citenamefont {Vaillant}\ \emph {et~al.}(2019)\citenamefont
-  {Vaillant}, \citenamefont {Althorpe},\ and\ \citenamefont
-  {Wales}}]{Vaillant2019}%
-  \BibitemOpen
-  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {C.~L.}\ \bibnamefont
-  {Vaillant}}, \bibinfo {author} {\bibfnamefont {S.~C.}\ \bibnamefont
-  {Althorpe}},\ and\ \bibinfo {author} {\bibfnamefont {D.~J.}\ \bibnamefont
-  {Wales}},\ }\href {https://doi.org/10.1021/acs.jctc.8b00675} {\bibfield
-  {journal} {\bibinfo  {journal} {Journal of Chemical Theory and Computation}\
-  }\textbf {\bibinfo {volume} {15}},\ \bibinfo {pages} {33} (\bibinfo {year}
-  {2019})}\BibitemShut {NoStop}%
-\bibitem [{\citenamefont {Richard}\ and\ \citenamefont
-  {Speck}(2018)}]{Richard2018}%
-  \BibitemOpen
-  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {D.}~\bibnamefont
-  {Richard}}\ and\ \bibinfo {author} {\bibfnamefont {T.}~\bibnamefont
-  {Speck}},\ }\href {https://doi.org/10.1063/1.5016277} {\bibfield  {journal}
-  {\bibinfo  {journal} {The Journal of Chemical Physics}\ }\textbf {\bibinfo
-  {volume} {148}},\ \bibinfo {pages} {124110} (\bibinfo {year}
-  {2018})}\BibitemShut {NoStop}%
-\bibitem [{\citenamefont {Wales}\ \emph {et~al.}(1998)\citenamefont {Wales},
-  \citenamefont {Miller},\ and\ \citenamefont {Walsh}}]{Wales1998}%
-  \BibitemOpen
-  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {D.~J.}\ \bibnamefont
-  {Wales}}, \bibinfo {author} {\bibfnamefont {M.~A.}\ \bibnamefont {Miller}},\
-  and\ \bibinfo {author} {\bibfnamefont {T.~R.}\ \bibnamefont {Walsh}},\ }\href
-  {https://doi.org/10.1038/29487} {\bibfield  {journal} {\bibinfo  {journal}
-  {Nature}\ }\textbf {\bibinfo {volume} {394}},\ \bibinfo {pages} {758}
-  (\bibinfo {year} {1998})}\BibitemShut {NoStop}%
-\bibitem [{\citenamefont {Wales}(2012)}]{Wales2012}%
-  \BibitemOpen
-  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {D.~J.}\ \bibnamefont
-  {Wales}},\ }\href {https://doi.org/10.1098/rsta.2011.0208} {\bibfield
-  {journal} {\bibinfo  {journal} {Philosophical Transactions of the Royal
-  Society A: Mathematical, Physical and Engineering Sciences}\ }\textbf
-  {\bibinfo {volume} {370}},\ \bibinfo {pages} {2877} (\bibinfo {year}
-  {2012})}\BibitemShut {NoStop}%
-\bibitem [{\citenamefont {Panter}\ \emph
-  {et~al.}(2019{\natexlab{a}})\citenamefont {Panter}, \citenamefont {Chen},
-  \citenamefont {Zhang},\ and\ \citenamefont {Kusumaatmaja}}]{Panter2019}%
-  \BibitemOpen
-  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {J.~R.}\ \bibnamefont
-  {Panter}}, \bibinfo {author} {\bibfnamefont {J.}~\bibnamefont {Chen}},
-  \bibinfo {author} {\bibfnamefont {T.}~\bibnamefont {Zhang}},\ and\ \bibinfo
-  {author} {\bibfnamefont {H.}~\bibnamefont {Kusumaatmaja}},\ }\href
-  {https://doi.org/10.1038/s42005-019-0251-4} {\bibfield  {journal} {\bibinfo
-  {journal} {Communications Physics}\ }\textbf {\bibinfo {volume} {2}},\
-  \bibinfo {pages} {151} (\bibinfo {year} {2019}{\natexlab{a}})}\BibitemShut
-  {NoStop}%
-\bibitem [{\citenamefont {Hutchinson}\ and\ \citenamefont
-  {Thompson}(2018)}]{Hutchinson2018}%
-  \BibitemOpen
-  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {J.~W.}\ \bibnamefont
-  {Hutchinson}}\ and\ \bibinfo {author} {\bibfnamefont {J.~M.~T.}\ \bibnamefont
-  {Thompson}},\ }\href {https://doi.org/10.1016/j.ijsolstr.2018.01.030}
-  {\bibfield  {journal} {\bibinfo  {journal} {International Journal of Solids
-  and Structures}\ }\textbf {\bibinfo {volume} {148-149}},\ \bibinfo {pages}
-  {157} (\bibinfo {year} {2018})}\BibitemShut {NoStop}%
-\bibitem [{\citenamefont {Zhang}\ and\ \citenamefont {Ren}(2014)}]{Zhang2014}%
-  \BibitemOpen
-  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {Y.}~\bibnamefont
-  {Zhang}}\ and\ \bibinfo {author} {\bibfnamefont {W.}~\bibnamefont {Ren}},\
-  }\href {https://doi.org/10.1063/1.4904947} {\bibfield  {journal} {\bibinfo
-  {journal} {The Journal of Chemical Physics}\ }\textbf {\bibinfo {volume}
-  {141}},\ \bibinfo {pages} {244705} (\bibinfo {year} {2014})}\BibitemShut
-  {NoStop}%
-\bibitem [{\citenamefont {Panter}\ \emph
-  {et~al.}(2019{\natexlab{b}})\citenamefont {Panter}, \citenamefont {Gizaw},\
-  and\ \citenamefont {Kusumaatmaja}}]{Panter2019b}%
-  \BibitemOpen
-  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {J.~R.}\ \bibnamefont
-  {Panter}}, \bibinfo {author} {\bibfnamefont {Y.}~\bibnamefont {Gizaw}},\ and\
-  \bibinfo {author} {\bibfnamefont {H.}~\bibnamefont {Kusumaatmaja}},\ }\href
-  {https://doi.org/10.1126/sciadv.aav7328} {\bibfield  {journal} {\bibinfo
-  {journal} {Science Advances}\ }\textbf {\bibinfo {volume} {5}},\ \bibinfo
-  {pages} {eaav7328} (\bibinfo {year} {2019}{\natexlab{b}})}\BibitemShut
-  {NoStop}%
-\bibitem [{\citenamefont {Amabili}\ \emph {et~al.}(2017)\citenamefont
-  {Amabili}, \citenamefont {Giacomello}, \citenamefont {Meloni},\ and\
-  \citenamefont {Casciola}}]{Amabili2017}%
-  \BibitemOpen
-  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {M.}~\bibnamefont
-  {Amabili}}, \bibinfo {author} {\bibfnamefont {A.}~\bibnamefont {Giacomello}},
-  \bibinfo {author} {\bibfnamefont {S.}~\bibnamefont {Meloni}},\ and\ \bibinfo
-  {author} {\bibfnamefont {C.~M.}\ \bibnamefont {Casciola}},\ }\href
-  {https://doi.org/10.1103/PhysRevFluids.2.034202} {\bibfield  {journal}
-  {\bibinfo  {journal} {Physical Review Fluids}\ }\textbf {\bibinfo {volume}
-  {2}},\ \bibinfo {pages} {034202} (\bibinfo {year} {2017})}\BibitemShut
-  {NoStop}%
-\bibitem [{\citenamefont {Othayoth}\ \emph {et~al.}(2020)\citenamefont
-  {Othayoth}, \citenamefont {Thoms},\ and\ \citenamefont {Li}}]{Othayoth2020}%
-  \BibitemOpen
-  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {R.}~\bibnamefont
-  {Othayoth}}, \bibinfo {author} {\bibfnamefont {G.}~\bibnamefont {Thoms}},\
-  and\ \bibinfo {author} {\bibfnamefont {C.}~\bibnamefont {Li}},\ }\href
-  {https://doi.org/10.1073/pnas.1918297117} {\bibfield  {journal} {\bibinfo
-  {journal} {Proceedings of the National Academy of Sciences}\ }\textbf
-  {\bibinfo {volume} {117}},\ \bibinfo {pages} {14987} (\bibinfo {year}
-  {2020})}\BibitemShut {NoStop}%
-\bibitem [{\citenamefont {Filipov}\ \emph {et~al.}(2015)\citenamefont
-  {Filipov}, \citenamefont {Tachi}, \citenamefont {Paulino},\ and\
-  \citenamefont {Weitz}}]{Filipov2015}%
-  \BibitemOpen
-  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {E.~T.}\ \bibnamefont
-  {Filipov}}, \bibinfo {author} {\bibfnamefont {T.}~\bibnamefont {Tachi}},
-  \bibinfo {author} {\bibfnamefont {G.~H.}\ \bibnamefont {Paulino}},\ and\
-  \bibinfo {author} {\bibfnamefont {D.~A.}\ \bibnamefont {Weitz}},\ }\href
-  {https://doi.org/10.1073/pnas.1509465112} {\bibfield  {journal} {\bibinfo
-  {journal} {Proceedings of the National Academy of Sciences of the United
-  States of America}\ }\textbf {\bibinfo {volume} {112}},\ \bibinfo {pages}
-  {12321} (\bibinfo {year} {2015})}\BibitemShut {NoStop}%
-\bibitem [{\citenamefont {Zhai}\ \emph {et~al.}(2018)\citenamefont {Zhai},
-  \citenamefont {Wang},\ and\ \citenamefont {Jiang}}]{Zhai2018}%
-  \BibitemOpen
-  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {Z.}~\bibnamefont
-  {Zhai}}, \bibinfo {author} {\bibfnamefont {Y.}~\bibnamefont {Wang}},\ and\
-  \bibinfo {author} {\bibfnamefont {H.}~\bibnamefont {Jiang}},\ }\href
-  {https://doi.org/10.1073/pnas.1720171115} {\bibfield  {journal} {\bibinfo
-  {journal} {Proceedings of the National Academy of Sciences of the United
-  States of America}\ }\textbf {\bibinfo {volume} {115}},\ \bibinfo {pages}
-  {2032} (\bibinfo {year} {2018})}\BibitemShut {NoStop}%
-\bibitem [{\citenamefont {Bertoldi}\ \emph {et~al.}(2017)\citenamefont
-  {Bertoldi}, \citenamefont {Vitelli}, \citenamefont {Christensen},\ and\
-  \citenamefont {{Van Hecke}}}]{Bertoldi2017}%
-  \BibitemOpen
-  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {K.}~\bibnamefont
-  {Bertoldi}}, \bibinfo {author} {\bibfnamefont {V.}~\bibnamefont {Vitelli}},
-  \bibinfo {author} {\bibfnamefont {J.}~\bibnamefont {Christensen}},\ and\
-  \bibinfo {author} {\bibfnamefont {M.}~\bibnamefont {{Van Hecke}}},\ }\href
-  {https://doi.org/10.1038/natrevmats.2017.66} {\bibfield  {journal} {\bibinfo
-  {journal} {Nature Reviews Materials}\ }\textbf {\bibinfo {volume} {2}},\
-  \bibinfo {pages} {17066} (\bibinfo {year} {2017})}\BibitemShut {NoStop}%
-\bibitem [{\citenamefont {Truby}\ and\ \citenamefont
-  {Lewis}(2016)}]{Truby2016}%
-  \BibitemOpen
-  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {R.~L.}\ \bibnamefont
-  {Truby}}\ and\ \bibinfo {author} {\bibfnamefont {J.~A.}\ \bibnamefont
-  {Lewis}},\ }\href {https://doi.org/10.1038/nature21003} {\bibfield  {journal}
-  {\bibinfo  {journal} {Nature}\ }\textbf {\bibinfo {volume} {540}},\ \bibinfo
-  {pages} {371} (\bibinfo {year} {2016})}\BibitemShut {NoStop}%
-\bibitem [{\citenamefont {Chi}\ \emph {et~al.}(2022)\citenamefont {Chi},
-  \citenamefont {Li}, \citenamefont {Zhao}, \citenamefont {Hong}, \citenamefont
-  {Tang},\ and\ \citenamefont {Yin}}]{Chi2022}%
-  \BibitemOpen
-  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {Y.}~\bibnamefont
-  {Chi}}, \bibinfo {author} {\bibfnamefont {Y.}~\bibnamefont {Li}}, \bibinfo
-  {author} {\bibfnamefont {Y.}~\bibnamefont {Zhao}}, \bibinfo {author}
-  {\bibfnamefont {Y.}~\bibnamefont {Hong}}, \bibinfo {author} {\bibfnamefont
-  {Y.}~\bibnamefont {Tang}},\ and\ \bibinfo {author} {\bibfnamefont
-  {J.}~\bibnamefont {Yin}},\ }\bibfield  {journal} {\bibinfo  {journal}
-  {Advanced Materials}\ }\href {https://doi.org/10.1002/adma.202110384}
-  {10.1002/adma.202110384} (\bibinfo {year} {2022})\BibitemShut {NoStop}%
-\bibitem [{\citenamefont {Bonfanti}\ \emph {et~al.}(2020)\citenamefont
-  {Bonfanti}, \citenamefont {Guerra}, \citenamefont {Font-Clos}, \citenamefont
-  {Rayneau-Kirkhope},\ and\ \citenamefont {Zapperi}}]{Bonfanti2020}%
-  \BibitemOpen
-  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {S.}~\bibnamefont
-  {Bonfanti}}, \bibinfo {author} {\bibfnamefont {R.}~\bibnamefont {Guerra}},
-  \bibinfo {author} {\bibfnamefont {F.}~\bibnamefont {Font-Clos}}, \bibinfo
-  {author} {\bibfnamefont {D.}~\bibnamefont {Rayneau-Kirkhope}},\ and\ \bibinfo
-  {author} {\bibfnamefont {S.}~\bibnamefont {Zapperi}},\ }\href
-  {https://doi.org/10.1038/s41467-020-17947-2} {\bibfield  {journal} {\bibinfo
-  {journal} {Nature Communications}\ }\textbf {\bibinfo {volume} {11}},\
-  \bibinfo {pages} {4162} (\bibinfo {year} {2020})}\BibitemShut {NoStop}%
-\bibitem [{\citenamefont {Shan}\ \emph {et~al.}(2015)\citenamefont {Shan},
-  \citenamefont {Kang}, \citenamefont {Raney}, \citenamefont {Wang},
-  \citenamefont {Fang}, \citenamefont {Candido}, \citenamefont {Lewis},\ and\
-  \citenamefont {Bertoldi}}]{Shan2015}%
-  \BibitemOpen
-  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {S.}~\bibnamefont
-  {Shan}}, \bibinfo {author} {\bibfnamefont {S.~H.}\ \bibnamefont {Kang}},
-  \bibinfo {author} {\bibfnamefont {J.~R.}\ \bibnamefont {Raney}}, \bibinfo
-  {author} {\bibfnamefont {P.}~\bibnamefont {Wang}}, \bibinfo {author}
-  {\bibfnamefont {L.}~\bibnamefont {Fang}}, \bibinfo {author} {\bibfnamefont
-  {F.}~\bibnamefont {Candido}}, \bibinfo {author} {\bibfnamefont {J.~A.}\
-  \bibnamefont {Lewis}},\ and\ \bibinfo {author} {\bibfnamefont
-  {K.}~\bibnamefont {Bertoldi}},\ }\href
-  {https://doi.org/10.1002/adma.201501708} {\bibfield  {journal} {\bibinfo
-  {journal} {Advanced Materials}\ }\textbf {\bibinfo {volume} {27}},\ \bibinfo
-  {pages} {4296} (\bibinfo {year} {2015})}\BibitemShut {NoStop}%
-\bibitem [{\citenamefont {Giri}\ and\ \citenamefont {Mailen}(2021)}]{Giri2021}%
-  \BibitemOpen
-  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {T.~R.}\ \bibnamefont
-  {Giri}}\ and\ \bibinfo {author} {\bibfnamefont {R.}~\bibnamefont {Mailen}},\
-  }\href {https://doi.org/10.1016/j.ijmecsci.2021.106541} {\bibfield  {journal}
-  {\bibinfo  {journal} {International Journal of Mechanical Sciences}\ }\textbf
-  {\bibinfo {volume} {204}},\ \bibinfo {pages} {106541} (\bibinfo {year}
-  {2021})}\BibitemShut {NoStop}%
-\bibitem [{\citenamefont {Cerjan}\ and\ \citenamefont
-  {Miller}(1981)}]{Cerjan1981}%
-  \BibitemOpen
-  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {C.~J.}\ \bibnamefont
-  {Cerjan}}\ and\ \bibinfo {author} {\bibfnamefont {W.~H.}\ \bibnamefont
-  {Miller}},\ }\href {https://doi.org/10.1063/1.442352} {\bibfield  {journal}
-  {\bibinfo  {journal} {The Journal of Chemical Physics}\ }\textbf {\bibinfo
-  {volume} {75}},\ \bibinfo {pages} {2800} (\bibinfo {year}
-  {1981})}\BibitemShut {NoStop}%
-\bibitem [{\citenamefont {Heyden}\ \emph {et~al.}(2005)\citenamefont {Heyden},
-  \citenamefont {Bell},\ and\ \citenamefont {Keil}}]{Heyden2005}%
-  \BibitemOpen
-  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {A.}~\bibnamefont
-  {Heyden}}, \bibinfo {author} {\bibfnamefont {A.~T.}\ \bibnamefont {Bell}},\
-  and\ \bibinfo {author} {\bibfnamefont {F.~J.}\ \bibnamefont {Keil}},\ }\href
-  {https://doi.org/10.1063/1.2104507} {\bibfield  {journal} {\bibinfo
-  {journal} {Journal of Chemical Physics}\ }\textbf {\bibinfo {volume} {123}},\
-  \bibinfo {pages} {224101} (\bibinfo {year} {2005})}\BibitemShut {NoStop}%
-\bibitem [{\citenamefont {K{\"{a}}stner}\ and\ \citenamefont
-  {Sherwood}(2008)}]{Kastner2008}%
-  \BibitemOpen
-  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {J.}~\bibnamefont
-  {K{\"{a}}stner}}\ and\ \bibinfo {author} {\bibfnamefont {P.}~\bibnamefont
-  {Sherwood}},\ }\href {https://doi.org/10.1063/1.2815812} {\bibfield
-  {journal} {\bibinfo  {journal} {Journal of Chemical Physics}\ }\textbf
-  {\bibinfo {volume} {128}},\ \bibinfo {pages} {014106} (\bibinfo {year}
-  {2008})}\BibitemShut {NoStop}%
-\bibitem [{\citenamefont {Zhang}\ \emph {et~al.}(2016)\citenamefont {Zhang},
-  \citenamefont {Du},\ and\ \citenamefont {Zheng}}]{Zhang2016}%
-  \BibitemOpen
-  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {L.}~\bibnamefont
-  {Zhang}}, \bibinfo {author} {\bibfnamefont {Q.}~\bibnamefont {Du}},\ and\
-  \bibinfo {author} {\bibfnamefont {Z.}~\bibnamefont {Zheng}},\ }\href
-  {https://doi.org/10.1137/140972676} {\bibfield  {journal} {\bibinfo
-  {journal} {SIAM Journal on Scientific Computing}\ }\textbf {\bibinfo {volume}
-  {38}},\ \bibinfo {pages} {A528} (\bibinfo {year} {2016})}\BibitemShut
-  {NoStop}%
-\bibitem [{\citenamefont {E}\ \emph {et~al.}(2007)\citenamefont {E},
-  \citenamefont {Ren},\ and\ \citenamefont {Vanden-Eijnden}}]{E2007}%
-  \BibitemOpen
-  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {W.}~\bibnamefont {E}},
-  \bibinfo {author} {\bibfnamefont {W.}~\bibnamefont {Ren}},\ and\ \bibinfo
-  {author} {\bibfnamefont {E.}~\bibnamefont {Vanden-Eijnden}},\ }\href
-  {https://doi.org/10.1063/1.2720838} {\bibfield  {journal} {\bibinfo
-  {journal} {The Journal of Chemical Physics}\ }\textbf {\bibinfo {volume}
-  {126}},\ \bibinfo {pages} {164103} (\bibinfo {year} {2007})}\BibitemShut
-  {NoStop}%
-\bibitem [{\citenamefont {Ren}\ and\ \citenamefont
-  {Vanden-Eijnden}(2013)}]{Ren2013}%
-  \BibitemOpen
-  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {W.}~\bibnamefont
-  {Ren}}\ and\ \bibinfo {author} {\bibfnamefont {E.}~\bibnamefont
-  {Vanden-Eijnden}},\ }\href {https://doi.org/10.1063/1.4798344} {\bibfield
-  {journal} {\bibinfo  {journal} {Journal of Chemical Physics}\ }\textbf
-  {\bibinfo {volume} {138}},\ \bibinfo {pages} {134105} (\bibinfo {year}
-  {2013})}\BibitemShut {NoStop}%
-\bibitem [{\citenamefont {E}\ \emph {et~al.}(2002)\citenamefont {E},
-  \citenamefont {Ren},\ and\ \citenamefont {Vanden-Eijnden}}]{E2002}%
-  \BibitemOpen
-  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {W.}~\bibnamefont {E}},
-  \bibinfo {author} {\bibfnamefont {W.}~\bibnamefont {Ren}},\ and\ \bibinfo
-  {author} {\bibfnamefont {E.}~\bibnamefont {Vanden-Eijnden}},\ }\href
-  {https://doi.org/10.1103/PhysRevB.66.052301} {\bibfield  {journal} {\bibinfo
-  {journal} {Physical Review B}\ }\textbf {\bibinfo {volume} {66}},\ \bibinfo
-  {pages} {052301} (\bibinfo {year} {2002})}\BibitemShut {NoStop}%
-\bibitem [{\citenamefont {Trygubenko}\ and\ \citenamefont
-  {Wales}(2004)}]{Trygubenko2004}%
-  \BibitemOpen
-  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {S.~A.}\ \bibnamefont
-  {Trygubenko}}\ and\ \bibinfo {author} {\bibfnamefont {D.~J.}\ \bibnamefont
-  {Wales}},\ }\href {https://doi.org/10.1063/1.1636455} {\bibfield  {journal}
-  {\bibinfo  {journal} {Journal of Chemical Physics}\ }\textbf {\bibinfo
-  {volume} {120}},\ \bibinfo {pages} {2082} (\bibinfo {year}
-  {2004})}\BibitemShut {NoStop}%
-\bibitem [{\citenamefont {Wales}\ and\ \citenamefont
-  {Carr}(2012)}]{Wales2012a}%
-  \BibitemOpen
-  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {D.~J.}\ \bibnamefont
-  {Wales}}\ and\ \bibinfo {author} {\bibfnamefont {J.~M.}\ \bibnamefont
-  {Carr}},\ }\href {https://doi.org/10.1021/ct3004832} {\bibfield  {journal}
-  {\bibinfo  {journal} {Journal of Chemical Theory and Computation}\ }\textbf
-  {\bibinfo {volume} {8}},\ \bibinfo {pages} {5020} (\bibinfo {year}
-  {2012})}\BibitemShut {NoStop}%
-\bibitem [{\citenamefont {Trefethen}\ and\ \citenamefont
-  {Thiyagalingam}(2013)}]{Trefethen2013}%
-  \BibitemOpen
-  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {A.~E.}\ \bibnamefont
-  {Trefethen}}\ and\ \bibinfo {author} {\bibfnamefont {J.}~\bibnamefont
-  {Thiyagalingam}},\ }\href {https://doi.org/10.1016/j.jocs.2013.01.005}
-  {\bibfield  {journal} {\bibinfo  {journal} {Journal of Computational
-  Science}\ }\textbf {\bibinfo {volume} {4}},\ \bibinfo {pages} {444} (\bibinfo
-  {year} {2013})}\BibitemShut {NoStop}%
-\bibitem [{\citenamefont {Shalf}(2020)}]{Shalf2020}%
-  \BibitemOpen
-  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {J.}~\bibnamefont
-  {Shalf}},\ }\href {https://doi.org/10.1098/rsta.2019.0061} {\bibfield
-  {journal} {\bibinfo  {journal} {Philosophical Transactions Royal Society}\
-  }\textbf {\bibinfo {volume} {378}},\ \bibinfo {pages} {20190061} (\bibinfo
-  {year} {2020})}\BibitemShut {NoStop}%
-\bibitem [{\citenamefont {Alexander}\ \emph {et~al.}(2020)\citenamefont
-  {Alexander}, \citenamefont {Almgren}, \citenamefont {Bell}, \citenamefont
-  {Bhattacharjee}, \citenamefont {Chen}, \citenamefont {Colella}, \citenamefont
-  {Daniel}, \citenamefont {DeSlippe}, \citenamefont {Diachin}, \citenamefont
-  {Draeger}, \citenamefont {Dubey}, \citenamefont {Dunning}, \citenamefont
-  {Evans}, \citenamefont {Foster}, \citenamefont {Francois}, \citenamefont
-  {Germann}, \citenamefont {Gordon}, \citenamefont {Habib}, \citenamefont
-  {Halappanavar}, \citenamefont {Hamilton}, \citenamefont {Hart}, \citenamefont
-  {Huang}, \citenamefont {Hungerford}, \citenamefont {Kasen}, \citenamefont
-  {Kent}, \citenamefont {Kolev}, \citenamefont {Kothe}, \citenamefont
-  {Kronfeld}, \citenamefont {Luo}, \citenamefont {Mackenzie}, \citenamefont
-  {McCallen}, \citenamefont {Messer}, \citenamefont {Mniszewski}, \citenamefont
-  {Oehmen}, \citenamefont {Perazzo}, \citenamefont {Perez}, \citenamefont
-  {Richards}, \citenamefont {Rider}, \citenamefont {Rieben}, \citenamefont
-  {Roche}, \citenamefont {Siegel}, \citenamefont {Sprague}, \citenamefont
-  {Steefel}, \citenamefont {Stevens}, \citenamefont {Syamlal}, \citenamefont
-  {Taylor}, \citenamefont {Turner}, \citenamefont {Vay}, \citenamefont {Voter},
-  \citenamefont {Windus},\ and\ \citenamefont {Yelick}}]{Alexander2020}%
-  \BibitemOpen
-  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {F.}~\bibnamefont
-  {Alexander}}, \bibinfo {author} {\bibfnamefont {A.}~\bibnamefont {Almgren}},
-  \bibinfo {author} {\bibfnamefont {J.}~\bibnamefont {Bell}}, \bibinfo {author}
-  {\bibfnamefont {A.}~\bibnamefont {Bhattacharjee}}, \bibinfo {author}
-  {\bibfnamefont {J.}~\bibnamefont {Chen}}, \bibinfo {author} {\bibfnamefont
-  {P.}~\bibnamefont {Colella}}, \bibinfo {author} {\bibfnamefont
-  {D.}~\bibnamefont {Daniel}}, \bibinfo {author} {\bibfnamefont
-  {J.}~\bibnamefont {DeSlippe}}, \bibinfo {author} {\bibfnamefont
-  {L.}~\bibnamefont {Diachin}}, \bibinfo {author} {\bibfnamefont
-  {E.}~\bibnamefont {Draeger}}, \bibinfo {author} {\bibfnamefont
-  {A.}~\bibnamefont {Dubey}}, \bibinfo {author} {\bibfnamefont
-  {T.}~\bibnamefont {Dunning}}, \bibinfo {author} {\bibfnamefont
-  {T.}~\bibnamefont {Evans}}, \bibinfo {author} {\bibfnamefont
-  {I.}~\bibnamefont {Foster}}, \bibinfo {author} {\bibfnamefont
-  {M.}~\bibnamefont {Francois}}, \bibinfo {author} {\bibfnamefont
-  {T.}~\bibnamefont {Germann}}, \bibinfo {author} {\bibfnamefont
-  {M.}~\bibnamefont {Gordon}}, \bibinfo {author} {\bibfnamefont
-  {S.}~\bibnamefont {Habib}}, \bibinfo {author} {\bibfnamefont
-  {M.}~\bibnamefont {Halappanavar}}, \bibinfo {author} {\bibfnamefont
-  {S.}~\bibnamefont {Hamilton}}, \bibinfo {author} {\bibfnamefont
-  {W.}~\bibnamefont {Hart}}, \bibinfo {author} {\bibfnamefont {Z.}~\bibnamefont
-  {Huang}}, \bibinfo {author} {\bibfnamefont {A.}~\bibnamefont {Hungerford}},
-  \bibinfo {author} {\bibfnamefont {D.}~\bibnamefont {Kasen}}, \bibinfo
-  {author} {\bibfnamefont {P.~R.}\ \bibnamefont {Kent}}, \bibinfo {author}
-  {\bibfnamefont {T.}~\bibnamefont {Kolev}}, \bibinfo {author} {\bibfnamefont
-  {D.~B.}\ \bibnamefont {Kothe}}, \bibinfo {author} {\bibfnamefont
-  {A.}~\bibnamefont {Kronfeld}}, \bibinfo {author} {\bibfnamefont
-  {Y.}~\bibnamefont {Luo}}, \bibinfo {author} {\bibfnamefont {P.}~\bibnamefont
-  {Mackenzie}}, \bibinfo {author} {\bibfnamefont {D.}~\bibnamefont {McCallen}},
-  \bibinfo {author} {\bibfnamefont {B.}~\bibnamefont {Messer}}, \bibinfo
-  {author} {\bibfnamefont {S.}~\bibnamefont {Mniszewski}}, \bibinfo {author}
-  {\bibfnamefont {C.}~\bibnamefont {Oehmen}}, \bibinfo {author} {\bibfnamefont
-  {A.}~\bibnamefont {Perazzo}}, \bibinfo {author} {\bibfnamefont
-  {D.}~\bibnamefont {Perez}}, \bibinfo {author} {\bibfnamefont
-  {D.}~\bibnamefont {Richards}}, \bibinfo {author} {\bibfnamefont {W.~J.}\
-  \bibnamefont {Rider}}, \bibinfo {author} {\bibfnamefont {R.}~\bibnamefont
-  {Rieben}}, \bibinfo {author} {\bibfnamefont {K.}~\bibnamefont {Roche}},
-  \bibinfo {author} {\bibfnamefont {A.}~\bibnamefont {Siegel}}, \bibinfo
-  {author} {\bibfnamefont {M.}~\bibnamefont {Sprague}}, \bibinfo {author}
-  {\bibfnamefont {C.}~\bibnamefont {Steefel}}, \bibinfo {author} {\bibfnamefont
-  {R.}~\bibnamefont {Stevens}}, \bibinfo {author} {\bibfnamefont
-  {M.}~\bibnamefont {Syamlal}}, \bibinfo {author} {\bibfnamefont
-  {M.}~\bibnamefont {Taylor}}, \bibinfo {author} {\bibfnamefont
-  {J.}~\bibnamefont {Turner}}, \bibinfo {author} {\bibfnamefont {J.~L.}\
-  \bibnamefont {Vay}}, \bibinfo {author} {\bibfnamefont {A.~F.}\ \bibnamefont
-  {Voter}}, \bibinfo {author} {\bibfnamefont {T.~L.}\ \bibnamefont {Windus}},\
-  and\ \bibinfo {author} {\bibfnamefont {K.}~\bibnamefont {Yelick}},\ }\href
-  {https://doi.org/10.1098/rsta.2019.0056} {\bibfield  {journal} {\bibinfo
-  {journal} {Philosophical Transactions of the Royal Society A}\ }\textbf
-  {\bibinfo {volume} {378}},\ \bibinfo {pages} {20190056} (\bibinfo {year}
-  {2020})}\BibitemShut {NoStop}%
-\bibitem [{\citenamefont {McMullen}\ \emph {et~al.}(2018)\citenamefont
-  {McMullen}, \citenamefont {Holmes-Cerfon}, \citenamefont {Sciortino},
-  \citenamefont {Grosberg},\ and\ \citenamefont {Brujic}}]{McMullen2018}%
-  \BibitemOpen
-  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {A.}~\bibnamefont
-  {McMullen}}, \bibinfo {author} {\bibfnamefont {M.}~\bibnamefont
-  {Holmes-Cerfon}}, \bibinfo {author} {\bibfnamefont {F.}~\bibnamefont
-  {Sciortino}}, \bibinfo {author} {\bibfnamefont {A.~Y.}\ \bibnamefont
-  {Grosberg}},\ and\ \bibinfo {author} {\bibfnamefont {J.}~\bibnamefont
-  {Brujic}},\ }\href {https://doi.org/10.1103/PhysRevLett.121.138002}
-  {\bibfield  {journal} {\bibinfo  {journal} {Physical Review Letters}\
-  }\textbf {\bibinfo {volume} {121}},\ \bibinfo {pages} {138002} (\bibinfo
-  {year} {2018})}\BibitemShut {NoStop}%
-\bibitem [{\citenamefont {Nguemaha}\ and\ \citenamefont
-  {Zhou}(2018)}]{Nguemaha2018}%
-  \BibitemOpen
-  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {V.}~\bibnamefont
-  {Nguemaha}}\ and\ \bibinfo {author} {\bibfnamefont {H.~X.}\ \bibnamefont
-  {Zhou}},\ }\href {https://doi.org/10.1038/s41598-018-25132-1} {\bibfield
-  {journal} {\bibinfo  {journal} {Scientific Reports}\ }\textbf {\bibinfo
-  {volume} {8}},\ \bibinfo {pages} {1} (\bibinfo {year} {2018})}\BibitemShut
-  {NoStop}%
-\bibitem [{\citenamefont {Chen}\ \emph {et~al.}(2018)\citenamefont {Chen},
-  \citenamefont {Zhang},\ and\ \citenamefont {Torquato}}]{Chen2018b}%
-  \BibitemOpen
-  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {D.}~\bibnamefont
-  {Chen}}, \bibinfo {author} {\bibfnamefont {G.}~\bibnamefont {Zhang}},\ and\
-  \bibinfo {author} {\bibfnamefont {S.}~\bibnamefont {Torquato}},\ }\href
-  {https://doi.org/10.1021/acs.jpcb.8b05627} {\bibfield  {journal} {\bibinfo
-  {journal} {Journal of Physical Chemistry B}\ }\textbf {\bibinfo {volume}
-  {122}},\ \bibinfo {pages} {8462} (\bibinfo {year} {2018})}\BibitemShut
-  {NoStop}%
-\bibitem [{\citenamefont {Santra}\ \emph {et~al.}(2018)\citenamefont {Santra},
-  \citenamefont {Singh},\ and\ \citenamefont {Bagchi}}]{Santra2018}%
-  \BibitemOpen
-  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {M.}~\bibnamefont
-  {Santra}}, \bibinfo {author} {\bibfnamefont {R.~S.}\ \bibnamefont {Singh}},\
-  and\ \bibinfo {author} {\bibfnamefont {B.}~\bibnamefont {Bagchi}},\ }\href
-  {https://doi.org/10.1103/PhysRevE.98.032606} {\bibfield  {journal} {\bibinfo
-  {journal} {Physical Review E}\ }\textbf {\bibinfo {volume} {98}},\ \bibinfo
-  {pages} {032606} (\bibinfo {year} {2018})}\BibitemShut {NoStop}%
-\bibitem [{\citenamefont {M{\"{o}}kk{\"{o}}nen}\ \emph
-  {et~al.}(2016)\citenamefont {M{\"{o}}kk{\"{o}}nen}, \citenamefont
-  {Ala-Nissila},\ and\ \citenamefont {J{\'{o}}nsson}}]{Mokkonen2016}%
-  \BibitemOpen
-  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {H.}~\bibnamefont
-  {M{\"{o}}kk{\"{o}}nen}}, \bibinfo {author} {\bibfnamefont {T.}~\bibnamefont
-  {Ala-Nissila}},\ and\ \bibinfo {author} {\bibfnamefont {H.}~\bibnamefont
-  {J{\'{o}}nsson}},\ }\href {https://doi.org/10.1063/1.4962167} {\bibfield
-  {journal} {\bibinfo  {journal} {The Journal of Chemical Physics}\ }\textbf
-  {\bibinfo {volume} {145}},\ \bibinfo {pages} {094901} (\bibinfo {year}
-  {2016})}\BibitemShut {NoStop}%
-\bibitem [{\citenamefont {Wriggers}(2006)}]{Wriggers2006}%
-  \BibitemOpen
-  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {P.}~\bibnamefont
-  {Wriggers}},\ }\href {https://doi.org/10.1007/978-3-540-32609-0} {\emph
-  {\bibinfo {title} {{Computational Contact Mechanics}}}}\ (\bibinfo
-  {publisher} {Springer Berlin Heidelberg},\ \bibinfo {address} {Berlin,
-  Heidelberg},\ \bibinfo {year} {2006})\BibitemShut {NoStop}%
-\bibitem [{\citenamefont {Page}\ and\ \citenamefont {McIver}(1988)}]{Page1988}%
-  \BibitemOpen
-  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {M.}~\bibnamefont
-  {Page}}\ and\ \bibinfo {author} {\bibfnamefont {J.~W.}\ \bibnamefont
-  {McIver}},\ }\href {https://doi.org/10.1063/1.454172} {\bibfield  {journal}
-  {\bibinfo  {journal} {The Journal of Chemical Physics}\ }\textbf {\bibinfo
-  {volume} {88}},\ \bibinfo {pages} {922} (\bibinfo {year} {1988})}\BibitemShut
-  {NoStop}%
-\bibitem [{\citenamefont {Liu}\ and\ \citenamefont {Nocedal}(1989)}]{Liu1989}%
-  \BibitemOpen
-  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {D.~C.}\ \bibnamefont
-  {Liu}}\ and\ \bibinfo {author} {\bibfnamefont {J.}~\bibnamefont {Nocedal}},\
-  }\href@noop {} {\bibfield  {journal} {\bibinfo  {journal} {Mathematical
-  Programming}\ }\textbf {\bibinfo {volume} {45}},\ \bibinfo {pages} {503}
-  (\bibinfo {year} {1989})}\BibitemShut {NoStop}%
-\bibitem [{\citenamefont {Wales}(2002)}]{Wales2002}%
-  \BibitemOpen
-  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {D.~J.}\ \bibnamefont
-  {Wales}},\ }\href {https://doi.org/10.1080/00268970210162691} {\bibfield
-  {journal} {\bibinfo  {journal} {Molecular Physics}\ }\textbf {\bibinfo
-  {volume} {100}},\ \bibinfo {pages} {3285} (\bibinfo {year}
-  {2002})}\BibitemShut {NoStop}%
-\bibitem [{\citenamefont {Passerone}\ and\ \citenamefont
-  {Parrinello}(2001)}]{Passerone2001}%
-  \BibitemOpen
-  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {D.}~\bibnamefont
-  {Passerone}}\ and\ \bibinfo {author} {\bibfnamefont {M.}~\bibnamefont
-  {Parrinello}},\ }\href {https://doi.org/10.1103/PhysRevLett.87.108302}
-  {\bibfield  {journal} {\bibinfo  {journal} {Physical Review Letters}\
-  }\textbf {\bibinfo {volume} {87}},\ \bibinfo {pages} {108302} (\bibinfo
-  {year} {2001})}\BibitemShut {NoStop}%
-\bibitem [{\citenamefont {Virot}\ \emph {et~al.}(2017)\citenamefont {Virot},
-  \citenamefont {Kreilos}, \citenamefont {Schneider},\ and\ \citenamefont
-  {Rubinstein}}]{Virot2017}%
-  \BibitemOpen
-  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {E.}~\bibnamefont
-  {Virot}}, \bibinfo {author} {\bibfnamefont {T.}~\bibnamefont {Kreilos}},
-  \bibinfo {author} {\bibfnamefont {T.~M.}\ \bibnamefont {Schneider}},\ and\
-  \bibinfo {author} {\bibfnamefont {S.~M.}\ \bibnamefont {Rubinstein}},\ }\href
-  {https://doi.org/10.1103/PhysRevLett.119.224101} {\bibfield  {journal}
-  {\bibinfo  {journal} {Physical Review Letters}\ }\textbf {\bibinfo {volume}
-  {119}},\ \bibinfo {pages} {224101} (\bibinfo {year} {2017})}\BibitemShut
-  {NoStop}%
-\bibitem [{\citenamefont {Kusumaatmaja}\ \emph {et~al.}(2006)\citenamefont
-  {Kusumaatmaja}, \citenamefont {L{\'{e}}opold{\`{e}}s}, \citenamefont
-  {Dupuis},\ and\ \citenamefont {Yeomans}}]{Kusumaatmaja2006}%
-  \BibitemOpen
-  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {H.}~\bibnamefont
-  {Kusumaatmaja}}, \bibinfo {author} {\bibfnamefont {J.}~\bibnamefont
-  {L{\'{e}}opold{\`{e}}s}}, \bibinfo {author} {\bibfnamefont {A.}~\bibnamefont
-  {Dupuis}},\ and\ \bibinfo {author} {\bibfnamefont {J.~M.}\ \bibnamefont
-  {Yeomans}},\ }\href {https://doi.org/10.1209/epl/i2005-10452-0} {\bibfield
-  {journal} {\bibinfo  {journal} {Europhysics Letters}\ }\textbf {\bibinfo
-  {volume} {73}},\ \bibinfo {pages} {740} (\bibinfo {year} {2006})}\BibitemShut
-  {NoStop}%
-\bibitem [{\citenamefont {Brown}\ and\ \citenamefont
-  {Bhushan}(2016)}]{Brown2016}%
-  \BibitemOpen
-  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {P.~S.}\ \bibnamefont
-  {Brown}}\ and\ \bibinfo {author} {\bibfnamefont {B.}~\bibnamefont
-  {Bhushan}},\ }\href {https://doi.org/10.1098/rsta.2016.0135} {\bibfield
-  {journal} {\bibinfo  {journal} {Philosophical Transactions of the Royal
-  Society A}\ }\textbf {\bibinfo {volume} {374}},\ \bibinfo {pages} {20160135}
-  (\bibinfo {year} {2016})}\BibitemShut {NoStop}%
-\bibitem [{\citenamefont {Kirkpatrick}\ \emph {et~al.}(1983)\citenamefont
-  {Kirkpatrick}, \citenamefont {Gelatt},\ and\ \citenamefont
-  {Vecchi}}]{Kirkpatrick1983}%
-  \BibitemOpen
-  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {S.}~\bibnamefont
-  {Kirkpatrick}}, \bibinfo {author} {\bibfnamefont {C.~D.}\ \bibnamefont
-  {Gelatt}},\ and\ \bibinfo {author} {\bibfnamefont {M.~P.}\ \bibnamefont
-  {Vecchi}},\ }\href {https://doi.org/10.1126/science.220.4598.671} {\bibfield
-  {journal} {\bibinfo  {journal} {Science}\ }\textbf {\bibinfo {volume}
-  {220}},\ \bibinfo {pages} {671} (\bibinfo {year} {1983})}\BibitemShut
-  {NoStop}%
-\end{thebibliography}%
+\begin{thebibliography}{50}
+\expandafter\ifx\csname natexlab\endcsname\relax\def\natexlab#1{#1}\fi
+\expandafter\ifx\csname bibnamefont\endcsname\relax
+  \def\bibnamefont#1{#1}\fi
+\expandafter\ifx\csname bibfnamefont\endcsname\relax
+  \def\bibfnamefont#1{#1}\fi
+\expandafter\ifx\csname citenamefont\endcsname\relax
+  \def\citenamefont#1{#1}\fi
+\expandafter\ifx\csname url\endcsname\relax
+  \def\url#1{\texttt{#1}}\fi
+\expandafter\ifx\csname urlprefix\endcsname\relax\def\urlprefix{URL }\fi
+\providecommand{\bibinfo}[2]{#2}
+\providecommand{\eprint}[2][]{\url{#2}}
+
+\bibitem[{\citenamefont{Bryngelson et~al.}(1995)\citenamefont{Bryngelson,
+  Onuchic, Socci, and Wolynes}}]{Bryngelson1995}
+\bibinfo{author}{\bibfnamefont{J.~D.} \bibnamefont{Bryngelson}},
+  \bibinfo{author}{\bibfnamefont{J.~N.} \bibnamefont{Onuchic}},
+  \bibinfo{author}{\bibfnamefont{N.~D.} \bibnamefont{Socci}}, \bibnamefont{and}
+  \bibinfo{author}{\bibfnamefont{P.~G.} \bibnamefont{Wolynes}},
+  \bibinfo{journal}{Proteins: Structure, Function, and Bioinformatics}
+  \textbf{\bibinfo{volume}{21}}, \bibinfo{pages}{167} (\bibinfo{year}{1995}).
+
+\bibitem[{\citenamefont{Onuchic et~al.}(1997)\citenamefont{Onuchic,
+  Luthey-Schulten, and Wolynes}}]{Onuchic1997}
+\bibinfo{author}{\bibfnamefont{J.~N.} \bibnamefont{Onuchic}},
+  \bibinfo{author}{\bibfnamefont{Z.}~\bibnamefont{Luthey-Schulten}},
+  \bibnamefont{and} \bibinfo{author}{\bibfnamefont{P.~G.}
+  \bibnamefont{Wolynes}}, \bibinfo{journal}{Annual Review of Physical
+  Chemistry} \textbf{\bibinfo{volume}{48}}, \bibinfo{pages}{545}
+  (\bibinfo{year}{1997}).
+
+\bibitem[{\citenamefont{Boehr et~al.}(2006)\citenamefont{Boehr, McElheny,
+  Dyson, and Wrightt}}]{Boehr2006}
+\bibinfo{author}{\bibfnamefont{D.~D.} \bibnamefont{Boehr}},
+  \bibinfo{author}{\bibfnamefont{D.}~\bibnamefont{McElheny}},
+  \bibinfo{author}{\bibfnamefont{H.~J.} \bibnamefont{Dyson}}, \bibnamefont{and}
+  \bibinfo{author}{\bibfnamefont{P.~E.} \bibnamefont{Wrightt}},
+  \bibinfo{journal}{Science} \textbf{\bibinfo{volume}{313}},
+  \bibinfo{pages}{1638} (\bibinfo{year}{2006}).
+
+\bibitem[{\citenamefont{Kerns et~al.}(2015)\citenamefont{Kerns, Agafonov, Cho,
+  Pontiggia, Otten, Pachov, Kutter, Phung, Murphy, Thai et~al.}}]{Kerns2015}
+\bibinfo{author}{\bibfnamefont{S.~J.} \bibnamefont{Kerns}},
+  \bibinfo{author}{\bibfnamefont{R.~V.} \bibnamefont{Agafonov}},
+  \bibinfo{author}{\bibfnamefont{Y.~J.} \bibnamefont{Cho}},
+  \bibinfo{author}{\bibfnamefont{F.}~\bibnamefont{Pontiggia}},
+  \bibinfo{author}{\bibfnamefont{R.}~\bibnamefont{Otten}},
+  \bibinfo{author}{\bibfnamefont{D.~V.} \bibnamefont{Pachov}},
+  \bibinfo{author}{\bibfnamefont{S.}~\bibnamefont{Kutter}},
+  \bibinfo{author}{\bibfnamefont{L.~A.} \bibnamefont{Phung}},
+  \bibinfo{author}{\bibfnamefont{P.~N.} \bibnamefont{Murphy}},
+  \bibinfo{author}{\bibfnamefont{V.}~\bibnamefont{Thai}}, \bibnamefont{et~al.},
+  \bibinfo{journal}{Nature Structural and Molecular Biology}
+  \textbf{\bibinfo{volume}{22}}, \bibinfo{pages}{124} (\bibinfo{year}{2015}).
+
+\bibitem[{\citenamefont{Guo et~al.}(2018)\citenamefont{Guo, Wang, Wang, Wang,
+  and Hu}}]{Guo2018a}
+\bibinfo{author}{\bibfnamefont{C.}~\bibnamefont{Guo}},
+  \bibinfo{author}{\bibfnamefont{Z.}~\bibnamefont{Wang}},
+  \bibinfo{author}{\bibfnamefont{D.}~\bibnamefont{Wang}},
+  \bibinfo{author}{\bibfnamefont{H.~F.} \bibnamefont{Wang}}, \bibnamefont{and}
+  \bibinfo{author}{\bibfnamefont{P.}~\bibnamefont{Hu}},
+  \bibinfo{journal}{Journal of Physical Chemistry C}
+  \textbf{\bibinfo{volume}{122}}, \bibinfo{pages}{21478}
+  (\bibinfo{year}{2018}).
+
+\bibitem[{\citenamefont{Richardson et~al.}(2016)\citenamefont{Richardson,
+  P{\'{e}}rez, Lobsiger, Reid, Temelso, Shields, Kisiel, Wales, Pate, and
+  Althorpe}}]{Richardson2016}
+\bibinfo{author}{\bibfnamefont{J.~O.} \bibnamefont{Richardson}},
+  \bibinfo{author}{\bibfnamefont{C.}~\bibnamefont{P{\'{e}}rez}},
+  \bibinfo{author}{\bibfnamefont{S.}~\bibnamefont{Lobsiger}},
+  \bibinfo{author}{\bibfnamefont{A.~A.} \bibnamefont{Reid}},
+  \bibinfo{author}{\bibfnamefont{B.}~\bibnamefont{Temelso}},
+  \bibinfo{author}{\bibfnamefont{G.~C.} \bibnamefont{Shields}},
+  \bibinfo{author}{\bibfnamefont{Z.}~\bibnamefont{Kisiel}},
+  \bibinfo{author}{\bibfnamefont{D.~J.} \bibnamefont{Wales}},
+  \bibinfo{author}{\bibfnamefont{B.~H.} \bibnamefont{Pate}}, \bibnamefont{and}
+  \bibinfo{author}{\bibfnamefont{S.~C.} \bibnamefont{Althorpe}},
+  \bibinfo{journal}{Science} \textbf{\bibinfo{volume}{351}},
+  \bibinfo{pages}{1310} (\bibinfo{year}{2016}).
+
+\bibitem[{\citenamefont{Vaillant et~al.}(2019)\citenamefont{Vaillant, Althorpe,
+  and Wales}}]{Vaillant2019}
+\bibinfo{author}{\bibfnamefont{C.~L.} \bibnamefont{Vaillant}},
+  \bibinfo{author}{\bibfnamefont{S.~C.} \bibnamefont{Althorpe}},
+  \bibnamefont{and} \bibinfo{author}{\bibfnamefont{D.~J.} \bibnamefont{Wales}},
+  \bibinfo{journal}{Journal of Chemical Theory and Computation}
+  \textbf{\bibinfo{volume}{15}}, \bibinfo{pages}{33} (\bibinfo{year}{2019}).
+
+\bibitem[{\citenamefont{Richard and Speck}(2018)}]{Richard2018}
+\bibinfo{author}{\bibfnamefont{D.}~\bibnamefont{Richard}} \bibnamefont{and}
+  \bibinfo{author}{\bibfnamefont{T.}~\bibnamefont{Speck}},
+  \bibinfo{journal}{The Journal of Chemical Physics}
+  \textbf{\bibinfo{volume}{148}}, \bibinfo{pages}{124110}
+  (\bibinfo{year}{2018}).
+
+\bibitem[{\citenamefont{Wales et~al.}(1998)\citenamefont{Wales, Miller, and
+  Walsh}}]{Wales1998}
+\bibinfo{author}{\bibfnamefont{D.~J.} \bibnamefont{Wales}},
+  \bibinfo{author}{\bibfnamefont{M.~A.} \bibnamefont{Miller}},
+  \bibnamefont{and} \bibinfo{author}{\bibfnamefont{T.~R.} \bibnamefont{Walsh}},
+  \bibinfo{journal}{Nature} \textbf{\bibinfo{volume}{394}},
+  \bibinfo{pages}{758} (\bibinfo{year}{1998}).
+
+\bibitem[{\citenamefont{Wales}(2012)}]{Wales2012}
+\bibinfo{author}{\bibfnamefont{D.~J.} \bibnamefont{Wales}},
+  \bibinfo{journal}{Philosophical Transactions of the Royal Society A:
+  Mathematical, Physical and Engineering Sciences}
+  \textbf{\bibinfo{volume}{370}}, \bibinfo{pages}{2877} (\bibinfo{year}{2012}).
+
+\bibitem[{\citenamefont{Panter et~al.}(2019{\natexlab{a}})\citenamefont{Panter,
+  Chen, Zhang, and Kusumaatmaja}}]{Panter2019}
+\bibinfo{author}{\bibfnamefont{J.~R.} \bibnamefont{Panter}},
+  \bibinfo{author}{\bibfnamefont{J.}~\bibnamefont{Chen}},
+  \bibinfo{author}{\bibfnamefont{T.}~\bibnamefont{Zhang}}, \bibnamefont{and}
+  \bibinfo{author}{\bibfnamefont{H.}~\bibnamefont{Kusumaatmaja}},
+  \bibinfo{journal}{Communications Physics} \textbf{\bibinfo{volume}{2}},
+  \bibinfo{pages}{151} (\bibinfo{year}{2019}{\natexlab{a}}).
+
+\bibitem[{\citenamefont{Hutchinson and Thompson}(2018)}]{Hutchinson2018}
+\bibinfo{author}{\bibfnamefont{J.~W.} \bibnamefont{Hutchinson}}
+  \bibnamefont{and} \bibinfo{author}{\bibfnamefont{J.~M.~T.}
+  \bibnamefont{Thompson}}, \bibinfo{journal}{International Journal of Solids
+  and Structures} \textbf{\bibinfo{volume}{148-149}}, \bibinfo{pages}{157}
+  (\bibinfo{year}{2018}).
+
+\bibitem[{\citenamefont{Zhang and Ren}(2014)}]{Zhang2014}
+\bibinfo{author}{\bibfnamefont{Y.}~\bibnamefont{Zhang}} \bibnamefont{and}
+  \bibinfo{author}{\bibfnamefont{W.}~\bibnamefont{Ren}}, \bibinfo{journal}{The
+  Journal of Chemical Physics} \textbf{\bibinfo{volume}{141}},
+  \bibinfo{pages}{244705} (\bibinfo{year}{2014}).
+
+\bibitem[{\citenamefont{Panter et~al.}(2019{\natexlab{b}})\citenamefont{Panter,
+  Gizaw, and Kusumaatmaja}}]{Panter2019b}
+\bibinfo{author}{\bibfnamefont{J.~R.} \bibnamefont{Panter}},
+  \bibinfo{author}{\bibfnamefont{Y.}~\bibnamefont{Gizaw}}, \bibnamefont{and}
+  \bibinfo{author}{\bibfnamefont{H.}~\bibnamefont{Kusumaatmaja}},
+  \bibinfo{journal}{Science Advances} \textbf{\bibinfo{volume}{5}},
+  \bibinfo{pages}{eaav7328} (\bibinfo{year}{2019}{\natexlab{b}}).
+
+\bibitem[{\citenamefont{Amabili et~al.}(2017)\citenamefont{Amabili, Giacomello,
+  Meloni, and Casciola}}]{Amabili2017}
+\bibinfo{author}{\bibfnamefont{M.}~\bibnamefont{Amabili}},
+  \bibinfo{author}{\bibfnamefont{A.}~\bibnamefont{Giacomello}},
+  \bibinfo{author}{\bibfnamefont{S.}~\bibnamefont{Meloni}}, \bibnamefont{and}
+  \bibinfo{author}{\bibfnamefont{C.~M.} \bibnamefont{Casciola}},
+  \bibinfo{journal}{Physical Review Fluids} \textbf{\bibinfo{volume}{2}},
+  \bibinfo{pages}{034202} (\bibinfo{year}{2017}).
+
+\bibitem[{\citenamefont{Othayoth et~al.}(2020)\citenamefont{Othayoth, Thoms,
+  and Li}}]{Othayoth2020}
+\bibinfo{author}{\bibfnamefont{R.}~\bibnamefont{Othayoth}},
+  \bibinfo{author}{\bibfnamefont{G.}~\bibnamefont{Thoms}}, \bibnamefont{and}
+  \bibinfo{author}{\bibfnamefont{C.}~\bibnamefont{Li}},
+  \bibinfo{journal}{Proceedings of the National Academy of Sciences}
+  \textbf{\bibinfo{volume}{117}}, \bibinfo{pages}{14987}
+  (\bibinfo{year}{2020}).
+
+\bibitem[{\citenamefont{Filipov et~al.}(2015)\citenamefont{Filipov, Tachi,
+  Paulino, and Weitz}}]{Filipov2015}
+\bibinfo{author}{\bibfnamefont{E.~T.} \bibnamefont{Filipov}},
+  \bibinfo{author}{\bibfnamefont{T.}~\bibnamefont{Tachi}},
+  \bibinfo{author}{\bibfnamefont{G.~H.} \bibnamefont{Paulino}},
+  \bibnamefont{and} \bibinfo{author}{\bibfnamefont{D.~A.} \bibnamefont{Weitz}},
+  \bibinfo{journal}{Proceedings of the National Academy of Sciences of the
+  United States of America} \textbf{\bibinfo{volume}{112}},
+  \bibinfo{pages}{12321} (\bibinfo{year}{2015}).
+
+\bibitem[{\citenamefont{Zhai et~al.}(2018)\citenamefont{Zhai, Wang, and
+  Jiang}}]{Zhai2018}
+\bibinfo{author}{\bibfnamefont{Z.}~\bibnamefont{Zhai}},
+  \bibinfo{author}{\bibfnamefont{Y.}~\bibnamefont{Wang}}, \bibnamefont{and}
+  \bibinfo{author}{\bibfnamefont{H.}~\bibnamefont{Jiang}},
+  \bibinfo{journal}{Proceedings of the National Academy of Sciences of the
+  United States of America} \textbf{\bibinfo{volume}{115}},
+  \bibinfo{pages}{2032} (\bibinfo{year}{2018}).
+
+\bibitem[{\citenamefont{Bertoldi et~al.}(2017)\citenamefont{Bertoldi, Vitelli,
+  Christensen, and {Van Hecke}}}]{Bertoldi2017}
+\bibinfo{author}{\bibfnamefont{K.}~\bibnamefont{Bertoldi}},
+  \bibinfo{author}{\bibfnamefont{V.}~\bibnamefont{Vitelli}},
+  \bibinfo{author}{\bibfnamefont{J.}~\bibnamefont{Christensen}},
+  \bibnamefont{and} \bibinfo{author}{\bibfnamefont{M.}~\bibnamefont{{Van
+  Hecke}}}, \bibinfo{journal}{Nature Reviews Materials}
+  \textbf{\bibinfo{volume}{2}}, \bibinfo{pages}{17066} (\bibinfo{year}{2017}).
+
+\bibitem[{\citenamefont{Truby and Lewis}(2016)}]{Truby2016}
+\bibinfo{author}{\bibfnamefont{R.~L.} \bibnamefont{Truby}} \bibnamefont{and}
+  \bibinfo{author}{\bibfnamefont{J.~A.} \bibnamefont{Lewis}},
+  \bibinfo{journal}{Nature} \textbf{\bibinfo{volume}{540}},
+  \bibinfo{pages}{371} (\bibinfo{year}{2016}).
+
+\bibitem[{\citenamefont{Chi et~al.}(2022)\citenamefont{Chi, Li, Zhao, Hong,
+  Tang, and Yin}}]{Chi2022}
+\bibinfo{author}{\bibfnamefont{Y.}~\bibnamefont{Chi}},
+  \bibinfo{author}{\bibfnamefont{Y.}~\bibnamefont{Li}},
+  \bibinfo{author}{\bibfnamefont{Y.}~\bibnamefont{Zhao}},
+  \bibinfo{author}{\bibfnamefont{Y.}~\bibnamefont{Hong}},
+  \bibinfo{author}{\bibfnamefont{Y.}~\bibnamefont{Tang}}, \bibnamefont{and}
+  \bibinfo{author}{\bibfnamefont{J.}~\bibnamefont{Yin}},
+  \bibinfo{journal}{Advanced Materials}  (\bibinfo{year}{2022}).
+
+\bibitem[{\citenamefont{Bonfanti et~al.}(2020)\citenamefont{Bonfanti, Guerra,
+  Font-Clos, Rayneau-Kirkhope, and Zapperi}}]{Bonfanti2020}
+\bibinfo{author}{\bibfnamefont{S.}~\bibnamefont{Bonfanti}},
+  \bibinfo{author}{\bibfnamefont{R.}~\bibnamefont{Guerra}},
+  \bibinfo{author}{\bibfnamefont{F.}~\bibnamefont{Font-Clos}},
+  \bibinfo{author}{\bibfnamefont{D.}~\bibnamefont{Rayneau-Kirkhope}},
+  \bibnamefont{and} \bibinfo{author}{\bibfnamefont{S.}~\bibnamefont{Zapperi}},
+  \bibinfo{journal}{Nature Communications} \textbf{\bibinfo{volume}{11}},
+  \bibinfo{pages}{4162} (\bibinfo{year}{2020}).
+
+\bibitem[{\citenamefont{Shan et~al.}(2015)\citenamefont{Shan, Kang, Raney,
+  Wang, Fang, Candido, Lewis, and Bertoldi}}]{Shan2015}
+\bibinfo{author}{\bibfnamefont{S.}~\bibnamefont{Shan}},
+  \bibinfo{author}{\bibfnamefont{S.~H.} \bibnamefont{Kang}},
+  \bibinfo{author}{\bibfnamefont{J.~R.} \bibnamefont{Raney}},
+  \bibinfo{author}{\bibfnamefont{P.}~\bibnamefont{Wang}},
+  \bibinfo{author}{\bibfnamefont{L.}~\bibnamefont{Fang}},
+  \bibinfo{author}{\bibfnamefont{F.}~\bibnamefont{Candido}},
+  \bibinfo{author}{\bibfnamefont{J.~A.} \bibnamefont{Lewis}}, \bibnamefont{and}
+  \bibinfo{author}{\bibfnamefont{K.}~\bibnamefont{Bertoldi}},
+  \bibinfo{journal}{Advanced Materials} \textbf{\bibinfo{volume}{27}},
+  \bibinfo{pages}{4296} (\bibinfo{year}{2015}).
+
+\bibitem[{\citenamefont{Giri and Mailen}(2021)}]{Giri2021}
+\bibinfo{author}{\bibfnamefont{T.~R.} \bibnamefont{Giri}} \bibnamefont{and}
+  \bibinfo{author}{\bibfnamefont{R.}~\bibnamefont{Mailen}},
+  \bibinfo{journal}{International Journal of Mechanical Sciences}
+  \textbf{\bibinfo{volume}{204}}, \bibinfo{pages}{106541}
+  (\bibinfo{year}{2021}).
+
+\bibitem[{\citenamefont{Cerjan and Miller}(1981)}]{Cerjan1981}
+\bibinfo{author}{\bibfnamefont{C.~J.} \bibnamefont{Cerjan}} \bibnamefont{and}
+  \bibinfo{author}{\bibfnamefont{W.~H.} \bibnamefont{Miller}},
+  \bibinfo{journal}{The Journal of Chemical Physics}
+  \textbf{\bibinfo{volume}{75}}, \bibinfo{pages}{2800} (\bibinfo{year}{1981}).
+
+\bibitem[{\citenamefont{Heyden et~al.}(2005)\citenamefont{Heyden, Bell, and
+  Keil}}]{Heyden2005}
+\bibinfo{author}{\bibfnamefont{A.}~\bibnamefont{Heyden}},
+  \bibinfo{author}{\bibfnamefont{A.~T.} \bibnamefont{Bell}}, \bibnamefont{and}
+  \bibinfo{author}{\bibfnamefont{F.~J.} \bibnamefont{Keil}},
+  \bibinfo{journal}{Journal of Chemical Physics}
+  \textbf{\bibinfo{volume}{123}}, \bibinfo{pages}{224101}
+  (\bibinfo{year}{2005}).
+
+\bibitem[{\citenamefont{K{\"{a}}stner and Sherwood}(2008)}]{Kastner2008}
+\bibinfo{author}{\bibfnamefont{J.}~\bibnamefont{K{\"{a}}stner}}
+  \bibnamefont{and} \bibinfo{author}{\bibfnamefont{P.}~\bibnamefont{Sherwood}},
+  \bibinfo{journal}{Journal of Chemical Physics}
+  \textbf{\bibinfo{volume}{128}}, \bibinfo{pages}{014106}
+  (\bibinfo{year}{2008}).
+
+\bibitem[{\citenamefont{Zhang et~al.}(2016)\citenamefont{Zhang, Du, and
+  Zheng}}]{Zhang2016}
+\bibinfo{author}{\bibfnamefont{L.}~\bibnamefont{Zhang}},
+  \bibinfo{author}{\bibfnamefont{Q.}~\bibnamefont{Du}}, \bibnamefont{and}
+  \bibinfo{author}{\bibfnamefont{Z.}~\bibnamefont{Zheng}},
+  \bibinfo{journal}{SIAM Journal on Scientific Computing}
+  \textbf{\bibinfo{volume}{38}}, \bibinfo{pages}{A528} (\bibinfo{year}{2016}).
+
+\bibitem[{\citenamefont{E et~al.}(2007)\citenamefont{E, Ren, and
+  Vanden-Eijnden}}]{E2007}
+\bibinfo{author}{\bibfnamefont{W.}~\bibnamefont{E}},
+  \bibinfo{author}{\bibfnamefont{W.}~\bibnamefont{Ren}}, \bibnamefont{and}
+  \bibinfo{author}{\bibfnamefont{E.}~\bibnamefont{Vanden-Eijnden}},
+  \bibinfo{journal}{The Journal of Chemical Physics}
+  \textbf{\bibinfo{volume}{126}}, \bibinfo{pages}{164103}
+  (\bibinfo{year}{2007}).
+
+\bibitem[{\citenamefont{Ren and Vanden-Eijnden}(2013)}]{Ren2013}
+\bibinfo{author}{\bibfnamefont{W.}~\bibnamefont{Ren}} \bibnamefont{and}
+  \bibinfo{author}{\bibfnamefont{E.}~\bibnamefont{Vanden-Eijnden}},
+  \bibinfo{journal}{Journal of Chemical Physics}
+  \textbf{\bibinfo{volume}{138}}, \bibinfo{pages}{134105}
+  (\bibinfo{year}{2013}).
+
+\bibitem[{\citenamefont{E et~al.}(2002)\citenamefont{E, Ren, and
+  Vanden-Eijnden}}]{E2002}
+\bibinfo{author}{\bibfnamefont{W.}~\bibnamefont{E}},
+  \bibinfo{author}{\bibfnamefont{W.}~\bibnamefont{Ren}}, \bibnamefont{and}
+  \bibinfo{author}{\bibfnamefont{E.}~\bibnamefont{Vanden-Eijnden}},
+  \bibinfo{journal}{Physical Review B} \textbf{\bibinfo{volume}{66}},
+  \bibinfo{pages}{052301} (\bibinfo{year}{2002}).
+
+\bibitem[{\citenamefont{Trygubenko and Wales}(2004)}]{Trygubenko2004}
+\bibinfo{author}{\bibfnamefont{S.~A.} \bibnamefont{Trygubenko}}
+  \bibnamefont{and} \bibinfo{author}{\bibfnamefont{D.~J.} \bibnamefont{Wales}},
+  \bibinfo{journal}{Journal of Chemical Physics}
+  \textbf{\bibinfo{volume}{120}}, \bibinfo{pages}{2082} (\bibinfo{year}{2004}).
+
+\bibitem[{\citenamefont{Wales and Carr}(2012)}]{Wales2012a}
+\bibinfo{author}{\bibfnamefont{D.~J.} \bibnamefont{Wales}} \bibnamefont{and}
+  \bibinfo{author}{\bibfnamefont{J.~M.} \bibnamefont{Carr}},
+  \bibinfo{journal}{Journal of Chemical Theory and Computation}
+  \textbf{\bibinfo{volume}{8}}, \bibinfo{pages}{5020} (\bibinfo{year}{2012}).
+
+\bibitem[{\citenamefont{Trefethen and Thiyagalingam}(2013)}]{Trefethen2013}
+\bibinfo{author}{\bibfnamefont{A.~E.} \bibnamefont{Trefethen}}
+  \bibnamefont{and}
+  \bibinfo{author}{\bibfnamefont{J.}~\bibnamefont{Thiyagalingam}},
+  \bibinfo{journal}{Journal of Computational Science}
+  \textbf{\bibinfo{volume}{4}}, \bibinfo{pages}{444} (\bibinfo{year}{2013}).
+
+\bibitem[{\citenamefont{Shalf}(2020)}]{Shalf2020}
+\bibinfo{author}{\bibfnamefont{J.}~\bibnamefont{Shalf}},
+  \bibinfo{journal}{Philosophical Transactions Royal Society}
+  \textbf{\bibinfo{volume}{378}}, \bibinfo{pages}{20190061}
+  (\bibinfo{year}{2020}).
+
+\bibitem[{\citenamefont{Alexander et~al.}(2020)\citenamefont{Alexander,
+  Almgren, Bell, Bhattacharjee, Chen, Colella, Daniel, DeSlippe, Diachin,
+  Draeger et~al.}}]{Alexander2020}
+\bibinfo{author}{\bibfnamefont{F.}~\bibnamefont{Alexander}},
+  \bibinfo{author}{\bibfnamefont{A.}~\bibnamefont{Almgren}},
+  \bibinfo{author}{\bibfnamefont{J.}~\bibnamefont{Bell}},
+  \bibinfo{author}{\bibfnamefont{A.}~\bibnamefont{Bhattacharjee}},
+  \bibinfo{author}{\bibfnamefont{J.}~\bibnamefont{Chen}},
+  \bibinfo{author}{\bibfnamefont{P.}~\bibnamefont{Colella}},
+  \bibinfo{author}{\bibfnamefont{D.}~\bibnamefont{Daniel}},
+  \bibinfo{author}{\bibfnamefont{J.}~\bibnamefont{DeSlippe}},
+  \bibinfo{author}{\bibfnamefont{L.}~\bibnamefont{Diachin}},
+  \bibinfo{author}{\bibfnamefont{E.}~\bibnamefont{Draeger}},
+  \bibnamefont{et~al.}, \bibinfo{journal}{Philosophical Transactions of the
+  Royal Society A} \textbf{\bibinfo{volume}{378}}, \bibinfo{pages}{20190056}
+  (\bibinfo{year}{2020}).
+
+\bibitem[{\citenamefont{McMullen et~al.}(2018)\citenamefont{McMullen,
+  Holmes-Cerfon, Sciortino, Grosberg, and Brujic}}]{McMullen2018}
+\bibinfo{author}{\bibfnamefont{A.}~\bibnamefont{McMullen}},
+  \bibinfo{author}{\bibfnamefont{M.}~\bibnamefont{Holmes-Cerfon}},
+  \bibinfo{author}{\bibfnamefont{F.}~\bibnamefont{Sciortino}},
+  \bibinfo{author}{\bibfnamefont{A.~Y.} \bibnamefont{Grosberg}},
+  \bibnamefont{and} \bibinfo{author}{\bibfnamefont{J.}~\bibnamefont{Brujic}},
+  \bibinfo{journal}{Physical Review Letters} \textbf{\bibinfo{volume}{121}},
+  \bibinfo{pages}{138002} (\bibinfo{year}{2018}).
+
+\bibitem[{\citenamefont{Nguemaha and Zhou}(2018)}]{Nguemaha2018}
+\bibinfo{author}{\bibfnamefont{V.}~\bibnamefont{Nguemaha}} \bibnamefont{and}
+  \bibinfo{author}{\bibfnamefont{H.~X.} \bibnamefont{Zhou}},
+  \bibinfo{journal}{Scientific Reports} \textbf{\bibinfo{volume}{8}},
+  \bibinfo{pages}{1} (\bibinfo{year}{2018}).
+
+\bibitem[{\citenamefont{Chen et~al.}(2018)\citenamefont{Chen, Zhang, and
+  Torquato}}]{Chen2018b}
+\bibinfo{author}{\bibfnamefont{D.}~\bibnamefont{Chen}},
+  \bibinfo{author}{\bibfnamefont{G.}~\bibnamefont{Zhang}}, \bibnamefont{and}
+  \bibinfo{author}{\bibfnamefont{S.}~\bibnamefont{Torquato}},
+  \bibinfo{journal}{Journal of Physical Chemistry B}
+  \textbf{\bibinfo{volume}{122}}, \bibinfo{pages}{8462} (\bibinfo{year}{2018}).
+
+\bibitem[{\citenamefont{Santra et~al.}(2018)\citenamefont{Santra, Singh, and
+  Bagchi}}]{Santra2018}
+\bibinfo{author}{\bibfnamefont{M.}~\bibnamefont{Santra}},
+  \bibinfo{author}{\bibfnamefont{R.~S.} \bibnamefont{Singh}}, \bibnamefont{and}
+  \bibinfo{author}{\bibfnamefont{B.}~\bibnamefont{Bagchi}},
+  \bibinfo{journal}{Physical Review E} \textbf{\bibinfo{volume}{98}},
+  \bibinfo{pages}{032606} (\bibinfo{year}{2018}).
+
+\bibitem[{\citenamefont{M{\"{o}}kk{\"{o}}nen
+  et~al.}(2016)\citenamefont{M{\"{o}}kk{\"{o}}nen, Ala-Nissila, and
+  J{\'{o}}nsson}}]{Mokkonen2016}
+\bibinfo{author}{\bibfnamefont{H.}~\bibnamefont{M{\"{o}}kk{\"{o}}nen}},
+  \bibinfo{author}{\bibfnamefont{T.}~\bibnamefont{Ala-Nissila}},
+  \bibnamefont{and}
+  \bibinfo{author}{\bibfnamefont{H.}~\bibnamefont{J{\'{o}}nsson}},
+  \bibinfo{journal}{The Journal of Chemical Physics}
+  \textbf{\bibinfo{volume}{145}}, \bibinfo{pages}{094901}
+  (\bibinfo{year}{2016}).
+
+\bibitem[{\citenamefont{Wriggers}(2006)}]{Wriggers2006}
+\bibinfo{author}{\bibfnamefont{P.}~\bibnamefont{Wriggers}},
+  \emph{\bibinfo{title}{{Computational Contact Mechanics}}}
+  (\bibinfo{publisher}{Springer Berlin Heidelberg}, \bibinfo{address}{Berlin,
+  Heidelberg}, \bibinfo{year}{2006}).
+
+\bibitem[{\citenamefont{Page and McIver}(1988)}]{Page1988}
+\bibinfo{author}{\bibfnamefont{M.}~\bibnamefont{Page}} \bibnamefont{and}
+  \bibinfo{author}{\bibfnamefont{J.~W.} \bibnamefont{McIver}},
+  \bibinfo{journal}{The Journal of Chemical Physics}
+  \textbf{\bibinfo{volume}{88}}, \bibinfo{pages}{922} (\bibinfo{year}{1988}).
+
+\bibitem[{\citenamefont{Liu and Nocedal}(1989)}]{Liu1989}
+\bibinfo{author}{\bibfnamefont{D.~C.} \bibnamefont{Liu}} \bibnamefont{and}
+  \bibinfo{author}{\bibfnamefont{J.}~\bibnamefont{Nocedal}},
+  \bibinfo{journal}{Mathematical Programming} \textbf{\bibinfo{volume}{45}},
+  \bibinfo{pages}{503} (\bibinfo{year}{1989}).
+
+\bibitem[{\citenamefont{Wales}(2002)}]{Wales2002}
+\bibinfo{author}{\bibfnamefont{D.~J.} \bibnamefont{Wales}},
+  \bibinfo{journal}{Molecular Physics} \textbf{\bibinfo{volume}{100}},
+  \bibinfo{pages}{3285} (\bibinfo{year}{2002}).
+
+\bibitem[{\citenamefont{Passerone and Parrinello}(2001)}]{Passerone2001}
+\bibinfo{author}{\bibfnamefont{D.}~\bibnamefont{Passerone}} \bibnamefont{and}
+  \bibinfo{author}{\bibfnamefont{M.}~\bibnamefont{Parrinello}},
+  \bibinfo{journal}{Physical Review Letters} \textbf{\bibinfo{volume}{87}},
+  \bibinfo{pages}{108302} (\bibinfo{year}{2001}).
+
+\bibitem[{\citenamefont{Virot et~al.}(2017)\citenamefont{Virot, Kreilos,
+  Schneider, and Rubinstein}}]{Virot2017}
+\bibinfo{author}{\bibfnamefont{E.}~\bibnamefont{Virot}},
+  \bibinfo{author}{\bibfnamefont{T.}~\bibnamefont{Kreilos}},
+  \bibinfo{author}{\bibfnamefont{T.~M.} \bibnamefont{Schneider}},
+  \bibnamefont{and} \bibinfo{author}{\bibfnamefont{S.~M.}
+  \bibnamefont{Rubinstein}}, \bibinfo{journal}{Physical Review Letters}
+  \textbf{\bibinfo{volume}{119}}, \bibinfo{pages}{224101}
+  (\bibinfo{year}{2017}).
+
+\bibitem[{\citenamefont{Kusumaatmaja et~al.}(2006)\citenamefont{Kusumaatmaja,
+  L{\'{e}}opold{\`{e}}s, Dupuis, and Yeomans}}]{Kusumaatmaja2006}
+\bibinfo{author}{\bibfnamefont{H.}~\bibnamefont{Kusumaatmaja}},
+  \bibinfo{author}{\bibfnamefont{J.}~\bibnamefont{L{\'{e}}opold{\`{e}}s}},
+  \bibinfo{author}{\bibfnamefont{A.}~\bibnamefont{Dupuis}}, \bibnamefont{and}
+  \bibinfo{author}{\bibfnamefont{J.~M.} \bibnamefont{Yeomans}},
+  \bibinfo{journal}{Europhysics Letters} \textbf{\bibinfo{volume}{73}},
+  \bibinfo{pages}{740} (\bibinfo{year}{2006}).
+
+\bibitem[{\citenamefont{Brown and Bhushan}(2016)}]{Brown2016}
+\bibinfo{author}{\bibfnamefont{P.~S.} \bibnamefont{Brown}} \bibnamefont{and}
+  \bibinfo{author}{\bibfnamefont{B.}~\bibnamefont{Bhushan}},
+  \bibinfo{journal}{Philosophical Transactions of the Royal Society A}
+  \textbf{\bibinfo{volume}{374}}, \bibinfo{pages}{20160135}
+  (\bibinfo{year}{2016}).
+
+\bibitem[{\citenamefont{Kirkpatrick et~al.}(1983)\citenamefont{Kirkpatrick,
+  Gelatt, and Vecchi}}]{Kirkpatrick1983}
+\bibinfo{author}{\bibfnamefont{S.}~\bibnamefont{Kirkpatrick}},
+  \bibinfo{author}{\bibfnamefont{C.~D.} \bibnamefont{Gelatt}},
+  \bibnamefont{and} \bibinfo{author}{\bibfnamefont{M.~P.}
+  \bibnamefont{Vecchi}}, \bibinfo{journal}{Science}
+  \textbf{\bibinfo{volume}{220}}, \bibinfo{pages}{671} (\bibinfo{year}{1983}).
+
+\end{thebibliography}
 %% end bib

### 2022-04-18 manuscript.tex
Add discussion of hybrid methods to conclusion, modify string/DNEB, add distance metric.

@@
 A reduction factor of $f = 0.5$ is successful for most applications, but this can be made smaller to ensure that the states do not slide off the ridge between the two basins of attraction.
-Different metrics may be used to compute the distance.
-%######
+Different metrics may be used to compute this distance, although in this work we simply use the Euclidean distance,
+\begin{equation}
+  \mathrm{d}(\bm{x}_1, \bm{x}_2) = \sqrt{\sum_i (x_{1,i} - x_{2,i})^2}.
+\end{equation}
 To further ensure that neither state is pulled over the ridge, a secondary constraint enforces equal energies for the two states.
@@
 \end{multline}
-where $E_1$ and $E_2$ are the single state energies, $\kappa_e$ and $\kappa_d$ parametrise the strengths of the energy and distance constraints, and $\mathrm{d}(\bm{x}_1, \bm{x}_2)$ is the measure of distance between the two states.
+where $E_1$ and $E_2$ are the single state energies, and $\kappa_e$ and $\kappa_d$ parametrise the strengths of the energy and distance constraints.
 
@@
 Once BITSS has identified the transition state, it is possible to find the full minimum energy pathway by tracing the trajectory of downhill minimisations from the two final states, either side of the transition state.
-In the case where there is a chain of transition states between the two starting minima, BITSS will identify the transition state with the highest energy in the chain.
-If all of transition states or the full pathway are desired instead, BITSS can be continually repeated from one of the minima downhill from the located transition state and one of the initial minima until the initial minima are piecewise connected by a full pathway.
+In the case where there are intermediaries, resulting in a chain of multiple transition states between the two minima, BITSS will identify the transition state with the highest energy in the chain.
+This enables the identification of the overall energy barrier, providing estimates about the overall ease of the transition, or the rate for chemical processes.
+However, if all of transition states or the full pathway are desired, BITSS can be continually repeated from one of the minima downhill from the located transition state and one of the initial minima until the initial minima are piecewise connected by a full pathway.
 
@@
 Overall, we have developed the binary image transition state search (BITSS) algorithm for the efficient location of transition states in traditionally challenging landscapes.
-Principally, the demonstrated speed and memory-efficiency will be key as we move towards simulating systems with increasingly large numbers of degrees of freedom, such as in large biomolecules, or with increasingly fine resolution, such as in finite element domains.
+This has distinct advantages for complex pathways owing to the lack of a required initial pathway estimate, as well as the identification of the transition state that provides the overall energy barrier in multi-step pathways.
+Furthermore, the demonstrated speed and memory-efficiency will be key as we move towards simulating systems with increasingly large numbers of degrees of freedom, such as in large biomolecules, or with increasingly fine resolution, such as in finite element domains.
 
@@
 We demonstrated how transition states could be found by both increasing the resolution upon convergence, and coupling systems with different discretisations.
-The ease of coupling two copies of a system and adaptive remeshing, now leads to the possibility of incorporating BITSS into existing optimisation methods, such as surface evolver or finite element analysis software, to provide important energy barrier functionality.
+The ease of coupling two copies of a system and adaptive remeshing, now leads to the possibility of incorporating BITSS into existing optimisation methods, such as surface evolver \cite{Brakke1992} or finite element analysis software, to provide important energy barrier functionality.
 
@@
 This opens up possibilities for studying a broad range of systems previously out of reach of conventional landscape methods, but where transition information is valuable.
-These include systems with very short range interactions or contact forces, such as in colloidal clusters, wrinkling and buckling of elastic materials, or locomotion and environmental interaction in robotics.
+These include systems with very short range interactions or contact forces, such as in colloidal clusters, wrinkling and folding of elastic materials, or locomotion and environmental interaction in robotics.
 
-The distance metric between the two BITSS images proves interesting to analyse further in the future.
+During the comparison with other methods, we have not considered hybrid methods, which involve switching to a single-ended method when close to the transition state, for greater accuracy and efficiency.
+While BITSS does not need to use such a hybrid method to accurately find the transition state, it could be utilised to further increase the efficiency of the algorithm.
+Therefore, future work is to look into how best to implement this and see how it compares against other hybrid methods.
+
+The distance metric between the two BITSS images also proves interesting to analyse further.
 One question that emerges is whether transition states can be located by coupling two images through a small number of collective properties, rather than the total distance between all degrees of freedom in the system.
@@
 \section{Methods}
+
+\subsection{Implementing the string and DNEB methods}
+In the convergence rate comparison in \cref{fig:speedtest}, the string method and doubly-nudged elastic band method (DNEB) are used, based upon \cite{E2007} and \cite{Trygubenko2004}, respectively.
+Each method is initialised with 5, 10, or 20 images, using a linear interpolation between the chosen end states.
+
+In each iteration of the string method, each image is evolved downhill for a number of LBFGS iterations before redistributing the images along a cubic-spline interpolated path.
+This number of iterations is varied to obtain the fastest convergence, for which we find 2, 50, and 20 to be optimal for the particle cluster, cylidrical buckling, and striped wetting examples, respectively.
+
+In the case of DNEB, the spring constant between the images is instead optimised.
+For the particle cluster system, a spring constant of $1$ is used for the 5 image case, and $0.1$ for 10 and 20 images.
+For the cylindrical buckling, the spring constant is $0.01$ in all cases.
+And for the striped wetting, $10^{-4}$ is used for 5 and 10 images, and $10^{-3}$ for 20 images.
 
@@
 %% mid bib
-\begin{thebibliography}{50}
+\begin{thebibliography}{51}
 \expandafter\ifx\csname natexlab\endcsname\relax\def\natexlab#1{#1}\fi
@@
 
+\bibitem[{\citenamefont{Brakke}(1992)}]{Brakke1992}
+\bibinfo{author}{\bibfnamefont{K.~A.} \bibnamefont{Brakke}},
+  \bibinfo{journal}{Experimental Mathematics} \textbf{\bibinfo{volume}{1}},
+  \bibinfo{pages}{141} (\bibinfo{year}{1992}).
+
 \bibitem[{\citenamefont{Kirkpatrick et~al.}(1983)\citenamefont{Kirkpatrick,

### 2022-04-20 fig/make_adaptivemesh/plot.py
Figures font and dpi updated

@@ -270,7 +270,7 @@ def main():
     plot_cb(fig, h2/h, h)
     plot_sw(fig, h2/h, h)
 
-    lt.savefig('../adaptivemesh.pdf', dpi=500)
+    lt.savefig('../adaptivemesh.pdf')
 
 
 if (__name__ == "__main__"):

### 2022-04-20 fig/make_flatdiscontinuous/plot.py

@@ -304,7 +304,7 @@ def main():
     fig = lt.figure(1, h)
     plot_flat(fig, [h2/h, h1/h])
     plot_discontinuous(fig, [0, h2/h])
-    lt.savefig('../flatdiscontinuous.pdf', dpi=500)
+    lt.savefig('../flatdiscontinuous.pdf')
 
 
 if (__name__ == '__main__'):

### 2022-04-20 fig/make_speedtest/plot.py

@@ -8,7 +8,7 @@ import pyutils.latexify as lt
 # Get default style for paper
 import sys; sys.path.insert(0, '..')
 import style
-lt.update_width('r4-double')
+lt.update_width('natcomm-double')
 
 # Data generated by energyLandscapes/bits_test/speed_test/{system}/view_convergence.py
 
@@ -119,4 +119,4 @@ for isub, subfig in enumerate(['a', 'b', 'c']):
         if (i==1):
             tmp_ax.text(0.25, 1, '*', va='top', ha='center', size='xx-large', transform=tmp_ax.transAxes)
 
-lt.savefig(f'../speedtest.pdf', dpi=300)
+lt.savefig(f'../speedtest.pdf')

### 2022-04-20 fig/make_toy2d/plot.py

@@ -61,7 +61,7 @@ fig = plt.figure(frameon=False, figsize=(xlim[1]-xlim[0], ylim[1]-ylim[0]))
 ax = fig.add_axes([0,0,1,1])
 plt.contourf(x, y, e, cmap=cmap, levels=10)
 ax.axis('off')
-plt.savefig(f'potential.png', dpi=500)
+plt.savefig(f'potential.png')
 
 
 ### Read data
@@ -189,4 +189,4 @@ axc.text(0.78, 0.4, r'$\bm{\hat\tau}$', transform=axc.transAxes)#.set_path_effec
 #plt.quiver(bits[i,:,0], bits[i,:,1], gd[:,0], gd[:,1], **arrow_args)
 
 # plt.show()
-lt.savefig('../toy2d.pdf', dpi=400)
+lt.savefig('../toy2d.pdf')

### 2022-04-20 fig/style.py

@@ -1,12 +1,26 @@
 #!/usr/bin/env python3
 
+import matplotlib as mpl
 import matplotlib.pyplot as plt
 import pyutils.latexify as lt
 
-lt.update_width('r4-single')
+lt.dpi = 500
+lt.update_width('natcomm-single')
+
+# Font size
 plt.rc('font', size=9)
 plt.rc('axes', labelsize=9)
 
+# Helvetica font
+mpl.rcParams['font.family'] = 'sans-serif'
+mpl.rcParams['font.sans-serif'] = ['Helvetica']
+mpl.rcParams['text.latex.preamble'] = "\n".join([mpl.rcParams['text.latex.preamble'],
+                                                 r"\usepackage{helvet}",
+                                                 r"\usepackage{sansmath}",
+                                                 r"\sansmath"])
+
+# Colours
+plt.rc('font', size=9)
 c1 = 'tab:orange'
 c2 = 'tab:red'
 c3 = 'tab:blue'

### 2022-04-21 manuscript.tex
Figures font and dpi updated
Changed bib to nature style

@@
 \subsection{BITSS method}
-\begin{figure}[htb]
-  \includegraphics{toy2d.pdf}
+\begin{figure}[tb]
+  \includegraphics[width=\linewidth]{toy2d.pdf}
   \caption{\label{fig:toy2d}
@@
 \begin{figure*}[tb]
-  \includegraphics{speedtest.pdf}
+  \includegraphics[width=\linewidth]{speedtest.pdf}
   \caption{\label{fig:speedtest}
@@
 
-\subsection{Adaptive discretisation}
-\label{sec:adaptive}
+\subsection{Adaptive discretisation}\label{sec:adaptive}
 \begin{figure}[tb]
-  \includegraphics{adaptivemesh.pdf}
+  \includegraphics[width=\linewidth]{adaptivemesh.pdf}
   \caption{\label{fig:adaptivemesh}
@@
 \begin{figure}[tb]
-  \includegraphics{flatdiscontinuous.pdf}
+  \includegraphics[width=\linewidth]{flatdiscontinuous.pdf}
   \caption{\label{fig:flatdiscontinuous}
@@
 %% start bib
+% % \bibliography{../../library.bib}
 % \bibliography{bibexport.bib}
-% % \bibliography{../../library.bib}
-% % \bibliographystyle{apsrev4}
+% \bibliographystyle{naturemag}
 %% mid bib
-\begin{thebibliography}{51}
-\expandafter\ifx\csname natexlab\endcsname\relax\def\natexlab#1{#1}\fi
-\expandafter\ifx\csname bibnamefont\endcsname\relax
-  \def\bibnamefont#1{#1}\fi
-\expandafter\ifx\csname bibfnamefont\endcsname\relax
-  \def\bibfnamefont#1{#1}\fi
-\expandafter\ifx\csname citenamefont\endcsname\relax
-  \def\citenamefont#1{#1}\fi
+\begin{thebibliography}{10}
 \expandafter\ifx\csname url\endcsname\relax
@@
 
-\bibitem[{\citenamefont{Bryngelson et~al.}(1995)\citenamefont{Bryngelson,
-  Onuchic, Socci, and Wolynes}}]{Bryngelson1995}
-\bibinfo{author}{\bibfnamefont{J.~D.} \bibnamefont{Bryngelson}},
-  \bibinfo{author}{\bibfnamefont{J.~N.} \bibnamefont{Onuchic}},
-  \bibinfo{author}{\bibfnamefont{N.~D.} \bibnamefont{Socci}}, \bibnamefont{and}
-  \bibinfo{author}{\bibfnamefont{P.~G.} \bibnamefont{Wolynes}},
-  \bibinfo{journal}{Proteins: Structure, Function, and Bioinformatics}
-  \textbf{\bibinfo{volume}{21}}, \bibinfo{pages}{167} (\bibinfo{year}{1995}).
+\bibitem{Bryngelson1995}
+\bibinfo{author}{Bryngelson, J.~D.}, \bibinfo{author}{Onuchic, J.~N.},
+  \bibinfo{author}{Socci, N.~D.} \& \bibinfo{author}{Wolynes, P.~G.}
+\newblock \bibinfo{title}{{Funnels, pathways, and the energy landscape of
+  protein folding: A synthesis}}.
+\newblock \emph{\bibinfo{journal}{Proteins: Structure, Function, and
+  Bioinformatics}} \textbf{\bibinfo{volume}{21}}, \bibinfo{pages}{167--195}
+  (\bibinfo{year}{1995}).
 
-\bibitem[{\citenamefont{Onuchic et~al.}(1997)\citenamefont{Onuchic,
-  Luthey-Schulten, and Wolynes}}]{Onuchic1997}
-\bibinfo{author}{\bibfnamefont{J.~N.} \bibnamefont{Onuchic}},
-  \bibinfo{author}{\bibfnamefont{Z.}~\bibnamefont{Luthey-Schulten}},
-  \bibnamefont{and} \bibinfo{author}{\bibfnamefont{P.~G.}
-  \bibnamefont{Wolynes}}, \bibinfo{journal}{Annual Review of Physical
-  Chemistry} \textbf{\bibinfo{volume}{48}}, \bibinfo{pages}{545}
+\bibitem{Onuchic1997}
+\bibinfo{author}{Onuchic, J.~N.}, \bibinfo{author}{Luthey-Schulten, Z.} \&
+  \bibinfo{author}{Wolynes, P.~G.}
+\newblock \bibinfo{title}{{Theory of Protein Folding: The Energy Landscape
+  Perspective}}.
+\newblock \emph{\bibinfo{journal}{Annual Review of Physical Chemistry}}
+  \textbf{\bibinfo{volume}{48}}, \bibinfo{pages}{545--600}
   (\bibinfo{year}{1997}).
 
-\bibitem[{\citenamefont{Boehr et~al.}(2006)\citenamefont{Boehr, McElheny,
-  Dyson, and Wrightt}}]{Boehr2006}
-\bibinfo{author}{\bibfnamefont{D.~D.} \bibnamefont{Boehr}},
-  \bibinfo{author}{\bibfnamefont{D.}~\bibnamefont{McElheny}},
-  \bibinfo{author}{\bibfnamefont{H.~J.} \bibnamefont{Dyson}}, \bibnamefont{and}
-  \bibinfo{author}{\bibfnamefont{P.~E.} \bibnamefont{Wrightt}},
-  \bibinfo{journal}{Science} \textbf{\bibinfo{volume}{313}},
-  \bibinfo{pages}{1638} (\bibinfo{year}{2006}).
+\bibitem{Boehr2006}
+\bibinfo{author}{Boehr, D.~D.}, \bibinfo{author}{McElheny, D.},
+  \bibinfo{author}{Dyson, H.~J.} \& \bibinfo{author}{Wrightt, P.~E.}
+\newblock \bibinfo{title}{{The dynamic energy landscape of dihydrofolate
+  reductase catalysis}}.
+\newblock \emph{\bibinfo{journal}{Science}} \textbf{\bibinfo{volume}{313}},
+  \bibinfo{pages}{1638--1642} (\bibinfo{year}{2006}).
 
-\bibitem[{\citenamefont{Kerns et~al.}(2015)\citenamefont{Kerns, Agafonov, Cho,
-  Pontiggia, Otten, Pachov, Kutter, Phung, Murphy, Thai et~al.}}]{Kerns2015}
-\bibinfo{author}{\bibfnamefont{S.~J.} \bibnamefont{Kerns}},
-  \bibinfo{author}{\bibfnamefont{R.~V.} \bibnamefont{Agafonov}},
-  \bibinfo{author}{\bibfnamefont{Y.~J.} \bibnamefont{Cho}},
-  \bibinfo{author}{\bibfnamefont{F.}~\bibnamefont{Pontiggia}},
-  \bibinfo{author}{\bibfnamefont{R.}~\bibnamefont{Otten}},
-  \bibinfo{author}{\bibfnamefont{D.~V.} \bibnamefont{Pachov}},
-  \bibinfo{author}{\bibfnamefont{S.}~\bibnamefont{Kutter}},
-  \bibinfo{author}{\bibfnamefont{L.~A.} \bibnamefont{Phung}},
-  \bibinfo{author}{\bibfnamefont{P.~N.} \bibnamefont{Murphy}},
-  \bibinfo{author}{\bibfnamefont{V.}~\bibnamefont{Thai}}, \bibnamefont{et~al.},
-  \bibinfo{journal}{Nature Structural and Molecular Biology}
-  \textbf{\bibinfo{volume}{22}}, \bibinfo{pages}{124} (\bibinfo{year}{2015}).
+\bibitem{Kerns2015}
+\bibinfo{author}{Kerns, S.~J.} \emph{et~al.}
+\newblock \bibinfo{title}{{The energy landscape of adenylate kinase during
+  catalysis}}.
+\newblock \emph{\bibinfo{journal}{Nature Structural and Molecular Biology}}
+  \textbf{\bibinfo{volume}{22}}, \bibinfo{pages}{124--131}
+  (\bibinfo{year}{2015}).
 
-\bibitem[{\citenamefont{Guo et~al.}(2018)\citenamefont{Guo, Wang, Wang, Wang,
-  and Hu}}]{Guo2018a}
-\bibinfo{author}{\bibfnamefont{C.}~\bibnamefont{Guo}},
-  \bibinfo{author}{\bibfnamefont{Z.}~\bibnamefont{Wang}},
-  \bibinfo{author}{\bibfnamefont{D.}~\bibnamefont{Wang}},
-  \bibinfo{author}{\bibfnamefont{H.~F.} \bibnamefont{Wang}}, \bibnamefont{and}
-  \bibinfo{author}{\bibfnamefont{P.}~\bibnamefont{Hu}},
-  \bibinfo{journal}{Journal of Physical Chemistry C}
-  \textbf{\bibinfo{volume}{122}}, \bibinfo{pages}{21478}
+\bibitem{Guo2018a}
+\bibinfo{author}{Guo, C.}, \bibinfo{author}{Wang, Z.}, \bibinfo{author}{Wang,
+  D.}, \bibinfo{author}{Wang, H.~F.} \& \bibinfo{author}{Hu, P.}
+\newblock \bibinfo{title}{{First-Principles Determination of CO Adsorption and
+  Desorption on Pt(111) in the Free Energy Landscape}}.
+\newblock \emph{\bibinfo{journal}{Journal of Physical Chemistry C}}
+  \textbf{\bibinfo{volume}{122}}, \bibinfo{pages}{21478--21483}
   (\bibinfo{year}{2018}).
 
-\bibitem[{\citenamefont{Richardson et~al.}(2016)\citenamefont{Richardson,
-  P{\'{e}}rez, Lobsiger, Reid, Temelso, Shields, Kisiel, Wales, Pate, and
-  Althorpe}}]{Richardson2016}
-\bibinfo{author}{\bibfnamefont{J.~O.} \bibnamefont{Richardson}},
-  \bibinfo{author}{\bibfnamefont{C.}~\bibnamefont{P{\'{e}}rez}},
-  \bibinfo{author}{\bibfnamefont{S.}~\bibnamefont{Lobsiger}},
-  \bibinfo{author}{\bibfnamefont{A.~A.} \bibnamefont{Reid}},
-  \bibinfo{author}{\bibfnamefont{B.}~\bibnamefont{Temelso}},
-  \bibinfo{author}{\bibfnamefont{G.~C.} \bibnamefont{Shields}},
-  \bibinfo{author}{\bibfnamefont{Z.}~\bibnamefont{Kisiel}},
-  \bibinfo{author}{\bibfnamefont{D.~J.} \bibnamefont{Wales}},
-  \bibinfo{author}{\bibfnamefont{B.~H.} \bibnamefont{Pate}}, \bibnamefont{and}
-  \bibinfo{author}{\bibfnamefont{S.~C.} \bibnamefont{Althorpe}},
-  \bibinfo{journal}{Science} \textbf{\bibinfo{volume}{351}},
+\bibitem{Richardson2016}
+\bibinfo{author}{Richardson, J.~O.} \emph{et~al.}
+\newblock \bibinfo{title}{{Concerted hydrogen-bond breaking by quantum
+  tunneling in the water hexamer prism}}.
+\newblock \emph{\bibinfo{journal}{Science}} \textbf{\bibinfo{volume}{351}},
   \bibinfo{pages}{1310} (\bibinfo{year}{2016}).
 
-\bibitem[{\citenamefont{Vaillant et~al.}(2019)\citenamefont{Vaillant, Althorpe,
-  and Wales}}]{Vaillant2019}
-\bibinfo{author}{\bibfnamefont{C.~L.} \bibnamefont{Vaillant}},
-  \bibinfo{author}{\bibfnamefont{S.~C.} \bibnamefont{Althorpe}},
-  \bibnamefont{and} \bibinfo{author}{\bibfnamefont{D.~J.} \bibnamefont{Wales}},
-  \bibinfo{journal}{Journal of Chemical Theory and Computation}
-  \textbf{\bibinfo{volume}{15}}, \bibinfo{pages}{33} (\bibinfo{year}{2019}).
+\bibitem{Vaillant2019}
+\bibinfo{author}{Vaillant, C.~L.}, \bibinfo{author}{Althorpe, S.~C.} \&
+  \bibinfo{author}{Wales, D.~J.}
+\newblock \bibinfo{title}{{Path Integral Energy Landscapes for Water
+  Clusters}}.
+\newblock \emph{\bibinfo{journal}{Journal of Chemical Theory and Computation}}
+  \textbf{\bibinfo{volume}{15}}, \bibinfo{pages}{33--42}
+  (\bibinfo{year}{2019}).
 
-\bibitem[{\citenamefont{Richard and Speck}(2018)}]{Richard2018}
-\bibinfo{author}{\bibfnamefont{D.}~\bibnamefont{Richard}} \bibnamefont{and}
-  \bibinfo{author}{\bibfnamefont{T.}~\bibnamefont{Speck}},
-  \bibinfo{journal}{The Journal of Chemical Physics}
+\bibitem{Richard2018}
+\bibinfo{author}{Richard, D.} \& \bibinfo{author}{Speck, T.}
+\newblock \bibinfo{title}{{Crystallization of hard spheres revisited. I.
+  Extracting kinetics and free energy landscape from forward flux sampling}}.
+\newblock \emph{\bibinfo{journal}{The Journal of Chemical Physics}}
   \textbf{\bibinfo{volume}{148}}, \bibinfo{pages}{124110}
@@
 
-\bibitem[{\citenamefont{Wales et~al.}(1998)\citenamefont{Wales, Miller, and
-  Walsh}}]{Wales1998}
-\bibinfo{author}{\bibfnamefont{D.~J.} \bibnamefont{Wales}},
-  \bibinfo{author}{\bibfnamefont{M.~A.} \bibnamefont{Miller}},
-  \bibnamefont{and} \bibinfo{author}{\bibfnamefont{T.~R.} \bibnamefont{Walsh}},
-  \bibinfo{journal}{Nature} \textbf{\bibinfo{volume}{394}},
-  \bibinfo{pages}{758} (\bibinfo{year}{1998}).
+\bibitem{Wales1998}
+\bibinfo{author}{Wales, D.~J.}, \bibinfo{author}{Miller, M.~A.} \&
+  \bibinfo{author}{Walsh, T.~R.}
+\newblock \bibinfo{title}{{Archetypal energy landscapes}}.
+\newblock \emph{\bibinfo{journal}{Nature}} \textbf{\bibinfo{volume}{394}},
+  \bibinfo{pages}{758--760} (\bibinfo{year}{1998}).
 
-\bibitem[{\citenamefont{Wales}(2012)}]{Wales2012}
-\bibinfo{author}{\bibfnamefont{D.~J.} \bibnamefont{Wales}},
-  \bibinfo{journal}{Philosophical Transactions of the Royal Society A:
-  Mathematical, Physical and Engineering Sciences}
-  \textbf{\bibinfo{volume}{370}}, \bibinfo{pages}{2877} (\bibinfo{year}{2012}).
+\bibitem{Wales2012}
+\bibinfo{author}{Wales, D.~J.}
+\newblock \bibinfo{title}{{Decoding the energy landscape: Extracting structure,
+  dynamics and thermodynamics}}.
+\newblock \emph{\bibinfo{journal}{Philosophical Transactions of the Royal
+  Society A: Mathematical, Physical and Engineering Sciences}}
+  \textbf{\bibinfo{volume}{370}}, \bibinfo{pages}{2877--2899}
+  (\bibinfo{year}{2012}).
 
-\bibitem[{\citenamefont{Panter et~al.}(2019{\natexlab{a}})\citenamefont{Panter,
-  Chen, Zhang, and Kusumaatmaja}}]{Panter2019}
-\bibinfo{author}{\bibfnamefont{J.~R.} \bibnamefont{Panter}},
-  \bibinfo{author}{\bibfnamefont{J.}~\bibnamefont{Chen}},
-  \bibinfo{author}{\bibfnamefont{T.}~\bibnamefont{Zhang}}, \bibnamefont{and}
-  \bibinfo{author}{\bibfnamefont{H.}~\bibnamefont{Kusumaatmaja}},
-  \bibinfo{journal}{Communications Physics} \textbf{\bibinfo{volume}{2}},
-  \bibinfo{pages}{151} (\bibinfo{year}{2019}{\natexlab{a}}).
+\bibitem{Panter2019}
+\bibinfo{author}{Panter, J.~R.}, \bibinfo{author}{Chen, J.},
+  \bibinfo{author}{Zhang, T.} \& \bibinfo{author}{Kusumaatmaja, H.}
+\newblock \bibinfo{title}{{Harnessing energy landscape exploration to control
+  the buckling of cylindrical shells}}.
+\newblock \emph{\bibinfo{journal}{Communications Physics}}
+  \textbf{\bibinfo{volume}{2}}, \bibinfo{pages}{151} (\bibinfo{year}{2019}).
 
-\bibitem[{\citenamefont{Hutchinson and Thompson}(2018)}]{Hutchinson2018}
-\bibinfo{author}{\bibfnamefont{J.~W.} \bibnamefont{Hutchinson}}
-  \bibnamefont{and} \bibinfo{author}{\bibfnamefont{J.~M.~T.}
-  \bibnamefont{Thompson}}, \bibinfo{journal}{International Journal of Solids
-  and Structures} \textbf{\bibinfo{volume}{148-149}}, \bibinfo{pages}{157}
+\bibitem{Hutchinson2018}
+\bibinfo{author}{Hutchinson, J.~W.} \& \bibinfo{author}{Thompson, J. M.~T.}
+\newblock \bibinfo{title}{{Imperfections and energy barriers in shell
+  buckling}}.
+\newblock \emph{\bibinfo{journal}{International Journal of Solids and
+  Structures}} \textbf{\bibinfo{volume}{148-149}}, \bibinfo{pages}{157--168}
   (\bibinfo{year}{2018}).
 
-\bibitem[{\citenamefont{Zhang and Ren}(2014)}]{Zhang2014}
-\bibinfo{author}{\bibfnamefont{Y.}~\bibnamefont{Zhang}} \bibnamefont{and}
-  \bibinfo{author}{\bibfnamefont{W.}~\bibnamefont{Ren}}, \bibinfo{journal}{The
-  Journal of Chemical Physics} \textbf{\bibinfo{volume}{141}},
-  \bibinfo{pages}{244705} (\bibinfo{year}{2014}).
+\bibitem{Zhang2014}
+\bibinfo{author}{Zhang, Y.} \& \bibinfo{author}{Ren, W.}
+\newblock \bibinfo{title}{{Numerical study of the effects of surface topography
+  and chemistry on the wetting transition using the string method}}.
+\newblock \emph{\bibinfo{journal}{The Journal of Chemical Physics}}
+  \textbf{\bibinfo{volume}{141}}, \bibinfo{pages}{244705}
+  (\bibinfo{year}{2014}).
 
-\bibitem[{\citenamefont{Panter et~al.}(2019{\natexlab{b}})\citenamefont{Panter,
-  Gizaw, and Kusumaatmaja}}]{Panter2019b}
-\bibinfo{author}{\bibfnamefont{J.~R.} \bibnamefont{Panter}},
-  \bibinfo{author}{\bibfnamefont{Y.}~\bibnamefont{Gizaw}}, \bibnamefont{and}
-  \bibinfo{author}{\bibfnamefont{H.}~\bibnamefont{Kusumaatmaja}},
-  \bibinfo{journal}{Science Advances} \textbf{\bibinfo{volume}{5}},
-  \bibinfo{pages}{eaav7328} (\bibinfo{year}{2019}{\natexlab{b}}).
+\bibitem{Panter2019b}
+\bibinfo{author}{Panter, J.~R.}, \bibinfo{author}{Gizaw, Y.} \&
+  \bibinfo{author}{Kusumaatmaja, H.}
+\newblock \bibinfo{title}{{Multifaceted design optimization for superomniphobic
+  surfaces}}.
+\newblock \emph{\bibinfo{journal}{Science Advances}}
+  \textbf{\bibinfo{volume}{5}}, \bibinfo{pages}{eaav7328}
+  (\bibinfo{year}{2019}).
 
-\bibitem[{\citenamefont{Amabili et~al.}(2017)\citenamefont{Amabili, Giacomello,
-  Meloni, and Casciola}}]{Amabili2017}
-\bibinfo{author}{\bibfnamefont{M.}~\bibnamefont{Amabili}},
-  \bibinfo{author}{\bibfnamefont{A.}~\bibnamefont{Giacomello}},
-  \bibinfo{author}{\bibfnamefont{S.}~\bibnamefont{Meloni}}, \bibnamefont{and}
-  \bibinfo{author}{\bibfnamefont{C.~M.} \bibnamefont{Casciola}},
-  \bibinfo{journal}{Physical Review Fluids} \textbf{\bibinfo{volume}{2}},
-  \bibinfo{pages}{034202} (\bibinfo{year}{2017}).
+\bibitem{Amabili2017}
+\bibinfo{author}{Amabili, M.}, \bibinfo{author}{Giacomello, A.},
+  \bibinfo{author}{Meloni, S.} \& \bibinfo{author}{Casciola, C.~M.}
+\newblock \bibinfo{title}{{Collapse of superhydrophobicity on nanopillared
+  surfaces}}.
+\newblock \emph{\bibinfo{journal}{Physical Review Fluids}}
+  \textbf{\bibinfo{volume}{2}}, \bibinfo{pages}{034202} (\bibinfo{year}{2017}).
 
-\bibitem[{\citenamefont{Othayoth et~al.}(2020)\citenamefont{Othayoth, Thoms,
-  and Li}}]{Othayoth2020}
-\bibinfo{author}{\bibfnamefont{R.}~\bibnamefont{Othayoth}},
-  \bibinfo{author}{\bibfnamefont{G.}~\bibnamefont{Thoms}}, \bibnamefont{and}
-  \bibinfo{author}{\bibfnamefont{C.}~\bibnamefont{Li}},
-  \bibinfo{journal}{Proceedings of the National Academy of Sciences}
-  \textbf{\bibinfo{volume}{117}}, \bibinfo{pages}{14987}
+\bibitem{Othayoth2020}
+\bibinfo{author}{Othayoth, R.}, \bibinfo{author}{Thoms, G.} \&
+  \bibinfo{author}{Li, C.}
+\newblock \bibinfo{title}{{An energy landscape approach to locomotor
+  transitions in complex 3D terrain}}.
+\newblock \emph{\bibinfo{journal}{Proceedings of the National Academy of
+  Sciences}} \textbf{\bibinfo{volume}{117}}, \bibinfo{pages}{14987--14995}
   (\bibinfo{year}{2020}).
 
-\bibitem[{\citenamefont{Filipov et~al.}(2015)\citenamefont{Filipov, Tachi,
-  Paulino, and Weitz}}]{Filipov2015}
-\bibinfo{author}{\bibfnamefont{E.~T.} \bibnamefont{Filipov}},
-  \bibinfo{author}{\bibfnamefont{T.}~\bibnamefont{Tachi}},
-  \bibinfo{author}{\bibfnamefont{G.~H.} \bibnamefont{Paulino}},
-  \bibnamefont{and} \bibinfo{author}{\bibfnamefont{D.~A.} \bibnamefont{Weitz}},
-  \bibinfo{journal}{Proceedings of the National Academy of Sciences of the
-  United States of America} \textbf{\bibinfo{volume}{112}},
+\bibitem{Filipov2015}
+\bibinfo{author}{Filipov, E.~T.}, \bibinfo{author}{Tachi, T.},
+  \bibinfo{author}{Paulino, G.~H.} \& \bibinfo{author}{Weitz, D.~A.}
+\newblock \bibinfo{title}{{Origami tubes assembled into stiff, yet
+  reconfigurable structures and metamaterials}}.
+\newblock \emph{\bibinfo{journal}{Proceedings of the National Academy of
+  Sciences of the United States of America}} \textbf{\bibinfo{volume}{112}},
   \bibinfo{pages}{12321} (\bibinfo{year}{2015}).
 
-\bibitem[{\citenamefont{Zhai et~al.}(2018)\citenamefont{Zhai, Wang, and
-  Jiang}}]{Zhai2018}
-\bibinfo{author}{\bibfnamefont{Z.}~\bibnamefont{Zhai}},
-  \bibinfo{author}{\bibfnamefont{Y.}~\bibnamefont{Wang}}, \bibnamefont{and}
-  \bibinfo{author}{\bibfnamefont{H.}~\bibnamefont{Jiang}},
-  \bibinfo{journal}{Proceedings of the National Academy of Sciences of the
-  United States of America} \textbf{\bibinfo{volume}{115}},
-  \bibinfo{pages}{2032} (\bibinfo{year}{2018}).
+\bibitem{Zhai2018}
+\bibinfo{author}{Zhai, Z.}, \bibinfo{author}{Wang, Y.} \&
+  \bibinfo{author}{Jiang, H.}
+\newblock \bibinfo{title}{{Origami-inspired, on-demand deployable and
+  collapsible mechanical metamaterials with tunable stiffness}}.
+\newblock \emph{\bibinfo{journal}{Proceedings of the National Academy of
+  Sciences of the United States of America}} \textbf{\bibinfo{volume}{115}},
+  \bibinfo{pages}{2032--2037} (\bibinfo{year}{2018}).
 
-\bibitem[{\citenamefont{Bertoldi et~al.}(2017)\citenamefont{Bertoldi, Vitelli,
-  Christensen, and {Van Hecke}}}]{Bertoldi2017}
-\bibinfo{author}{\bibfnamefont{K.}~\bibnamefont{Bertoldi}},
-  \bibinfo{author}{\bibfnamefont{V.}~\bibnamefont{Vitelli}},
-  \bibinfo{author}{\bibfnamefont{J.}~\bibnamefont{Christensen}},
-  \bibnamefont{and} \bibinfo{author}{\bibfnamefont{M.}~\bibnamefont{{Van
-  Hecke}}}, \bibinfo{journal}{Nature Reviews Materials}
+\bibitem{Bertoldi2017}
+\bibinfo{author}{Bertoldi, K.}, \bibinfo{author}{Vitelli, V.},
+  \bibinfo{author}{Christensen, J.} \& \bibinfo{author}{{Van Hecke}, M.}
+\newblock \bibinfo{title}{{Flexible mechanical metamaterials}}.
+\newblock \emph{\bibinfo{journal}{Nature Reviews Materials}}
   \textbf{\bibinfo{volume}{2}}, \bibinfo{pages}{17066} (\bibinfo{year}{2017}).
 
-\bibitem[{\citenamefont{Truby and Lewis}(2016)}]{Truby2016}
-\bibinfo{author}{\bibfnamefont{R.~L.} \bibnamefont{Truby}} \bibnamefont{and}
-  \bibinfo{author}{\bibfnamefont{J.~A.} \bibnamefont{Lewis}},
-  \bibinfo{journal}{Nature} \textbf{\bibinfo{volume}{540}},
-  \bibinfo{pages}{371} (\bibinfo{year}{2016}).
+\bibitem{Truby2016}
+\bibinfo{author}{Truby, R.~L.} \& \bibinfo{author}{Lewis, J.~A.}
+\newblock \bibinfo{title}{{Printing soft matter in three dimensions}}.
+\newblock \emph{\bibinfo{journal}{Nature}} \textbf{\bibinfo{volume}{540}},
+  \bibinfo{pages}{371--378} (\bibinfo{year}{2016}).
 
-\bibitem[{\citenamefont{Chi et~al.}(2022)\citenamefont{Chi, Li, Zhao, Hong,
-  Tang, and Yin}}]{Chi2022}
-\bibinfo{author}{\bibfnamefont{Y.}~\bibnamefont{Chi}},
-  \bibinfo{author}{\bibfnamefont{Y.}~\bibnamefont{Li}},
-  \bibinfo{author}{\bibfnamefont{Y.}~\bibnamefont{Zhao}},
-  \bibinfo{author}{\bibfnamefont{Y.}~\bibnamefont{Hong}},
-  \bibinfo{author}{\bibfnamefont{Y.}~\bibnamefont{Tang}}, \bibnamefont{and}
-  \bibinfo{author}{\bibfnamefont{J.}~\bibnamefont{Yin}},
-  \bibinfo{journal}{Advanced Materials}  (\bibinfo{year}{2022}).
+\bibitem{Chi2022}
+\bibinfo{author}{Chi, Y.} \emph{et~al.}
+\newblock \bibinfo{title}{{Bistable and Multistable Actuators for Soft Robots:
+  Structures, Materials, and Functionalities}}.
+\newblock \emph{\bibinfo{journal}{Advanced Materials}}  (\bibinfo{year}{2022}).
 
-\bibitem[{\citenamefont{Bonfanti et~al.}(2020)\citenamefont{Bonfanti, Guerra,
-  Font-Clos, Rayneau-Kirkhope, and Zapperi}}]{Bonfanti2020}
-\bibinfo{author}{\bibfnamefont{S.}~\bibnamefont{Bonfanti}},
-  \bibinfo{author}{\bibfnamefont{R.}~\bibnamefont{Guerra}},
-  \bibinfo{author}{\bibfnamefont{F.}~\bibnamefont{Font-Clos}},
-  \bibinfo{author}{\bibfnamefont{D.}~\bibnamefont{Rayneau-Kirkhope}},
-  \bibnamefont{and} \bibinfo{author}{\bibfnamefont{S.}~\bibnamefont{Zapperi}},
-  \bibinfo{journal}{Nature Communications} \textbf{\bibinfo{volume}{11}},
-  \bibinfo{pages}{4162} (\bibinfo{year}{2020}).
+\bibitem{Bonfanti2020}
+\bibinfo{author}{Bonfanti, S.}, \bibinfo{author}{Guerra, R.},
+  \bibinfo{author}{Font-Clos, F.}, \bibinfo{author}{Rayneau-Kirkhope, D.} \&
+  \bibinfo{author}{Zapperi, S.}
+\newblock \bibinfo{title}{{Automatic design of mechanical metamaterial
+  actuators}}.
+\newblock \emph{\bibinfo{journal}{Nature Communications}}
+  \textbf{\bibinfo{volume}{11}}, \bibinfo{pages}{4162} (\bibinfo{year}{2020}).
 
-\bibitem[{\citenamefont{Shan et~al.}(2015)\citenamefont{Shan, Kang, Raney,
-  Wang, Fang, Candido, Lewis, and Bertoldi}}]{Shan2015}
-\bibinfo{author}{\bibfnamefont{S.}~\bibnamefont{Shan}},
-  \bibinfo{author}{\bibfnamefont{S.~H.} \bibnamefont{Kang}},
-  \bibinfo{author}{\bibfnamefont{J.~R.} \bibnamefont{Raney}},
-  \bibinfo{author}{\bibfnamefont{P.}~\bibnamefont{Wang}},
-  \bibinfo{author}{\bibfnamefont{L.}~\bibnamefont{Fang}},
-  \bibinfo{author}{\bibfnamefont{F.}~\bibnamefont{Candido}},
-  \bibinfo{author}{\bibfnamefont{J.~A.} \bibnamefont{Lewis}}, \bibnamefont{and}
-  \bibinfo{author}{\bibfnamefont{K.}~\bibnamefont{Bertoldi}},
-  \bibinfo{journal}{Advanced Materials} \textbf{\bibinfo{volume}{27}},
-  \bibinfo{pages}{4296} (\bibinfo{year}{2015}).
+\bibitem{Shan2015}
+\bibinfo{author}{Shan, S.} \emph{et~al.}
+\newblock \bibinfo{title}{{Multistable Architected Materials for Trapping
+  Elastic Strain Energy}}.
+\newblock \emph{\bibinfo{journal}{Advanced Materials}}
+  \textbf{\bibinfo{volume}{27}}, \bibinfo{pages}{4296--4301}
+  (\bibinfo{year}{2015}).
 
-\bibitem[{\citenamefont{Giri and Mailen}(2021)}]{Giri2021}
-\bibinfo{author}{\bibfnamefont{T.~R.} \bibnamefont{Giri}} \bibnamefont{and}
-  \bibinfo{author}{\bibfnamefont{R.}~\bibnamefont{Mailen}},
-  \bibinfo{journal}{International Journal of Mechanical Sciences}
-  \textbf{\bibinfo{volume}{204}}, \bibinfo{pages}{106541}
+\bibitem{Giri2021}
+\bibinfo{author}{Giri, T.~R.} \& \bibinfo{author}{Mailen, R.}
+\newblock \bibinfo{title}{{Controlled snapping sequence and energy absorption
+  in multistable mechanical metamaterial cylinders}}.
+\newblock \emph{\bibinfo{journal}{International Journal of Mechanical
+  Sciences}} \textbf{\bibinfo{volume}{204}}, \bibinfo{pages}{106541}
   (\bibinfo{year}{2021}).
 
-\bibitem[{\citenamefont{Cerjan and Miller}(1981)}]{Cerjan1981}
-\bibinfo{author}{\bibfnamefont{C.~J.} \bibnamefont{Cerjan}} \bibnamefont{and}
-  \bibinfo{author}{\bibfnamefont{W.~H.} \bibnamefont{Miller}},
-  \bibinfo{journal}{The Journal of Chemical Physics}
-  \textbf{\bibinfo{volume}{75}}, \bibinfo{pages}{2800} (\bibinfo{year}{1981}).
+\bibitem{Cerjan1981}
+\bibinfo{author}{Cerjan, C.~J.} \& \bibinfo{author}{Miller, W.~H.}
+\newblock \bibinfo{title}{{On finding transition states}}.
+\newblock \emph{\bibinfo{journal}{The Journal of Chemical Physics}}
+  \textbf{\bibinfo{volume}{75}}, \bibinfo{pages}{2800--2806}
+  (\bibinfo{year}{1981}).
 
-\bibitem[{\citenamefont{Heyden et~al.}(2005)\citenamefont{Heyden, Bell, and
-  Keil}}]{Heyden2005}
-\bibinfo{author}{\bibfnamefont{A.}~\bibnamefont{Heyden}},
-  \bibinfo{author}{\bibfnamefont{A.~T.} \bibnamefont{Bell}}, \bibnamefont{and}
-  \bibinfo{author}{\bibfnamefont{F.~J.} \bibnamefont{Keil}},
-  \bibinfo{journal}{Journal of Chemical Physics}
+\bibitem{Heyden2005}
+\bibinfo{author}{Heyden, A.}, \bibinfo{author}{Bell, A.~T.} \&
+  \bibinfo{author}{Keil, F.~J.}
+\newblock \bibinfo{title}{{Efficient methods for finding transition states in
+  chemical reactions: Comparison of improved dimer method and partitioned
+  rational function optimization method}}.
+\newblock \emph{\bibinfo{journal}{Journal of Chemical Physics}}
   \textbf{\bibinfo{volume}{123}}, \bibinfo{pages}{224101}
@@
 
-\bibitem[{\citenamefont{K{\"{a}}stner and Sherwood}(2008)}]{Kastner2008}
-\bibinfo{author}{\bibfnamefont{J.}~\bibnamefont{K{\"{a}}stner}}
-  \bibnamefont{and} \bibinfo{author}{\bibfnamefont{P.}~\bibnamefont{Sherwood}},
-  \bibinfo{journal}{Journal of Chemical Physics}
+\bibitem{Kastner2008}
+\bibinfo{author}{K{\"{a}}stner, J.} \& \bibinfo{author}{Sherwood, P.}
+\newblock \bibinfo{title}{{Superlinearly converging dimer method for transition
+  state search}}.
+\newblock \emph{\bibinfo{journal}{Journal of Chemical Physics}}
   \textbf{\bibinfo{volume}{128}}, \bibinfo{pages}{014106}
@@
 
-\bibitem[{\citenamefont{Zhang et~al.}(2016)\citenamefont{Zhang, Du, and
-  Zheng}}]{Zhang2016}
-\bibinfo{author}{\bibfnamefont{L.}~\bibnamefont{Zhang}},
-  \bibinfo{author}{\bibfnamefont{Q.}~\bibnamefont{Du}}, \bibnamefont{and}
-  \bibinfo{author}{\bibfnamefont{Z.}~\bibnamefont{Zheng}},
-  \bibinfo{journal}{SIAM Journal on Scientific Computing}
-  \textbf{\bibinfo{volume}{38}}, \bibinfo{pages}{A528} (\bibinfo{year}{2016}).
+\bibitem{Zhang2016}
+\bibinfo{author}{Zhang, L.}, \bibinfo{author}{Du, Q.} \&
+  \bibinfo{author}{Zheng, Z.}
+\newblock \bibinfo{title}{{Optimization-based Shrinking Dimer Method for
+  Finding Transition States}}.
+\newblock \emph{\bibinfo{journal}{SIAM Journal on Scientific Computing}}
+  \textbf{\bibinfo{volume}{38}}, \bibinfo{pages}{A528--A544}
+  (\bibinfo{year}{2016}).
 
-\bibitem[{\citenamefont{E et~al.}(2007)\citenamefont{E, Ren, and
-  Vanden-Eijnden}}]{E2007}
-\bibinfo{author}{\bibfnamefont{W.}~\bibnamefont{E}},
-  \bibinfo{author}{\bibfnamefont{W.}~\bibnamefont{Ren}}, \bibnamefont{and}
-  \bibinfo{author}{\bibfnamefont{E.}~\bibnamefont{Vanden-Eijnden}},
-  \bibinfo{journal}{The Journal of Chemical Physics}
+\bibitem{E2007}
+\bibinfo{author}{E, W.}, \bibinfo{author}{Ren, W.} \&
+  \bibinfo{author}{Vanden-Eijnden, E.}
+\newblock \bibinfo{title}{{Simplified and improved string method for computing
+  the minimum energy paths in barrier-crossing events}}.
+\newblock \emph{\bibinfo{journal}{The Journal of Chemical Physics}}
   \textbf{\bibinfo{volume}{126}}, \bibinfo{pages}{164103}
@@
 
-\bibitem[{\citenamefont{Ren and Vanden-Eijnden}(2013)}]{Ren2013}
-\bibinfo{author}{\bibfnamefont{W.}~\bibnamefont{Ren}} \bibnamefont{and}
-  \bibinfo{author}{\bibfnamefont{E.}~\bibnamefont{Vanden-Eijnden}},
-  \bibinfo{journal}{Journal of Chemical Physics}
+\bibitem{Ren2013}
+\bibinfo{author}{Ren, W.} \& \bibinfo{author}{Vanden-Eijnden, E.}
+\newblock \bibinfo{title}{{A climbing string method for saddle point search}}.
+\newblock \emph{\bibinfo{journal}{Journal of Chemical Physics}}
   \textbf{\bibinfo{volume}{138}}, \bibinfo{pages}{134105}
@@
 
-\bibitem[{\citenamefont{E et~al.}(2002)\citenamefont{E, Ren, and
-  Vanden-Eijnden}}]{E2002}
-\bibinfo{author}{\bibfnamefont{W.}~\bibnamefont{E}},
-  \bibinfo{author}{\bibfnamefont{W.}~\bibnamefont{Ren}}, \bibnamefont{and}
-  \bibinfo{author}{\bibfnamefont{E.}~\bibnamefont{Vanden-Eijnden}},
-  \bibinfo{journal}{Physical Review B} \textbf{\bibinfo{volume}{66}},
-  \bibinfo{pages}{052301} (\bibinfo{year}{2002}).
+\bibitem{E2002}
+\bibinfo{author}{E, W.}, \bibinfo{author}{Ren, W.} \&
+  \bibinfo{author}{Vanden-Eijnden, E.}
+\newblock \bibinfo{title}{{String method for the study of rare events}}.
+\newblock \emph{\bibinfo{journal}{Physical Review B}}
+  \textbf{\bibinfo{volume}{66}}, \bibinfo{pages}{052301}
+  (\bibinfo{year}{2002}).
 
-\bibitem[{\citenamefont{Trygubenko and Wales}(2004)}]{Trygubenko2004}
-\bibinfo{author}{\bibfnamefont{S.~A.} \bibnamefont{Trygubenko}}
-  \bibnamefont{and} \bibinfo{author}{\bibfnamefont{D.~J.} \bibnamefont{Wales}},
-  \bibinfo{journal}{Journal of Chemical Physics}
-  \textbf{\bibinfo{volume}{120}}, \bibinfo{pages}{2082} (\bibinfo{year}{2004}).
+\bibitem{Trygubenko2004}
+\bibinfo{author}{Trygubenko, S.~A.} \& \bibinfo{author}{Wales, D.~J.}
+\newblock \bibinfo{title}{{A doubly nudged elastic band method for finding
+  transition states}}.
+\newblock \emph{\bibinfo{journal}{Journal of Chemical Physics}}
+  \textbf{\bibinfo{volume}{120}}, \bibinfo{pages}{2082--2094}
+  (\bibinfo{year}{2004}).
 
-\bibitem[{\citenamefont{Wales and Carr}(2012)}]{Wales2012a}
-\bibinfo{author}{\bibfnamefont{D.~J.} \bibnamefont{Wales}} \bibnamefont{and}
-  \bibinfo{author}{\bibfnamefont{J.~M.} \bibnamefont{Carr}},
-  \bibinfo{journal}{Journal of Chemical Theory and Computation}
-  \textbf{\bibinfo{volume}{8}}, \bibinfo{pages}{5020} (\bibinfo{year}{2012}).
+\bibitem{Wales2012a}
+\bibinfo{author}{Wales, D.~J.} \& \bibinfo{author}{Carr, J.~M.}
+\newblock \bibinfo{title}{{Quasi-Continuous Interpolation Scheme for Pathways
+  between Distant Configurations}}.
+\newblock \emph{\bibinfo{journal}{Journal of Chemical Theory and Computation}}
+  \textbf{\bibinfo{volume}{8}}, \bibinfo{pages}{5020--5034}
+  (\bibinfo{year}{2012}).
 
-\bibitem[{\citenamefont{Trefethen and Thiyagalingam}(2013)}]{Trefethen2013}
-\bibinfo{author}{\bibfnamefont{A.~E.} \bibnamefont{Trefethen}}
-  \bibnamefont{and}
-  \bibinfo{author}{\bibfnamefont{J.}~\bibnamefont{Thiyagalingam}},
-  \bibinfo{journal}{Journal of Computational Science}
-  \textbf{\bibinfo{volume}{4}}, \bibinfo{pages}{444} (\bibinfo{year}{2013}).
+\bibitem{Trefethen2013}
+\bibinfo{author}{Trefethen, A.~E.} \& \bibinfo{author}{Thiyagalingam, J.}
+\newblock \bibinfo{title}{{Energy-aware software: Challenges, opportunities and
+  strategies}}.
+\newblock \emph{\bibinfo{journal}{Journal of Computational Science}}
+  \textbf{\bibinfo{volume}{4}}, \bibinfo{pages}{444--449}
+  (\bibinfo{year}{2013}).
 
-\bibitem[{\citenamefont{Shalf}(2020)}]{Shalf2020}
-\bibinfo{author}{\bibfnamefont{J.}~\bibnamefont{Shalf}},
-  \bibinfo{journal}{Philosophical Transactions Royal Society}
+\bibitem{Shalf2020}
+\bibinfo{author}{Shalf, J.}
+\newblock \bibinfo{title}{{The future of computing beyond Moore's Law}}.
+\newblock \emph{\bibinfo{journal}{Philosophical Transactions Royal Society}}
   \textbf{\bibinfo{volume}{378}}, \bibinfo{pages}{20190061}
@@
 
-\bibitem[{\citenamefont{Alexander et~al.}(2020)\citenamefont{Alexander,
-  Almgren, Bell, Bhattacharjee, Chen, Colella, Daniel, DeSlippe, Diachin,
-  Draeger et~al.}}]{Alexander2020}
-\bibinfo{author}{\bibfnamefont{F.}~\bibnamefont{Alexander}},
-  \bibinfo{author}{\bibfnamefont{A.}~\bibnamefont{Almgren}},
-  \bibinfo{author}{\bibfnamefont{J.}~\bibnamefont{Bell}},
-  \bibinfo{author}{\bibfnamefont{A.}~\bibnamefont{Bhattacharjee}},
-  \bibinfo{author}{\bibfnamefont{J.}~\bibnamefont{Chen}},
-  \bibinfo{author}{\bibfnamefont{P.}~\bibnamefont{Colella}},
-  \bibinfo{author}{\bibfnamefont{D.}~\bibnamefont{Daniel}},
-  \bibinfo{author}{\bibfnamefont{J.}~\bibnamefont{DeSlippe}},
-  \bibinfo{author}{\bibfnamefont{L.}~\bibnamefont{Diachin}},
-  \bibinfo{author}{\bibfnamefont{E.}~\bibnamefont{Draeger}},
-  \bibnamefont{et~al.}, \bibinfo{journal}{Philosophical Transactions of the
-  Royal Society A} \textbf{\bibinfo{volume}{378}}, \bibinfo{pages}{20190056}
+\bibitem{Alexander2020}
+\bibinfo{author}{Alexander, F.} \emph{et~al.}
+\newblock \bibinfo{title}{{Exascale applications: Skin in the game}}.
+\newblock \emph{\bibinfo{journal}{Philosophical Transactions of the Royal
+  Society A}} \textbf{\bibinfo{volume}{378}}, \bibinfo{pages}{20190056}
   (\bibinfo{year}{2020}).
 
-\bibitem[{\citenamefont{McMullen et~al.}(2018)\citenamefont{McMullen,
-  Holmes-Cerfon, Sciortino, Grosberg, and Brujic}}]{McMullen2018}
-\bibinfo{author}{\bibfnamefont{A.}~\bibnamefont{McMullen}},
-  \bibinfo{author}{\bibfnamefont{M.}~\bibnamefont{Holmes-Cerfon}},
-  \bibinfo{author}{\bibfnamefont{F.}~\bibnamefont{Sciortino}},
-  \bibinfo{author}{\bibfnamefont{A.~Y.} \bibnamefont{Grosberg}},
-  \bibnamefont{and} \bibinfo{author}{\bibfnamefont{J.}~\bibnamefont{Brujic}},
-  \bibinfo{journal}{Physical Review Letters} \textbf{\bibinfo{volume}{121}},
-  \bibinfo{pages}{138002} (\bibinfo{year}{2018}).
+\bibitem{McMullen2018}
+\bibinfo{author}{McMullen, A.}, \bibinfo{author}{Holmes-Cerfon, M.},
+  \bibinfo{author}{Sciortino, F.}, \bibinfo{author}{Grosberg, A.~Y.} \&
+  \bibinfo{author}{Brujic, J.}
+\newblock \bibinfo{title}{{Freely Jointed Polymers Made of Droplets}}.
+\newblock \emph{\bibinfo{journal}{Physical Review Letters}}
+  \textbf{\bibinfo{volume}{121}}, \bibinfo{pages}{138002}
+  (\bibinfo{year}{2018}).
 
-\bibitem[{\citenamefont{Nguemaha and Zhou}(2018)}]{Nguemaha2018}
-\bibinfo{author}{\bibfnamefont{V.}~\bibnamefont{Nguemaha}} \bibnamefont{and}
-  \bibinfo{author}{\bibfnamefont{H.~X.} \bibnamefont{Zhou}},
-  \bibinfo{journal}{Scientific Reports} \textbf{\bibinfo{volume}{8}},
-  \bibinfo{pages}{1} (\bibinfo{year}{2018}).
+\bibitem{Nguemaha2018}
+\bibinfo{author}{Nguemaha, V.} \& \bibinfo{author}{Zhou, H.~X.}
+\newblock \bibinfo{title}{{Liquid-Liquid Phase Separation of Patchy Particles
+  Illuminates Diverse Effects of Regulatory Components on Protein Droplet
+  Formation}}.
+\newblock \emph{\bibinfo{journal}{Scientific Reports}}
+  \textbf{\bibinfo{volume}{8}}, \bibinfo{pages}{1--11} (\bibinfo{year}{2018}).
 
-\bibitem[{\citenamefont{Chen et~al.}(2018)\citenamefont{Chen, Zhang, and
-  Torquato}}]{Chen2018b}
-\bibinfo{author}{\bibfnamefont{D.}~\bibnamefont{Chen}},
-  \bibinfo{author}{\bibfnamefont{G.}~\bibnamefont{Zhang}}, \bibnamefont{and}
-  \bibinfo{author}{\bibfnamefont{S.}~\bibnamefont{Torquato}},
-  \bibinfo{journal}{Journal of Physical Chemistry B}
-  \textbf{\bibinfo{volume}{122}}, \bibinfo{pages}{8462} (\bibinfo{year}{2018}).
+\bibitem{Chen2018b}
+\bibinfo{author}{Chen, D.}, \bibinfo{author}{Zhang, G.} \&
+  \bibinfo{author}{Torquato, S.}
+\newblock \bibinfo{title}{{Inverse Design of Colloidal Crystals via Optimized
+  Patchy Interactions}}.
+\newblock \emph{\bibinfo{journal}{Journal of Physical Chemistry B}}
+  \textbf{\bibinfo{volume}{122}}, \bibinfo{pages}{8462--8468}
+  (\bibinfo{year}{2018}).
 
-\bibitem[{\citenamefont{Santra et~al.}(2018)\citenamefont{Santra, Singh, and
-  Bagchi}}]{Santra2018}
-\bibinfo{author}{\bibfnamefont{M.}~\bibnamefont{Santra}},
-  \bibinfo{author}{\bibfnamefont{R.~S.} \bibnamefont{Singh}}, \bibnamefont{and}
-  \bibinfo{author}{\bibfnamefont{B.}~\bibnamefont{Bagchi}},
-  \bibinfo{journal}{Physical Review E} \textbf{\bibinfo{volume}{98}},
-  \bibinfo{pages}{032606} (\bibinfo{year}{2018}).
+\bibitem{Santra2018}
+\bibinfo{author}{Santra, M.}, \bibinfo{author}{Singh, R.~S.} \&
+  \bibinfo{author}{Bagchi, B.}
+\newblock \bibinfo{title}{{Polymorph selection during crystallization of a
+  model colloidal fluid with a free energy landscape containing a metastable
+  solid}}.
+\newblock \emph{\bibinfo{journal}{Physical Review E}}
+  \textbf{\bibinfo{volume}{98}}, \bibinfo{pages}{032606}
+  (\bibinfo{year}{2018}).
 
-\bibitem[{\citenamefont{M{\"{o}}kk{\"{o}}nen
-  et~al.}(2016)\citenamefont{M{\"{o}}kk{\"{o}}nen, Ala-Nissila, and
-  J{\'{o}}nsson}}]{Mokkonen2016}
-\bibinfo{author}{\bibfnamefont{H.}~\bibnamefont{M{\"{o}}kk{\"{o}}nen}},
-  \bibinfo{author}{\bibfnamefont{T.}~\bibnamefont{Ala-Nissila}},
-  \bibnamefont{and}
-  \bibinfo{author}{\bibfnamefont{H.}~\bibnamefont{J{\'{o}}nsson}},
-  \bibinfo{journal}{The Journal of Chemical Physics}
+\bibitem{Mokkonen2016}
+\bibinfo{author}{M{\"{o}}kk{\"{o}}nen, H.}, \bibinfo{author}{Ala-Nissila, T.}
+  \& \bibinfo{author}{J{\'{o}}nsson, H.}
+\newblock \bibinfo{title}{{Efficient dynamical correction of the transition
+  state theory rate estimate for a flat energy barrier}}.
+\newblock \emph{\bibinfo{journal}{The Journal of Chemical Physics}}
   \textbf{\bibinfo{volume}{145}}, \bibinfo{pages}{094901}
@@
 
-\bibitem[{\citenamefont{Wriggers}(2006)}]{Wriggers2006}
-\bibinfo{author}{\bibfnamefont{P.}~\bibnamefont{Wriggers}},
-  \emph{\bibinfo{title}{{Computational Contact Mechanics}}}
+\bibitem{Wriggers2006}
+\bibinfo{author}{Wriggers, P.}
+\newblock \emph{\bibinfo{title}{{Computational Contact Mechanics}}}
   (\bibinfo{publisher}{Springer Berlin Heidelberg}, \bibinfo{address}{Berlin,
@@
 
-\bibitem[{\citenamefont{Page and McIver}(1988)}]{Page1988}
-\bibinfo{author}{\bibfnamefont{M.}~\bibnamefont{Page}} \bibnamefont{and}
-  \bibinfo{author}{\bibfnamefont{J.~W.} \bibnamefont{McIver}},
-  \bibinfo{journal}{The Journal of Chemical Physics}
-  \textbf{\bibinfo{volume}{88}}, \bibinfo{pages}{922} (\bibinfo{year}{1988}).
+\bibitem{Page1988}
+\bibinfo{author}{Page, M.} \& \bibinfo{author}{McIver, J.~W.}
+\newblock \bibinfo{title}{{On evaluating the reaction path Hamiltonian}}.
+\newblock \emph{\bibinfo{journal}{The Journal of Chemical Physics}}
+  \textbf{\bibinfo{volume}{88}}, \bibinfo{pages}{922--935}
+  (\bibinfo{year}{1988}).
 
-\bibitem[{\citenamefont{Liu and Nocedal}(1989)}]{Liu1989}
-\bibinfo{author}{\bibfnamefont{D.~C.} \bibnamefont{Liu}} \bibnamefont{and}
-  \bibinfo{author}{\bibfnamefont{J.}~\bibnamefont{Nocedal}},
-  \bibinfo{journal}{Mathematical Programming} \textbf{\bibinfo{volume}{45}},
-  \bibinfo{pages}{503} (\bibinfo{year}{1989}).
+\bibitem{Liu1989}
+\bibinfo{author}{Liu, D.~C.} \& \bibinfo{author}{Nocedal, J.}
+\newblock \bibinfo{title}{{On the limited memory bfgs method for large scale
+  optimization}}.
+\newblock \emph{\bibinfo{journal}{Mathematical Programming}}
+  \textbf{\bibinfo{volume}{45}}, \bibinfo{pages}{503--528}
+  (\bibinfo{year}{1989}).
 
-\bibitem[{\citenamefont{Wales}(2002)}]{Wales2002}
-\bibinfo{author}{\bibfnamefont{D.~J.} \bibnamefont{Wales}},
-  \bibinfo{journal}{Molecular Physics} \textbf{\bibinfo{volume}{100}},
-  \bibinfo{pages}{3285} (\bibinfo{year}{2002}).
+\bibitem{Wales2002}
+\bibinfo{author}{Wales, D.~J.}
+\newblock \bibinfo{title}{{Discrete path sampling}}.
+\newblock \emph{\bibinfo{journal}{Molecular Physics}}
+  \textbf{\bibinfo{volume}{100}}, \bibinfo{pages}{3285--3305}
+  (\bibinfo{year}{2002}).
 
-\bibitem[{\citenamefont{Passerone and Parrinello}(2001)}]{Passerone2001}
-\bibinfo{author}{\bibfnamefont{D.}~\bibnamefont{Passerone}} \bibnamefont{and}
-  \bibinfo{author}{\bibfnamefont{M.}~\bibnamefont{Parrinello}},
-  \bibinfo{journal}{Physical Review Letters} \textbf{\bibinfo{volume}{87}},
-  \bibinfo{pages}{108302} (\bibinfo{year}{2001}).
+\bibitem{Passerone2001}
+\bibinfo{author}{Passerone, D.} \& \bibinfo{author}{Parrinello, M.}
+\newblock \bibinfo{title}{{Action-Derived Molecular Dynamics in the Study of
+  Rare Events}}.
+\newblock \emph{\bibinfo{journal}{Physical Review Letters}}
+  \textbf{\bibinfo{volume}{87}}, \bibinfo{pages}{108302}
+  (\bibinfo{year}{2001}).
 
-\bibitem[{\citenamefont{Virot et~al.}(2017)\citenamefont{Virot, Kreilos,
-  Schneider, and Rubinstein}}]{Virot2017}
-\bibinfo{author}{\bibfnamefont{E.}~\bibnamefont{Virot}},
-  \bibinfo{author}{\bibfnamefont{T.}~\bibnamefont{Kreilos}},
-  \bibinfo{author}{\bibfnamefont{T.~M.} \bibnamefont{Schneider}},
-  \bibnamefont{and} \bibinfo{author}{\bibfnamefont{S.~M.}
-  \bibnamefont{Rubinstein}}, \bibinfo{journal}{Physical Review Letters}
+\bibitem{Virot2017}
+\bibinfo{author}{Virot, E.}, \bibinfo{author}{Kreilos, T.},
+  \bibinfo{author}{Schneider, T.~M.} \& \bibinfo{author}{Rubinstein, S.~M.}
+\newblock \bibinfo{title}{{Stability Landscape of Shell Buckling}}.
+\newblock \emph{\bibinfo{journal}{Physical Review Letters}}
   \textbf{\bibinfo{volume}{119}}, \bibinfo{pages}{224101}
@@
 
-\bibitem[{\citenamefont{Kusumaatmaja et~al.}(2006)\citenamefont{Kusumaatmaja,
-  L{\'{e}}opold{\`{e}}s, Dupuis, and Yeomans}}]{Kusumaatmaja2006}
-\bibinfo{author}{\bibfnamefont{H.}~\bibnamefont{Kusumaatmaja}},
-  \bibinfo{author}{\bibfnamefont{J.}~\bibnamefont{L{\'{e}}opold{\`{e}}s}},
-  \bibinfo{author}{\bibfnamefont{A.}~\bibnamefont{Dupuis}}, \bibnamefont{and}
-  \bibinfo{author}{\bibfnamefont{J.~M.} \bibnamefont{Yeomans}},
-  \bibinfo{journal}{Europhysics Letters} \textbf{\bibinfo{volume}{73}},
-  \bibinfo{pages}{740} (\bibinfo{year}{2006}).
+\bibitem{Kusumaatmaja2006}
+\bibinfo{author}{Kusumaatmaja, H.}, \bibinfo{author}{L{\'{e}}opold{\`{e}}s,
+  J.}, \bibinfo{author}{Dupuis, A.} \& \bibinfo{author}{Yeomans, J.~M.}
+\newblock \bibinfo{title}{{Drop dynamics on chemically patterned surfaces}}.
+\newblock \emph{\bibinfo{journal}{Europhysics Letters}}
+  \textbf{\bibinfo{volume}{73}}, \bibinfo{pages}{740--746}
+  (\bibinfo{year}{2006}).
 
-\bibitem[{\citenamefont{Brown and Bhushan}(2016)}]{Brown2016}
-\bibinfo{author}{\bibfnamefont{P.~S.} \bibnamefont{Brown}} \bibnamefont{and}
-  \bibinfo{author}{\bibfnamefont{B.}~\bibnamefont{Bhushan}},
-  \bibinfo{journal}{Philosophical Transactions of the Royal Society A}
-  \textbf{\bibinfo{volume}{374}}, \bibinfo{pages}{20160135}
+\bibitem{Brown2016}
+\bibinfo{author}{Brown, P.~S.} \& \bibinfo{author}{Bhushan, B.}
+\newblock \bibinfo{title}{{Bioinspired materials for water supply and
+  management: water collection, water purification and separation of water from
+  oil}}.
+\newblock \emph{\bibinfo{journal}{Philosophical Transactions of the Royal
+  Society A}} \textbf{\bibinfo{volume}{374}}, \bibinfo{pages}{20160135}
   (\bibinfo{year}{2016}).
 
-\bibitem[{\citenamefont{Brakke}(1992)}]{Brakke1992}
-\bibinfo{author}{\bibfnamefont{K.~A.} \bibnamefont{Brakke}},
-  \bibinfo{journal}{Experimental Mathematics} \textbf{\bibinfo{volume}{1}},
-  \bibinfo{pages}{141} (\bibinfo{year}{1992}).
+\bibitem{Brakke1992}
+\bibinfo{author}{Brakke, K.~A.}
+\newblock \bibinfo{title}{{The Surface Evolver}}.
+\newblock \emph{\bibinfo{journal}{Experimental Mathematics}}
+  \textbf{\bibinfo{volume}{1}}, \bibinfo{pages}{141--165}
+  (\bibinfo{year}{1992}).
 
-\bibitem[{\citenamefont{Kirkpatrick et~al.}(1983)\citenamefont{Kirkpatrick,
-  Gelatt, and Vecchi}}]{Kirkpatrick1983}
-\bibinfo{author}{\bibfnamefont{S.}~\bibnamefont{Kirkpatrick}},
-  \bibinfo{author}{\bibfnamefont{C.~D.} \bibnamefont{Gelatt}},
-  \bibnamefont{and} \bibinfo{author}{\bibfnamefont{M.~P.}
-  \bibnamefont{Vecchi}}, \bibinfo{journal}{Science}
-  \textbf{\bibinfo{volume}{220}}, \bibinfo{pages}{671} (\bibinfo{year}{1983}).
+\bibitem{Kirkpatrick1983}
+\bibinfo{author}{Kirkpatrick, S.}, \bibinfo{author}{Gelatt, C.~D.} \&
+  \bibinfo{author}{Vecchi, M.~P.}
+\newblock \bibinfo{title}{{Optimization By Simulated Annealing}}.
+\newblock \emph{\bibinfo{journal}{Science}} \textbf{\bibinfo{volume}{220}},
+  \bibinfo{pages}{671--680} (\bibinfo{year}{1983}).
 

### 2022-04-22 manuscript.tex
Jack's comparison with bracketing methods. Justification for locating highest TS. Mention of setting driving forces equal

@@
 \begin{equation}\label{eq:diteration}
-  d_i = (1 - f) d_{i-1}.
+  d_i = (1 - f) d_{i-1},
 \end{equation}
-With $d_0$ as the separation between the two initial states.
+with $d_0$ taking the value of the separation between the two initial states.
 A reduction factor of $f = 0.5$ is successful for most applications, but this can be made smaller to ensure that the states do not slide off the ridge between the two basins of attraction.
@@
 \end{multline}
-where $E_1$ and $E_2$ are the single state energies, and $\kappa_e$ and $\kappa_d$ parametrise the strengths of the energy and distance constraints.
+where $E_1$ and $E_2$ are the single-state energies, and $\kappa_e$ and $\kappa_d$ parametrise the strengths of the energy and distance constraints.
 
@@
 To ensure that the transition state is located successfully, the constraint strengths $\kappa_d$ and $\kappa_e$ are updated as the algorithm proceeds using information from the system.
-They are initially calculated at the start of each minimisation, and regularly recalculated throughout (once per 100 iterations is used in this work).
-They are set using the following equations such that each term in the gradient of \cref{eq:bitss} is of a similar size,
+These are set such that the driving forces due to the constraints and single-state energies are of similar size.
+This prevents the constraints from washing out the underlying potential or causing large jumps that make a state pass over the dividing ridge.
+This results in the following equations (see the supplementary information for the derivation),
 \begin{gather}
@@
 \end{gather}
-where $\grad E_1$ and $\grad E_2$ are the gradients of the energies of the two states, and $\alpha$ and $\beta$ are parameters with recommended values of $\alpha = 10$ and $\beta = 0.1$ (see supplementary information).
+where $\grad E_1$ and $\grad E_2$ are the gradients of the energies of the two states, and $\alpha$ and $\beta$ are parameters with recommended values of $\alpha = 10$ and $\beta = 0.1$.
 Here, $E_B$ is an estimation for the current energy barrier; evaluated using the difference between the highest energy along a linear interpolation between the two states and the average energy of the two states.
+These constraints are initially calculated at the start of each minimisation, and regularly recalculated throughout (once per 100 iterations is used in this work).
 
@@
 
-Using this approach, the typical trajectories of the states are demonstrated for a simple 2D potential in \cref{fig:toy2d}a.
+Using the BITSS approach, the typical trajectories of the states are demonstrated for a simple 2D potential in \cref{fig:toy2d}a.
 Initially, the lower energy state jumps up to satisfy the equal energy constraint and then moves to minimise the separation without increasing its energy.
@@
 So, BITSS automatically identifies the `reactive mode' and associated eigenvalue in addition to the transition state.
+Once the transition state has been identified, it is possible to find the full minimum energy pathway by tracing the trajectory of downhill minimisations from the two final states, which are either side of the saddle.
 
-Once BITSS has identified the transition state, it is possible to find the full minimum energy pathway by tracing the trajectory of downhill minimisations from the two final states, either side of the transition state.
-In the case where there are intermediaries, resulting in a chain of multiple transition states between the two minima, BITSS will identify the transition state with the highest energy in the chain.
+In the event that there are intermediate stable states, then there will be a chain of multiple transition states between the two minima.
+In this case, the equal-energy constraint does not restrict the states from passing over the lower energy transition states, and BITSS will converge to the transition state with the highest energy.
 This enables the identification of the overall energy barrier, providing estimates about the overall ease of the transition, or the rate for chemical processes.
 However, if all of transition states or the full pathway are desired, BITSS can be continually repeated from one of the minima downhill from the located transition state and one of the initial minima until the initial minima are piecewise connected by a full pathway.
+
+The BITSS potential in \cref{eq:bitss} and iterative steps above offer key advantages over existing bracketing methods that also use two states to locate the transition state.
+Two such methods are the Step and Slide method \cite{Miron2001} and the saddle method \cite{Dewar1984}.
+In the the Step and Slide method, the separation between two images is minimised while their energy is fixed (iteratively increasing the energy up to the transition state).
+Conversely in the saddle method, the energy of an image is minimised while the image separation is fixed (iteratively decreasing the separation and changing the frozen image up to the transition state).
+However, both of these methods fail if the energy of either image ever exceeds the transition state, as demonstrated in the SI.
+The BITSS method is more reliable, as principally the image pair can both approach the transition state from below, and descend down a ridge from above.
+
+Other bracketing methods experience a range of issues that we will show the BITSS method also overcomes.
+For instance, in the ridge method \cite{Ionova1993}, the two images are initially chosen to bracket the largest energy point on an interpolated path between the two endpoints.
+However, this is not guaranteed to be on the ridge containing the transition state, and specialist methods are required to avoid high-energy local maxima, or when the initial path contains multiple candidate maxima.
+In another example, the Double Ended Surface Walking method \cite{Zhang2013} requires Gaussian bias potentials to be added at each iteration to force two dimers to climb uphill in the landscape.
+For high numbers of degrees of freedom and many iterations this becomes computationally expensive.
+Furthermore, landscapes where the gradient is undefined or discontinuous cannot be explored.
 
@@
 
-As a result of the BITSS method using only two states, it has the potential to be significantly faster than chain-of-states approaches which typically use tens of states.
+Although reliable, chain-of-states approaches typically use tens of states.
+As a result of the BITSS method using only two states, it has the potential to be significantly faster.
 This is tested here by measuring the speed of convergence to the transition state for BITSS in comparison with the string method and DNEB for three diverse systems, exhibiting a broad range of energy landscapes.
@@
 
+\bibitem{Miron2001}
+\bibinfo{author}{Miron, R.~A.} \& \bibinfo{author}{Fichthorn, K.~A.}
+\newblock \bibinfo{title}{{The Step and Slide method for finding saddle points
+  on multidimensional potential surfaces}}.
+\newblock \emph{\bibinfo{journal}{The Journal of Chemical Physics}}
+  \textbf{\bibinfo{volume}{115}}, \bibinfo{pages}{8742--8747}
+  (\bibinfo{year}{2001}).
+
+\bibitem{Dewar1984}
+\bibinfo{author}{Dewar, M. J.~S.}, \bibinfo{author}{Healy, E.~F.} \&
+  \bibinfo{author}{Stewart, J. J.~P.}
+\newblock \bibinfo{title}{{Location of transition states in reaction
+  mechanisms}}.
+\newblock \emph{\bibinfo{journal}{Journal of the Chemical Society, Faraday
+  Transactions 2}} \textbf{\bibinfo{volume}{80}}, \bibinfo{pages}{227}
+  (\bibinfo{year}{1984}).
+
+\bibitem{Ionova1993}
+\bibinfo{author}{Ionova, I.~V.} \& \bibinfo{author}{Carter, E.~A.}
+\newblock \bibinfo{title}{{Ridge method for finding saddle points on potential
+  energy surfaces}}.
+\newblock \emph{\bibinfo{journal}{The Journal of Chemical Physics}}
+  \textbf{\bibinfo{volume}{98}}, \bibinfo{pages}{6377--6386}
+  (\bibinfo{year}{1993}).
+
+\bibitem{Zhang2013}
+\bibinfo{author}{Zhang, X.-J.}, \bibinfo{author}{Shang, C.} \&
+  \bibinfo{author}{Liu, Z.-P.}
+\newblock \bibinfo{title}{{Double-Ended Surface Walking Method for Pathway
+  Building and Transition State Location of Complex Reactions}}.
+\newblock \emph{\bibinfo{journal}{Journal of Chemical Theory and Computation}}
+  \textbf{\bibinfo{volume}{9}}, \bibinfo{pages}{5745--5753}
+  (\bibinfo{year}{2013}).
+
 \bibitem{Wales2002}

### 2022-05-09 manuscript.tex
Jack's changes to conclusion

@@
 \usepackage{enumitem}
+\usepackage{xcolor}
 
@@
 These are set such that the driving forces due to the constraints and single-state energies are of similar size.
-This prevents the constraints from washing out the underlying potential or causing large jumps that make a state pass over the dividing ridge.
+This prevents the constraints from washing out the underlying potential or causing large jumps that make a state pass over the ridge.
 This results in the following equations (see the supplementary information for the derivation),
@@
 
-In the event that there are intermediate stable states, then there will be a chain of multiple transition states between the two minima.
-In this case, the equal-energy constraint does not restrict the states from passing over the lower energy transition states, and BITSS will converge to the transition state with the highest energy.
+In the event that there are intermediate stable states, there will be a chain of multiple transition states between the two minima.
+In this case, the equal-energy constraint will not prevent the states from passing over the lower energy transition states, so BITSS will converge to the transition state with the highest energy.
 This enables the identification of the overall energy barrier, providing estimates about the overall ease of the transition, or the rate for chemical processes.
@@
 Overall, we have developed the binary image transition state search (BITSS) algorithm for the efficient location of transition states in traditionally challenging landscapes.
+The demonstrated speed and memory-efficiency will be key as we move towards simulating systems with increasingly large numbers of degrees of freedom, such as in large biomolecules \cite{Lee2018}, or with increasingly fine resolution, such as in finite element domains \cite{Kolev2021}.
 This has distinct advantages for complex pathways owing to the lack of a required initial pathway estimate, as well as the identification of the transition state that provides the overall energy barrier in multi-step pathways.
@@
 We demonstrated how transition states could be found by both increasing the resolution upon convergence, and coupling systems with different discretisations.
-The ease of coupling two copies of a system and adaptive remeshing, now leads to the possibility of incorporating BITSS into existing optimisation methods, such as surface evolver \cite{Brakke1992} or finite element analysis software, to provide important energy barrier functionality.
+The ease of coupling two copies of a system and adaptive remeshing, now leads to the possibility of incorporating BITSS into existing optimisation methods, such as surface evolver \cite{Brakke1992} or finite element methods \cite{Kolev2021}, to provide important energy barrier functionality.
 
@@
 This opens up possibilities for studying a broad range of systems previously out of reach of conventional landscape methods, but where transition information is valuable.
-These include systems with very short range interactions or contact forces, such as in colloidal clusters, wrinkling and folding of elastic materials, or locomotion and environmental interaction in robotics.
+These include systems with very short range interactions, such as in colloidal clusters, or hard contact forces, such as in the folding of elastic materials, or locomotion and environmental interaction in robotics.
 
-During the comparison with other methods, we have not considered hybrid methods, which involve switching to a single-ended method when close to the transition state, for greater accuracy and efficiency.
-While BITSS does not need to use such a hybrid method to accurately find the transition state, it could be utilised to further increase the efficiency of the algorithm.
-Therefore, future work is to look into how best to implement this and see how it compares against other hybrid methods.
+Throughout, we have demonstrated BITSS as a standalone method for the precise location of transition states.
+However, hybrid methods may also be employed to further increase speed and efficiency.
+Either BITSS could be used to approximately locate the transition state followed by a single ended method for refinement, or BITSS can be used as a refinement method, complimentary to existing chain of states implementations.
+This is scope for possible future work, and could be compared against other existing hybrid methods.
 
@@
 One question that emerges is whether transition states can be located by coupling two images through a small number of collective properties, rather than the total distance between all degrees of freedom in the system.
-A second question is that for landscapes with multiple pathways between states, how can the distance metric be biased to access transition states different from the most direct one?
+A second question concerns landscapes with multiple competing pathways between states.
+BITSS has advantages in these situations due to the lack of a required initial pathway estimate, as well as the identification of the transition state that provides the overall energy barrier in multi-step pathways.
+However, it would be also useful to access transition states different from the most direct one, which may be possible using a biased distance metric.
 Overall, these will enable BITSS to access even more challenging landscapes, and those not yet amenable to traditional landscape exploration techniques.
@@
 
+\bibitem{Lee2018}
+\bibinfo{author}{Lee, C.~T.} \& \bibinfo{author}{Amaro, R.~E.}
+\newblock \bibinfo{title}{{Exascale Computing: A New Dawn for Computational
+  Biology}}.
+\newblock \emph{\bibinfo{journal}{Computing in Science {\&} Engineering}}
+  \textbf{\bibinfo{volume}{20}}, \bibinfo{pages}{18--25}
+  (\bibinfo{year}{2018}).
+
+\bibitem{Kolev2021}
+\bibinfo{author}{Kolev, T.} \emph{et~al.}
+\newblock \bibinfo{title}{{Efficient exascale discretizations: High-order
+  finite element methods}}.
+\newblock \emph{\bibinfo{journal}{The International Journal of High Performance
+  Computing Applications}} \textbf{\bibinfo{volume}{35}},
+  \bibinfo{pages}{527--552} (\bibinfo{year}{2021}).
+
 \bibitem{Brakke1992}

### 2022-05-09 manuscript.tex
Added bracketing figure

@@
 
+\subsection{Other bracketing methods}
+\begin{figure}[htb]
+  \includegraphics[width=\linewidth]{bracketing.pdf}
+  \caption{\label{fig:bracketing}
+    Trajectories of the bracketing methods on a hooked potential with a single saddle point.
+    The minimum energy pathway is shown by the dashed line.
+  }
+\end{figure}
 The BITSS potential in \cref{eq:bitss} and iterative steps above offer key advantages over existing bracketing methods that also use two states to locate the transition state.

### 2022-05-09 fig/create_figs.sh

@@ -1,6 +1,6 @@
 #!/bin/bash
 
-py_figs=('toy2d' 'speedtest' 'adaptivemesh' 'flatdiscontinuous')
+py_figs=('toy2d' 'bracketing' 'speedtest' 'adaptivemesh' 'flatdiscontinuous')
 tex_figs=('BAHschematic')
 
 for fig in ${py_figs[@]}; do

### 2022-05-09 fig/make_bracketing/plot.py

@@ -1,0 +1,91 @@
+#!/usr/bin/env python3
+import numpy as np
+import matplotlib.pyplot as plt
+import matplotlib.image as mim
+import json
+import os
+import pyutils.latexify as lt
+# Get default style for paper
+import sys; sys.path.insert(0, '..')
+import style
+
+# Data generated using energyLandscapes/bits_test/hook_potential/view.py
+
+### Plot parameters
+ar = 0.6
+xlim = [-2.1, 1.8]
+ylim = [-1.75, 1.75]
+
+cpath = style.colors
+cts = 'w'#style.c2
+cmin = 'w'#style.c3
+cmap = 'Greys_r'
+mec = 'k'
+ms = 6
+
+def make_potential():
+    x, y = np.mgrid[xlim[0]:xlim[1]:100j, ylim[0]:ylim[1]:100j]
+
+    peaks = [[ -1.,  0.,  0., 3.162, 3.162],
+             [  1.,  0.,  0.,    1.,    1.],
+             [  5.,  2.,  0.,    1., .3162],
+             [ -1.,  1.,  1., .3162, .3162],
+             [ -1.,  1., -1., .3162, .3162],
+             [0.01,  0.,  0.,    1.,    1.],
+             [ 0.5, -2.,  0.,    1.,    1.]]
+
+    e = np.zeros_like(x)
+    for peak in peaks:
+        e += peak[0] * np.exp( -((x-peak[1])/peak[3])**2 - ((y-peak[2])/peak[4])**2 )
+
+    fig = plt.figure(frameon=False, figsize=(xlim[1]-xlim[0], ylim[1]-ylim[0]))
+    ax = fig.add_axes([0,0,1,1])
+    levels = np.arange(-1.5, 1.5, 0.25)
+    plt.contourf(x, y, e, cmap=cmap, levels=levels, extend='both')
+    ax.axis('off')
+    plt.savefig(f'potential.png')
+    plt.close()
+
+
+def load_data():
+    with open('data.json', 'r') as f:
+        d = json.load(f)
+    bits = np.array(d['bits'])
+    dhs = np.array(d['dhs'])
+    ss = np.array(d['ss'])
+    mep = np.array(d['mep'])
+    return bits, dhs, ss, mep
+
+def plot(minima, ts, paths, mep):
+    fig = lt.figure(1, ar)
+    ax = fig.add_axes([0,0,1,1])
+    # Plot potential
[…]

### 2022-05-09 manuscript.tex
Updates, including changes to bracketing methods

@@
 
-Existing transition state search methods generally fall into two categories, single- and double-ended methods.
+Transition state search methods generally fall into two categories, single- and double-ended methods.
 Single-ended methods are initialised at a single state and attempt to climb to a nearby saddle point.
 Examples include eigenvector following \cite{Cerjan1981}, the dimer method \cite{Heyden2005,Kastner2008,Zhang2016}, and climbing image methods \cite{E2007,Ren2013}.
-Double-ended methods, such as the string method \cite{E2002,E2007} and doubly-nudged elastic band (DNEB) \cite{Trygubenko2004}, involve initialising a chain of states between two minima and then minimising the total energy of the chain.
-An appropriate interpolation must be used for the initialisation, which can be challenging to produce \cite{Wales2012a}.
-These double-ended methods also provide an estimate for the full transition pathway in addition to approximating the transition state.
+Double-ended methods can be further subdivided into two groups.
+The first utilise a chain of states between two minima which is then minimised to provide an estimate for the full transition pathway in addition to the transition state.
+Examples are the string method \cite{E2002,E2007} and doubly-nudged elastic band (DNEB) \cite{Trygubenko2004}.
+These methods require an appropriate initial interpolation, which can sometimes be challenging to obtain \cite{Wales2012a}.
+The final group are bracketing methods, which involve two states converging to the transition state from either side.
+These include the Dewar-Healy-Stewart (DHS) algorithm \cite{Dewar1984}, ridge method \cite{Ionova1993}, the step and slide method \cite{Miron2001}, and the double-ended surface walking method \cite{Zhang2013}.
 
 However, a large range of landscapes prove challenging or impossible to explore via these methods.
-One key problem arises from the push towards larger and more complex systems \cite{Trefethen2013,Shalf2020,Alexander2020}, resulting in the need to develop algorithms that are more memory and computationally efficient, and can incorporate advanced optimisation strategies such as on-the-fly adaptive remeshing and coarse-graining.
-Current double-ended methods require a chain of tens of states to gain an accurate approximation, and have issues with remeshing due to the different number of degrees of freedom for each state.
-Single-ended methods are not well suited for identifying specific pathways and can spend a large amount of time searching for undesired transition states.
+One key problem arises from the push towards larger and more complex systems \cite{Trefethen2013,Shalf2020,Alexander2020}, resulting in the need to develop algorithms that are more computationally and memory efficient, and can incorporate optimisation strategies such as on-the-fly adaptive remeshing and coarse-graining.
+Chain-of-states methods, however, are not particularly efficient as they require tens of states to gain an accurate approximation, and they have issues with remeshing due to each state having a different number of degrees of freedom.
+Meanwhile, single-ended methods are not well suited for identifying specific pathways and can spend a large amount of time searching for undesired transition states.
 Another major challenge in studying complex energy landscapes relates to the presence of locally flat or discontinuous regions, such as when considering patchy \cite{McMullen2018,Nguemaha2018,Chen2018b} and hard-body \cite{Richard2018,Santra2018} interactions in atomistic simulations, systems of polymer chains \cite{Mokkonen2016}, or collision constraints for macroscopic objects \cite{Wriggers2006}.
-Flat zero-modes in the landscape pose issues for single-ended search methods that rely only upon local information.
+Flat zero-modes in the landscape pose issues for single-ended search methods and some bracketing methods that rely only upon local information.
 Specialist treatment can sometimes be used such as in the case of global rotation and translation \cite{Page1988}, but they are thwarted by local zero-modes.
-Meanwhile, current methods cannot typically be applied in the case of discontinuous potentials, or where the gradient is prohibitively expensive to compute, because continuous, differentiable optimisation functions are required.
+Finally, current methods cannot typically be applied in the case of discontinuous potentials, or if the gradient is prohibitively expensive to compute, because continuous, differentiable optimisation functions are required.
 
-In this work we introduce a new method, the Binary-Image Transition State Search (BITSS), and using a range of different applications, we will demonstrate how BITSS addresses each of the above challenges.
-BITSS is a double-ended method that uses just two states that converge toward a transition state from either side, therefore combining aspects of the two traditional transition state search categories.
-In addition, unlike other double-ended methods, BITSS does not require any initial interpolation.
+In this work we introduce a new bracketing method, the Binary-Image Transition State Search (BITSS) and, using a range of different applications, we demonstrate that it successfully addresses each of the above challenges.
+In addition, we also show that BITSS has an improved reliability in contrast to existing bracketing methods.
 
@@
 In the event that there are intermediate stable states, there will be a chain of multiple transition states between the two minima.
-In this case, the equal-energy constraint will not prevent the states from passing over the lower energy transition states, so BITSS will converge to the transition state with the highest energy.
+In this case, the equal-energy constraint will not prevent the states from passing over the lower energy transition states, so BITSS should converge to the transition state with the highest energy.
 This enables the identification of the overall energy barrier, providing estimates about the overall ease of the transition, or the rate for chemical processes.
-However, if all of transition states or the full pathway are desired, BITSS can be continually repeated from one of the minima downhill from the located transition state and one of the initial minima until the initial minima are piecewise connected by a full pathway.
+However, as demonstrated in the supplementary information, if multiple transition states have very similar energies then a smaller distance reduction factor, $f$, may be necessary to ensure that it does indeed converge to the highest transition state.
+If, instead, all of transition states or the full pathway are desired, BITSS can be continually repeated from one of the minima downhill from the located transition state and one of the initial minima until the initial minima are piecewise connected by a full pathway.
 
@@
 The BITSS potential in \cref{eq:bitss} and iterative steps above offer key advantages over existing bracketing methods that also use two states to locate the transition state.
-Two such methods are the Step and Slide method \cite{Miron2001} and the saddle method \cite{Dewar1984}.
-In the the Step and Slide method, the separation between two images is minimised while their energy is fixed (iteratively increasing the energy up to the transition state).
-Conversely in the saddle method, the energy of an image is minimised while the image separation is fixed (iteratively decreasing the separation and changing the frozen image up to the transition state).
-However, both of these methods fail if the energy of either image ever exceeds the transition state, as demonstrated in the SI.
-The BITSS method is more reliable, as principally the image pair can both approach the transition state from below, and descend down a ridge from above.
-
-Other bracketing methods experience a range of issues that we will show the BITSS method also overcomes.
 For instance, in the ridge method \cite{Ionova1993}, the two images are initially chosen to bracket the largest energy point on an interpolated path between the two endpoints.
 However, this is not guaranteed to be on the ridge containing the transition state, and specialist methods are required to avoid high-energy local maxima, or when the initial path contains multiple candidate maxima.
-In another example, the Double Ended Surface Walking method \cite{Zhang2013} requires Gaussian bias potentials to be added at each iteration to force two dimers to climb uphill in the landscape.
-For high numbers of degrees of freedom and many iterations this becomes computationally expensive.
-Furthermore, landscapes where the gradient is undefined or discontinuous cannot be explored.
+In another example, the double ended surface walking method \cite{Zhang2013} requires Gaussian bias potentials to be added at each iteration to force two dimers to climb uphill in the landscape.
+Although, for high numbers of degrees of freedom and many iterations this becomes computationally expensive.
+
+The two methods most similar to BITSS are the DHS and step and slide methods.
+In the the step and slide method, the separation between two images is minimised while their energy is fixed (iteratively increasing the energy up to the transition state).
+Conversely in the DHS method, the energy of an image is minimised while the image separation is fixed (iteratively decreasing the separation and changing the frozen image up to the transition state).
+However, both of these methods fail if the energy of either image ever exceeds the transition state, as demonstrated for the hooked potential in \cref{fig:bracketing}.
+Whereas the BITSS method is successful in this case, showing that it is more reliable when the image pair must descend down a ridge from above.
+
+Furthermore, BITSS has an improved efficiency over these two methods.
+In the case of DHS, fixing one state in place and optimising the other means that the amount that the separation is reduced must be much smaller than BITSS to ensure that it does not pass over the ridge.
+Meanwhile, using step and slide, it is difficult to obtain a reasonable energy increment when the two states are far from the transition state, also leading to a larger than necessary number of iterations.
 
@@
 The final system involves a droplet situated on a chemically striped surface with both hydrophilic and hydrophobic regions.
-Droplet transitions on patterned surfaces are vital to understand as powerful bio-inspired liquid manipulation strategies  \cite{Kusumaatmaja2006,Brown2016}.
+Droplet transitions on patterned surfaces such as this are vital to understand as powerful bio-inspired liquid manipulation strategies  \cite{Kusumaatmaja2006,Brown2016}.
 In the example shown in \cref{fig:speedtest}c, a droplet transitions from two hydrophilic patches to one patch.
@@
 Secondly, the BITSS method can more accurately approximate the transition state by orders of magnitude, particularly for the wetting example where the other methods do not significantly improve upon the initial pathway estimate.
-Therefore, unlike these other double-ended methods, BITSS does not require a second approach to accurately locate the transition state.
+Therefore, unlike these chain-of-states methods, BITSS does not require a second approach to accurately locate the transition state.
 
@@
 Adaptive remeshing and coarse-graining are widely used techniques that we can utilise to further increase the efficiency of BITSS.
-These techniques cause issues for existing double-ended methods because the coupled states may end up with different degrees of freedom.
+These techniques cause issues for most existing double-ended methods because the coupled states may end up with different degrees of freedom.
 However, in BITSS the only direct coupling is in the distance measure, $\mathrm{d}(\bm{x}_1,\bm{x}_2)$, which is relatively easy to adapt.
@@
 Overall, we have developed the binary image transition state search (BITSS) algorithm for the efficient location of transition states in traditionally challenging landscapes.
-The demonstrated speed and memory-efficiency will be key as we move towards simulating systems with increasingly large numbers of degrees of freedom, such as in large biomolecules \cite{Lee2018}, or with increasingly fine resolution, such as in finite element domains \cite{Kolev2021}.
 This has distinct advantages for complex pathways owing to the lack of a required initial pathway estimate, as well as the identification of the transition state that provides the overall energy barrier in multi-step pathways.
-Furthermore, the demonstrated speed and memory-efficiency will be key as we move towards simulating systems with increasingly large numbers of degrees of freedom, such as in large biomolecules, or with increasingly fine resolution, such as in finite element domains.
+Furthermore, the demonstrated speed and memory-efficiency will be key as we move towards simulating systems with increasingly large numbers of degrees of freedom, such as in large biomolecules \cite{Lee2018}, or with increasingly fine resolution, such as in finite element domains \cite{Kolev2021}.
 
@@
 A second question concerns landscapes with multiple competing pathways between states.
-BITSS has advantages in these situations due to the lack of a required initial pathway estimate, as well as the identification of the transition state that provides the overall energy barrier in multi-step pathways.
-However, it would be also useful to access transition states different from the most direct one, which may be possible using a biased distance metric.
+In such cases, it may be possible to access transition states different from the most direct one by using a biased distance metric.
 Overall, these will enable BITSS to access even more challenging landscapes, and those not yet amenable to traditional landscape exploration techniques.

### 2022-05-11 manuscript.tex
Jack and Halim's minor changes to manuscript

@@
 These methods require an appropriate initial interpolation, which can sometimes be challenging to obtain \cite{Wales2012a}.
-The final group are bracketing methods, which involve two states converging to the transition state from either side.
+The second group are bracketing methods, which involve two states converging to the transition state from either side.
 These include the Dewar-Healy-Stewart (DHS) algorithm \cite{Dewar1984}, ridge method \cite{Ionova1993}, the step and slide method \cite{Miron2001}, and the double-ended surface walking method \cite{Zhang2013}.
 
-However, a large range of landscapes prove challenging or impossible to explore via these methods.
+A large range of landscapes, however, prove challenging or impossible to explore via these methods.
 One key problem arises from the push towards larger and more complex systems \cite{Trefethen2013,Shalf2020,Alexander2020}, resulting in the need to develop algorithms that are more computationally and memory efficient, and can incorporate optimisation strategies such as on-the-fly adaptive remeshing and coarse-graining.
-Chain-of-states methods, however, are not particularly efficient as they require tens of states to gain an accurate approximation, and they have issues with remeshing due to each state having a different number of degrees of freedom.
+Chain-of-states methods are not very efficient as they require tens of states to gain an accurate approximation, and they have issues with remeshing due to each state having a different number of degrees of freedom.
 Meanwhile, single-ended methods are not well suited for identifying specific pathways and can spend a large amount of time searching for undesired transition states.
 Another major challenge in studying complex energy landscapes relates to the presence of locally flat or discontinuous regions, such as when considering patchy \cite{McMullen2018,Nguemaha2018,Chen2018b} and hard-body \cite{Richard2018,Santra2018} interactions in atomistic simulations, systems of polymer chains \cite{Mokkonen2016}, or collision constraints for macroscopic objects \cite{Wriggers2006}.
-Flat zero-modes in the landscape pose issues for single-ended search methods and some bracketing methods that rely only upon local information.
+Flat zero-modes in the landscape pose issues for single-ended search methods and current bracketing methods that rely only upon local information.
 Specialist treatment can sometimes be used such as in the case of global rotation and translation \cite{Page1988}, but they are thwarted by local zero-modes.
@@
 
-In this work we introduce a new bracketing method, the Binary-Image Transition State Search (BITSS) and, using a range of different applications, we demonstrate that it successfully addresses each of the above challenges.
-In addition, we also show that BITSS has an improved reliability in contrast to existing bracketing methods.
+In this work we introduce a new double-ended bracketing method, the Binary-Image Transition State Search (BITSS).
+Using a range of different applications, we demonstrate that it successfully addresses each of the above challenges.
+In addition, we show that BITSS is superior compared to existing bracketing methods, allowing us to access the transition states when other methods fail.
 
@@
 To further ensure that neither state is pulled over the ridge, a secondary constraint enforces equal energies for the two states.
-Using this strategy, the two states will meet at the lowest point on the ridge - the transition state.
+Using this strategy, the two states will meet at the lowest point on the ridge, the transition state.
 
@@
 These are set such that the driving forces due to the constraints and single-state energies are of similar size.
-This prevents the constraints from washing out the underlying potential or causing large jumps that make a state pass over the ridge.
+This prevents the constraints from dominating the underlying potential or causing large jumps that make a state pass over the ridge.
 This results in the following equations (see the supplementary information for the derivation),
@@
 where $\grad E_1$ and $\grad E_2$ are the gradients of the energies of the two states, and $\alpha$ and $\beta$ are parameters with recommended values of $\alpha = 10$ and $\beta = 0.1$.
-Here, $E_B$ is an estimation for the current energy barrier; evaluated using the difference between the highest energy along a linear interpolation between the two states and the average energy of the two states.
+Here, $E_B$ is an estimation for the current energy barrier, evaluated using the difference between the highest energy along a linear interpolation between the two states and the average energy of the two states.
 These constraints are initially calculated at the start of each minimisation, and regularly recalculated throughout (once per 100 iterations is used in this work).
@@
 However, as demonstrated in the supplementary information, if multiple transition states have very similar energies then a smaller distance reduction factor, $f$, may be necessary to ensure that it does indeed converge to the highest transition state.
-If, instead, all of transition states or the full pathway are desired, BITSS can be continually repeated from one of the minima downhill from the located transition state and one of the initial minima until the initial minima are piecewise connected by a full pathway.
+Furthermore, if all of transition states or the full pathway are desired, BITSS can be continually repeated from one of the minima downhill from the located transition state and one of the initial minima until the initial minima are piecewise connected by a full pathway.
 
@@
 In another example, the double ended surface walking method \cite{Zhang2013} requires Gaussian bias potentials to be added at each iteration to force two dimers to climb uphill in the landscape.
-Although, for high numbers of degrees of freedom and many iterations this becomes computationally expensive.
+For high numbers of degrees of freedom and many iterations, this becomes very computationally expensive.
 
@@
 Conversely in the DHS method, the energy of an image is minimised while the image separation is fixed (iteratively decreasing the separation and changing the frozen image up to the transition state).
-However, both of these methods fail if the energy of either image ever exceeds the transition state, as demonstrated for the hooked potential in \cref{fig:bracketing}.
-Whereas the BITSS method is successful in this case, showing that it is more reliable when the image pair must descend down a ridge from above.
+To illustrate how BITSS is superior compared to these methods, we consider the hooked 2d potential in \cref{fig:bracketing}.
+This shows that both of these methods fail if the energy of either image ever exceeds the transition state.
+In contrast, the BITSS method is successful in this case, showing that it is more reliable when the image pair must descend down a ridge from above.
 
@@
 For this we use the cylindrical buckling example with the resolution increasing from 40 to 100 triangles around the cylinder, corresponding to an increase from \num{1760} to \num{11000} degrees of freedom.
-This demonstrates that BITSS is able to converge to the transition state so long as the remeshing is not so significant as to shift a state into the basin of attraction of the other minima.
+This demonstrates that BITSS is able to converge to the transition state so long as the remeshing is not so significant as to shift a state into the basin of attraction of the other minimum.
 
@@
         Bottom inset: The pathway taken, with the edges of the flat regions marked by dashed lines.
-    (b) Disconnectivity graph of the energy landscape for a seven-particle cluster with a discontinuous hard-core pair potential (orange), and a standard Lennard-Jones potnetial (gray).
+    (b) The discontinuous hard-core pair potential used in the seven-particle cluster (orange).
+        The standard Lennard-Jones potential is also shown in grey.
+    (c) Disconnectivity graphs of the energy landscapes for the seven-particle cluster with the two potentials.
         The two graphs are offset for visibility.
-    (c) Plot of the discontinuous potential.
-        The repulsive section of the standard Lennard-Jones potential is also shown in grey.
   }
@@
 These changes are detailed in the methods section.
-This has been tested using a Lennard-Jones 7-particle cluster with hard cores, resulting in a discontinuous landscape.
-Using the gradient-free approach, BITSS is able to successfully find the transition states, allowing us to plot the disconnectivity graph of the system, shown in \cref{fig:flatdiscontinuous}b.
+This has been tested using a 7-particle cluster with a hard-core Lennard-Jones pair-potential, shown in \cref{fig:flatdiscontinuous}b, which results in a discontinuous landscape.
+Using the gradient-free approach, BITSS is able to successfully find the transition states, allowing us to plot the disconnectivity graph of the system, shown in \cref{fig:flatdiscontinuous}c.
 Compared with the results for the standard Lennard-Jones cluster, the energies of the minima are largely unchanged, but the energies of the transition states are found to be slightly higher.
@@
 We demonstrated how transition states could be found by both increasing the resolution upon convergence, and coupling systems with different discretisations.
-The ease of coupling two copies of a system and adaptive remeshing, now leads to the possibility of incorporating BITSS into existing optimisation methods, such as surface evolver \cite{Brakke1992} or finite element methods \cite{Kolev2021}, to provide important energy barrier functionality.
+The ease of coupling two copies of a system and adaptive remeshing, now leads to the possibility of incorporating BITSS into existing open-source optimisation methods, such as surface evolver \cite{Brakke1992} or finite element methods \cite{Kolev2021}, to provide important energy barrier functionality.
 

### 2022-05-11 fig/make_adaptivemesh/plot.py

@@ -97,7 +97,7 @@ def plot_cb(fig, y0, htot):
         # Arrow
         ax4.set_aspect('equal')
         ax4.arrow(0, 0, 1, 0, width=0.015, color='k')
-        fig.text(xax1+1.5*w2+wspace2,  y0+0.4*hspace4/htot, 'BITSS trajectory', ha='center', va='bottom')
+        fig.text(xax1+1.5*w2+wspace2,  y0+0.4*hspace4/htot, 'BITSS trajectory (increasing resolution)', ha='center', va='bottom')
         return axes
 
     def plot_cylinder(ax):
@@ -261,13 +261,14 @@ def plot_sw(fig, y1, htot):
 def main():
     h1 = 0.5
     h2 = 0.34
-    h = h1 + h2
+    hspace = 0.01
+    h = h1 + h2 + hspace
 
     fig = lt.figure(1, h)
     fig.text(0,  1, '(a)', ha='left', va='top')
     fig.text(0,  h2/h, '(b)', ha='left', va='top')
 
-    plot_cb(fig, h2/h, h)
+    plot_cb(fig, (h2+hspace)/h, h)
     plot_sw(fig, h2/h, h)
 
     lt.savefig('../adaptivemesh.pdf')

### 2022-05-11 fig/make_flatdiscontinuous/plot.py

@@ -160,10 +160,11 @@ def plot_flat(fig, hsize):
 
 
 def plot_discontinuous(fig, hsize):
-    space1 = 0.2
-    space2 = 0.1
-    w1 = 0.4
-    w2 = 0.25
+    space1 = 0.1
+    space2 = 0.2
+    space2label = 0.03
+    w1 = 0.3
+    w2 = 0.4
     h1 = 0.9
     h2 = 0.7
     y2 = 0.2
@@ -212,12 +213,12 @@ def plot_discontinuous(fig, hsize):
 
     def make_axes():
         fig.text(0, hsize[0]+0.95*hsize[1], '(b)', ha='left', va='top')
-        fig.text(w1+space1, hsize[0]+0.95*hsize[1], '(c)', ha='left', va='top')
-        ax = fig.add_axes([space1, hsize[0]+(1-h1)/2*hsize[1], w1, h1*hsize[1]])
-        pot_ax = fig.add_axes([w1+space1+space2, hsize[0]+y2*hsize[1], w2, h2*hsize[1]])
-        ax.set_ylabel(r'Energy / $\epsilon$')
-        ax.set_ylim(-13, -10.5)
-        return ax, pot_ax
+        fig.text(w1+space1+space2label, hsize[0]+0.95*hsize[1], '(c)', ha='left', va='top')
+        pot_ax = fig.add_axes([space1, hsize[0]+y2*hsize[1], w1, h2*hsize[1]])
+        dg_ax = fig.add_axes([w1+space1+space2, hsize[0]+(1-h1)/2*hsize[1], w2, h1*hsize[1]])
+        dg_ax.set_ylabel(r'Energy / $\epsilon$')
+        dg_ax.set_ylim(-13, -10.5)
+        return dg_ax, pot_ax
     
     def make_dgraph(nodes, ts):
         # Generate disconnectivity graph
@@ -279,26 +280,26 @@ def plot_discontinuous(fig, hsize):
     dg2.color_by_group([[0,1,2,3]], [c2])
 
     # Plot
-    ax, pot_ax = make_axes()
-    dg2.plot(axes=ax, linewidth=1)
-    dg1.plot(axes=ax, linewidth=1)
-    ax.tick_params(which='both', direction='in')
+    dg_ax, pot_ax = make_axes()
+    dg2.plot(axes=dg_ax, linewidth=1)
+    dg1.plot(axes=dg_ax, linewidth=1)
[…]

### 2022-05-12 si/supplementary_information.tex
Put distance and pair energy in results. Made Jack's changes.
Added highest TS test to SI

@@
-\documentclass[aps,physrev,10pt]{revtex4-2}
+\documentclass[10pt]{revtex4}
+
+% Text
+% \usepackage{amssymb}
 
@@
 \begin{document}
-\title{Binary Image Transition State Search \\ Supplementary Information}
+\title{A fast and memory-efficient transition state search method for complex energy landscapes \\ Supplementary Information}
 \author{Samuel J. Avis}
@@
 
+\section{Multiple transition states}
+Here we test how the BITSS method performs when there are multiple transition states in the pathway between the two starting minima.
+For this we use a 2D potential, shown in \cref{fig:multits}a, with a pathway that follows a chicane of two $135^\circ$ circular arcs.
+The energy is given by the squared distance from this path, plus two barriers resulting in transition states A and B, with energies $E_A$ and $E_B$.
+We then vary $E_B$ between 0 and $E_A$, and the size of the distance reduction factor, $f$, to see if BITSS successfully converges to the higher transition state A.
+For each pair of parameters we perform 5 runs with slight variations in the starting positions, with the results in \cref{fig:multits}b showing the points at which all 5 converge to A.
+
+We see that if the difference between the two barriers is sufficiently large ($\gtrsim 10\%$) then BITSS always converges to the higher transition state.
+However, as the difference decreases it starts to sometimes converge to the lower transition state if the separation is decreased quickly.
+Therefore, to ensure that BITSS always converges to the higher energy transition state it may be necessary to restrict the separation step size.
+
+Although the equal-energy constraint should cause the states to converge to A, this is not always the case because the discrete steps in the minimisation can cause the left image to jump over A before the other image passes B.
+If the minisation is fast and takes large steps then the chance for this to occur is increased.
+Therefore, systems with complex, high-dimensional landscapes can probably successfully locate the highest transition state for larger values of $f$ and smaller height differences than simpler systems such as this 2D example.
+
+\begin{figure}[htb]
+  \includegraphics{fig/multits.pdf}
+  \caption{\label{fig:multits}
+    (a) The potential used in the test.
+    M1 and M2 denote the two starting minima, and A and B are the two transition states.
+    The energy of the barrier to B, $E_B$, is varied between 0 and $E_A$.
+    (b) The results for the parameters under which BITSS reliably converges to A, and the points at which it sometimes converges to B.
+    The x-axis is the BITSS distance reduction factor, $f$, and the y-axis is the relative difference between the two barrier heights.
+  }
+\end{figure}
+
 \end{document}

### 2022-05-12 si/fig/create_figs.sh

@@ -1,7 +1,7 @@
 #!/bin/bash
 
-py_figs=('paramtest')
-tex_figs=('BAHschematic')
+py_figs=('paramtest' 'multits')
+tex_figs=()
 
 for fig in ${py_figs[@]}; do
   echo "Plotting $fig"

### 2022-05-12 si/fig/make_multits/plot.py

@@ -1,0 +1,104 @@
+#!/usr/bin/env python3
+import glob
+import numpy as np
+import pandas as pd
+import matplotlib.pyplot as plt
+import matplotlib.ticker as mtick
+import matplotlib.image as mim
+from pyutils import latexify as lt
+# Get default style for SI
+import sys; sys.path.insert(0, '..')
+import style
+
+c1 = style.c3
+c2 = style.c2
+
+h1 = 0.3
+h2 = 0.15
+arc_angle = 135
+
+def energy(x, y):
+    def arc_dist(x, y, direction):
+        x0 = np.sin(arc_angle/360*np.pi)
+        y0 = np.cos(arc_angle/360*np.pi)
+        xp = x + direction*x0
+        yp = y + direction*y0
+        s = np.abs(x0)
+        r = (xp**2 + yp**2)**0.5
+        theta = np.arctan2(xp, yp*direction)
+        d2ring = (r - 1)**2
+        d2tips = ((np.abs(xp) - s)**2 + y**2)
+        d2 = np.where(np.abs(theta)<arc_angle*np.pi/360, d2ring, d2tips)
+        return d2
+    def barrier(x, direction, h):
+        x0 = np.sin(arc_angle/360*np.pi)
+        xp = x - direction*x0
+        e = h * ((xp/x0)**2 - 1)**2
+        return e
+    e1 = arc_dist(x, y, +1)
+    e2 = arc_dist(x, y, -1)
+    e = np.where(e1<e2, e1, e2)
+    barrier1 = barrier(x, -1, h1)
+    barrier2 = barrier(x, +1, h2)
+    e = e + np.where(x<0, barrier1, barrier2)
+    return e
+
+def plot_potential(ax):
+    xlim=[-2.3, 2.3]
+    ylim=[-1.1, 1.1]
+    # Generate potential.png
+    x, y = np.mgrid[xlim[0]:xlim[1]:100j, ylim[0]:ylim[1]:100j]
+    e = energy(x, y)
+    fig_tmp = plt.figure(figsize=(xlim[1]-xlim[0], ylim[1]-ylim[0]))
+    ax_tmp = fig_tmp.add_axes([0,0,1,1])
+    ax_tmp.contourf(x, y, e, cmap='Greys_r', levels=np.linspace(np.min(e),np.percentile(e,70),20))
+    ax_tmp.axis('off')
+    fig_tmp.savefig('potential.png')
+    plt.close(fig_tmp)
[…]

### 2022-05-17 fig/make_adaptivemesh/plot.py
Updated figure colours and formatting

@@ -119,6 +119,8 @@ def plot_cb(fig, y0, htot):
 
     def plot_colorbar(ax, vmax):
         mpl.colorbar.ColorbarBase(ax, cmap=plt.get_cmap(cmap), norm=mpl.colors.Normalize(vmin=-vmax, vmax=vmax))
+        ax.yformatted = False
+        ax.format_axes()
         ax.yaxis.set_ticks_position('left')
 
     tri1, disp1, tri2, disp2, tri3, disp3 = load_data('cb_data.json')
@@ -150,7 +152,7 @@ def plot_sw(fig, y1, htot):
     cs1 = 'lightgrey' # hydrophobic
     cs2 = 'k'         # hydrophilic
     cz1 = style.c1
-    cz2 = style.c2
+    cz2 = style.c3
 
     def load_data(data_file):
         with open(data_file) as f:
@@ -191,7 +193,7 @@ def plot_sw(fig, y1, htot):
         ax3.axis('off')
         # Zoom indicator
         ind_lw = 0.8
-        ax15_trans = fig.add_axes([xc, yb, w1, h1/htot], sharex=ax15, sharey=ax15, fc='none')
+        ax15_trans = fig.add_axes([xc, yb, w1, h1/htot], sharex=ax15.ax, sharey=ax15.ax, fc='none')
         params = {'bounds':zoom_region, 'inset_ax':ax2, 'alpha':1, 'lw':ind_lw, 'zorder':99}
         _, conn1 = ax15_trans.indicate_inset(**params, edgecolor=cz1)
         _, conn2 = ax16.indicate_inset(**params, edgecolor=cz2)

### 2022-05-17 fig/make_bracketing/plot.py

@@ -16,7 +16,7 @@ ar = 0.6
 xlim = [-2.1, 1.8]
 ylim = [-1.75, 1.75]
 
-cpath = style.colors
+cpath = style.colors[::-1]
 cts = 'w'#style.c2
 cmin = 'w'#style.c3
 cmap = 'Greys_r'

### 2022-05-17 fig/make_flatdiscontinuous/plot.py

@@ -26,8 +26,8 @@ def plot_flat(fig, hsize):
     dx = 2.5
 
     cpath = style.c1
-    cts = style.c2
-    cmin = style.c3
+    cmin = style.c2
+    cts = style.c3
     ms = 5
     mec = 'k'
     lw = 1.2

### 2022-05-17 fig/make_speedtest/plot.py

@@ -56,8 +56,8 @@ for isub, subfig in enumerate(['a', 'b', 'c']):
     if (isub == 0):
         x0 = x0 + 0.01
         w1 = w1 - 0.01
-    ax1 = plt.axes((x0+xd0, hd11/h, w1, h1/h))
-    ax2 = plt.axes((x0+xd0, (hd11+h1+hd12)/h, w1, h1/h), sharex=ax1, sharey=ax1)
+    ax1 = fig.add_axes((x0+xd0, hd11/h, w1, h1/h))
+    ax2 = fig.add_axes((x0+xd0, (hd11+h1+hd12)/h, w1, h1/h), sharex=ax1.ax, sharey=ax1.ax)
     fig.text(x0, 1, f'({subfig})', va='top', ha='left')
 
     # Plot lines
@@ -105,7 +105,7 @@ for isub, subfig in enumerate(['a', 'b', 'c']):
         ax2.annotate('DNEB', [0.4, 0.7], [0.53, 0.53], xycoords='axes fraction', alpha=0,
                     arrowprops={'arrowstyle':'-'}, bbox={'pad':0, 'fc':'none', 'ec':'none'})
         # Big hidden axes for y label
-        ax_tmp = plt.axes((x0+xd0, hd11/h, w1, (2*h1+hd12)/h), sharey=ax1, frameon=False)
+        ax_tmp = plt.axes((x0+xd0, hd11/h, w1, (2*h1+hd12)/h), sharey=ax1.ax, frameon=False)
         ax_tmp.tick_params(labelcolor='none', which='both', top=False, bottom=False, left=False, right=False)
         ax_tmp.set_ylabel('Distance error / $d_0$', labelpad=-0.1)
 

### 2022-05-17 fig/make_toy2d/plot.py

@@ -21,14 +21,14 @@ ar2 = 0.5
 ldx = 0#.008
 
 cbits = style.c1
-cts = style.c2
-cmin = style.c3
-cenergy = style.c3
+cmin = style.c2
+cts = style.c3
 cdist = style.c2
+cenergy = style.c3
 cmap = 'Greys_r'
 mec = 'k'
 ms = 6
-clw = 1
+lw = 1.5
 tau_len = 1.5
 
 
@@ -112,8 +112,8 @@ axa.plot(minima[:,0], minima[:,1], c=cmin, marker='o', mec=mec, ms=ms, ls='none'
 axa.plot(ts[0], ts[1], c=cts, marker='o', mec=mec, ms=ms, zorder=99)
 
 # BITS
-axa.plot(bits[:,0,0], bits[:,0,1], c=cbits, zorder=2)
-axa.plot(bits[:,1,0], bits[:,1,1], c=cbits, zorder=2)
+axa.plot(bits[:,:,0], bits[:,:,1], c='k', lw=lw, zorder=2)
+axa.plot(bits[:,:,0], bits[:,:,1], c=cbits, lw=lw, zorder=2)
 
 # Pathway
 axa.plot(path[:,0], path[:,1], ls='--', c='k', zorder=1)
@@ -137,8 +137,6 @@ levels = np.delete(np.arange(np.min(e), np.max(e), (e0-np.min(e))/6), 6)
 cnt = axb.contourf(x, y, e, cmap=cmap, levels=levels)
 for c in cnt.collections:
     c.set_edgecolor('face')
-# axb.contour(x, y, e, levels=levels, colors='k', linestyles='solid', linewidths=clw)
-# axb.contour(x, y, e, levels=[e0], colors='k', linestyles='solid', linewidths=1.5*clw)
 
 axb.plot(x1[0], x1[1], c=cbits, marker='o', mec=mec, ms=ms, zorder=99)
 axb.plot(x2[0], x2[1], c=cbits, marker='o', mec=mec, ms=ms, zorder=99)
@@ -156,8 +154,8 @@ axb.quiver(x1[0], x1[1], gd[0], gd[1], color=cdist, **arrow_args)
 axb.quiver(x2[0], x2[1], -gd[0], -gd[1], color=cdist, **arrow_args)
 
 # axb.text(0.03, 0.35, '$F_P$', transform=axb.transAxes).set_path_effects([mpe.withStroke(linewidth=2, foreground='w')])
[…]

### 2022-05-17 fig/style.py

@@ -1,5 +1,6 @@
 #!/usr/bin/env python3
 
+import re
 import matplotlib as mpl
 import matplotlib.pyplot as plt
 import pyutils.latexify as lt
@@ -11,20 +12,42 @@ lt.update_width('natcomm-single')
 plt.rc('font', size=9)
 plt.rc('axes', labelsize=9)
 
+def formatter(s):
+    base = re.search(r'\$\\mathdefault\{(.*)\}\$', s)
+    if (base is None): return s
+    s = base.group(1)
+    s = s.replace('−', '-')
+    # Add thousands separator
+    if (re.search(r'\^', s) is None):
+        try:
+            value = int(s)
+        except ValueError:
+            value = float(s)
+        s = f'{value:,}'
+    # Convert numbers to normal text font
+    s = s.replace('^', r'}^\text{')
+    s = s.replace('-', r'}-\text{')
+    s = r'$\text{'+s+r'}$'
+    return s
+lt.axis_formatter = formatter
+
 # Helvetica font
 mpl.rcParams['font.family'] = 'sans-serif'
 mpl.rcParams['font.sans-serif'] = ['Helvetica']
 mpl.rcParams['text.latex.preamble'] = "\n".join([mpl.rcParams['text.latex.preamble'],
-                                                 r"\usepackage{helvet}",
-                                                 r"\usepackage{sansmath}",
-                                                 r"\sansmath"])
+                                                 r"\usepackage{helvet}",])
+                                                 # r"\usepackage{sansmath}",
+                                                 # r"\sansmath"])
+
+# Upright vectors
+mpl.rcParams['text.latex.preamble'] = "\n".join([mpl.rcParams['text.latex.preamble'], r'\renewcommand{\bm}[1]{\boldsymbol{\mathbf{#1}}}'])
 
 # Colours
 plt.rc('font', size=9)
 c1 = 'tab:orange'
-c2 = 'tab:red'
-c3 = 'tab:blue'
-colors = [c2, c1, c3]
+c2 = 'tab:blue'
+c3 = '#b00000'
+colors = [c1, c2, c3]
 
 
 ### Make sure this is reloaded by IPython ###

### 2022-05-17 manuscript.tex
Formatting of maths symbols

@@
 % Maths
-\usepackage{bm}
+% \usepackage{bm}
 \usepackage{amsmath}
+\newcommand{\bm}[1]{\boldsymbol{\mathbf{#1}}}
 \newcommand{\abs}[1]{\left| #1 \right|}
@@
         The transition state is shown by a red dot, and the minimum energy pathway by the dashed line.
-    (b) A snapshot of the BITSS minimisation showing the driving forces on each state due to the energy constraint, $\bm{F}_E$, and distance constraint, $\bm{F}_D$, with $E_1 < E_2$ and $\mathrm{d}(\bm{x}_1,\bm{x}_2) < d_i$.
+    (b) A snapshot of the BITSS minimisation showing the driving forces on each state due to the energy constraint, $\bm{F}_\mathrm{E}$, and distance constraint, $\bm{F}_\mathrm{D}$, with $E_1 < E_2$ and $d(\bm{x}_1,\bm{x}_2) < d_i$.
     (c) The final configuration of the BITSS method showing the two states in orange, the transition state in red, and the negative curvature eigenvector, $\bm{\hat{\tau}}$.
@@
 \begin{equation}
-  \mathrm{d}(\bm{x}_1, \bm{x}_2) = \sqrt{\sum_i (x_{1,i} - x_{2,i})^2}.
+  d(\bm{x}_1, \bm{x}_2) = \sqrt{\sum_i (x_{1,i} - x_{2,i})^2}.
 \end{equation}
@@
 \begin{multline}\label{eq:bitss}
-  E_\text{BITSS}(\bm{x}_1, \bm{x}_2) = E_1 + E_2
+  E_\mathrm{BITSS}(\bm{x}_1, \bm{x}_2) = E_1 + E_2
     + \kappa_e \left( E_1 - E_2 \right) ^2 \\
-    + \kappa_d \left( \mathrm{d}(\bm{x}_1, \bm{x}_2) - d_i \right) ^2,
+    + \kappa_d \left( d(\bm{x}_1, \bm{x}_2) - d_i \right) ^2,
 \end{multline}
@@
 \begin{gather}
-  \kappa_e = \frac {\alpha} {2 E_B},
+  \kappa_e = \frac {\alpha} {2 E_\mathrm{B}},
   \label{eq:ke}
@@
     \frac {\sqrt{\abs{\grad E_1}^2 + \abs{\grad E_2}^2}} {2\sqrt{2} \beta d_i} \; , \;
-    \frac{E_B}{\beta d_i^2} \right),
+    \frac{E_\mathrm{B}}{\beta d_i^2} \right),
   \label{eq:kd}
@@
 where $\grad E_1$ and $\grad E_2$ are the gradients of the energies of the two states, and $\alpha$ and $\beta$ are parameters with recommended values of $\alpha = 10$ and $\beta = 0.1$.
-Here, $E_B$ is an estimation for the current energy barrier, evaluated using the difference between the highest energy along a linear interpolation between the two states and the average energy of the two states.
+Here, $E_\mathrm{B}$ is an estimation for the current energy barrier, evaluated using the difference between the highest energy along a linear interpolation between the two states and the average energy of the two states.
 These constraints are initially calculated at the start of each minimisation, and regularly recalculated throughout (once per 100 iterations is used in this work).
@@
 These techniques cause issues for most existing double-ended methods because the coupled states may end up with different degrees of freedom.
-However, in BITSS the only direct coupling is in the distance measure, $\mathrm{d}(\bm{x}_1,\bm{x}_2)$, which is relatively easy to adapt.
+However, in BITSS the only direct coupling is in the distance measure, $d(\bm{x}_1,\bm{x}_2)$, which is relatively easy to adapt.
 Here we demonstrate the use of adaptive remeshing by considering two separate issues.
@@
 This has a chance of randomly jumping one state over the dividing barrier, but we can reduce this probability by limiting the initial temparature and maximum random displacement.
-We typically employ $T_0 = E_B / 10$, and $d_\text{max} = d(\bm{x}_1, \bm{x}_2) / 100$.
+We typically employ $T_0 = E_\mathrm{B} / 10$, and $d_\mathrm{max} = d(\bm{x}_1, \bm{x}_2) / 100$.
 
@@
 \begin{equation}
-  E = \sum_i k^S_i (r_i - r^0_i)^2 + \sum_j k^B_j [1 + \cos(\theta_j - \theta^0_j)].
+  E = \sum_i k^\mathrm{S}_i (r_i - r^0_i)^2 + \sum_j k^\mathrm{B}_j [1 + \cos(\theta_j - \theta^0_j)].
 \end{equation}
-The first term is the stretching energy, where $r_i$ is the length, $r^0_i$ is the equilibrium length, and $k^S_i$ is the stretching rigidity of bond $i$.
-The second term provides the bending energy, where $\theta_j$ is the dihedral angle, $\theta^0_j$ is the equilibrium angle, and $k^B_j$ is the bending rigidity of hinge $j$.
+The first term is the stretching energy, where $r_i$ is the length, $r^0_i$ is the equilibrium length, and $k^\mathrm{S}_i$ is the stretching rigidity of bond $i$.
+The second term provides the bending energy, where $\theta_j$ is the dihedral angle, $\theta^0_j$ is the equilibrium angle, and $k^\mathrm{B}_j$ is the bending rigidity of hinge $j$.
 
@@
 \begin{equation}
-  \frac{\partial E^S}{\partial \bm{x}_2} = - \frac{\partial E^S}{\partial \bm{x}_3} =
-    2 k^S (r - r^0) (\bm{x_2} - \bm{x_3}).
+  \frac{\partial E^\mathrm{S}}{\partial \bm{x}_2} = - \frac{\partial E^\mathrm{S}}{\partial \bm{x}_3} =
+    2 k^\mathrm{S} (r - r^0) (\bm{x_2} - \bm{x_3}).
 \end{equation}
@@
 \begin{align}
-  \frac{\partial E^B}{\partial \bm{x}_1} &= k^B \sin(\theta - \theta^0) \frac{\bm{\hat{n}}_a}{h_a}, \\
-  \frac{\partial E^B}{\partial \bm{x}_2} &= - k^B \sin(\theta - \theta^0) \left[\frac{\bm{\hat{n}}_a}{h_a} + \frac{\bm{\hat{n}}_a + \bm{\hat{n}}_b}{r}\right], \\
-  \frac{\partial E^B}{\partial \bm{x}_3} &= - k^B \sin(\theta - \theta^0) \left[\frac{\bm{\hat{n}}_b}{h_b} + \frac{\bm{\hat{n}}_a + \bm{\hat{n}}_b}{r}\right], \\
-  \frac{\partial E^B}{\partial \bm{x}_4} &= k^B \sin(\theta - \theta^0) \frac{\bm{\hat{n}}_b}{h_b}.
+  \frac{\partial E^\mathrm{B}}{\partial \bm{x}_1} &= k^\mathrm{B} \sin(\theta - \theta^0) \frac{\bm{\hat{n}}_a}{h_a}, \\
+  \frac{\partial E^\mathrm{B}}{\partial \bm{x}_2} &= - k^\mathrm{B} \sin(\theta - \theta^0) \left[\frac{\bm{\hat{n}}_a}{h_a} + \frac{\bm{\hat{n}}_a + \bm{\hat{n}}_b}{r}\right], \\
+  \frac{\partial E^\mathrm{B}}{\partial \bm{x}_3} &= - k^\mathrm{B} \sin(\theta - \theta^0) \left[\frac{\bm{\hat{n}}_b}{h_b} + \frac{\bm{\hat{n}}_a + \bm{\hat{n}}_b}{r}\right], \\
+  \frac{\partial E^\mathrm{B}}{\partial \bm{x}_4} &= k^\mathrm{B} \sin(\theta - \theta^0) \frac{\bm{\hat{n}}_b}{h_b}.
 \end{align}
@@
 \begin{equation} \label{eq:phasefield}
-  E[\phi] = E^B[\phi] + E^I[\phi] + E^S[\phi] + E^V[\phi].
+  E[\phi] = E^\mathrm{B}[\phi] + E^\mathrm{I}[\phi] + E^\mathrm{S}[\phi] + E^\mathrm{V}[\phi].
 \end{equation}
-The first term, $E^B$, uses a double well potential to set values of $\phi=\pm1$ in the bulk.
+The first term, $E^\mathrm{B}$, uses a double well potential to set values of $\phi=\pm1$ in the bulk.
 The second term then provides the interfacial energy between the liquid and gas by imposing an energy penalty to gradients in $\phi$.
-$E^S$ is the solid-liquid interaction energy, which sets the contact angles of the hydrophilic and hydrophobic regions to 60\si{\degree} and 110\si{\degree}, respectively.
-Finally, $E^V$ constrains the volume of the liquid drop by penalising any variation from the target volume.
+$E^\mathrm{S}$ is the solid-liquid interaction energy, which sets the contact angles of the hydrophilic and hydrophobic regions to 60\si{\degree} and 110\si{\degree}, respectively.
+Finally, $E^\mathrm{V}$ constrains the volume of the liquid drop by penalising any variation from the target volume.
 
@@
 \begin{align}
-  E^B[\phi] &= \sum_i \frac{1}{\epsilon} \left( \frac{{\phi_i}^4}{4} - \frac{{\phi_i}^2}{2} + \frac{1}{4} \right) \upDelta V,\\
-  E^I[\phi] &= \sum_i \frac{\epsilon}{2} \abs{\grad \phi_i}^2 \upDelta V,\\
-  E^S[\phi] &= \sum_j \sqrt{2}\cos\theta_j \left( \frac{{\phi_j}^3}{6} - \frac{\phi_j}{2} - \frac{1}{3} \right) \upDelta S,\\
-  E^V[\phi] &= k_V \left[ \sum_i \frac{\phi_i + 1}{2} \upDelta V - V_0 \right]^2,
+  E^\mathrm{B}[\phi] &= \sum_i \frac{1}{\epsilon} \left( \frac{{\phi_i}^4}{4} - \frac{{\phi_i}^2}{2} + \frac{1}{4} \right) \upDelta V,\\
+  E^\mathrm{I}[\phi] &= \sum_i \frac{\epsilon}{2} \abs{\grad \phi_i}^2 \upDelta V,\\
+  E^\mathrm{S}[\phi] &= \sum_j \sqrt{2}\cos\theta_j \left( \frac{{\phi_j}^3}{6} - \frac{\phi_j}{2} - \frac{1}{3} \right) \upDelta S,\\
+  E^\mathrm{V}[\phi] &= k_\mathrm{V} \left[ \sum_i \frac{\phi_i + 1}{2} \upDelta V - V_0 \right]^2,
 \end{align}
@@
 $\epsilon$ is the liquid-gas interface width (set to 2.5 lattice units), $\theta_j$ is the contact-angle with the solid surface, and $V_0$ is the constrained volume of the liquid drop.
-The strength of the volume constraint is parametrised by $k_V$ for which we use a value of $10^4$.
+The strength of the volume constraint is parametrised by $k_\mathrm{V}$ for which we use a value of $10^4$.
 The gradients of these terms are given by,
 \begin{align}
-  \frac{\partial E^B}{\partial \phi_i} &= \frac{1}{\epsilon} \left( {\phi_i}^3 - \phi_i \right) \upDelta V,\\
-  \frac{\partial E^I}{\partial \phi_i} &= \frac{\epsilon}{2} \left[
+  \frac{\partial E^\mathrm{B}}{\partial \phi_i} &= \frac{1}{\epsilon} \left( {\phi_i}^3 - \phi_i \right) \upDelta V,\\
+  \frac{\partial E^\mathrm{I}}{\partial \phi_i} &= \frac{\epsilon}{2} \left[
     \frac{\partial \abs{\grad \phi_i}^2}{\partial \phi_i} +
     \sum_k\frac{\partial \abs{\grad \phi_k}^2}{\partial \phi_i} \right] \upDelta V,\\
-  \frac{\partial E^S}{\partial \phi_j} &= \sqrt{2}\cos\theta_j \left( \frac{{\phi_j}^2}{2} - \frac{1}{2} \right) \upDelta S,\\
-  \frac{\partial E^V}{\partial \phi_i} &= k_V \left[ \sum_{i'} \frac{\phi_{i'} + 1}{2} \upDelta V - V_0 \right] \upDelta V,
+  \frac{\partial E^\mathrm{S}}{\partial \phi_j} &= \sqrt{2}\cos\theta_j \left( \frac{{\phi_j}^2}{2} - \frac{1}{2} \right) \upDelta S,\\
+  \frac{\partial E^\mathrm{V}}{\partial \phi_i} &= k_\mathrm{V} \left[ \sum_{i'} \frac{\phi_{i'} + 1}{2} \upDelta V - V_0 \right] \upDelta V,
 \end{align}

### 2022-05-17 fig/make_flatdiscontinuous/plot.py
Fixed flat pathlengh

@@ -96,7 +96,7 @@ def plot_flat(fig, hsize):
     def plot_path_energy(ax, path):
         path = np.concatenate((path[0], path[1,::-1]))
         e = energy(path[:,0], path[:,1])
-        dist = np.cumsum(np.linalg.norm(np.diff(path, axis=0, prepend=0), axis=1))
+        dist = np.cumsum(np.linalg.norm(np.diff(path, axis=0, prepend=[path[0]]), axis=1))
         dist = dist / np.max(dist)
         ax.plot(dist, e, c=cpath, lw=lw)
         ax.plot(dist[0] , e[0] , c=cmin, marker='o', ms=ms, mec=mec)

### 2022-05-17 manuscript.tex
Added summary sentences for the figures

@@
   \caption{\label{fig:toy2d}
-    (a) The trajectories of the two states under the BITSS method (orange line) for a simple 2D potential with two minima (blue dots).
-        The transition state is shown by a red dot, and the minimum energy pathway by the dashed line.
+    \textbf{Schematics of the BITSS method on a simple 2D potential with two minima.}
+    (a) The orange line shows the trajectories of the two states from the minima (blue) to the transition states (red) under the BITSS method.
+        The minimum energy pathway is shown by the dashed line.
     (b) A snapshot of the BITSS minimisation showing the driving forces on each state due to the energy constraint, $\bm{F}_\mathrm{E}$, and distance constraint, $\bm{F}_\mathrm{D}$, with $E_1 < E_2$ and $d(\bm{x}_1,\bm{x}_2) < d_i$.
@@
   \caption{\label{fig:bracketing}
-    Trajectories of the bracketing methods on a hooked potential with a single saddle point.
+    \textbf{Trajectories of the bracketing methods on a hooked potential with a single saddle point.}
     The minimum energy pathway is shown by the dashed line.
@@
   \caption{\label{fig:speedtest}
-    Comparisons between BITSS, DNEB, and the string method in the convergence to the transition state as a function of the number of calculations of the energy gradient.
+    \textbf{Comparisons between BITSS, DNEB, and the string method in the convergence to the transition state as a function of the number of calculations of the energy gradient.}
     Three test systems are used: (a) a Lennard-Jones seven-particle cluster, (b) cylindrical shell buckling, and (c) wetting of a chemically-striped surface.
@@
   \caption{\label{fig:adaptivemesh}
-    (a) Snapshots of the BITSS method applied to the buckling of a cylinder with a changing mesh.
+    \textbf{Demonstration of BITSS addressing the challenges associated with adaptive remeshing.}
+    (a) Snapshots of the BITSS method for the buckling of a cylinder with a changing mesh.
         The radial displacement relative the unbuckled cylinder is shown, as well as the underlying triangular mesh.
-    (b) BITSS applied to the striped wetting example with different resolutions for the two states.
+    (b) Snapshots for the striped wetting example with different resolutions for the two states.
         Each grid cell denotes 50x50 lattice nodes.
@@
   \caption{\label{fig:flatdiscontinuous}
+    \textbf{Demonstration of BITSS applied to flat and discontinuous potentials.}
     (a) Energy profile of the BITSS pathway on a 2D potential with flat regions.
@@
   \caption{\label{fig:BAHschematic}
-    Schematic of the bar and hinge model showing the relevent parameters for a single hinge element. $h_i$ and $\bm{\hat{n}}_i$ denote the height and unit normal of each triangle respectively.
+    \textbf{Schematic of the bar and hinge model showing the relevent parameters for a single hinge element.}
+    $h_i$ and $\bm{\hat{n}}_i$ denote the height and unit normal of each triangle respectively.
   }

### 2022-05-17 fig/make_flatdiscontinuous/plot.py
Fixed flat label and inset placement

@@ -19,7 +19,7 @@ def plot_flat(fig, hsize):
     ### Plot parameters
     ax_size = np.array([[0.15, 0.2, 0.83, 0.78],
                         [0.42, 0.25, 0.48, 0.38]])
-    axin_bounds = np.array([[0.675, 0.8], [-2,-1.45]])
+    axin_bounds = np.array([[0.57, 0.725], [-2,-1.45]])
     axin_scale = 50
 
     y0 = 0.3
@@ -121,13 +121,13 @@ def plot_flat(fig, hsize):
         axin.set_xticks([])
         axin.set_yticks([])
         axin.margins(0, 0.2)
-        axin.text(0.98, 0.95, f'$\\times{axin_scale}$',
+        axin.text(0.98, 0.95, r'$\times\text{'+str(axin_scale)+r'}$',
                   ha='right', va='top', transform=axin.transAxes)
         box, _ = ax.indicate_inset_zoom(axin, edgecolor='k')#, alpha=1)
         box.set_visible(False)
 
-        ax.text(0.54, -1.83, 'i', ha='center')
-        ax.text(0.91, -1.95, 'iii', ha='center')
+        ax.text(0.4, -1.83, 'i', ha='center')
+        ax.text(0.89, -1.95, 'iii', ha='center')
         axin.text(0.75, 0, 'ii', ha='center', va='bottom', transform=axin.transAxes)
 
     def plot_potential(ax):
@@ -138,7 +138,7 @@ def plot_flat(fig, hsize):
         ax.axvline(cut2, ls=':', c='k')
         ax.axvline(cut2+w, ls=':', c='k')
         ax.text(0.35, 0.29, 'i', ha='center', va='center', transform=ax.transAxes)
-        ax.text(0.62, 0.55, 'ii', ha='center', va='center', transform=ax.transAxes)
+        ax.text(0.61, 0.55, 'ii', ha='center', va='center', transform=ax.transAxes)
         ax.text(0.78, 0.22, 'iii', ha='center', va='center', transform=ax.transAxes)
 
     def plot_path(ax, path):

### 2022-05-17 manuscript.tex
CommPhys appendicies

@@
 % Text
-\usepackage{siunitx}
+\usepackage[group-separator={,}]{siunitx}
 \usepackage{enumitem}
@@
 This is a frequently used test system for studying transition rates \cite{Wales2002,Passerone2001}.
-Here, the \num{14} degrees of freedom are the particle coordinates.
+Here, the 14 degrees of freedom are the particle coordinates.
 The characteristic transition shown in \cref{fig:speedtest}a sees a particle rearrangement between two close-packed clusters.
@@
 
-\section{Methods}
+\appendix
+\section*{Methods}
 
@@
 
-\appendix
-\section*{}
-\begin{acknowledgments}
-  S.~J.~A. is supported by a studentship from the Engineering and Physical Sciences Research Council [Grant No. EP/R513039/1].
-  H.~K. and J.~R.~P. acknowledge funding from the Engineering and Physical Sciences Research Council [Grant No. EP/V034154/1].
-\end{acknowledgments}
+\section*{Data availability}
+The data that support the findings of this study are available from the corresponding author upon reasonable request.
+
+\section*{Code availability}
+The code used in this study is available from the corresponding author upon reasonable request.
 
@@
 
+\begin{acknowledgments}
+  S.~J.~A. is supported by a studentship from the Engineering and Physical Sciences Research Council [Grant No. EP/R513039/1].
+  H.~K. and J.~R.~P. acknowledge funding from the Engineering and Physical Sciences Research Council [Grant No. EP/V034154/1].
+\end{acknowledgments}
+
+\section*{Author contributions}
+S.~J.~A. and J.~R.~P. developed the theoretical model.
+S.~J.~A. performed the experiments and analysed the data.
+H.~K. supervised the study.
+S.~J.~A. wrote the paper, with review and input from H.~K. and J.~R.~P.
+
+\section*{Competing interests}
+The authors declare no competing interests.
+
 \end{document}

### 2022-05-17 manuscript.tex
SI upright subscripts and Supplementary Note labels

@@
 This prevents the constraints from dominating the underlying potential or causing large jumps that make a state pass over the ridge.
-This results in the following equations (see the supplementary information for the derivation),
+This results in the following equations (see Supplementary Note I for the derivation),
 \begin{gather}
@@
 This enables the identification of the overall energy barrier, providing estimates about the overall ease of the transition, or the rate for chemical processes.
-However, as demonstrated in the supplementary information, if multiple transition states have very similar energies then a smaller distance reduction factor, $f$, may be necessary to ensure that it does indeed converge to the highest transition state.
+However, as demonstrated in Supplementary Note II, if multiple transition states have very similar energies then a smaller distance reduction factor, $f$, may be necessary to ensure that it does indeed converge to the highest transition state.
 Furthermore, if all of transition states or the full pathway are desired, BITSS can be continually repeated from one of the minima downhill from the located transition state and one of the initial minima until the initial minima are piecewise connected by a full pathway.

### 2022-05-17 si/supplementary_information.tex
SI upright subscripts and Supplementary Note labels

@@
 % \usepackage{amssymb}
+\def\thesection{SUPPLEMENTARY NOTE \Roman{section}}
 
@@
 \begin{equation} \label{eq:gradBITSS}
-  \grad E_\text{BITSS} = \sum_{\substack{i=1,2 \\ j\neq i}} \left[ 1 + 2 \kappa_e (E_i - E_j) \right] \grad E_i + 2 \kappa_d (d - d_i) \grad d.
+  \grad E_\text{BITSS} = \sum_{\substack{i=1,2 \\ j\neq i}} \left[ 1 + 2 \kappa_\text{e} (E_i - E_j) \right] \grad E_i + 2 \kappa_\text{d} (d - d_i) \grad d.
 \end{equation}
-To obtain the expression for the energy coefficient, $\kappa_e$, we first assume that the separation is fixed, so the distance term can be ignored.
-The coefficient $\kappa_e$ must be high enough to prevent one state from being pulled over the ridge, for which the greatest risk occurs when the gradient on one state is much greater than the other, e.g.
+To obtain the expression for the energy coefficient, $\kappa_\text{e}$, we first assume that the separation is fixed, so the distance term can be ignored.
+The coefficient $\kappa_\text{e}$ must be high enough to prevent one state from being pulled over the ridge, for which the greatest risk occurs when the gradient on one state is much greater than the other, e.g.
 $\abs{\grad E_2} \gg \abs{\grad E_1}$.
@@
 \begin{equation}
-  \grad E_\text{BITSS} = \left[ 1 - 2 \kappa_e (E_1 - E_2) \right] \grad E_2.
+  \grad E_\text{BITSS} = \left[ 1 - 2 \kappa_\text{e} (E_1 - E_2) \right] \grad E_2.
 \end{equation}
-Therefore, when not at a transition state or a minimum in the landscape ($\abs{\grad E_2} \neq 0$) convergence will occur when the term in the square brackets is zero, resulting in $E_1 - E_2 = 1 / 2 \kappa_e$.
-This energy difference should be less than current energy barrier, so we can substitute it with $E_B / \alpha$, where $E_B$ is the energy barrier estimate described in the main paper and $\alpha$ is a constant greater than one.
+Therefore, when not at a transition state or a minimum in the landscape ($\abs{\grad E_2} \neq 0$) convergence will occur when the term in the square brackets is zero, resulting in $E_1 - E_2 = 1 / 2 \kappa_\text{e}$.
+This energy difference should be less than current energy barrier, so we can substitute it with $E_\text{B} / \alpha$, where $E_\text{B}$ is the energy barrier estimate described in the main paper and $\alpha$ is a constant greater than one.
 This leaves us with the expression,
 \begin{equation}
-  \kappa_e = \frac {\alpha} {2 E_B}.
+  \kappa_\text{e} = \frac {\alpha} {2 E_\text{B}}.
 \end{equation}
@@
 The distance coefficient is determined by assuming that the energies are equal and thus the energy constraint can be ignored.
-In this case, convergence will occur when $\grad E_1 + \grad E_2 = -2 \kappa_d (d - d_i) \grad d$.
-It is then possible to find the value of $\kappa_d$ for which the magnitude of each side of this equation is equal for a desired relative error in the distance, $\beta = (d - d_i) / d_i$,
+In this case, convergence will occur when $\grad E_1 + \grad E_2 = -2 \kappa_\text{d} (d - d_i) \grad d$.
+It is then possible to find the value of $\kappa_\text{d}$ for which the magnitude of each side of this equation is equal for a desired relative error in the distance, $\beta = (d - d_i) / d_i$,
 \begin{equation}
-  \kappa_d = \frac {\sqrt{\abs{\grad E_1}^2 + \abs{\grad E_2}^2}} {2 \sqrt{2} \beta d_i}.
+  \kappa_\text{d} = \frac {\sqrt{\abs{\grad E_1}^2 + \abs{\grad E_2}^2}} {2 \sqrt{2} \beta d_i}.
 \end{equation}
 (Note: The gradient of the distance with respect to a single state has a magnitude of 1, thus the magnitude of the gradient for the pair of states is $\abs{\grad d} = \sqrt{1^2+1^2} = \sqrt{2}$.)
-To ensure that the coefficient is not too small if the gradient is close to zero, such as when the states are initialised at the minima, a lower bound is set by replacing $\abs{\grad E_1}$ and $\abs{\grad E_2}$ with $2 E_B / d_i$.
+To ensure that the coefficient is not too small if the gradient is close to zero, such as when the states are initialised at the minima, a lower bound is set by replacing $\abs{\grad E_1}$ and $\abs{\grad E_2}$ with $2 E_\text{B} / d_i$.
 This gives the expression,
 \begin{equation}
-  \kappa_d = \mathrm{max} \! \left(
+  \kappa_\text{d} = \mathrm{max} \! \left(
   \frac {\sqrt{\abs{\grad E_1}^2 + \abs{\grad E_2}^2}} {2 \sqrt{2} \beta d_i}, \quad
-  \frac{E_B}{\beta d_i^2} \right).
+  \frac{E_\text{B}}{\beta d_i^2} \right).
 \end{equation}
@@
 For this we use a 2D potential, shown in \cref{fig:multits}a, with a pathway that follows a chicane of two $135^\circ$ circular arcs.
-The energy is given by the squared distance from this path, plus two barriers resulting in transition states A and B, with energies $E_A$ and $E_B$.
-We then vary $E_B$ between 0 and $E_A$, and the size of the distance reduction factor, $f$, to see if BITSS successfully converges to the higher transition state A.
+The energy is given by the squared distance from this path, plus two barriers resulting in transition states A and B, with energies $E_\text{A}$ and $E_\text{B}$.
+We then vary $E_\text{B}$ between 0 and $E_\text{A}$, and the size of the distance reduction factor, $f$, to see if BITSS successfully converges to the higher transition state A.
 For each pair of parameters we perform 5 runs with slight variations in the starting positions, with the results in \cref{fig:multits}b showing the points at which all 5 converge to A.
@@
     M1 and M2 denote the two starting minima, and A and B are the two transition states.
-    The energy of the barrier to B, $E_B$, is varied between 0 and $E_A$.
+    The energy of the barrier to B, $E_\text{B}$, is varied between 0 and $E_\text{A}$.
     (b) The results for the parameters under which BITSS reliably converges to A, and the points at which it sometimes converges to B.

### 2022-05-18 manuscript.tex
Updated citation information

@@
 
-In each iteration of the string method, each image is evolved downhill for a number of LBFGS iterations before redistributing the images along a cubic-spline interpolated path.
+In each iteration of the string method, each image is evolved downhill for a number of L-BFGS iterations before redistributing the images along a cubic-spline interpolated path.
 This number of iterations is varied to obtain the fastest convergence, for which we find 2, 50, and 20 to be optimal for the particle cluster, cylidrical buckling, and striped wetting examples, respectively.
@@
 \newblock \emph{\bibinfo{journal}{Philosophical Transactions of the Royal
-  Society A: Mathematical, Physical and Engineering Sciences}}
-  \textbf{\bibinfo{volume}{370}}, \bibinfo{pages}{2877--2899}
+  Society A}} \textbf{\bibinfo{volume}{370}}, \bibinfo{pages}{2877--2899}
   (\bibinfo{year}{2012}).
@@
 \newblock \emph{\bibinfo{journal}{Proceedings of the National Academy of
-  Sciences}} \textbf{\bibinfo{volume}{117}}, \bibinfo{pages}{14987--14995}
-  (\bibinfo{year}{2020}).
+  Sciences of the United States of America}} \textbf{\bibinfo{volume}{117}},
+  \bibinfo{pages}{14987--14995} (\bibinfo{year}{2020}).
 
@@
   Structures, Materials, and Functionalities}}.
-\newblock \emph{\bibinfo{journal}{Advanced Materials}}  (\bibinfo{year}{2022}).
+\newblock \emph{\bibinfo{journal}{Advanced Materials}}
+  \textbf{\bibinfo{volume}{34}}, \bibinfo{pages}{2110384}
+  (\bibinfo{year}{2022}).
 
@@
 
+\bibitem{Dewar1984}
+\bibinfo{author}{Dewar, M. J.~S.}, \bibinfo{author}{Healy, E.~F.} \&
+  \bibinfo{author}{Stewart, J. J.~P.}
+\newblock \bibinfo{title}{{Location of transition states in reaction
+  mechanisms}}.
+\newblock \emph{\bibinfo{journal}{Journal of the Chemical Society, Faraday
+  Transactions 2}} \textbf{\bibinfo{volume}{80}}, \bibinfo{pages}{227}
+  (\bibinfo{year}{1984}).
+
+\bibitem{Ionova1993}
+\bibinfo{author}{Ionova, I.~V.} \& \bibinfo{author}{Carter, E.~A.}
+\newblock \bibinfo{title}{{Ridge method for finding saddle points on potential
+  energy surfaces}}.
+\newblock \emph{\bibinfo{journal}{The Journal of Chemical Physics}}
+  \textbf{\bibinfo{volume}{98}}, \bibinfo{pages}{6377--6386}
+  (\bibinfo{year}{1993}).
+
+\bibitem{Miron2001}
+\bibinfo{author}{Miron, R.~A.} \& \bibinfo{author}{Fichthorn, K.~A.}
+\newblock \bibinfo{title}{{The Step and Slide method for finding saddle points
+  on multidimensional potential surfaces}}.
+\newblock \emph{\bibinfo{journal}{The Journal of Chemical Physics}}
+  \textbf{\bibinfo{volume}{115}}, \bibinfo{pages}{8742--8747}
+  (\bibinfo{year}{2001}).
+
+\bibitem{Zhang2013}
+\bibinfo{author}{Zhang, X.-J.}, \bibinfo{author}{Shang, C.} \&
+  \bibinfo{author}{Liu, Z.-P.}
+\newblock \bibinfo{title}{{Double-Ended Surface Walking Method for Pathway
+  Building and Transition State Location of Complex Reactions}}.
+\newblock \emph{\bibinfo{journal}{Journal of Chemical Theory and Computation}}
+  \textbf{\bibinfo{volume}{9}}, \bibinfo{pages}{5745--5753}
+  (\bibinfo{year}{2013}).
+
 \bibitem{Trefethen2013}
@@
 \newblock \bibinfo{title}{{The future of computing beyond Moore's Law}}.
-\newblock \emph{\bibinfo{journal}{Philosophical Transactions Royal Society}}
-  \textbf{\bibinfo{volume}{378}}, \bibinfo{pages}{20190061}
+\newblock \emph{\bibinfo{journal}{Philosophical Transactions of the Royal
+  Society A}} \textbf{\bibinfo{volume}{378}}, \bibinfo{pages}{20190061}
   (\bibinfo{year}{2020}).
@@
   (\bibinfo{year}{1989}).
-
-\bibitem{Miron2001}
-\bibinfo{author}{Miron, R.~A.} \& \bibinfo{author}{Fichthorn, K.~A.}
-\newblock \bibinfo{title}{{The Step and Slide method for finding saddle points
-  on multidimensional potential surfaces}}.
-\newblock \emph{\bibinfo{journal}{The Journal of Chemical Physics}}
-  \textbf{\bibinfo{volume}{115}}, \bibinfo{pages}{8742--8747}
-  (\bibinfo{year}{2001}).
-
-\bibitem{Dewar1984}
-\bibinfo{author}{Dewar, M. J.~S.}, \bibinfo{author}{Healy, E.~F.} \&
-  \bibinfo{author}{Stewart, J. J.~P.}
-\newblock \bibinfo{title}{{Location of transition states in reaction
-  mechanisms}}.
-\newblock \emph{\bibinfo{journal}{Journal of the Chemical Society, Faraday
-  Transactions 2}} \textbf{\bibinfo{volume}{80}}, \bibinfo{pages}{227}
-  (\bibinfo{year}{1984}).
-
-\bibitem{Ionova1993}
-\bibinfo{author}{Ionova, I.~V.} \& \bibinfo{author}{Carter, E.~A.}
-\newblock \bibinfo{title}{{Ridge method for finding saddle points on potential
-  energy surfaces}}.
-\newblock \emph{\bibinfo{journal}{The Journal of Chemical Physics}}
-  \textbf{\bibinfo{volume}{98}}, \bibinfo{pages}{6377--6386}
-  (\bibinfo{year}{1993}).
-
-\bibitem{Zhang2013}
-\bibinfo{author}{Zhang, X.-J.}, \bibinfo{author}{Shang, C.} \&
-  \bibinfo{author}{Liu, Z.-P.}
-\newblock \bibinfo{title}{{Double-Ended Surface Walking Method for Pathway
-  Building and Transition State Location of Complex Reactions}}.
-\newblock \emph{\bibinfo{journal}{Journal of Chemical Theory and Computation}}
-  \textbf{\bibinfo{volume}{9}}, \bibinfo{pages}{5745--5753}
-  (\bibinfo{year}{2013}).
 

### 2022-06-03 manuscript.tex
Typos and reword contributions.

@@
   It uses just two states that converge to the transition state, resulting in a fast, flexible, and memory-efficient method.
-  We demonstate its versatility by applying BITSS to three very different classes of problems: Lennard-Jones clusters, shell buckling, and multiphase phase-field models.
+  We demonstrate its versatility by applying BITSS to three very different classes of problems: Lennard-Jones clusters, shell buckling, and multiphase phase-field models.
 \end{abstract}
@@
 In each iteration of the string method, each image is evolved downhill for a number of L-BFGS iterations before redistributing the images along a cubic-spline interpolated path.
-This number of iterations is varied to obtain the fastest convergence, for which we find 2, 50, and 20 to be optimal for the particle cluster, cylidrical buckling, and striped wetting examples, respectively.
+This number of iterations is varied to obtain the fastest convergence, for which we find 2, 50, and 20 to be optimal for the particle cluster, cylindrical buckling, and striped wetting examples, respectively.
 
@@
 We must instead use a minimiser that does not require a differentiable optimisation function, for which we use simulated annealing \cite{Kirkpatrick1983}.
-This has a chance of randomly jumping one state over the dividing barrier, but we can reduce this probability by limiting the initial temparature and maximum random displacement.
+This has a chance of randomly jumping one state over the dividing barrier, but we can reduce this probability by limiting the initial temperature and maximum random displacement.
 We typically employ $T_0 = E_\mathrm{B} / 10$, and $d_\mathrm{max} = d(\bm{x}_1, \bm{x}_2) / 100$.
@@
   \caption{\label{fig:BAHschematic}
-    \textbf{Schematic of the bar and hinge model showing the relevent parameters for a single hinge element.}
+    \textbf{Schematic of the bar and hinge model showing the relevant parameters for a single hinge element.}
     $h_i$ and $\bm{\hat{n}}_i$ denote the height and unit normal of each triangle respectively.
@@
 \section*{Author contributions}
-S.~J.~A. and J.~R.~P. developed the theoretical model.
-S.~J.~A. performed the experiments and analysed the data.
-H.~K. supervised the study.
-S.~J.~A. wrote the paper, with review and input from H.~K. and J.~R.~P.
+S.~J.~A., J.~R.~P., and H.~K conceived and planned the project.
+S.~J.~A. performed the numerical experiments and analysed the data.
+J.~R.~P. and H.~K. supervised the study.
+S.~J.~A. wrote the paper, with review and input from and J.~R.~P. and H.~K.
 

### 2022-06-04 manuscript.tex
JCP formatting

@@
-\documentclass[twocolumn,10pt]{revtex4}
+\documentclass[aip,jcp,reprint,twocolumn]{revtex4-1}
 
 % Maths
-% \usepackage{bm}
+\usepackage{bm}
 \usepackage{amsmath}
-\newcommand{\bm}[1]{\boldsymbol{\mathbf{#1}}}
 \newcommand{\abs}[1]{\left| #1 \right|}
@@
 % Text
+\usepackage[utf8]{inputenc}
+\usepackage[T1]{fontenc}
 \usepackage[group-separator={,}]{siunitx}
@@
 
+% \usepackage[mathlines]{lineno}
+% \linenumbers\relax
+
 \begin{document}
 \title{A fast and memory-efficient transition state search method for complex energy landscapes}
+
 \author{Samuel J. Avis}
@@
 \affiliation{Department of Physics, Durham University, South Road, Durham DH1 3LE, UK}
+
+\date{\today}
 
@@
 
-\section{Results and discussion}
-\subsection{BITSS method}
+\section{BITSS method}
 \begin{figure}[tb]
@@
   \caption{\label{fig:toy2d}
-    \textbf{Schematics of the BITSS method on a simple 2D potential with two minima.}
+    Schematics of the BITSS method on a simple 2D potential with two minima.
     (a) The orange line shows the trajectories of the two states from the minima (blue) to the transition states (red) under the BITSS method.
@@
 
-\subsection{Other bracketing methods}
+\subsection{Changes for undefined gradients}
+A couple of alterations to the method must be made to account for situations where the gradients are unknown.
+First, the calculation of $\kappa_d$ in \cref{eq:kd} must be adapted to avoid the use of gradients.
+This can be done by simply removing the first term and just using the second term in the equation.
+Secondly, L-BFGS can no longer be used because it requires knowledge of the gradients.
+We must instead use a minimiser that does not require a differentiable optimisation function, for which we use simulated annealing \cite{Kirkpatrick1983}.
+This has a chance of randomly jumping one state over the dividing barrier, but we can reduce this probability by limiting the initial temperature and maximum random displacement.
+We typically employ $T_0 = E_\mathrm{B} / 10$, and $d_\mathrm{max} = d(\bm{x}_1, \bm{x}_2) / 100$.
+
+\section{Results and Discussion}
+\subsection{Comparison with other bracketing methods}
 \begin{figure}[htb]
@@
   \caption{\label{fig:bracketing}
-    \textbf{Trajectories of the bracketing methods on a hooked potential with a single saddle point.}
+    Trajectories of the bracketing methods on a hooked potential with a single saddle point.
     The minimum energy pathway is shown by the dashed line.
@@
 
-\subsection{Speed Comparison}
+\subsection{Speed comparison}
 \begin{figure*}[tb]
@@
   \caption{\label{fig:speedtest}
-    \textbf{Comparisons between BITSS, DNEB, and the string method in the convergence to the transition state as a function of the number of calculations of the energy gradient.}
+    Comparisons between BITSS, DNEB, and the string method in the convergence to the transition state as a function of the number of calculations of the energy gradient.
     Three test systems are used: (a) a Lennard-Jones seven-particle cluster, (b) cylindrical shell buckling, and (c) wetting of a chemically-striped surface.
@@
 As a result of the BITSS method using only two states, it has the potential to be significantly faster.
-This is tested here by measuring the speed of convergence to the transition state for BITSS in comparison with the string method and DNEB for three diverse systems, exhibiting a broad range of energy landscapes.
+This is tested here by measuring the speed of convergence to the transition state for BITSS in comparison with the string method \cite{E2007} and DNEB \cite{Trygubenko2004} for three diverse systems, exhibiting a broad range of energy landscapes.
 Details of each are presented in the methods section.
@@
   \caption{\label{fig:adaptivemesh}
-    \textbf{Demonstration of BITSS addressing the challenges associated with adaptive remeshing.}
+    Demonstration of BITSS addressing the challenges associated with adaptive remeshing.
     (a) Snapshots of the BITSS method for the buckling of a cylinder with a changing mesh.
@@
   \caption{\label{fig:flatdiscontinuous}
-    \textbf{Demonstration of BITSS applied to flat and discontinuous potentials.}
+    Demonstration of BITSS applied to flat and discontinuous potentials.
     (a) Energy profile of the BITSS pathway on a 2D potential with flat regions.
@@
 
-\subsection{BITSS: Changes for undefined gradients}
-A couple of alterations to the method must be made to account for situations where the gradients are unknown.
-First, the calculation of $\kappa_d$ in \cref{eq:kd} must be adapted to avoid the use of gradients.
-This can be done by simply removing the first term and just using the second term in the equation.
-Secondly, L-BFGS can no longer be used because it requires knowledge of the gradients.
-We must instead use a minimiser that does not require a differentiable optimisation function, for which we use simulated annealing \cite{Kirkpatrick1983}.
-This has a chance of randomly jumping one state over the dividing barrier, but we can reduce this probability by limiting the initial temperature and maximum random displacement.
-We typically employ $T_0 = E_\mathrm{B} / 10$, and $d_\mathrm{max} = d(\bm{x}_1, \bm{x}_2) / 100$.
-
 \subsection{Adaptive discretisation test details}
@@
   \caption{\label{fig:BAHschematic}
-    \textbf{Schematic of the bar and hinge model showing the relevant parameters for a single hinge element.}
+    Schematic of the bar and hinge model showing the relevant parameters for a single hinge element.
     $h_i$ and $\bm{\hat{n}}_i$ denote the height and unit normal of each triangle respectively.
@@
 
-\section*{Data availability}
-The data that support the findings of this study are available from the corresponding author upon reasonable request.
-
-\section*{Code availability}
-The code used in this study is available from the corresponding author upon reasonable request.
-
-%% start bib
-% % \bibliography{../../library.bib}
-% \bibliography{bibexport.bib}
-% \bibliographystyle{naturemag}
-%% mid bib
-\begin{thebibliography}{10}
-\expandafter\ifx\csname url\endcsname\relax
-  \def\url#1{\texttt{#1}}\fi
-\expandafter\ifx\csname urlprefix\endcsname\relax\def\urlprefix{URL }\fi
-\providecommand{\bibinfo}[2]{#2}
-\providecommand{\eprint}[2][]{\url{#2}}
-
-\bibitem{Bryngelson1995}
-\bibinfo{author}{Bryngelson, J.~D.}, \bibinfo{author}{Onuchic, J.~N.},
-  \bibinfo{author}{Socci, N.~D.} \& \bibinfo{author}{Wolynes, P.~G.}
-\newblock \bibinfo{title}{{Funnels, pathways, and the energy landscape of
-  protein folding: A synthesis}}.
-\newblock \emph{\bibinfo{journal}{Proteins: Structure, Function, and
-  Bioinformatics}} \textbf{\bibinfo{volume}{21}}, \bibinfo{pages}{167--195}
-  (\bibinfo{year}{1995}).
-
-\bibitem{Onuchic1997}
-\bibinfo{author}{Onuchic, J.~N.}, \bibinfo{author}{Luthey-Schulten, Z.} \&
-  \bibinfo{author}{Wolynes, P.~G.}
-\newblock \bibinfo{title}{{Theory of Protein Folding: The Energy Landscape
-  Perspective}}.
-\newblock \emph{\bibinfo{journal}{Annual Review of Physical Chemistry}}
-  \textbf{\bibinfo{volume}{48}}, \bibinfo{pages}{545--600}
-  (\bibinfo{year}{1997}).
-
-\bibitem{Boehr2006}
-\bibinfo{author}{Boehr, D.~D.}, \bibinfo{author}{McElheny, D.},
-  \bibinfo{author}{Dyson, H.~J.} \& \bibinfo{author}{Wrightt, P.~E.}
-\newblock \bibinfo{title}{{The dynamic energy landscape of dihydrofolate
-  reductase catalysis}}.
-\newblock \emph{\bibinfo{journal}{Science}} \textbf{\bibinfo{volume}{313}},
-  \bibinfo{pages}{1638--1642} (\bibinfo{year}{2006}).
-
-\bibitem{Kerns2015}
-\bibinfo{author}{Kerns, S.~J.} \emph{et~al.}
-\newblock \bibinfo{title}{{The energy landscape of adenylate kinase during
-  catalysis}}.
-\newblock \emph{\bibinfo{journal}{Nature Structural and Molecular Biology}}
-  \textbf{\bibinfo{volume}{22}}, \bibinfo{pages}{124--131}
-  (\bibinfo{year}{2015}).
-
-\bibitem{Guo2018a}
-\bibinfo{author}{Guo, C.}, \bibinfo{author}{Wang, Z.}, \bibinfo{author}{Wang,
-  D.}, \bibinfo{author}{Wang, H.~F.} \& \bibinfo{author}{Hu, P.}
-\newblock \bibinfo{title}{{First-Principles Determination of CO Adsorption and
-  Desorption on Pt(111) in the Free Energy Landscape}}.
-\newblock \emph{\bibinfo{journal}{Journal of Physical Chemistry C}}
-  \textbf{\bibinfo{volume}{122}}, \bibinfo{pages}{21478--21483}
-  (\bibinfo{year}{2018}).
-
-\bibitem{Richardson2016}
-\bibinfo{author}{Richardson, J.~O.} \emph{et~al.}
-\newblock \bibinfo{title}{{Concerted hydrogen-bond breaking by quantum
-  tunneling in the water hexamer prism}}.
-\newblock \emph{\bibinfo{journal}{Science}} \textbf{\bibinfo{volume}{351}},
-  \bibinfo{pages}{1310} (\bibinfo{year}{2016}).
-
-\bibitem{Vaillant2019}
-\bibinfo{author}{Vaillant, C.~L.}, \bibinfo{author}{Althorpe, S.~C.} \&
-  \bibinfo{author}{Wales, D.~J.}
-\newblock \bibinfo{title}{{Path Integral Energy Landscapes for Water
-  Clusters}}.
-\newblock \emph{\bibinfo{journal}{Journal of Chemical Theory and Computation}}
-  \textbf{\bibinfo{volume}{15}}, \bibinfo{pages}{33--42}
-  (\bibinfo{year}{2019}).
-
-\bibitem{Richard2018}
-\bibinfo{author}{Richard, D.} \& \bibinfo{author}{Speck, T.}
-\newblock \bibinfo{title}{{Crystallization of hard spheres revisited. I.
-  Extracting kinetics and free energy landscape from forward flux sampling}}.
-\newblock \emph{\bibinfo{journal}{The Journal of Chemical Physics}}
-  \textbf{\bibinfo{volume}{148}}, \bibinfo{pages}{124110}
-  (\bibinfo{year}{2018}).
-
-\bibitem{Wales1998}
-\bibinfo{author}{Wales, D.~J.}, \bibinfo{author}{Miller, M.~A.} \&
-  \bibinfo{author}{Walsh, T.~R.}
-\newblock \bibinfo{title}{{Archetypal energy landscapes}}.
-\newblock \emph{\bibinfo{journal}{Nature}} \textbf{\bibinfo{volume}{394}},
-  \bibinfo{pages}{758--760} (\bibinfo{year}{1998}).
-
-\bibitem{Wales2012}
-\bibinfo{author}{Wales, D.~J.}
-\newblock \bibinfo{title}{{Decoding the energy landscape: Extracting structure,
-  dynamics and thermodynamics}}.
-\newblock \emph{\bibinfo{journal}{Philosophical Transactions of the Royal
-  Society A}} \textbf{\bibinfo{volume}{370}}, \bibinfo{pages}{2877--2899}
-  (\bibinfo{year}{2012}).
-
-\bibitem{Panter2019}
-\bibinfo{author}{Panter, J.~R.}, \bibinfo{author}{Chen, J.},
-  \bibinfo{author}{Zhang, T.} \& \bibinfo{author}{Kusumaatmaja, H.}
-\newblock \bibinfo{title}{{Harnessing energy landscape exploration to control
-  the buckling of cylindrical shells}}.
-\newblock \emph{\bibinfo{journal}{Communications Physics}}
-  \textbf{\bibinfo{volume}{2}}, \bibinfo{pages}{151} (\bibinfo{year}{2019}).
-
-\bibitem{Hutchinson2018}
-\bibinfo{author}{Hutchinson, J.~W.} \& \bibinfo{author}{Thompson, J. M.~T.}
-\newblock \bibinfo{title}{{Imperfections and energy barriers in shell
-  buckling}}.
-\newblock \emph{\bibinfo{journal}{International Journal of Solids and
-  Structures}} \textbf{\bibinfo{volume}{148-149}}, \bibinfo{pages}{157--168}
-  (\bibinfo{year}{2018}).
-
-\bibitem{Zhang2014}
-\bibinfo{author}{Zhang, Y.} \& \bibinfo{author}{Ren, W.}
-\newblock \bibinfo{title}{{Numerical study of the effects of surface topography
-  and chemistry on the wetting transition using the string method}}.
-\newblock \emph{\bibinfo{journal}{The Journal of Chemical Physics}}
-  \textbf{\bibinfo{volume}{141}}, \bibinfo{pages}{244705}
-  (\bibinfo{year}{2014}).
-
-\bibitem{Panter2019b}
-\bibinfo{author}{Panter, J.~R.}, \bibinfo{author}{Gizaw, Y.} \&
-  \bibinfo{author}{Kusumaatmaja, H.}
-\newblock \bibinfo{title}{{Multifaceted design optimization for superomniphobic
-  surfaces}}.
-\newblock \emph{\bibinfo{journal}{Science Advances}}
-  \textbf{\bibinfo{volume}{5}}, \bibinfo{pages}{eaav7328}
-  (\bibinfo{year}{2019}).
-
-\bibitem{Amabili2017}
-\bibinfo{author}{Amabili, M.}, \bibinfo{author}{Giacomello, A.},
-  \bibinfo{author}{Meloni, S.} \& \bibinfo{author}{Casciola, C.~M.}
-\newblock \bibinfo{title}{{Collapse of superhydrophobicity on nanopillared
-  surfaces}}.
-\newblock \emph{\bibinfo{journal}{Physical Review Fluids}}
-  \textbf{\bibinfo{volume}{2}}, \bibinfo{pages}{034202} (\bibinfo{year}{2017}).
-
-\bibitem{Othayoth2020}
-\bibinfo{author}{Othayoth, R.}, \bibinfo{author}{Thoms, G.} \&
-  \bibinfo{author}{Li, C.}
-\newblock \bibinfo{title}{{An energy landscape approach to locomotor
-  transitions in complex 3D terrain}}.
-\newblock \emph{\bibinfo{journal}{Proceedings of the National Academy of
-  Sciences of the United States of America}} \textbf{\bibinfo{volume}{117}},
-  \bibinfo{pages}{14987--14995} (\bibinfo{year}{2020}).
-
-\bibitem{Filipov2015}
-\bibinfo{author}{Filipov, E.~T.}, \bibinfo{author}{Tachi, T.},
-  \bibinfo{author}{Paulino, G.~H.} \& \bibinfo{author}{Weitz, D.~A.}
-\newblock \bibinfo{title}{{Origami tubes assembled into stiff, yet
-  reconfigurable structures and metamaterials}}.
-\newblock \emph{\bibinfo{journal}{Proceedings of the National Academy of
-  Sciences of the United States of America}} \textbf{\bibinfo{volume}{112}},
-  \bibinfo{pages}{12321} (\bibinfo{year}{2015}).
-
-\bibitem{Zhai2018}
-\bibinfo{author}{Zhai, Z.}, \bibinfo{author}{Wang, Y.} \&
-  \bibinfo{author}{Jiang, H.}
-\newblock \bibinfo{title}{{Origami-inspired, on-demand deployable and
-  collapsible mechanical metamaterials with tunable stiffness}}.
-\newblock \emph{\bibinfo{journal}{Proceedings of the National Academy of
-  Sciences of the United States of America}} \textbf{\bibinfo{volume}{115}},
-  \bibinfo{pages}{2032--2037} (\bibinfo{year}{2018}).
-
-\bibitem{Bertoldi2017}
-\bibinfo{author}{Bertoldi, K.}, \bibinfo{author}{Vitelli, V.},
-  \bibinfo{author}{Christensen, J.} \& \bibinfo{author}{{Van Hecke}, M.}
-\newblock \bibinfo{title}{{Flexible mechanical metamaterials}}.
-\newblock \emph{\bibinfo{journal}{Nature Reviews Materials}}
-  \textbf{\bibinfo{volume}{2}}, \bibinfo{pages}{17066} (\bibinfo{year}{2017}).
-
-\bibitem{Truby2016}
-\bibinfo{author}{Truby, R.~L.} \& \bibinfo{author}{Lewis, J.~A.}
-\newblock \bibinfo{title}{{Printing soft matter in three dimensions}}.
-\newblock \emph{\bibinfo{journal}{Nature}} \textbf{\bibinfo{volume}{540}},
-  \bibinfo{pages}{371--378} (\bibinfo{year}{2016}).
-
-\bibitem{Chi2022}
-\bibinfo{author}{Chi, Y.} \emph{et~al.}
-\newblock \bibinfo{title}{{Bistable and Multistable Actuators for Soft Robots:
-  Structures, Materials, and Functionalities}}.
-\newblock \emph{\bibinfo{journal}{Advanced Materials}}
-  \textbf{\bibinfo{volume}{34}}, \bibinfo{pages}{2110384}
-  (\bibinfo{year}{2022}).
-
-\bibitem{Bonfanti2020}
-\bibinfo{author}{Bonfanti, S.}, \bibinfo{author}{Guerra, R.},
-  \bibinfo{author}{Font-Clos, F.}, \bibinfo{author}{Rayneau-Kirkhope, D.} \&
-  \bibinfo{author}{Zapperi, S.}
-\newblock \bibinfo{title}{{Automatic design of mechanical metamaterial
-  actuators}}.
-\newblock \emph{\bibinfo{journal}{Nature Communications}}
-  \textbf{\bibinfo{volume}{11}}, \bibinfo{pages}{4162} (\bibinfo{year}{2020}).
-
-\bibitem{Shan2015}
-\bibinfo{author}{Shan, S.} \emph{et~al.}
-\newblock \bibinfo{title}{{Multistable Architected Materials for Trapping
-  Elastic Strain Energy}}.
-\newblock \emph{\bibinfo{journal}{Advanced Materials}}
-  \textbf{\bibinfo{volume}{27}}, \bibinfo{pages}{4296--4301}
-  (\bibinfo{year}{2015}).
-
-\bibitem{Giri2021}
-\bibinfo{author}{Giri, T.~R.} \& \bibinfo{author}{Mailen, R.}
-\newblock \bibinfo{title}{{Controlled snapping sequence and energy absorption
-  in multistable mechanical metamaterial cylinders}}.
-\newblock \emph{\bibinfo{journal}{International Journal of Mechanical
-  Sciences}} \textbf{\bibinfo{volume}{204}}, \bibinfo{pages}{106541}
-  (\bibinfo{year}{2021}).
-
-\bibitem{Cerjan1981}
-\bibinfo{author}{Cerjan, C.~J.} \& \bibinfo{author}{Miller, W.~H.}
-\newblock \bibinfo{title}{{On finding transition states}}.
-\newblock \emph{\bibinfo{journal}{The Journal of Chemical Physics}}
-  \textbf{\bibinfo{volume}{75}}, \bibinfo{pages}{2800--2806}
-  (\bibinfo{year}{1981}).
-
-\bibitem{Heyden2005}
-\bibinfo{author}{Heyden, A.}, \bibinfo{author}{Bell, A.~T.} \&
-  \bibinfo{author}{Keil, F.~J.}
-\newblock \bibinfo{title}{{Efficient methods for finding transition states in
-  chemical reactions: Comparison of improved dimer method and partitioned
-  rational function optimization method}}.
-\newblock \emph{\bibinfo{journal}{Journal of Chemical Physics}}
-  \textbf{\bibinfo{volume}{123}}, \bibinfo{pages}{224101}
-  (\bibinfo{year}{2005}).
-
-\bibitem{Kastner2008}
-\bibinfo{author}{K{\"{a}}stner, J.} \& \bibinfo{author}{Sherwood, P.}
-\newblock \bibinfo{title}{{Superlinearly converging dimer method for transition
-  state search}}.
-\newblock \emph{\bibinfo{journal}{Journal of Chemical Physics}}
-  \textbf{\bibinfo{volume}{128}}, \bibinfo{pages}{014106}
-  (\bibinfo{year}{2008}).
-
-\bibitem{Zhang2016}
-\bibinfo{author}{Zhang, L.}, \bibinfo{author}{Du, Q.} \&
-  \bibinfo{author}{Zheng, Z.}
-\newblock \bibinfo{title}{{Optimization-based Shrinking Dimer Method for
-  Finding Transition States}}.
-\newblock \emph{\bibinfo{journal}{SIAM Journal on Scientific Computing}}
-  \textbf{\bibinfo{volume}{38}}, \bibinfo{pages}{A528--A544}
-  (\bibinfo{year}{2016}).
-
-\bibitem{E2007}
-\bibinfo{author}{E, W.}, \bibinfo{author}{Ren, W.} \&
-  \bibinfo{author}{Vanden-Eijnden, E.}
-\newblock \bibinfo{title}{{Simplified and improved string method for computing
-  the minimum energy paths in barrier-crossing events}}.
-\newblock \emph{\bibinfo{journal}{The Journal of Chemical Physics}}
-  \textbf{\bibinfo{volume}{126}}, \bibinfo{pages}{164103}
-  (\bibinfo{year}{2007}).
-
-\bibitem{Ren2013}
-\bibinfo{author}{Ren, W.} \& \bibinfo{author}{Vanden-Eijnden, E.}
-\newblock \bibinfo{title}{{A climbing string method for saddle point search}}.
-\newblock \emph{\bibinfo{journal}{Journal of Chemical Physics}}
-  \textbf{\bibinfo{volume}{138}}, \bibinfo{pages}{134105}
-  (\bibinfo{year}{2013}).
-
-\bibitem{E2002}
-\bibinfo{author}{E, W.}, \bibinfo{author}{Ren, W.} \&
-  \bibinfo{author}{Vanden-Eijnden, E.}
-\newblock \bibinfo{title}{{String method for the study of rare events}}.
-\newblock \emph{\bibinfo{journal}{Physical Review B}}
-  \textbf{\bibinfo{volume}{66}}, \bibinfo{pages}{052301}
-  (\bibinfo{year}{2002}).
-
-\bibitem{Trygubenko2004}
-\bibinfo{author}{Trygubenko, S.~A.} \& \bibinfo{author}{Wales, D.~J.}
-\newblock \bibinfo{title}{{A doubly nudged elastic band method for finding
-  transition states}}.
-\newblock \emph{\bibinfo{journal}{Journal of Chemical Physics}}
-  \textbf{\bibinfo{volume}{120}}, \bibinfo{pages}{2082--2094}
-  (\bibinfo{year}{2004}).
-
-\bibitem{Wales2012a}
-\bibinfo{author}{Wales, D.~J.} \& \bibinfo{author}{Carr, J.~M.}
-\newblock \bibinfo{title}{{Quasi-Continuous Interpolation Scheme for Pathways
-  between Distant Configurations}}.
-\newblock \emph{\bibinfo{journal}{Journal of Chemical Theory and Computation}}
-  \textbf{\bibinfo{volume}{8}}, \bibinfo{pages}{5020--5034}
-  (\bibinfo{year}{2012}).
-
-\bibitem{Dewar1984}
-\bibinfo{author}{Dewar, M. J.~S.}, \bibinfo{author}{Healy, E.~F.} \&
-  \bibinfo{author}{Stewart, J. J.~P.}
-\newblock \bibinfo{title}{{Location of transition states in reaction
-  mechanisms}}.
-\newblock \emph{\bibinfo{journal}{Journal of the Chemical Society, Faraday
-  Transactions 2}} \textbf{\bibinfo{volume}{80}}, \bibinfo{pages}{227}
-  (\bibinfo{year}{1984}).
-
-\bibitem{Ionova1993}
-\bibinfo{author}{Ionova, I.~V.} \& \bibinfo{author}{Carter, E.~A.}
-\newblock \bibinfo{title}{{Ridge method for finding saddle points on potential
-  energy surfaces}}.
-\newblock \emph{\bibinfo{journal}{The Journal of Chemical Physics}}
-  \textbf{\bibinfo{volume}{98}}, \bibinfo{pages}{6377--6386}
-  (\bibinfo{year}{1993}).
-
-\bibitem{Miron2001}
-\bibinfo{author}{Miron, R.~A.} \& \bibinfo{author}{Fichthorn, K.~A.}
-\newblock \bibinfo{title}{{The Step and Slide method for finding saddle points
-  on multidimensional potential surfaces}}.
-\newblock \emph{\bibinfo{journal}{The Journal of Chemical Physics}}
-  \textbf{\bibinfo{volume}{115}}, \bibinfo{pages}{8742--8747}
-  (\bibinfo{year}{2001}).
-
-\bibitem{Zhang2013}
-\bibinfo{author}{Zhang, X.-J.}, \bibinfo{author}{Shang, C.} \&
-  \bibinfo{author}{Liu, Z.-P.}
-\newblock \bibinfo{title}{{Double-Ended Surface Walking Method for Pathway
-  Building and Transition State Location of Complex Reactions}}.
-\newblock \emph{\bibinfo{journal}{Journal of Chemical Theory and Computation}}
-  \textbf{\bibinfo{volume}{9}}, \bibinfo{pages}{5745--5753}
-  (\bibinfo{year}{2013}).
-
-\bibitem{Trefethen2013}
-\bibinfo{author}{Trefethen, A.~E.} \& \bibinfo{author}{Thiyagalingam, J.}
-\newblock \bibinfo{title}{{Energy-aware software: Challenges, opportunities and
-  strategies}}.
-\newblock \emph{\bibinfo{journal}{Journal of Computational Science}}
-  \textbf{\bibinfo{volume}{4}}, \bibinfo{pages}{444--449}
-  (\bibinfo{year}{2013}).
-
-\bibitem{Shalf2020}
-\bibinfo{author}{Shalf, J.}
-\newblock \bibinfo{title}{{The future of computing beyond Moore's Law}}.
-\newblock \emph{\bibinfo{journal}{Philosophical Transactions of the Royal
-  Society A}} \textbf{\bibinfo{volume}{378}}, \bibinfo{pages}{20190061}
-  (\bibinfo{year}{2020}).
-
-\bibitem{Alexander2020}
-\bibinfo{author}{Alexander, F.} \emph{et~al.}
-\newblock \bibinfo{title}{{Exascale applications: Skin in the game}}.
-\newblock \emph{\bibinfo{journal}{Philosophical Transactions of the Royal
-  Society A}} \textbf{\bibinfo{volume}{378}}, \bibinfo{pages}{20190056}
-  (\bibinfo{year}{2020}).
-
-\bibitem{McMullen2018}
-\bibinfo{author}{McMullen, A.}, \bibinfo{author}{Holmes-Cerfon, M.},
-  \bibinfo{author}{Sciortino, F.}, \bibinfo{author}{Grosberg, A.~Y.} \&
-  \bibinfo{author}{Brujic, J.}
-\newblock \bibinfo{title}{{Freely Jointed Polymers Made of Droplets}}.
-\newblock \emph{\bibinfo{journal}{Physical Review Letters}}
-  \textbf{\bibinfo{volume}{121}}, \bibinfo{pages}{138002}
-  (\bibinfo{year}{2018}).
-
-\bibitem{Nguemaha2018}
-\bibinfo{author}{Nguemaha, V.} \& \bibinfo{author}{Zhou, H.~X.}
-\newblock \bibinfo{title}{{Liquid-Liquid Phase Separation of Patchy Particles
-  Illuminates Diverse Effects of Regulatory Components on Protein Droplet
-  Formation}}.
-\newblock \emph{\bibinfo{journal}{Scientific Reports}}
-  \textbf{\bibinfo{volume}{8}}, \bibinfo{pages}{1--11} (\bibinfo{year}{2018}).
-
-\bibitem{Chen2018b}
-\bibinfo{author}{Chen, D.}, \bibinfo{author}{Zhang, G.} \&
-  \bibinfo{author}{Torquato, S.}
-\newblock \bibinfo{title}{{Inverse Design of Colloidal Crystals via Optimized
-  Patchy Interactions}}.
-\newblock \emph{\bibinfo{journal}{Journal of Physical Chemistry B}}
-  \textbf{\bibinfo{volume}{122}}, \bibinfo{pages}{8462--8468}
-  (\bibinfo{year}{2018}).
-
-\bibitem{Santra2018}
-\bibinfo{author}{Santra, M.}, \bibinfo{author}{Singh, R.~S.} \&
-  \bibinfo{author}{Bagchi, B.}
-\newblock \bibinfo{title}{{Polymorph selection during crystallization of a
-  model colloidal fluid with a free energy landscape containing a metastable
-  solid}}.
-\newblock \emph{\bibinfo{journal}{Physical Review E}}
-  \textbf{\bibinfo{volume}{98}}, \bibinfo{pages}{032606}
-  (\bibinfo{year}{2018}).
-
-\bibitem{Mokkonen2016}
-\bibinfo{author}{M{\"{o}}kk{\"{o}}nen, H.}, \bibinfo{author}{Ala-Nissila, T.}
-  \& \bibinfo{author}{J{\'{o}}nsson, H.}
-\newblock \bibinfo{title}{{Efficient dynamical correction of the transition
-  state theory rate estimate for a flat energy barrier}}.
-\newblock \emph{\bibinfo{journal}{The Journal of Chemical Physics}}
-  \textbf{\bibinfo{volume}{145}}, \bibinfo{pages}{094901}
-  (\bibinfo{year}{2016}).
-
-\bibitem{Wriggers2006}
-\bibinfo{author}{Wriggers, P.}
-\newblock \emph{\bibinfo{title}{{Computational Contact Mechanics}}}
-  (\bibinfo{publisher}{Springer Berlin Heidelberg}, \bibinfo{address}{Berlin,
-  Heidelberg}, \bibinfo{year}{2006}).
-
-\bibitem{Page1988}
-\bibinfo{author}{Page, M.} \& \bibinfo{author}{McIver, J.~W.}
-\newblock \bibinfo{title}{{On evaluating the reaction path Hamiltonian}}.
-\newblock \emph{\bibinfo{journal}{The Journal of Chemical Physics}}
-  \textbf{\bibinfo{volume}{88}}, \bibinfo{pages}{922--935}
-  (\bibinfo{year}{1988}).
-
-\bibitem{Liu1989}
-\bibinfo{author}{Liu, D.~C.} \& \bibinfo{author}{Nocedal, J.}
-\newblock \bibinfo{title}{{On the limited memory bfgs method for large scale
-  optimization}}.
-\newblock \emph{\bibinfo{journal}{Mathematical Programming}}
-  \textbf{\bibinfo{volume}{45}}, \bibinfo{pages}{503--528}
-  (\bibinfo{year}{1989}).
-
-\bibitem{Wales2002}
-\bibinfo{author}{Wales, D.~J.}
-\newblock \bibinfo{title}{{Discrete path sampling}}.
-\newblock \emph{\bibinfo{journal}{Molecular Physics}}
-  \textbf{\bibinfo{volume}{100}}, \bibinfo{pages}{3285--3305}
-  (\bibinfo{year}{2002}).
-
-\bibitem{Passerone2001}
-\bibinfo{author}{Passerone, D.} \& \bibinfo{author}{Parrinello, M.}
-\newblock \bibinfo{title}{{Action-Derived Molecular Dynamics in the Study of
-  Rare Events}}.
-\newblock \emph{\bibinfo{journal}{Physical Review Letters}}
-  \textbf{\bibinfo{volume}{87}}, \bibinfo{pages}{108302}
-  (\bibinfo{year}{2001}).
-
-\bibitem{Virot2017}
-\bibinfo{author}{Virot, E.}, \bibinfo{author}{Kreilos, T.},
-  \bibinfo{author}{Schneider, T.~M.} \& \bibinfo{author}{Rubinstein, S.~M.}
-\newblock \bibinfo{title}{{Stability Landscape of Shell Buckling}}.
-\newblock \emph{\bibinfo{journal}{Physical Review Letters}}
-  \textbf{\bibinfo{volume}{119}}, \bibinfo{pages}{224101}
-  (\bibinfo{year}{2017}).
-
-\bibitem{Kusumaatmaja2006}
-\bibinfo{author}{Kusumaatmaja, H.}, \bibinfo{author}{L{\'{e}}opold{\`{e}}s,
-  J.}, \bibinfo{author}{Dupuis, A.} \& \bibinfo{author}{Yeomans, J.~M.}
-\newblock \bibinfo{title}{{Drop dynamics on chemically patterned surfaces}}.
-\newblock \emph{\bibinfo{journal}{Europhysics Letters}}
-  \textbf{\bibinfo{volume}{73}}, \bibinfo{pages}{740--746}
-  (\bibinfo{year}{2006}).
-
-\bibitem{Brown2016}
-\bibinfo{author}{Brown, P.~S.} \& \bibinfo{author}{Bhushan, B.}
-\newblock \bibinfo{title}{{Bioinspired materials for water supply and
-  management: water collection, water purification and separation of water from
-  oil}}.
-\newblock \emph{\bibinfo{journal}{Philosophical Transactions of the Royal
-  Society A}} \textbf{\bibinfo{volume}{374}}, \bibinfo{pages}{20160135}
-  (\bibinfo{year}{2016}).
-
-\bibitem{Lee2018}
-\bibinfo{author}{Lee, C.~T.} \& \bibinfo{author}{Amaro, R.~E.}
-\newblock \bibinfo{title}{{Exascale Computing: A New Dawn for Computational
-  Biology}}.
-\newblock \emph{\bibinfo{journal}{Computing in Science {\&} Engineering}}
-  \textbf{\bibinfo{volume}{20}}, \bibinfo{pages}{18--25}
-  (\bibinfo{year}{2018}).
-
-\bibitem{Kolev2021}
-\bibinfo{author}{Kolev, T.} \emph{et~al.}
-\newblock \bibinfo{title}{{Efficient exascale discretizations: High-order
-  finite element methods}}.
-\newblock \emph{\bibinfo{journal}{The International Journal of High Performance
-  Computing Applications}} \textbf{\bibinfo{volume}{35}},
-  \bibinfo{pages}{527--552} (\bibinfo{year}{2021}).
-
-\bibitem{Brakke1992}
-\bibinfo{author}{Brakke, K.~A.}
-\newblock \bibinfo{title}{{The Surface Evolver}}.
-\newblock \emph{\bibinfo{journal}{Experimental Mathematics}}
-  \textbf{\bibinfo{volume}{1}}, \bibinfo{pages}{141--165}
-  (\bibinfo{year}{1992}).
-
-\bibitem{Kirkpatrick1983}
-\bibinfo{author}{Kirkpatrick, S.}, \bibinfo{author}{Gelatt, C.~D.} \&
-  \bibinfo{author}{Vecchi, M.~P.}
-\newblock \bibinfo{title}{{Optimization By Simulated Annealing}}.
-\newblock \emph{\bibinfo{journal}{Science}} \textbf{\bibinfo{volume}{220}},
-  \bibinfo{pages}{671--680} (\bibinfo{year}{1983}).
-
-\end{thebibliography}
-%% end bib
+\section*{Supplementary material}
+See the supplementary material for derivations of the expressions of the constraint coefficients in \cref{eq:kd,eq:ke}, and the demonstration of the BITSS method applied to a path with multiple transition states.
 
@@
 
-\section*{Author contributions}
-S.~J.~A., J.~R.~P., and H.~K conceived and planned the project.
+\section*{Conflict of Interest}
+The authors have no conflicts to disclose.
+
+\section*{Author Contributions}
+All authors conceived and planned the project.
 S.~J.~A. performed the numerical experiments and analysed the data.
@@
 
-\section*{Competing interests}
-The authors declare no competing interests.
+\section*{Data availability}
+The data that support the findings of this study are available from the corresponding author upon reasonable request.
+
+%% start bib
+\bibliographystyle{aipnum4-1}
+\bibliography{bibexport.bib}
+% % \bibliography{../../library.bib}
+%% mid bib
+%% end bib
 

### 2022-06-04 fig/make_bracketing/plot.py

@@ -43,7 +43,7 @@ def make_potential():
     levels = np.arange(-1.5, 1.5, 0.25)
     plt.contourf(x, y, e, cmap=cmap, levels=levels, extend='both')
     ax.axis('off')
-    plt.savefig(f'potential.png')
+    plt.savefig(f'potential.png', dpi=600)
     plt.close()
 
 

### 2022-06-04 fig/make_flatdiscontinuous/plot.py

@@ -73,7 +73,7 @@ def plot_flat(fig, hsize):
         ax = fig.add_axes([0,0,1,1])
         plt.contourf(x, y, e, cmap='Greys_r', levels=10)
         ax.axis('off')
-        plt.savefig(f'potential.png', dpi=500)
+        plt.savefig(f'potential.png', dpi=600)
         plt.close(fig)
 
     def read_data():

### 2022-06-04 fig/style.py

@@ -5,13 +5,14 @@ import matplotlib as mpl
 import matplotlib.pyplot as plt
 import pyutils.latexify as lt
 
-lt.dpi = 500
-lt.update_width('natcomm-single')
+lt.dpi = 1200
+lt.update_width('aip-single')
 
 # Font size
 plt.rc('font', size=9)
 plt.rc('axes', labelsize=9)
 
+# Use text font for axes
 def formatter(s):
     base = re.search(r'\$\\mathdefault\{(.*)\}\$', s)
     if (base is None): return s
@@ -31,16 +32,16 @@ def formatter(s):
     return s
 lt.axis_formatter = formatter
 
-# Helvetica font
-mpl.rcParams['font.family'] = 'sans-serif'
-mpl.rcParams['font.sans-serif'] = ['Helvetica']
-mpl.rcParams['text.latex.preamble'] = "\n".join([mpl.rcParams['text.latex.preamble'],
-                                                 r"\usepackage{helvet}",])
-                                                 # r"\usepackage{sansmath}",
-                                                 # r"\sansmath"])
+# # Helvetica font
+# mpl.rcParams['font.family'] = 'sans-serif'
+# mpl.rcParams['font.sans-serif'] = ['Helvetica']
+# mpl.rcParams['text.latex.preamble'] = "\n".join([mpl.rcParams['text.latex.preamble'],
+#                                                  r"\usepackage{helvet}",])
+#                                                  # r"\usepackage{sansmath}",
+#                                                  # r"\sansmath"])
 
-# Upright vectors
-mpl.rcParams['text.latex.preamble'] = "\n".join([mpl.rcParams['text.latex.preamble'], r'\renewcommand{\bm}[1]{\boldsymbol{\mathbf{#1}}}'])
+# # Upright vectors
+# mpl.rcParams['text.latex.preamble'] = "\n".join([mpl.rcParams['text.latex.preamble'], r'\renewcommand{\bm}[1]{\boldsymbol{\mathbf{#1}}}'])
 
 # Colours
 plt.rc('font', size=9)

### 2022-06-04 manuscript.tex
Chain of states details moved into main text

@@
 As a result of the BITSS method using only two states, it has the potential to be significantly faster.
-This is tested here by measuring the speed of convergence to the transition state for BITSS in comparison with the string method \cite{E2007} and DNEB \cite{Trygubenko2004} for three diverse systems, exhibiting a broad range of energy landscapes.
-Details of each are presented in the methods section.
+This is tested here by measuring the speed of convergence to the transition state for BITSS in comparison with the string method \cite{E2007} and DNEB \cite{Trygubenko2004} using 5, 10, and 20 images for three diverse systems, exhibiting a broad range of energy landscapes.
 
@@
 The speed of this convergence is evaluated through comparison with the number of calculations of the potential gradient for a single state.
+
+The parameters used in the chain-of-states methods are also chosen such that they optimise the speed of convergence.
+For the string method, this is the number of downhill iterations before the images are redistributed.
+For which, the optimal values are found to be 2, 50, and 20 for the particle cluster, cylindrical buckling, and striped wetting examples, respectively.
+In the case of DNEB, the spring constant between the images is optimised instead.
+For the particle cluster system, a spring constant of $1$ is used for the 5 image case, and $0.1$ for 10 and 20 images.
+For the cylindrical buckling, the spring constant is $0.01$ in all cases.
+And for the striped wetting, $10^{-4}$ is used for 5 and 10 images, and $10^{-3}$ for 20 images.
 
@@
 \section*{Methods}
-
-\subsection{Implementing the string and DNEB methods}
-In the convergence rate comparison in \cref{fig:speedtest}, the string method and doubly-nudged elastic band method (DNEB) are used, based upon \cite{E2007} and \cite{Trygubenko2004}, respectively.
-Each method is initialised with 5, 10, or 20 images, using a linear interpolation between the chosen end states.
-
-In each iteration of the string method, each image is evolved downhill for a number of L-BFGS iterations before redistributing the images along a cubic-spline interpolated path.
-This number of iterations is varied to obtain the fastest convergence, for which we find 2, 50, and 20 to be optimal for the particle cluster, cylindrical buckling, and striped wetting examples, respectively.
-
-In the case of DNEB, the spring constant between the images is instead optimised.
-For the particle cluster system, a spring constant of $1$ is used for the 5 image case, and $0.1$ for 10 and 20 images.
-For the cylindrical buckling, the spring constant is $0.01$ in all cases.
-And for the striped wetting, $10^{-4}$ is used for 5 and 10 images, and $10^{-3}$ for 20 images.
 

### 2022-06-06 manuscript.tex
Moving methods into main text and si

@@
 
-Firstly, we show in \cref{fig:adaptivemesh}a that BITSS is able to handle the discretisation adapting, and the number of degrees of freedom changing, as the method runs.
-For this we use the cylindrical buckling example with the resolution increasing from 40 to 100 triangles around the cylinder, corresponding to an increase from \num{1760} to \num{11000} degrees of freedom.
-This demonstrates that BITSS is able to converge to the transition state so long as the remeshing is not so significant as to shift a state into the basin of attraction of the other minimum.
+% Firstly, we show in \cref{fig:adaptivemesh}a that BITSS is able to handle the discretisation adapting, and the number of degrees of freedom changing, as the method runs.
+% For this we use the cylindrical buckling example with the resolution increasing from 40 to 100 triangles around the cylinder, corresponding to an increase from \num{1760} to \num{11000} degrees of freedom.
+% This demonstrates that BITSS is able to converge to the transition state so long as the remeshing is not so significant as to shift a state into the basin of attraction of the other minimum.
 
-In the second test, shown in \cref{fig:adaptivemesh}b, we demonstrate the use of different meshes for the two states in the striped wetting example.
-In this case, the distance measure is adapted by interpolating one state onto the other mesh and computing the Euclidean distance.
+Firstly, we test if BITSS is able to handle the discretisation adapting, and the number of degrees of freedom changing, as the method runs.
+For this we use the cylindrical buckling example with the resolution being refined at the end of each iteration of the BITSS method, each time the separation between the two states has halved.
+This involves the number of triangles around the circumference of the cylinder increasing along the sequence: $40 \rightarrow 60 \rightarrow 80 \rightarrow 100$; with the number of degrees of freedom increasing by: $\num{1760} \rightarrow \num{3960} \rightarrow \num{7040} \rightarrow \num{11000}$.
+The positions of the nodes on the new grid, $\{\bm{n}_i\}$, are determined by linear interpolation from the previous grid $\{\bm{p}_i\}$, using the positions of the unbuckled meshes, $\{\bm{n'}_i\}$ and $\{\bm{p'}_i\}$.
+For each node of the new grid, $\bm{n'}_i$, the triangle that contains it is first identified, which we will denote $\{\bm{p'}_1,\bm{p'}_2,\bm{p'}_3\}$, and the barycentric coordinates of the point are computed, $\{\lambda_1,\lambda_2,\lambda_3\}$.
+The new position is then given by $\bm{n}_i = \lambda_1 \bm{p}_1 + \lambda_2 \bm{p}_2 + \lambda_3 \bm{p}_3$.
+The results in \cref{fig:adaptivemesh}a demonstrates that BITSS is indeed able to converge to the transition state.
+In general, it will be successful so long as the remeshing is not so significant as to shift a state into the basin of attraction of the other minimum.
+
+% In the second test, shown in \cref{fig:adaptivemesh}b, we demonstrate the use of different meshes for the two states in the striped wetting example.
+% In this case, the distance measure is adapted by interpolating one state onto the other mesh and computing the Euclidean distance.
+% However, for some applications a simpler measure may be sufficient, such as the difference between average values of the system.
+% Using this approach, BITSS is able to closely approach the transition state.
+% The precision of this convergence is now limited by the transition state energy differing slightly on each grid, but this effect will be reduced when using an adaptive method or a higher resolution.
+
+In the second test, we demonstrate the use of different meshes for the two states in the striped wetting example.
+In this case, the distance measure is adapted by first interpolating one state onto the other mesh.
+To do this the phase field is mapped from the higher resolution grid, $\{\phi_{k,l} | k,l \in \{0,1,\cdots,399\}\}$, to the low resolution grid, $\{\phi'_{i,j} | i,j \in \{0,1,\cdots,199\}\}$.
+Since a square grid is used with a resolution ratio of two, the involves averaging each 2x2 block to a single point:
+\begin{equation}
+  \phi'_{i,j} = \frac{1}{4} \left( \phi_{2i,2j} + \phi_{2i+1,2j} + \phi_{2i,2j+1} + \phi_{2i+1,2j+1} \right).
+\end{equation}
+The separation between the states is then computed with the 2-norm.
+Finally, the gradient of the distance with respect to each point is mapped back to the higher-resolution grid.
 However, for some applications a simpler measure may be sufficient, such as the difference between average values of the system.
@@
 For the cylindrical buckling example with a changing mesh, the resolution is refined each time the separation between the two states has halved, and is performed at the end of each iteration of the BITSS method.
-This involves the number of triangles around the circumference of the cylinder increasing along the sequence: $40 \rightarrow 60 \rightarrow 80 \rightarrow 100$; with the number of degrees of freedom increasing by: $1760 \rightarrow 3960 \rightarrow 7040 \rightarrow 11000$.
+This involves the number of triangles around the circumference of the cylinder increasing along the sequence: $40 \rightarrow 60 \rightarrow 80 \rightarrow 100$; with the number of degrees of freedom increasing by: $\num{1760} \rightarrow \num{3960} \rightarrow \num{7040} \rightarrow \num{11000}$.
 The positions of the nodes on the new grid, $\{\bm{n}_i\}$, are determined by linear interpolation from the previous grid $\{\bm{p}_i\}$, using the positions of the unbuckled meshes, $\{\bm{n'}_i\}$ and $\{\bm{p'}_i\}$.
@@
 
-\subsection{Energy and gradient expressions for the example systems}
-\subsubsection{Particle cluster system}
-In the particle cluster example system, the Lennard-Jones potential is used for the interaction between each pair of particles.
-Therefore, the potential and its gradient for each pair of particles are
-\begin{gather}
-  E = 4\epsilon \left[ \left(\frac{\sigma}{r}\right)^{12} - \left(\frac{\sigma}{r}\right)^6 \right], \\
-  \frac{\partial E}{\partial \bm{x}_1} = -\frac{\partial E}{\partial \bm{x}_2} =
-    \frac{24 \epsilon (\bm{x}_2 - \bm{x}_1)}{r^2} \left[ 2 \left(\frac{\sigma}{r}\right)^{12} - \left(\frac{\sigma}{r}\right)^6 \right],
-\end{gather}
-where $\bm{x}_1$ and $\bm{x}_2$ are the positions of the two particles, $r$ is their separation, $\epsilon$ is the interaction strength, and $\sigma$ is the particle radius.
-
-\subsubsection{Cylindrical buckling system}
-A 2D triangular mesh is used to model the cylindrical buckling system, with the ends of the cylinder fixed in place to apply an axial compression of 0.14\%.
-The energy of the system is evaluated by treating all bonds in the mesh as an elastic spring to obtain the stretching energy, and all pairs of adjacent triangles to be connected by elastic hinges, providing the bending energy.
-Their expressions are given by
-\begin{equation}
-  E = \sum_i k^\mathrm{S}_i (r_i - r^0_i)^2 + \sum_j k^\mathrm{B}_j [1 + \cos(\theta_j - \theta^0_j)].
-\end{equation}
-The first term is the stretching energy, where $r_i$ is the length, $r^0_i$ is the equilibrium length, and $k^\mathrm{S}_i$ is the stretching rigidity of bond $i$.
-The second term provides the bending energy, where $\theta_j$ is the dihedral angle, $\theta^0_j$ is the equilibrium angle, and $k^\mathrm{B}_j$ is the bending rigidity of hinge $j$.
-
-\begin{figure}[htb]
-  \includegraphics{fig/BAHschematic.pdf}
-  \caption{\label{fig:BAHschematic}
-    Schematic of the bar and hinge model showing the relevant parameters for a single hinge element.
-    $h_i$ and $\bm{\hat{n}}_i$ denote the height and unit normal of each triangle respectively.
-  }
-\end{figure}
-The gradient of the energy can be obtained by individually considering the stretching and bending energies of a single bond and hinge.
-For simplicity, we will ignore the index for the bond and hinge.
-Using the variables shown in the schematic in \cref{fig:BAHschematic}, the gradient of the stretching energy of the bond between $\bm{x}_2$ and $\bm{x}_3$ is given by,
-\begin{equation}
-  \frac{\partial E^\mathrm{S}}{\partial \bm{x}_2} = - \frac{\partial E^\mathrm{S}}{\partial \bm{x}_3} =
-    2 k^\mathrm{S} (r - r^0) (\bm{x_2} - \bm{x_3}).
-\end{equation}
-The gradients of the bending energy of the hinge are
-\begin{align}
-  \frac{\partial E^\mathrm{B}}{\partial \bm{x}_1} &= k^\mathrm{B} \sin(\theta - \theta^0) \frac{\bm{\hat{n}}_a}{h_a}, \\
-  \frac{\partial E^\mathrm{B}}{\partial \bm{x}_2} &= - k^\mathrm{B} \sin(\theta - \theta^0) \left[\frac{\bm{\hat{n}}_a}{h_a} + \frac{\bm{\hat{n}}_a + \bm{\hat{n}}_b}{r}\right], \\
-  \frac{\partial E^\mathrm{B}}{\partial \bm{x}_3} &= - k^\mathrm{B} \sin(\theta - \theta^0) \left[\frac{\bm{\hat{n}}_b}{h_b} + \frac{\bm{\hat{n}}_a + \bm{\hat{n}}_b}{r}\right], \\
-  \frac{\partial E^\mathrm{B}}{\partial \bm{x}_4} &= k^\mathrm{B} \sin(\theta - \theta^0) \frac{\bm{\hat{n}}_b}{h_b}.
-\end{align}
-
-\subsubsection{Striped wetting system}
-This modelled on a 200x200 2D grid (and 400x400 in \cref{sec:adaptive}) using a phase-field model \cite{Panter2019b}, which has an order parameter, $\phi(\bm{r})$, representing the phase of the liquid ($\phi=-1$ for gas, $\phi=1$ for liquid).
-The energy functional has four separate terms,
-\begin{equation} \label{eq:phasefield}
-  E[\phi] = E^\mathrm{B}[\phi] + E^\mathrm{I}[\phi] + E^\mathrm{S}[\phi] + E^\mathrm{V}[\phi].
-\end{equation}
-The first term, $E^\mathrm{B}$, uses a double well potential to set values of $\phi=\pm1$ in the bulk.
-The second term then provides the interfacial energy between the liquid and gas by imposing an energy penalty to gradients in $\phi$.
-$E^\mathrm{S}$ is the solid-liquid interaction energy, which sets the contact angles of the hydrophilic and hydrophobic regions to 60\si{\degree} and 110\si{\degree}, respectively.
-Finally, $E^\mathrm{V}$ constrains the volume of the liquid drop by penalising any variation from the target volume.
-
-These four sections of the phase-field model are obtained using the following equations,
-\begin{align}
-  E^\mathrm{B}[\phi] &= \sum_i \frac{1}{\epsilon} \left( \frac{{\phi_i}^4}{4} - \frac{{\phi_i}^2}{2} + \frac{1}{4} \right) \upDelta V,\\
-  E^\mathrm{I}[\phi] &= \sum_i \frac{\epsilon}{2} \abs{\grad \phi_i}^2 \upDelta V,\\
-  E^\mathrm{S}[\phi] &= \sum_j \sqrt{2}\cos\theta_j \left( \frac{{\phi_j}^3}{6} - \frac{\phi_j}{2} - \frac{1}{3} \right) \upDelta S,\\
-  E^\mathrm{V}[\phi] &= k_\mathrm{V} \left[ \sum_i \frac{\phi_i + 1}{2} \upDelta V - V_0 \right]^2,
-\end{align}
-where the index $i$ includes all of the nodes, while $j$ represents the nodes along the solid surface.
-$\upDelta V$ and $\upDelta S$ are, respectively, the volume and solid surface areas contained by each individual node.
-$\epsilon$ is the liquid-gas interface width (set to 2.5 lattice units), $\theta_j$ is the contact-angle with the solid surface, and $V_0$ is the constrained volume of the liquid drop.
-The strength of the volume constraint is parametrised by $k_\mathrm{V}$ for which we use a value of $10^4$.
-The gradients of these terms are given by,
-\begin{align}
-  \frac{\partial E^\mathrm{B}}{\partial \phi_i} &= \frac{1}{\epsilon} \left( {\phi_i}^3 - \phi_i \right) \upDelta V,\\
-  \frac{\partial E^\mathrm{I}}{\partial \phi_i} &= \frac{\epsilon}{2} \left[
-    \frac{\partial \abs{\grad \phi_i}^2}{\partial \phi_i} +
-    \sum_k\frac{\partial \abs{\grad \phi_k}^2}{\partial \phi_i} \right] \upDelta V,\\
-  \frac{\partial E^\mathrm{S}}{\partial \phi_j} &= \sqrt{2}\cos\theta_j \left( \frac{{\phi_j}^2}{2} - \frac{1}{2} \right) \upDelta S,\\
-  \frac{\partial E^\mathrm{V}}{\partial \phi_i} &= k_\mathrm{V} \left[ \sum_{i'} \frac{\phi_{i'} + 1}{2} \upDelta V - V_0 \right] \upDelta V,
-\end{align}
-where index $k$ denotes neighboring nodes at which the evaluation of the gradient uses $\phi_i$.
-
 \section*{Supplementary material}
-See the supplementary material for derivations of the expressions of the constraint coefficients in \cref{eq:kd,eq:ke}, and the demonstration of the BITSS method applied to a path with multiple transition states.
+See the supplementary material for derivations of the expressions of the constraint coefficients in \cref{eq:kd,eq:ke}, details of the potentials used in example systems, and the demonstration of the BITSS method applied to a path with multiple transition states.
 

### 2022-06-06 si/supplementary_information.tex
Moving methods into main text and si

@@
-\documentclass[10pt]{revtex4}
+\documentclass[aip,jcp,11pt]{revtex4-2}
 
 % Text
-% \usepackage{amssymb}
-\def\thesection{SUPPLEMENTARY NOTE \Roman{section}}
+\usepackage[utf8]{inputenc}
+\usepackage[T1]{fontenc}
+\usepackage[group-separator={,}]{siunitx}
+\def\thesection{S\Roman{section}}
 
@@
 \usepackage{graphicx}
-\usepackage{placeins}
 
@@
 \affiliation{Department of Physics, Durham University, South Road, Durham DH1 3LE, UK}
+\date{\today}
 \maketitle
@@
 The constraint coefficients are chosen to set comparable sizes for each term in the gradient of the BITSS potential,
-\begin{equation} \label{eq:gradBITSS}
+\begin{equation}
   \grad E_\text{BITSS} = \sum_{\substack{i=1,2 \\ j\neq i}} \left[ 1 + 2 \kappa_\text{e} (E_i - E_j) \right] \grad E_i + 2 \kappa_\text{d} (d - d_i) \grad d.
@@
 
+\section{Energy and gradient expressions for the example systems}
+\subsection{Particle cluster system}
+In the particle cluster example system, the Lennard-Jones potential is used for the interaction between each pair of particles.
+Therefore, the potential and its gradient for each pair of particles are
+\begin{gather}
+  E = 4\epsilon \left[ \left(\frac{\sigma}{r}\right)^{12} - \left(\frac{\sigma}{r}\right)^6 \right], \\
+  \frac{\partial E}{\partial \bm{x}_1} = -\frac{\partial E}{\partial \bm{x}_2} =
+    \frac{24 \epsilon (\bm{x}_2 - \bm{x}_1)}{r^2} \left[ 2 \left(\frac{\sigma}{r}\right)^{12} - \left(\frac{\sigma}{r}\right)^6 \right],
+\end{gather}
+where $\bm{x}_1$ and $\bm{x}_2$ are the positions of the two particles, $r$ is their separation, $\epsilon$ is the interaction strength, and $\sigma$ is the particle radius.
+
+\subsection{Cylindrical buckling system}
+A 2D triangular mesh is used to model the cylindrical buckling system, with the ends of the cylinder fixed in place to apply an axial compression of 0.14\%.
+The energy of the system is evaluated by treating all bonds in the mesh as an elastic spring to obtain the stretching energy, and all pairs of adjacent triangles to be connected by elastic hinges, providing the bending energy.
+Their expressions are given by
+\begin{equation}
+  E = \sum_i k^\mathrm{S}_i (r_i - r^0_i)^2 + \sum_j k^\mathrm{B}_j [1 + \cos(\theta_j - \theta^0_j)].
+\end{equation}
+The first term is the stretching energy, where $r_i$ is the length, $r^0_i$ is the equilibrium length, and $k^\mathrm{S}_i$ is the stretching rigidity of bond $i$.
+The second term provides the bending energy, where $\theta_j$ is the dihedral angle, $\theta^0_j$ is the equilibrium angle, and $k^\mathrm{B}_j$ is the bending rigidity of hinge $j$.
+
+\begin{figure}[htb]
+  \includegraphics{fig/BAHschematic.pdf}
+  \caption{\label{fig:BAHschematic}
+    Schematic of the bar and hinge model showing the relevant parameters for a single hinge element.
+    $h_i$ and $\bm{\hat{n}}_i$ denote the height and unit normal of each triangle respectively.
+  }
+\end{figure}
+The gradient of the energy can be obtained by individually considering the stretching and bending energies of a single bond and hinge.
+For simplicity, we will ignore the index for the bond and hinge.
+Using the variables shown in the schematic in \cref{fig:BAHschematic}, the gradient of the stretching energy of the bond between $\bm{x}_2$ and $\bm{x}_3$ is given by,
+\begin{equation}
+  \frac{\partial E^\mathrm{S}}{\partial \bm{x}_2} = - \frac{\partial E^\mathrm{S}}{\partial \bm{x}_3} =
+    2 k^\mathrm{S} (r - r^0) (\bm{x_2} - \bm{x_3}).
+\end{equation}
+The gradients of the bending energy of the hinge are
+\begin{align}
+  \frac{\partial E^\mathrm{B}}{\partial \bm{x}_1} &= k^\mathrm{B} \sin(\theta - \theta^0) \frac{\bm{\hat{n}}_a}{h_a}, \\
+  \frac{\partial E^\mathrm{B}}{\partial \bm{x}_2} &= - k^\mathrm{B} \sin(\theta - \theta^0) \left[\frac{\bm{\hat{n}}_a}{h_a} + \frac{\bm{\hat{n}}_a + \bm{\hat{n}}_b}{r}\right], \\
+  \frac{\partial E^\mathrm{B}}{\partial \bm{x}_3} &= - k^\mathrm{B} \sin(\theta - \theta^0) \left[\frac{\bm{\hat{n}}_b}{h_b} + \frac{\bm{\hat{n}}_a + \bm{\hat{n}}_b}{r}\right], \\
+  \frac{\partial E^\mathrm{B}}{\partial \bm{x}_4} &= k^\mathrm{B} \sin(\theta - \theta^0) \frac{\bm{\hat{n}}_b}{h_b}.
+\end{align}
+
+\subsection{Striped wetting system}
+This modelled on a 200x200 2D grid (and 400x400 in the adaptive grid test) using a phase-field model \cite{Panter2019b}, which has an order parameter, $\phi(\bm{r})$, representing the phase of the liquid ($\phi=-1$ for gas, $\phi=1$ for liquid).
+The energy functional has four separate terms,
+\begin{equation} \label{eq:phasefield}
+  E[\phi] = E^\mathrm{B}[\phi] + E^\mathrm{I}[\phi] + E^\mathrm{S}[\phi] + E^\mathrm{V}[\phi].
+\end{equation}
+The first term, $E^\mathrm{B}$, uses a double well potential to set values of $\phi=\pm1$ in the bulk.
+The second term then provides the interfacial energy between the liquid and gas by imposing an energy penalty to gradients in $\phi$.
+$E^\mathrm{S}$ is the solid-liquid interaction energy, which sets the contact angles of the hydrophilic and hydrophobic regions to 60\si{\degree} and 110\si{\degree}, respectively.
+Finally, $E^\mathrm{V}$ constrains the volume of the liquid drop by penalising any variation from the target volume.
+
+These four sections of the phase-field model are obtained using the following equations,
+\begin{align}
+  E^\mathrm{B}[\phi] &= \sum_i \frac{1}{\epsilon} \left( \frac{{\phi_i}^4}{4} - \frac{{\phi_i}^2}{2} + \frac{1}{4} \right) \upDelta V,\\
+  E^\mathrm{I}[\phi] &= \sum_i \frac{\epsilon}{2} \abs{\grad \phi_i}^2 \upDelta V,\\
+  E^\mathrm{S}[\phi] &= \sum_j \sqrt{2}\cos\theta_j \left( \frac{{\phi_j}^3}{6} - \frac{\phi_j}{2} - \frac{1}{3} \right) \upDelta S,\\
+  E^\mathrm{V}[\phi] &= k_\mathrm{V} \left[ \sum_i \frac{\phi_i + 1}{2} \upDelta V - V_0 \right]^2,
+\end{align}
+where the index $i$ includes all of the nodes, while $j$ represents the nodes along the solid surface.
+$\upDelta V$ and $\upDelta S$ are, respectively, the volume and solid surface areas contained by each individual node.
+$\epsilon$ is the liquid-gas interface width (set to 2.5 lattice units), $\theta_j$ is the contact-angle with the solid surface, and $V_0$ is the constrained volume of the liquid drop.
+The strength of the volume constraint is parametrised by $k_\mathrm{V}$ for which we use a value of $10^4$.
+The gradients of these terms are given by,
+\begin{align}
+  \frac{\partial E^\mathrm{B}}{\partial \phi_i} &= \frac{1}{\epsilon} \left( {\phi_i}^3 - \phi_i \right) \upDelta V,\\
+  \frac{\partial E^\mathrm{I}}{\partial \phi_i} &= \frac{\epsilon}{2} \left[
+    \frac{\partial \abs{\grad \phi_i}^2}{\partial \phi_i} +
+    \sum_k\frac{\partial \abs{\grad \phi_k}^2}{\partial \phi_i} \right] \upDelta V,\\
+  \frac{\partial E^\mathrm{S}}{\partial \phi_j} &= \sqrt{2}\cos\theta_j \left( \frac{{\phi_j}^2}{2} - \frac{1}{2} \right) \upDelta S,\\
+  \frac{\partial E^\mathrm{V}}{\partial \phi_i} &= k_\mathrm{V} \left[ \sum_{i'} \frac{\phi_{i'} + 1}{2} \upDelta V - V_0 \right] \upDelta V,
+\end{align}
+where index $k$ denotes neighboring nodes at which the evaluation of the gradient uses $\phi_i$.
+
 \section{Multiple transition states}
@@
 
+\bibliographystyle{aipnum4-1}
+\bibliography{bibexport.bib}
+% \bibliography{../../../library.bib}
+
 \end{document}

### 2022-06-06 manuscript.tex
Moved methods details back to main paper as appendices

--- 2022-06-04 manuscript.tex
@@
 \title{A fast and memory-efficient transition state search method for complex energy landscapes}
+\date{\today}
 
@@
 \affiliation{Department of Physics, Durham University, South Road, Durham DH1 3LE, UK}
-
-\date{\today}
 
@@
 Furthermore, if all of transition states or the full pathway are desired, BITSS can be continually repeated from one of the minima downhill from the located transition state and one of the initial minima until the initial minima are piecewise connected by a full pathway.
-
-\subsection{Changes for undefined gradients}
-A couple of alterations to the method must be made to account for situations where the gradients are unknown.
-First, the calculation of $\kappa_d$ in \cref{eq:kd} must be adapted to avoid the use of gradients.
-This can be done by simply removing the first term and just using the second term in the equation.
-Secondly, L-BFGS can no longer be used because it requires knowledge of the gradients.
-We must instead use a minimiser that does not require a differentiable optimisation function, for which we use simulated annealing \cite{Kirkpatrick1983}.
-This has a chance of randomly jumping one state over the dividing barrier, but we can reduce this probability by limiting the initial temperature and maximum random displacement.
-We typically employ $T_0 = E_\mathrm{B} / 10$, and $d_\mathrm{max} = d(\bm{x}_1, \bm{x}_2) / 100$.
 
@@
 
+\section*{Supplementary material}
+See the supplementary material for derivations of the expressions of the constraint coefficients in \cref{eq:kd,eq:ke}, and the demonstration of the BITSS method applied to a path with multiple transition states.
+
+\begin{acknowledgments}
+  S.~J.~A. is supported by a studentship from the Engineering and Physical Sciences Research Council [Grant No. EP/R513039/1].
+  H.~K. and J.~R.~P. acknowledge funding from the Engineering and Physical Sciences Research Council [Grant No. EP/V034154/1].
+\end{acknowledgments}
+
+\section*{Conflict of Interest}
+The authors have no conflicts to disclose.
+
+\section*{Author Contributions}
+All authors conceived and planned the project.
+S.~J.~A. performed the numerical experiments and analysed the data.
+J.~R.~P. and H.~K. supervised the study.
+S.~J.~A. wrote the paper, with review and input from and J.~R.~P. and H.~K.
+
+\section*{Data availability}
+The data that support the findings of this study are available from the corresponding author upon reasonable request.
+
 \appendix
-\section*{Methods}
+\section{BITSS: Changes for undefined gradients}
+A couple of alterations to the method must be made to account for situations where the gradients are unknown.
+First, the calculation of $\kappa_d$ in \cref{eq:kd} must be adapted to avoid the use of gradients.
+This can be done by simply removing the first term and just using the second term in the equation.
+Secondly, L-BFGS can no longer be used because it requires knowledge of the gradients.
+We must instead use a minimiser that does not require a differentiable optimisation function, for which we use simulated annealing \cite{Kirkpatrick1983}.
+This has a chance of randomly jumping one state over the dividing barrier, but we can reduce this probability by limiting the initial temperature and maximum random displacement.
+We typically employ $T_0 = E_\mathrm{B} / 10$, and $d_\mathrm{max} = d(\bm{x}_1, \bm{x}_2) / 100$.
 
-\subsection{Adaptive discretisation test details}
+\section{Adaptive discretisation test details}
 Here we provide the details for the interpolations and mapping involved in the two examples demonstrating the feasibility of using an adaptive discretisation method.
 For the cylindrical buckling example with a changing mesh, the resolution is refined each time the separation between the two states has halved, and is performed at the end of each iteration of the BITSS method.
-This involves the number of triangles around the circumference of the cylinder increasing along the sequence: $40 \rightarrow 60 \rightarrow 80 \rightarrow 100$; with the number of degrees of freedom increasing by: $1760 \rightarrow 3960 \rightarrow 7040 \rightarrow 11000$.
+This involves the number of triangles around the circumference of the cylinder increasing along the sequence: $40 \rightarrow 60 \rightarrow 80 \rightarrow 100$; with the number of degrees of freedom increasing by: $\num{1760} \rightarrow \num{3960} \rightarrow \num{7040} \rightarrow \num{11000}$.
 The positions of the nodes on the new grid, $\{\bm{n}_i\}$, are determined by linear interpolation from the previous grid $\{\bm{p}_i\}$, using the positions of the unbuckled meshes, $\{\bm{n'}_i\}$ and $\{\bm{p'}_i\}$.
@@
 
-\subsection{Energy and gradient expressions for the example systems}
-\subsubsection{Particle cluster system}
+\section{Energy and gradient expressions for the example systems}
+\subsection{Particle cluster system}
 In the particle cluster example system, the Lennard-Jones potential is used for the interaction between each pair of particles.
@@
 
-\subsubsection{Cylindrical buckling system}
+\subsection{Cylindrical buckling system}
 A 2D triangular mesh is used to model the cylindrical buckling system, with the ends of the cylinder fixed in place to apply an axial compression of 0.14\%.
@@
 
-\subsubsection{Striped wetting system}
-This modelled on a 200x200 2D grid (and 400x400 in \cref{sec:adaptive}) using a phase-field model \cite{Panter2019b}, which has an order parameter, $\phi(\bm{r})$, representing the phase of the liquid ($\phi=-1$ for gas, $\phi=1$ for liquid).
+\subsection{Striped wetting system}
+This is modelled on a 200x200 2D grid (and 400x400 in \cref{sec:adaptive}) using a phase-field model \cite{Panter2019b}, which has an order parameter, $\phi(\bm{r})$, representing the phase of the liquid ($\phi=-1$ for gas, $\phi=1$ for liquid).
 The energy functional has four separate terms,
@@
 
-\section*{Supplementary material}
-See the supplementary material for derivations of the expressions of the constraint coefficients in \cref{eq:kd,eq:ke}, and the demonstration of the BITSS method applied to a path with multiple transition states.
-
-\begin{acknowledgments}
-  S.~J.~A. is supported by a studentship from the Engineering and Physical Sciences Research Council [Grant No. EP/R513039/1].
-  H.~K. and J.~R.~P. acknowledge funding from the Engineering and Physical Sciences Research Council [Grant No. EP/V034154/1].
-\end{acknowledgments}
-
-\section*{Conflict of Interest}
-The authors have no conflicts to disclose.
-
-\section*{Author Contributions}
-All authors conceived and planned the project.
-S.~J.~A. performed the numerical experiments and analysed the data.
-J.~R.~P. and H.~K. supervised the study.
-S.~J.~A. wrote the paper, with review and input from and J.~R.~P. and H.~K.
-
-\section*{Data availability}
-The data that support the findings of this study are available from the corresponding author upon reasonable request.
-
 %% start bib

### 2022-06-07 fig/make_speedtest/plot.py
Speedtest image width

@@ -8,7 +8,7 @@ import pyutils.latexify as lt
 # Get default style for paper
 import sys; sys.path.insert(0, '..')
 import style
-lt.update_width('natcomm-double')
+lt.update_width('aip-double')
 
 # Data generated by energyLandscapes/bits_test/speed_test/{system}/view_convergence.py
 

### 2022-07-13 manuscript.tex
Reviewer 2 typos

@@
 The two methods most similar to BITSS are the DHS and step and slide methods.
-In the the step and slide method, the separation between two images is minimised while their energy is fixed (iteratively increasing the energy up to the transition state).
+In \temp{the} step and slide method, the separation between two images is minimised while their energy is fixed (iteratively increasing the energy up to the transition state).
 Conversely in the DHS method, the energy of an image is minimised while the image separation is fixed (iteratively decreasing the separation and changing the frozen image up to the transition state).
@@
     (a) Snapshots of the BITSS method for the buckling of a cylinder with a changing mesh.
-        The radial displacement relative the unbuckled cylinder is shown, as well as the underlying triangular mesh.
+        The radial displacement \temp{relative to the} unbuckled cylinder is shown, as well as the underlying triangular mesh.
     (b) Snapshots for the striped wetting example with different resolutions for the two states.

### 2022-07-29 manuscript.tex
Response to reviewers

--- 2022-06-06 manuscript.tex
@@
 \usepackage{enumitem}
+
 \usepackage{xcolor}
+\usepackage{soul}
 
@@
 \graphicspath{{fig/}}
+
+% Table
+\usepackage{multirow}
+% \setlength{\tabcolsep}{4pt}
 
@@
 One key problem arises from the push towards larger and more complex systems \cite{Trefethen2013,Shalf2020,Alexander2020}, resulting in the need to develop algorithms that are more computationally and memory efficient, and can incorporate optimisation strategies such as on-the-fly adaptive remeshing and coarse-graining.
-Chain-of-states methods are not very efficient as they require tens of states to gain an accurate approximation, and they have issues with remeshing due to each state having a different number of degrees of freedom.
-Meanwhile, single-ended methods are not well suited for identifying specific pathways and can spend a large amount of time searching for undesired transition states.
+\hl{These typically involve changing the discretisation of continuous systems to focus the computational time on important regions, for example, using a higher resolution mesh in regions of high stress in finite element simulations {\cite{Lee1994}}.
+However, chain-of-states methods involve a coupling between the configurations of each state, and so there is an issue if they have different discretisations and numbers of degrees of freedom.}
+Meanwhile, single-ended methods can be inefficient because they are not well suited for identifying specific pathways and can spend a large amount of time searching for undesired transition states.
 Another major challenge in studying complex energy landscapes relates to the presence of locally flat or discontinuous regions, such as when considering patchy \cite{McMullen2018,Nguemaha2018,Chen2018b} and hard-body \cite{Richard2018,Santra2018} interactions in atomistic simulations, systems of polymer chains \cite{Mokkonen2016}, or collision constraints for macroscopic objects \cite{Wriggers2006}.
@@
 The two methods most similar to BITSS are the DHS and step and slide methods.
-In the the step and slide method, the separation between two images is minimised while their energy is fixed (iteratively increasing the energy up to the transition state).
+In \hl{the} step and slide method, the separation between two images is minimised while their energy is fixed (iteratively increasing the energy up to the transition state).
 Conversely in the DHS method, the energy of an image is minimised while the image separation is fixed (iteratively decreasing the separation and changing the frozen image up to the transition state).
 To illustrate how BITSS is superior compared to these methods, we consider the hooked 2d potential in \cref{fig:bracketing}.
-This shows that both of these methods fail if the energy of either image ever exceeds the transition state.
+\hl{For this potential the energies of the images ascend higher than that of the transition state and consequently both of these methods fail to converge to the saddle point regardless of the parameters that are used.
+The step and slide method fails in this situation because it always expects that the energy of the two states is below the saddle point if they have not converged, so it has no means of descending down the ridge.
+For DHS, the images reach a certain point at which one state can pass over the ridge by minimising its energy.
+At this point DHS will fail even if the distance is reduced very slowly.}
 In contrast, the BITSS method is successful in this case, showing that it is more reliable when the image pair must descend down a ridge from above.
 
-Furthermore, BITSS has an improved efficiency over these two methods.
+Furthermore, \hl{using both an energy and distance constraint with BITSS provides improved efficiency over these methods which each use just one.}
 In the case of DHS, fixing one state in place and optimising the other means that the amount that the separation is reduced must be much smaller than BITSS to ensure that it does not pass over the ridge.
-Meanwhile, using step and slide, it is difficult to obtain a reasonable energy increment when the two states are far from the transition state, also leading to a larger than necessary number of iterations.
+Meanwhile, in step and slide, it is difficult to obtain a reasonable energy increment when the two states are far from the transition state, leading to a larger than necessary number of iterations.
+\hl{Also, restricting the minimisation to a constant energy surface can result in a considerably more complex method, as the states must be constantly projected back onto this surface.}
 
-\subsection{Speed comparison}
+\subsection{\hl{Comparison with chain-of-states methods}}
 \begin{figure*}[tb]
@@
   \caption{\label{fig:speedtest}
-    Comparisons between BITSS, DNEB, and the string method in the convergence to the transition state as a function of the number of calculations of the energy gradient.
+    Comparisons between BITSS, DNEB, and the string method in the \hl{distance from} the transition state as a function of the number of calculations of the energy gradient.
     Three test systems are used: (a) a Lennard-Jones seven-particle cluster, (b) cylindrical shell buckling, and (c) wetting of a chemically-striped surface.
@@
 
-Although reliable, chain-of-states approaches typically use tens of states.
-As a result of the BITSS method using only two states, it has the potential to be significantly faster.
-This is tested here by measuring the speed of convergence to the transition state for BITSS in comparison with the string method \cite{E2007} and DNEB \cite{Trygubenko2004} using 5, 10, and 20 images for three diverse systems, exhibiting a broad range of energy landscapes.
+Although reliable, chain-of-states approaches \hl{may need to use tens of states for systems if the transition pathway is highly complex or non-linear.
+However, because the BITSS method uses just two states, it has the potential to be significantly faster in these cases.}
+This is tested here by measuring convergence to the transition state for BITSS in comparison with the string method \cite{E2007} and DNEB \cite{Trygubenko2004} using 5, 10, and 20 images \hl{(including the endpoints, which are fixed in place at the minima).
+These methods are often used in conjuction with another method to accurately find the transition state, although we will first examine just the basic methods.
+Three diverse systems are used for this comparison}, exhibiting a broad range of energy landscapes.
 
@@
 
-The parameters used in the chain-of-states methods are also chosen such that they optimise the speed of convergence.
+The parameters used in the chain-of-states methods are chosen such that they optimise the speed of convergence.
 For the string method, this is the number of downhill iterations before the images are redistributed.
@@
 In the case of DNEB, the spring constant between the images is optimised instead.
-For the particle cluster system, a spring constant of $1$ is used for the 5 image case, and $0.1$ for 10 and 20 images.
-For the cylindrical buckling, the spring constant is $0.01$ in all cases.
-And for the striped wetting, $10^{-4}$ is used for 5 and 10 images, and $10^{-3}$ for 20 images.
+\hl{The spring constants that have been used are $0.1$, $0.01$, and $10^{-4}$ for the three respective systems.}
 
-The results for this test, shown in \cref{fig:speedtest}, demonstrate two main advantages for the BITSS method.
-Firstly, the slope illustrates that the rate of convergence is indeed much greater for the BITSS method.
-It is matched only by the initial rates of DNEB and the string method using fewer than ten images, however these soon slow and are relatively inaccurate.
-Secondly, the BITSS method can more accurately approximate the transition state by orders of magnitude, particularly for the wetting example where the other methods do not significantly improve upon the initial pathway estimate.
-Therefore, unlike these chain-of-states methods, BITSS does not require a second approach to accurately locate the transition state.
+\hl{The results in {\cref{fig:speedtest}}, demonstrate one main advantage for the BITSS method: it is able to accurately approximate the transition state without the need for a hybrid method.
+In contrast, the chain-of-states are several orders of magnitude less accurate at obtaining the transition state configuration.
+In particular, in the highly non-linear wetting example they do not significantly improve upon the initial pathway estimate.
+However, it is worth noting that while these do not converge to the transition state, they do converge to the minimum energy pathway (or a close approximation of it).
+This convergence occurs relatively quickly and causes the lines to plateau in {\cref{fig:speedtest}}.}
+
+\hl{To accurately obtain the transition state the chain-of-states methods are often used in conjuction with another method.
+Climbing image hybrid methods {\cite{Henkelman2000a,E2007}} are often used, but if the pathway is non-linear these can require a large number of images.
+Hybrid eigenvector-following methods {\cite{Cerjan1981}} are another commonly used approach, starting from the state with the highest on the chain.
+In this approach the eigenvector with the smallest eigenvalue of the Hessian is found, along which direction the state is then moved uphill until eventually it reaches the transition state.
+For completeness, we also use a hybrid eigenvector-following with BITSS.
+For this we set the criterion for switching to the eigenvector-following based upon the size of the change in the average of the two states over a BITSS step.}
+
+\begin{table}[]
+  \begin{tabular}{ccccccc}
+    \hline\hline
+    \multirow{2}{*}{System} & \multirow{2}{*}{BITSS} &
+    \multirow{2}{*}{\begin{tabular}[c]{@{}c@{}}BITSS-\\HEVF\end{tabular}} &
+    \multicolumn{4}{c}{DNEB-HEVF} \\
+             &             &             & 3           & 5           & 10          & 20          \\
+    \hline
+    LJ-7     & 148         & 140         & 135         & 138         & 208         & 361         \\
+    Wetting  & \num{12100} & \num{15537} & \num{17840} & \num{17721} & \num{20221} & \num{48286} \\
+    \hline\hline
+  \end{tabular}
+  \caption{\label{tab:speed}
+    \hl{
+    Number of potential gradient calculations required to reach the transition state for the Lennard-Jones cluster and the droplet wetting examples.
+    The DNEB hybrid eigenvector-following has been run for different numbers of images.
+    Convergence is determined as when the root-mean-square of the gradient is less than $10^{-4}$.
+    }
+  }
+\end{table}
+
+\hl{We have compared the speed of convergence to the transition state for BITSS, BITSS with hybrid eigenvector-following, and DNEB with hybrid eigenvector-following.
+The results of which are shown in \mbox{\cref{tab:speed}}.
+We see that for these examples, the speed of BITSS with hybrid eigenvector-following does not significantly improve upon the speed of BITSS alone.
+Indeed, for the wetting example it is considerably slower.
+Therefore, it is probably reasonable to use the basic BITSS method for many applications.
+Secondly, it is shown that DNEB with a small number of images is the fastest method for the Lennard-Jones cluster, whereas for the droplet wetting DNEB is considerably slower even with a small number of images.
+This agrees with our expectation that BITSS offers an efficiency advantage for complex pathways.}
 
@@
     (a) Snapshots of the BITSS method for the buckling of a cylinder with a changing mesh.
-        The radial displacement relative the unbuckled cylinder is shown, as well as the underlying triangular mesh.
+        The radial displacement \hl{relative to the} unbuckled cylinder is shown, as well as the underlying triangular mesh.
     (b) Snapshots for the striped wetting example with different resolutions for the two states.
@@
 
+\hl{An additional consideration is the case where the potential energy surface is flat at the top of the pathway.
+There are two possibilities here, one is that the potential is flat in a direction perpendicular to the tangent of the pathway, such that the ridge is level.
+In this case BITSS is unaffected and it will be able to converge to some point along the ridge.
+An example of this is the free global rotation and translation of the Lennard-Jones cluster in {\cref{fig:speedtest}a}.
+The other possibility is that the flat mode is in the direction of the pathway.
+In this case there is no single transition state along the pathway, but instead a region.
+BITSS would be ill suited in this situation because the equal-energy constraint would not prevent the images from passing over the saddle and falling to a minimum.}
+
 Finally, we investigate the application of BITSS to systems with undefined gradients, such as when the landscape is discontinuous.
@@
 
-Throughout, we have demonstrated BITSS as a standalone method for the precise location of transition states.
-However, hybrid methods may also be employed to further increase speed and efficiency.
-Either BITSS could be used to approximately locate the transition state followed by a single ended method for refinement, or BITSS can be used as a refinement method, complimentary to existing chain of states implementations.
-This is scope for possible future work, and could be compared against other existing hybrid methods.
+% Throughout, we have demonstrated BITSS as a standalone method for the precise location of transition states.
+% However, hybrid methods may also be employed to further increase speed and efficiency.
+% Either BITSS could be used to approximately locate the transition state followed by a single ended method for refinement, or BITSS can be used as a refinement method, complimentary to existing chain of states implementations.
+% This is scope for possible future work, and could be compared against other existing hybrid methods.
 

### 2022-07-29 fig/make_bracketing/plot.py

@@ -66,7 +66,7 @@ def plot(minima, ts, paths, mep):
     plt.plot(minima[:,0], minima[:,1], c=cmin, marker='o', mec=mec, ms=ms, ls='none', zorder=99)
     plt.plot(ts[0], ts[1], c=cts, marker='o', mec=mec, ms=ms, ls='none', zorder=99)
     # Plot path
-    labels = ['BITSS', 'Step \& Slide', 'DHS']
+    labels = ['BITSS', 'DHS', 'Step \& Slide']
     for i, path in enumerate(paths):
         plt.plot(path[0,:,0], path[0,:,1], c=cpath[i], zorder=2, label=labels[i])
         plt.plot(path[1,:,0], path[1,:,1], c=cpath[i], zorder=2)
@@ -85,7 +85,7 @@ def main():
     minima = bits[:,0]
     ts = np.mean(bits[:,-1], axis=0)
 
-    plot(minima, ts, [bits, ss, dhs], mep)
+    plot(minima, ts, [bits, dhs, ss], mep)
 
 if (__name__ == "__main__"):
     main()

### 2022-07-30 manuscript.tex
Jack and Halim's changes

@@
     The minimum energy pathway is shown by the dashed line.
+    {\color{green}Sam, can you put the equation for this landscape in the methods section? }
   }
@@
 
-The two methods most similar to BITSS are the DHS and step and slide methods.
+The two methods most similar to BITSS are the DHS \cite{Dewar1984} and step and slide \cite{Miron2001} methods.
 In \hl{the} step and slide method, the separation between two images is minimised while their energy is fixed (iteratively increasing the energy up to the transition state).
@@
 For DHS, the images reach a certain point at which one state can pass over the ridge by minimising its energy.
-At this point DHS will fail even if the distance is reduced very slowly.}
-In contrast, the BITSS method is successful in this case, showing that it is more reliable when the image pair must descend down a ridge from above.
+At this point DHS will fail even if the distance is reduced very slowly.
+In contrast, the BITSS method is successful for this potential.
+This is because the combination of distance and energy constraints allow BITSS to approach a transition state from below and above (by sliding down a ridge).}
 
@@
 Although reliable, chain-of-states approaches \hl{may need to use tens of states for systems if the transition pathway is highly complex or non-linear.
-However, because the BITSS method uses just two states, it has the potential to be significantly faster in these cases.}
-This is tested here by measuring convergence to the transition state for BITSS in comparison with the string method \cite{E2007} and DNEB \cite{Trygubenko2004} using 5, 10, and 20 images \hl{(including the endpoints, which are fixed in place at the minima).
-These methods are often used in conjuction with another method to accurately find the transition state, although we will first examine just the basic methods.
-Three diverse systems are used for this comparison}, exhibiting a broad range of energy landscapes.
+However, because the BITSS method uses just two states, it has the potential to be more efficient in these cases.
+This is analysed here in two ways.
+First, we measure how quickly BITSS reduces the distance to the transition state, compared to the string method {\cite{E2007}} and DNEB {\cite{Trygubenko2004}} using 5, 10, and 20 images (including the endpoints, which are fixed in place at the minima).
+Second, these methods are often used in conjunction with another method to accurately find the transition state.
+Here we compare the number of potential gradient calculations required to reach the transition state for BITSS, BITSS in combination with hybrid eigenvector-following, and DNEB in combination with hybrid eigenvector-following.
 
+Three diverse systems are used for this comparison, exhibiting a broad range of energy landscapes.}
 The first system is a two-dimensional, seven-particle cluster, interacting via a Lennard-Jones pair potential.
@@
 
-Convergence is measured using the distance from the transition state.
+\hl{{\Cref{fig:speedtest}} shows the comparison between BITSS, DNEB and the string method.
+Here, the $x$-axis corresponds to the number of calculations of the potential gradient.
+The measure in the $y$-axis is the distance from the true transition state.}
 For BITSS, the average of the two states is used for this, whereas for the chain-of-states methods, the closest point on a cubic spline interpolation is used.
-The speed of this convergence is evaluated through comparison with the number of calculations of the potential gradient for a single state.
-
 The parameters used in the chain-of-states methods are chosen such that they optimise the speed of convergence.
 For the string method, this is the number of downhill iterations before the images are redistributed.
-For which, the optimal values are found to be 2, 50, and 20 for the particle cluster, cylindrical buckling, and striped wetting examples, respectively.
+The optimal values are found to be 2, 50, and 20 for the particle cluster, cylindrical buckling, and striped wetting examples, respectively.
 In the case of DNEB, the spring constant between the images is optimised instead.
@@
 
-\hl{The results in {\cref{fig:speedtest}}, demonstrate one main advantage for the BITSS method: it is able to accurately approximate the transition state without the need for a hybrid method.
-In contrast, the chain-of-states are several orders of magnitude less accurate at obtaining the transition state configuration.
-In particular, in the highly non-linear wetting example they do not significantly improve upon the initial pathway estimate.
-However, it is worth noting that while these do not converge to the transition state, they do converge to the minimum energy pathway (or a close approximation of it).
-This convergence occurs relatively quickly and causes the lines to plateau in {\cref{fig:speedtest}}.}
+\hl{In {\cref{fig:speedtest}}, for each system, BITSS quickly converges to the transition state.
+In contrast, DNEB and the string method converge quickly to an approximation of the minimum energy pathway.
+However, as the images are spaced along the chain of states, it is unlikely that they closely approach the transition state.
+It is interesting to note that for the high-dimensional, non-linear pathways of wetting example shown in {\cref{fig:speedtest}}c, DNEB and the string method to not substantially reduce the distance to the transition state compared to the initial interpolation.}
 
-\hl{To accurately obtain the transition state the chain-of-states methods are often used in conjuction with another method.
-Climbing image hybrid methods {\cite{Henkelman2000a,E2007}} are often used, but if the pathway is non-linear these can require a large number of images.
-Hybrid eigenvector-following methods {\cite{Cerjan1981}} are another commonly used approach, starting from the state with the highest on the chain.
+\hl{To accurately obtain the transition state, the chain-of-states methods are often used in conjuction with another refinement method.
+One common set of methods are the climbing image hybrid methods {\cite{Henkelman2000a,E2007}}, but if the pathway is non-linear these can require a large number of images.
+For example, in the wetting example of {\cref{fig:speedtest}}c, we find even an 100-image initial double-ended search is not sufficient for the climbing image method to then successfully refine the transition state.
+Hybrid eigenvector-following methods {\cite{Cerjan1981}} are another commonly used approach, starting from the state with the highest energy on the chain.
 In this approach the eigenvector with the smallest eigenvalue of the Hessian is found, along which direction the state is then moved uphill until eventually it reaches the transition state.
-For completeness, we also use a hybrid eigenvector-following with BITSS.
-For this we set the criterion for switching to the eigenvector-following based upon the size of the change in the average of the two states over a BITSS step.}
+For completeness, we also use a hybrid method combining eigenvector-following with BITSS.
+For this, the criterion for switching to the eigenvector-following is when the change in the average of the two states is less than half of the distance reduction during a BITSS step.}
 
@@
     Number of potential gradient calculations required to reach the transition state for the Lennard-Jones cluster and the droplet wetting examples.
-    The DNEB hybrid eigenvector-following has been run for different numbers of images.
-    Convergence is determined as when the root-mean-square of the gradient is less than $10^{-4}$.
-    }
+    The approach combining DNEB and hybrid eigenvector-following (HEVF) has been run for different numbers of images.
+    Convergence is determined as when the root-mean-square of the gradient is less than $10^{-4}$.} {\color{green} Need to add the buckling result.}
   }
@@
 
-\hl{We have compared the speed of convergence to the transition state for BITSS, BITSS with hybrid eigenvector-following, and DNEB with hybrid eigenvector-following.
-The results of which are shown in \mbox{\cref{tab:speed}}.
-We see that for these examples, the speed of BITSS with hybrid eigenvector-following does not significantly improve upon the speed of BITSS alone.
-Indeed, for the wetting example it is considerably slower.
-Therefore, it is probably reasonable to use the basic BITSS method for many applications.
-Secondly, it is shown that DNEB with a small number of images is the fastest method for the Lennard-Jones cluster, whereas for the droplet wetting DNEB is considerably slower even with a small number of images.
-This agrees with our expectation that BITSS offers an efficiency advantage for complex pathways.}
+\hl{In \mbox{\cref{tab:speed}}, we compare the speed of convergence to the transition state for BITSS, BITSS with hybrid eigenvector-following, and DNEB with hybrid eigenvector-following.
+We do not carry out systematic calculations combining the string method with hybrid eigenvector-following because the results are essentially similar to those for DNEB with hybrid eigenvector-following.
+We see that, for the examples in \mbox{\cref{tab:speed}}, the speed of BITSS with hybrid eigenvector-following does not significantly improve upon the speed of BITSS alone.
+Indeed, for the wetting example it is considerably slower.}
+{\color{green}Secondly, it is shown that DNEB with a small number of images is the fastest method for the Lennard-Jones cluster, whereas for the droplet wetting DNEB is considerably slower, even with a small number of images.
+This agrees with our expectation that BITSS offers an efficiency advantage for complex pathways.
+WE NEED TO UPDATE THIS DISCUSSION WHEN WE HAVE THE BUCKLING RESULT.}
 
@@
 In such cases, it may be possible to access transition states different from the most direct one by using a biased distance metric.
-Overall, these will enable BITSS to access even more challenging landscapes, and those not yet amenable to traditional landscape exploration techniques.
+\hl{A further investigation that is now open to pursue, is when discontinuities in the landscape occur at `stationary points' (now properly referred to as critical points).
+In this case, a transition state can no longer be defined by its Hessian eigenvalues, but instead is more broadly defined as a region of locally minimal energy that separates two basins of attraction to minima.
+Overall, it will be interesting to explore how BITSS enables access to even more challenging landscapes, and those not yet amenable to traditional landscape exploration techniques.}
 

### 2022-08-02 manuscript.tex
Buckling speedtest and hook potential equation

@@
 \usepackage{multirow}
-% \setlength{\tabcolsep}{4pt}
+\setlength{\tabcolsep}{4pt}
 
@@
     Trajectories of the bracketing methods on a hooked potential with a single saddle point.
+    \hl{The equation for this potential is provided in \mbox{\cref{sec:bracketingpotential}}.}
     The minimum energy pathway is shown by the dashed line.
-    {\color{green}Sam, can you put the equation for this landscape in the methods section? }
   }
@@
 In contrast, the BITSS method is successful for this potential.
-This is because the combination of distance and energy constraints allow BITSS to approach a transition state from below and above (by sliding down a ridge).}
+This is because the combination of distance and energy constraints allow BITSS to approach a transition state from both below and above (by sliding down a ridge).}
 
@@
 Here, the system is represented by a diffuse-interface model, in which the \num{40000} degrees of freedom are the local fluid compositions at each site of the discretised domain.
+\hl{The pathway for this example is highly non-linear in the coordinate space because each degree of freedom only varies when it is at the interface of the droplet.
+As a result, the initial pathway for the chain of states methods cannot be a simple linear interpolation.
+Instead, the position of a semi-circular droplet is interpolated between the two final positions.}
 
@@
 However, as the images are spaced along the chain of states, it is unlikely that they closely approach the transition state.
-It is interesting to note that for the high-dimensional, non-linear pathways of wetting example shown in {\cref{fig:speedtest}}c, DNEB and the string method to not substantially reduce the distance to the transition state compared to the initial interpolation.}
+It is interesting to note that for the high-dimensional, non-linear pathways of wetting example shown in {\cref{fig:speedtest}}c, DNEB and the string method do not substantially reduce the distance to the transition state compared to the initial interpolation.}
 
@@
 For completeness, we also use a hybrid method combining eigenvector-following with BITSS.
-For this, the criterion for switching to the eigenvector-following is when the change in the average of the two states is less than half of the distance reduction during a BITSS step.}
+For this, the criterion for switching to the eigenvector-following is when the change in the average of the two states is less than a tenth of the distance reduction during a BITSS step.}
 
-\begin{table}[]
-  \begin{tabular}{ccccccc}
+\begin{table}[h]
+  \begin{tabular*}{\linewidth}{c@{\extracolsep{\fill}}cccccc}
     \hline\hline
@@
     \hline
-    LJ-7     & 148         & 140         & 135         & 138         & 208         & 361         \\
-    Wetting  & \num{12100} & \num{15537} & \num{17840} & \num{17721} & \num{20221} & \num{48286} \\
+    LJ-7     & 148         & 144         & 135         & 138         & 208         & 361         \\
+    Buckling & \num{12866} & \num{14446} & ---         & \num{7315}  & \num{6242}  & \num{12094} \\
+    Wetting  & \num{12100} & \num{17262} & \num{17840} & \num{17721} & \num{20221} & \num{48286} \\
     \hline\hline
-  \end{tabular}
+  \end{tabular*}
   \caption{\label{tab:speed}
     \hl{
-    Number of potential gradient calculations required to reach the transition state for the Lennard-Jones cluster and the droplet wetting examples.
+    Number of potential gradient calculations required to reach the transition state for the three comparison examples.
     The approach combining DNEB and hybrid eigenvector-following (HEVF) has been run for different numbers of images.
-    Convergence is determined as when the root-mean-square of the gradient is less than $10^{-4}$.} {\color{green} Need to add the buckling result.}
+    Convergence is determined as when the root-mean-square of the gradient is less than $10^{-4}$.}
   }
@@
 We see that, for the examples in \mbox{\cref{tab:speed}}, the speed of BITSS with hybrid eigenvector-following does not significantly improve upon the speed of BITSS alone.
-Indeed, for the wetting example it is considerably slower.}
-{\color{green}Secondly, it is shown that DNEB with a small number of images is the fastest method for the Lennard-Jones cluster, whereas for the droplet wetting DNEB is considerably slower, even with a small number of images.
-This agrees with our expectation that BITSS offers an efficiency advantage for complex pathways.
-WE NEED TO UPDATE THIS DISCUSSION WHEN WE HAVE THE BUCKLING RESULT.}
+Indeed, for the wetting example it is considerably slower.
+Secondly, it is shown that DNEB with a small number of images is the fastest method for the Lennard-Jones cluster, and an intermediate number of images is optimal for the buckling because if there are too few images it will not converge to the correct transition state.
+On the other hand, for the droplet wetting DNEB is considerably slower, even with a small number of images.
+This is in agreement with our expectation that BITSS offers an efficiency advantage for complex pathways.}
 
@@
 \section{Energy and gradient expressions for the example systems}
+\subsection{Hook potential equation}\label{sec:bracketingpotential}
+\hl{
+The 2D potential used for the comparison of bracketing methods in {\cref{fig:bracketing}} uses a sum of Gaussian potentials, {\cref{eq:bracketingparams}}, the parameters for which are provided in \mbox{\cref{tab:bracketingparams}}.
+}
+\begin{equation}
+  E(x,y) = \sum_i a_i \exp\!\left( \frac{(x-b_{x,i})^2}{c_{x,i}} + \frac{(y-b_{y,i})^2}{c_{y,i}} \right)
+  \label{eq:bracketingparams}
+\end{equation}
+\begin{table}[ht]
+  \begin{tabular}{ccccc}
+    \hline\hline
+    $a$  & $b_x$ & $b_x$ & $c_x$ & $c_y$ \\
+    \hline
+    -1   &   0   &   0   &  10   &  10   \\
+     1   &   0   &   0   &   1   &   1   \\
+     5   &   2   &   0   &   1   &  0.1  \\
+    -1   &   1   &   1   &  0.1  &  0.1  \\
+    -1   &   1   &  -1   &  0.1  &  0.1  \\
+    0.01 &   0   &   0   &   1   &   1   \\
+    0.5  &  -2   &   0   &   1   &   1   \\
+    \hline\hline
+  \end{tabular}
+  \caption{\label{tab:bracketingparams}
+    Parameters for the Gaussians to produce the potential used in \cref{fig:bracketing}.
+  }
+\end{table}
+
 \subsection{Particle cluster system}

### 2022-08-02 manuscript.tex
Halim's changes

@@
   It uses just two states that converge to the transition state, resulting in a fast, flexible, and memory-efficient method.
+  \hl{We also snow it is more robust compared to existing bracketing methods that use only two states.}
   We demonstrate its versatility by applying BITSS to three very different classes of problems: Lennard-Jones clusters, shell buckling, and multiphase phase-field models.
@@
 One key problem arises from the push towards larger and more complex systems \cite{Trefethen2013,Shalf2020,Alexander2020}, resulting in the need to develop algorithms that are more computationally and memory efficient, and can incorporate optimisation strategies such as on-the-fly adaptive remeshing and coarse-graining.
-\hl{These typically involve changing the discretisation of continuous systems to focus the computational time on important regions, for example, using a higher resolution mesh in regions of high stress in finite element simulations {\cite{Lee1994}}.
+\hl{These typically involve changing the resolution or discretisation of the systems to focus the computational time on important regions, such as using a higher resolution mesh in regions of high stress in finite element simulations {\cite{Lee1994}}.
 However, chain-of-states methods involve a coupling between the configurations of each state, and so there is an issue if they have different discretisations and numbers of degrees of freedom.}
@@
 
-Furthermore, \hl{using both an energy and distance constraint with BITSS provides improved efficiency over these methods which each use just one.}
+Furthermore, \hl{using both an energy and distance constraint with BITSS provides improved efficiency over these methods which each use just one of the constraints.}
 In the case of DHS, fixing one state in place and optimising the other means that the amount that the separation is reduced must be much smaller than BITSS to ensure that it does not pass over the ridge.
@@
 
-Although reliable, chain-of-states approaches \hl{may need to use tens of states for systems if the transition pathway is highly complex or non-linear.
-However, because the BITSS method uses just two states, it has the potential to be more efficient in these cases.
+Although reliable, chain-of-states approaches \hl{may need to use a large number of states in cases where the transition pathway is highly complex or non-linear.
+Since the BITSS method uses just two states, it has the potential to be more efficient in these cases.
 This is analysed here in two ways.
@@
 As a result, the initial pathway for the chain of states methods cannot be a simple linear interpolation.
-Instead, the position of a semi-circular droplet is interpolated between the two final positions.}
+Instead, the position of a semi-circular droplet is interpolated between the two final positions.
+In contrast, it is unneccessary to assume any initial interpolations for the BITSS method.}
 
@@
 For example, in the wetting example of {\cref{fig:speedtest}}c, we find even an 100-image initial double-ended search is not sufficient for the climbing image method to then successfully refine the transition state.
-Hybrid eigenvector-following methods {\cite{Cerjan1981}} are another commonly used approach, starting from the state with the highest energy on the chain.
+Hybrid eigenvector-following (HEVF) methods {\cite{Cerjan1981}} are another commonly used approach, starting from the state with the highest energy on the chain.
 In this approach the eigenvector with the smallest eigenvalue of the Hessian is found, along which direction the state is then moved uphill until eventually it reaches the transition state.
@@
 Indeed, for the wetting example it is considerably slower.
-Secondly, it is shown that DNEB with a small number of images is the fastest method for the Lennard-Jones cluster, and an intermediate number of images is optimal for the buckling because if there are too few images it will not converge to the correct transition state.
-On the other hand, for the droplet wetting DNEB is considerably slower, even with a small number of images.
-This is in agreement with our expectation that BITSS offers an efficiency advantage for complex pathways.}
+Secondly, when the pathways are near-linear, the combination of DNEB and HEVF leads to the fastest convergence.
+For the Lennard-Jones cluster a small number of images is the most efficient, while an intermediate number of images is optimal for the buckling problem because it will not converge to the correct transition state if there are too few images.
+On the other hand, for the droplet wetting example, DNEB-HEVF is considerably slower, even with a small number of images.
+This is in agreement with our expectation that BITSS offers an efficiency advantage for complex, non-linear pathways.}
 
@@
 This has distinct advantages for complex pathways owing to the lack of a required initial pathway estimate, as well as the identification of the transition state that provides the overall energy barrier in multi-step pathways.
-Furthermore, the demonstrated speed and memory-efficiency will be key as we move towards simulating systems with increasingly large numbers of degrees of freedom, such as in large biomolecules \cite{Lee2018}, or with increasingly fine resolution, such as in finite element domains \cite{Kolev2021}.
+\hl{From the speed analysis, we find that the combination of chain-of-states methods with single-ended transition state search methods provides good performance for near-linear pathways, such as for the Lennard-Jones cluster and cylindrical buckling.
+However, for highly complex and non-linear pathways, as exhibited by the striped wetting example, BITSS is superior.
+Indeed, the demonstrated speed and memory-efficiency will be key as we move towards studying larger and more complex systems using BITSS.}
 
@@
 
-The distance metric between the two BITSS images also proves interesting to analyse further.
+The distance metric between the two BITSS images is interesting to analyse further.
 One question that emerges is whether transition states can be located by coupling two images through a small number of collective properties, rather than the total distance between all degrees of freedom in the system.

### 2022-08-03 manuscript.tex
Text about buckling being linear

@@
   It uses just two states that converge to the transition state, resulting in a fast, flexible, and memory-efficient method.
-  \hl{We also snow it is more robust compared to existing bracketing methods that use only two states.}
+  \hl{We also show it is more robust compared to existing bracketing methods that use only two states.}
   We demonstrate its versatility by applying BITSS to three very different classes of problems: Lennard-Jones clusters, shell buckling, and multiphase phase-field models.
@@
 The two methods most similar to BITSS are the DHS \cite{Dewar1984} and step and slide \cite{Miron2001} methods.
-In \hl{the} step and slide method, the separation between two images is minimised while their energy is fixed (iteratively increasing the energy up to the transition state).
+In the step and slide method, the separation between two images is minimised while their energy is fixed (iteratively increasing the energy up to the transition state).
 Conversely in the DHS method, the energy of an image is minimised while the image separation is fixed (iteratively decreasing the separation and changing the frozen image up to the transition state).
@@
   \caption{\label{fig:speedtest}
-    Comparisons between BITSS, DNEB, and the string method in the \hl{distance from} the transition state as a function of the number of calculations of the energy gradient.
+    Comparisons between BITSS, DNEB, and the string method in the distance from the transition state as a function of the number of calculations of the energy gradient.
     Three test systems are used: (a) a Lennard-Jones seven-particle cluster, (b) cylindrical shell buckling, and (c) wetting of a chemically-striped surface.
@@
 Instead, the position of a semi-circular droplet is interpolated between the two final positions.
-In contrast, it is unneccessary to assume any initial interpolations for the BITSS method.}
+In contrast, it is unnecessary to assume any initial interpolation for the BITSS method.}
 
@@
 In the case of DNEB, the spring constant between the images is optimised instead.
-\hl{The spring constants that have been used are $0.1$, $0.01$, and $10^{-4}$ for the three respective systems.}
+\hl{The spring constants that have been used are $0.1$, $0.01$, and $10^{-4}$ for the three respective systems.
 
-\hl{In {\cref{fig:speedtest}}, for each system, BITSS quickly converges to the transition state.
+In {\cref{fig:speedtest}}, for each system, BITSS quickly converges to the transition state.
 In contrast, DNEB and the string method converge quickly to an approximation of the minimum energy pathway.
 However, as the images are spaced along the chain of states, it is unlikely that they closely approach the transition state.
-It is interesting to note that for the high-dimensional, non-linear pathways of wetting example shown in {\cref{fig:speedtest}}c, DNEB and the string method do not substantially reduce the distance to the transition state compared to the initial interpolation.}
+It is interesting to note that for the high-dimensional, non-linear pathways of wetting example shown in {\cref{fig:speedtest}}c, DNEB and the string method do not substantially reduce the distance to the transition state compared to the initial interpolation.
 
-\hl{To accurately obtain the transition state, the chain-of-states methods are often used in conjuction with another refinement method.
+To accurately obtain the transition state, the chain-of-states methods are often used in conjunction with another refinement method.
 One common set of methods are the climbing image hybrid methods {\cite{Henkelman2000a,E2007}}, but if the pathway is non-linear these can require a large number of images.
@@
 
-\begin{table}[h]
+\begin{table}[ht]
   \begin{tabular*}{\linewidth}{c@{\extracolsep{\fill}}cccccc}
@@
 Secondly, when the pathways are near-linear, the combination of DNEB and HEVF leads to the fastest convergence.
-For the Lennard-Jones cluster a small number of images is the most efficient, while an intermediate number of images is optimal for the buckling problem because it will not converge to the correct transition state if there are too few images.
+For the Lennard-Jones cluster, a small number of images is the most efficient, while an intermediate number of images is optimal for the buckling problem because it will not converge to the correct transition state if there are too few images.
+Despite the large number of degrees of freedom, this buckling mode in {\cref{fig:speedtest}}c is known to exhibit a linear pathway close to the transition state, being controlled simply by the dimple depth increasing{\cite{Panter2019}}.
 On the other hand, for the droplet wetting example, DNEB-HEVF is considerably slower, even with a small number of images.
@@
     (a) Snapshots of the BITSS method for the buckling of a cylinder with a changing mesh.
-        The radial displacement \hl{relative to the} unbuckled cylinder is shown, as well as the underlying triangular mesh.
+        The radial displacement relative to the unbuckled cylinder is shown, as well as the underlying triangular mesh.
     (b) Snapshots for the striped wetting example with different resolutions for the two states.
@@
 In such cases, it may be possible to access transition states different from the most direct one by using a biased distance metric.
-\hl{A further investigation that is now open to pursue, is when discontinuities in the landscape occur at `stationary points' (now properly referred to as critical points).
+\hl{A further investigation that is now open to pursue is when discontinuities in the landscape occur at `stationary points' (now properly referred to as critical points).
 In this case, a transition state can no longer be defined by its Hessian eigenvalues, but instead is more broadly defined as a region of locally minimal energy that separates two basins of attraction to minima.
@@
 \section{Energy and gradient expressions for the example systems}
-\subsection{Hook potential equation}\label{sec:bracketingpotential}
+\subsection{\hl{Hook potential equation}}\label{sec:bracketingpotential}
 \hl{
@@
   \caption{\label{tab:bracketingparams}
-    Parameters for the Gaussians to produce the potential used in \cref{fig:bracketing}.
+  \hl{
+    Parameters for the Gaussians to produce the potential used in {\cref{fig:bracketing}}.
+  }
   }

### 2022-08-03 fig/make_toy2d/plot.py
Toy2D resolution and ruled tables

@@ -61,7 +61,7 @@ fig = plt.figure(frameon=False, figsize=(xlim[1]-xlim[0], ylim[1]-ylim[0]))
 ax = fig.add_axes([0,0,1,1])
 plt.contourf(x, y, e, cmap=cmap, levels=10)
 ax.axis('off')
-plt.savefig(f'potential.png')
+plt.savefig(f'potential.png', dpi=500)
 
 
 ### Read data

### 2022-08-03 manuscript.tex
Toy2D resolution and ruled tables
Changed title
Removed markup

@@
 \usepackage{multirow}
-\setlength{\tabcolsep}{4pt}
+% \setlength{\tabcolsep}{4pt}
 
@@
 \begin{document}
-\title{A fast and memory-efficient transition state search method for complex energy landscapes}
+\title{A robust and memory-efficient transition state search method for complex energy landscapes}
 \date{\today}
@@
   It uses just two states that converge to the transition state, resulting in a fast, flexible, and memory-efficient method.
-  \hl{We also show it is more robust compared to existing bracketing methods that use only two states.}
+  We also show it is more robust compared to existing bracketing methods that use only two states.
   We demonstrate its versatility by applying BITSS to three very different classes of problems: Lennard-Jones clusters, shell buckling, and multiphase phase-field models.
@@
 One key problem arises from the push towards larger and more complex systems \cite{Trefethen2013,Shalf2020,Alexander2020}, resulting in the need to develop algorithms that are more computationally and memory efficient, and can incorporate optimisation strategies such as on-the-fly adaptive remeshing and coarse-graining.
-\hl{These typically involve changing the resolution or discretisation of the systems to focus the computational time on important regions, such as using a higher resolution mesh in regions of high stress in finite element simulations {\cite{Lee1994}}.
-However, chain-of-states methods involve a coupling between the configurations of each state, and so there is an issue if they have different discretisations and numbers of degrees of freedom.}
+These typically involve changing the resolution or discretisation of the systems to focus the computational time on important regions, such as using a higher resolution mesh in regions of high stress in finite element simulations \cite{Lee1994}.
+However, chain-of-states methods involve a coupling between the configurations of each state, and so there is an issue if they have different discretisations and numbers of degrees of freedom.
 Meanwhile, single-ended methods can be inefficient because they are not well suited for identifying specific pathways and can spend a large amount of time searching for undesired transition states.
@@
     Trajectories of the bracketing methods on a hooked potential with a single saddle point.
-    \hl{The equation for this potential is provided in \mbox{\cref{sec:bracketingpotential}}.}
+    The equation for this potential is provided in \cref{sec:bracketingpotential}.
     The minimum energy pathway is shown by the dashed line.
@@
 To illustrate how BITSS is superior compared to these methods, we consider the hooked 2d potential in \cref{fig:bracketing}.
-\hl{For this potential the energies of the images ascend higher than that of the transition state and consequently both of these methods fail to converge to the saddle point regardless of the parameters that are used.
+For this potential the energies of the images ascend higher than that of the transition state and consequently both of these methods fail to converge to the saddle point regardless of the parameters that are used.
 The step and slide method fails in this situation because it always expects that the energy of the two states is below the saddle point if they have not converged, so it has no means of descending down the ridge.
@@
 In contrast, the BITSS method is successful for this potential.
-This is because the combination of distance and energy constraints allow BITSS to approach a transition state from both below and above (by sliding down a ridge).}
+This is because the combination of distance and energy constraints allow BITSS to approach a transition state from both below and above (by sliding down a ridge).
 
-Furthermore, \hl{using both an energy and distance constraint with BITSS provides improved efficiency over these methods which each use just one of the constraints.}
+Furthermore, using both an energy and distance constraint with BITSS provides improved efficiency over these methods which each use just one of the constraints.
 In the case of DHS, fixing one state in place and optimising the other means that the amount that the separation is reduced must be much smaller than BITSS to ensure that it does not pass over the ridge.
 Meanwhile, in step and slide, it is difficult to obtain a reasonable energy increment when the two states are far from the transition state, leading to a larger than necessary number of iterations.
-\hl{Also, restricting the minimisation to a constant energy surface can result in a considerably more complex method, as the states must be constantly projected back onto this surface.}
+Also, restricting the minimisation to a constant energy surface can result in a considerably more complex method, as the states must be constantly projected back onto this surface.
 
-\subsection{\hl{Comparison with chain-of-states methods}}
+\subsection{Comparison with chain-of-states methods}
 \begin{figure*}[tb]
@@
 
-Although reliable, chain-of-states approaches \hl{may need to use a large number of states in cases where the transition pathway is highly complex or non-linear.
+Although reliable, chain-of-states approaches may need to use a large number of states in cases where the transition pathway is highly complex or non-linear.
 Since the BITSS method uses just two states, it has the potential to be more efficient in these cases.
 This is analysed here in two ways.
-First, we measure how quickly BITSS reduces the distance to the transition state, compared to the string method {\cite{E2007}} and DNEB {\cite{Trygubenko2004}} using 5, 10, and 20 images (including the endpoints, which are fixed in place at the minima).
+First, we measure how quickly BITSS reduces the distance to the transition state, compared to the string method \cite{E2007} and DNEB \cite{Trygubenko2004} using 5, 10, and 20 images (including the endpoints, which are fixed in place at the minima).
 Second, these methods are often used in conjunction with another method to accurately find the transition state.
@@
 
-Three diverse systems are used for this comparison, exhibiting a broad range of energy landscapes.}
+Three diverse systems are used for this comparison, exhibiting a broad range of energy landscapes.
 The first system is a two-dimensional, seven-particle cluster, interacting via a Lennard-Jones pair potential.
@@
 Here, the system is represented by a diffuse-interface model, in which the \num{40000} degrees of freedom are the local fluid compositions at each site of the discretised domain.
-\hl{The pathway for this example is highly non-linear in the coordinate space because each degree of freedom only varies when it is at the interface of the droplet.
+The pathway for this example is highly non-linear in the coordinate space because each degree of freedom only varies when it is at the interface of the droplet.
 As a result, the initial pathway for the chain of states methods cannot be a simple linear interpolation.
 Instead, the position of a semi-circular droplet is interpolated between the two final positions.
-In contrast, it is unnecessary to assume any initial interpolation for the BITSS method.}
+In contrast, it is unnecessary to assume any initial interpolation for the BITSS method.
 
-\hl{{\Cref{fig:speedtest}} shows the comparison between BITSS, DNEB and the string method.
+{\Cref{fig:speedtest}} shows the comparison between BITSS, DNEB and the string method.
 Here, the $x$-axis corresponds to the number of calculations of the potential gradient.
-The measure in the $y$-axis is the distance from the true transition state.}
+The measure in the $y$-axis is the distance from the true transition state.
 For BITSS, the average of the two states is used for this, whereas for the chain-of-states methods, the closest point on a cubic spline interpolation is used.
@@
 In the case of DNEB, the spring constant between the images is optimised instead.
-\hl{The spring constants that have been used are $0.1$, $0.01$, and $10^{-4}$ for the three respective systems.
+The spring constants that have been used are $0.1$, $0.01$, and $10^{-4}$ for the three respective systems.
 
-In {\cref{fig:speedtest}}, for each system, BITSS quickly converges to the transition state.
+In \cref{fig:speedtest}, for each system, BITSS quickly converges to the transition state.
 In contrast, DNEB and the string method converge quickly to an approximation of the minimum energy pathway.
 However, as the images are spaced along the chain of states, it is unlikely that they closely approach the transition state.
-It is interesting to note that for the high-dimensional, non-linear pathways of wetting example shown in {\cref{fig:speedtest}}c, DNEB and the string method do not substantially reduce the distance to the transition state compared to the initial interpolation.
+It is interesting to note that for the high-dimensional, non-linear pathways of wetting example shown in \cref{fig:speedtest}c, DNEB and the string method do not substantially reduce the distance to the transition state compared to the initial interpolation.
 
 To accurately obtain the transition state, the chain-of-states methods are often used in conjunction with another refinement method.
-One common set of methods are the climbing image hybrid methods {\cite{Henkelman2000a,E2007}}, but if the pathway is non-linear these can require a large number of images.
-For example, in the wetting example of {\cref{fig:speedtest}}c, we find even an 100-image initial double-ended search is not sufficient for the climbing image method to then successfully refine the transition state.
-Hybrid eigenvector-following (HEVF) methods {\cite{Cerjan1981}} are another commonly used approach, starting from the state with the highest energy on the chain.
+One common set of methods are the climbing image hybrid methods \cite{Henkelman2000a,E2007}, but if the pathway is non-linear these can require a large number of images.
+For example, in the wetting example of \cref{fig:speedtest}c, we find even an 100-image initial double-ended search is not sufficient for the climbing image method to then successfully refine the transition state.
+Hybrid eigenvector-following (HEVF) methods \cite{Cerjan1981} are another commonly used approach, starting from the state with the highest energy on the chain.
 In this approach the eigenvector with the smallest eigenvalue of the Hessian is found, along which direction the state is then moved uphill until eventually it reaches the transition state.
 For completeness, we also use a hybrid method combining eigenvector-following with BITSS.
-For this, the criterion for switching to the eigenvector-following is when the change in the average of the two states is less than a tenth of the distance reduction during a BITSS step.}
+For this, the criterion for switching to the eigenvector-following is when the change in the average of the two states is less than a tenth of the distance reduction during a BITSS step.
 
 \begin{table}[ht]
-  \begin{tabular*}{\linewidth}{c@{\extracolsep{\fill}}cccccc}
-    \hline\hline
+  \begin{ruledtabular}
+  \begin{tabular}{ccccccc}
     \multirow{2}{*}{System} & \multirow{2}{*}{BITSS} &
@@
     Wetting  & \num{12100} & \num{17262} & \num{17840} & \num{17721} & \num{20221} & \num{48286} \\
-    \hline\hline
-  \end{tabular*}
+  \end{tabular}
+  \end{ruledtabular}
   \caption{\label{tab:speed}
-    \hl{
     Number of potential gradient calculations required to reach the transition state for the three comparison examples.
     The approach combining DNEB and hybrid eigenvector-following (HEVF) has been run for different numbers of images.
-    Convergence is determined as when the root-mean-square of the gradient is less than $10^{-4}$.}
+    Convergence is determined as when the root-mean-square of the gradient is less than $10^{-4}$.
   }
@@
 
-\hl{In \mbox{\cref{tab:speed}}, we compare the speed of convergence to the transition state for BITSS, BITSS with hybrid eigenvector-following, and DNEB with hybrid eigenvector-following.
+In \cref{tab:speed}, we compare the speed of convergence to the transition state for BITSS, BITSS with hybrid eigenvector-following, and DNEB with hybrid eigenvector-following.
 We do not carry out systematic calculations combining the string method with hybrid eigenvector-following because the results are essentially similar to those for DNEB with hybrid eigenvector-following.
-We see that, for the examples in \mbox{\cref{tab:speed}}, the speed of BITSS with hybrid eigenvector-following does not significantly improve upon the speed of BITSS alone.
+We see that, for the examples in \cref{tab:speed}, the speed of BITSS with hybrid eigenvector-following does not significantly improve upon the speed of BITSS alone.
 Indeed, for the wetting example it is considerably slower.
@@
 For the Lennard-Jones cluster, a small number of images is the most efficient, while an intermediate number of images is optimal for the buckling problem because it will not converge to the correct transition state if there are too few images.
-Despite the large number of degrees of freedom, this buckling mode in {\cref{fig:speedtest}}c is known to exhibit a linear pathway close to the transition state, being controlled simply by the dimple depth increasing{\cite{Panter2019}}.
+Despite the large number of degrees of freedom, this buckling mode in \cref{fig:speedtest}c is known to exhibit a linear pathway close to the transition state, being controlled simply by the dimple depth increasing\cite{Panter2019}.
 On the other hand, for the droplet wetting example, DNEB-HEVF is considerably slower, even with a small number of images.
-This is in agreement with our expectation that BITSS offers an efficiency advantage for complex, non-linear pathways.}
+This is in agreement with our expectation that BITSS offers an efficiency advantage for complex, non-linear pathways.
 
@@
 
-\hl{An additional consideration is the case where the potential energy surface is flat at the top of the pathway.
+An additional consideration is the case where the potential energy surface is flat at the top of the pathway.
 There are two possibilities here, one is that the potential is flat in a direction perpendicular to the tangent of the pathway, such that the ridge is level.
 In this case BITSS is unaffected and it will be able to converge to some point along the ridge.
-An example of this is the free global rotation and translation of the Lennard-Jones cluster in {\cref{fig:speedtest}a}.
+An example of this is the free global rotation and translation of the Lennard-Jones cluster in \cref{fig:speedtest}a.
 The other possibility is that the flat mode is in the direction of the pathway.
 In this case there is no single transition state along the pathway, but instead a region.
-BITSS would be ill suited in this situation because the equal-energy constraint would not prevent the images from passing over the saddle and falling to a minimum.}
+BITSS would be ill suited in this situation because the equal-energy constraint would not prevent the images from passing over the saddle and falling to a minimum.
 
@@
 This has distinct advantages for complex pathways owing to the lack of a required initial pathway estimate, as well as the identification of the transition state that provides the overall energy barrier in multi-step pathways.
-\hl{From the speed analysis, we find that the combination of chain-of-states methods with single-ended transition state search methods provides good performance for near-linear pathways, such as for the Lennard-Jones cluster and cylindrical buckling.
+From the speed analysis, we find that the combination of chain-of-states methods with single-ended transition state search methods provides good performance for near-linear pathways, such as for the Lennard-Jones cluster and cylindrical buckling.
 However, for highly complex and non-linear pathways, as exhibited by the striped wetting example, BITSS is superior.
-Indeed, the demonstrated speed and memory-efficiency will be key as we move towards studying larger and more complex systems using BITSS.}
+Indeed, the demonstrated speed and memory-efficiency will be key as we move towards studying larger and more complex systems using BITSS.
 
@@
 In such cases, it may be possible to access transition states different from the most direct one by using a biased distance metric.
-\hl{A further investigation that is now open to pursue is when discontinuities in the landscape occur at `stationary points' (now properly referred to as critical points).
+A further investigation that is now open to pursue is when discontinuities in the landscape occur at `stationary points' (now properly referred to as critical points).
 In this case, a transition state can no longer be defined by its Hessian eigenvalues, but instead is more broadly defined as a region of locally minimal energy that separates two basins of attraction to minima.
-Overall, it will be interesting to explore how BITSS enables access to even more challenging landscapes, and those not yet amenable to traditional landscape exploration techniques.}
+Overall, it will be interesting to explore how BITSS enables access to even more challenging landscapes, and those not yet amenable to traditional landscape exploration techniques.
 
@@
 \section{Energy and gradient expressions for the example systems}
-\subsection{\hl{Hook potential equation}}\label{sec:bracketingpotential}
-\hl{
-The 2D potential used for the comparison of bracketing methods in {\cref{fig:bracketing}} uses a sum of Gaussian potentials, {\cref{eq:bracketingparams}}, the parameters for which are provided in \mbox{\cref{tab:bracketingparams}}.
-}
+\subsection{Hook potential equation}\label{sec:bracketingpotential}
+The 2D potential used for the comparison of bracketing methods in \cref{fig:bracketing} uses a sum of Gaussian potentials, \cref{eq:bracketingparams}, the parameters for which are provided in \cref{tab:bracketingparams}.
 \begin{equation}
@@
 \begin{table}[ht]
+  \begin{ruledtabular}
   \begin{tabular}{ccccc}
-    \hline\hline
     $a$  & $b_x$ & $b_x$ & $c_x$ & $c_y$ \\
@@
     0.5  &  -2   &   0   &   1   &   1   \\
-    \hline\hline
   \end{tabular}
+  \end{ruledtabular}
   \caption{\label{tab:bracketingparams}
-  \hl{
-    Parameters for the Gaussians to produce the potential used in {\cref{fig:bracketing}}.
-  }
+    Parameters for the Gaussians to produce the potential used in \cref{fig:bracketing}.
   }
@@
 %% start bib
-\bibliographystyle{aipnum4-1}
+% \bibliographystyle{aipnum4-1}
 \bibliography{bibexport.bib}

### 2022-08-22 fig/make_speedtest/make_sw.py
Removed DNEB / string speed comparison figure

@@ -31,7 +31,7 @@ levels = np.linspace(limits[0], limits[1], 7)
 
 ##### Visualise
 for i, state in enumerate(data):
-    fig = plt.figure(figsize=(5,5))
+    fig = plt.figure(figsize=(5,3))
     ax = plt.axes((0.01,0.01,0.98,0.98))
     plt.axis('off')
     ax.set_aspect('equal')
@@ -39,7 +39,7 @@ for i, state in enumerate(data):
     plt.contourf(state.T, cmap='Blues', levels=levels)
     plt.pcolormesh(surface_x, surface_y, surface, cmap='Greys_r', vmax=140, zorder=2)
 
-    plt.ylim((surface_y[0,0], n/2))
+    plt.ylim((surface_y[0,0], n*2/5))
     ax.axhline(surface_y[0,0], c='k')
     ax.axhline(surface_y[0,1], c='k')
 

### 2022-08-22 fig/make_speedtest/plot.py

@@ -8,114 +8,34 @@ import pyutils.latexify as lt
 # Get default style for paper
 import sys; sys.path.insert(0, '..')
 import style
-lt.update_width('aip-double')
+lt.update_width('aip-single')
 
 # Data generated by energyLandscapes/bits_test/speed_test/{system}/view_convergence.py
 
 def str_converter(instr):
     return np.fromstring(instr[1:-1],sep=' ')
 
-hd11 = 0.045
-hd12 = 0.01
-hd2 = -0.01
-h1 = 0.4/3 # height of lower axes relative to width
-h2 = 1/9 # height of upper axes relative to width
-h = hd11 + hd12 + hd2 + 2*h1 + h2
-fig = lt.figure(1, h)
+w = 3/5
+hi = [1/3, 1/3, 1/5] # height of axes relative to width
+hd = 0
+h = np.sum(hi) + 2*hd
+fig = lt.figure(w, h)
 
 for isub, subfig in enumerate(['a', 'b', 'c']):
 
-    ### Load data
-    if (subfig == 'a'):
-        file = 'lj_data'
-    elif (subfig == 'b'):
-        file = 'cb_data'
-    elif (subfig == 'c'):
-        file = 'sw_data'
-    df = pd.read_csv(file, converters={'calls':str_converter, 'distance':str_converter})
-
-    bits_data = df[df['method']=='bits']
-    bits_calls = bits_data['calls'][0]
-    bits_dist = bits_data['distance'][0]
-
-    string_data = df[df['method']=='string']
-    string_n = np.array(string_data['n'])
-    string_calls = np.array(string_data['calls'])
-    string_dist = np.array(string_data['distance'])
-
-    dneb_data = df[df['method']=='dneb']
-    dneb_n = np.array(dneb_data['n'])
-    dneb_calls = np.array(dneb_data['calls'])
-    dneb_dist = np.array(dneb_data['distance'])
-
-
-    ### Plot data
-    x0 = isub/3
-    xd0 = 0.055
-    w1 = 1/3-0.005 - xd0
-    if (isub == 0):
-        x0 = x0 + 0.01
-        w1 = w1 - 0.01
-    ax1 = fig.add_axes((x0+xd0, hd11/h, w1, h1/h))
[…]

### 2022-08-22 manuscript.tex
Tidy up manuscript
Renamed speedtest -> testsystems

@@
 
-\usepackage{xcolor}
-\usepackage{soul}
-
 % Figures
@@
 \usepackage{multirow}
-% \setlength{\tabcolsep}{4pt}
 
@@
 \Crefname{figure}{Fig.}{Figs.}
-
-% \usepackage[mathlines]{lineno}
-% \linenumbers\relax
 
@@
 \begin{figure*}[tb]
-  \includegraphics[width=\linewidth]{speedtest.pdf}
-  \caption{\label{fig:speedtest}
+  \includegraphics[width=\linewidth]{testsystems.pdf}
+  \caption{\label{fig:testsystems}
     Comparisons between BITSS, DNEB, and the string method in the distance from the transition state as a function of the number of calculations of the energy gradient.
@@
 Here, the 14 degrees of freedom are the particle coordinates.
-The characteristic transition shown in \cref{fig:speedtest}a sees a particle rearrangement between two close-packed clusters.
+The characteristic transition shown in \cref{fig:testsystems}a sees a particle rearrangement between two close-packed clusters.
 
@@
 The \num{35400} degrees of freedom are the node coordinates in three-dimensional space.
-The characteristic transition in \cref{fig:speedtest}b shows the formation of a stable dimple from an initially unbuckled cylinder.
+The characteristic transition in \cref{fig:testsystems}b shows the formation of a stable dimple from an initially unbuckled cylinder.
 This transition is essential to capture to predict mechanical failure under strain \cite{Panter2019,Virot2017}.
@@
 Droplet transitions on patterned surfaces such as this are vital to understand as powerful bio-inspired liquid manipulation strategies  \cite{Kusumaatmaja2006,Brown2016}.
-In the example shown in \cref{fig:speedtest}c, a droplet transitions from two hydrophilic patches to one patch.
+In the example shown in \cref{fig:testsystems}c, a droplet transitions from two hydrophilic patches to one patch.
 Here, the system is represented by a diffuse-interface model, in which the \num{40000} degrees of freedom are the local fluid compositions at each site of the discretised domain.
@@
 
-{\Cref{fig:speedtest}} shows the comparison between BITSS, DNEB and the string method.
+{\Cref{fig:testsystems}} shows the comparison between BITSS, DNEB and the string method.
 Here, the $x$-axis corresponds to the number of calculations of the potential gradient.
@@
 
-In \cref{fig:speedtest}, for each system, BITSS quickly converges to the transition state.
+In \cref{fig:testsystems}, for each system, BITSS quickly converges to the transition state.
 In contrast, DNEB and the string method converge quickly to an approximation of the minimum energy pathway.
 However, as the images are spaced along the chain of states, it is unlikely that they closely approach the transition state.
-It is interesting to note that for the high-dimensional, non-linear pathways of wetting example shown in \cref{fig:speedtest}c, DNEB and the string method do not substantially reduce the distance to the transition state compared to the initial interpolation.
+It is interesting to note that for the high-dimensional, non-linear pathways of wetting example shown in \cref{fig:testsystems}c, DNEB and the string method do not substantially reduce the distance to the transition state compared to the initial interpolation.
 
@@
 One common set of methods are the climbing image hybrid methods \cite{Henkelman2000a,E2007}, but if the pathway is non-linear these can require a large number of images.
-For example, in the wetting example of \cref{fig:speedtest}c, we find even an 100-image initial double-ended search is not sufficient for the climbing image method to then successfully refine the transition state.
+For example, in the wetting example of \cref{fig:testsystems}c, we find even an 100-image initial double-ended search is not sufficient for the climbing image method to then successfully refine the transition state.
 Hybrid eigenvector-following (HEVF) methods \cite{Cerjan1981} are another commonly used approach, starting from the state with the highest energy on the chain.
@@
 For the Lennard-Jones cluster, a small number of images is the most efficient, while an intermediate number of images is optimal for the buckling problem because it will not converge to the correct transition state if there are too few images.
-Despite the large number of degrees of freedom, this buckling mode in \cref{fig:speedtest}c is known to exhibit a linear pathway close to the transition state, being controlled simply by the dimple depth increasing\cite{Panter2019}.
+Despite the large number of degrees of freedom, this buckling mode in \cref{fig:testsystems}c is known to exhibit a linear pathway close to the transition state, being controlled simply by the dimple depth increasing\cite{Panter2019}.
 On the other hand, for the droplet wetting example, DNEB-HEVF is considerably slower, even with a small number of images.
@@
 In this case BITSS is unaffected and it will be able to converge to some point along the ridge.
-An example of this is the free global rotation and translation of the Lennard-Jones cluster in \cref{fig:speedtest}a.
+An example of this is the free global rotation and translation of the Lennard-Jones cluster in \cref{fig:testsystems}a.
 The other possibility is that the flat mode is in the direction of the pathway.
@@
 These include systems with very short range interactions, such as in colloidal clusters, or hard contact forces, such as in the folding of elastic materials, or locomotion and environmental interaction in robotics.
-
-% Throughout, we have demonstrated BITSS as a standalone method for the precise location of transition states.
-% However, hybrid methods may also be employed to further increase speed and efficiency.
-% Either BITSS could be used to approximately locate the transition state followed by a single ended method for refinement, or BITSS can be used as a refinement method, complimentary to existing chain of states implementations.
-% This is scope for possible future work, and could be compared against other existing hybrid methods.
 
@@
 \begin{figure}[htb]
-  \includegraphics{fig/BAHschematic.pdf}
+  \includegraphics{BAHschematic.pdf}
   \caption{\label{fig:BAHschematic}
@@
 
-%% start bib
-% \bibliographystyle{aipnum4-1}
 \bibliography{bibexport.bib}
-% % \bibliography{../../library.bib}
-%% mid bib
-%% end bib
 

### 2022-08-22 fig/create_figs.sh

@@ -1,6 +1,6 @@
 #!/bin/bash
 
-py_figs=('toy2d' 'bracketing' 'speedtest' 'adaptivemesh' 'flatdiscontinuous')
+py_figs=('toy2d' 'bracketing' 'testsystems' 'adaptivemesh' 'flatdiscontinuous')
 tex_figs=('BAHschematic')
 
 for fig in ${py_figs[@]}; do

### 2022-08-22 fig/make_testsystems/plot.py

@@ -10,8 +10,6 @@ import sys; sys.path.insert(0, '..')
 import style
 lt.update_width('aip-single')
 
-# Data generated by energyLandscapes/bits_test/speed_test/{system}/view_convergence.py
-
 def str_converter(instr):
     return np.fromstring(instr[1:-1],sep=' ')
 
@@ -39,4 +37,4 @@ for isub, subfig in enumerate(['a', 'b', 'c']):
         if (i==1):
             tmp_ax.text(0.25, 1, '*', va='top', ha='center', size='xx-large', transform=tmp_ax.transAxes)
 
-lt.savefig(f'../speedtest.pdf')
+lt.savefig(f'../testsystems.pdf')

### 2022-08-22 manuscript.tex
Updated size and caption of fig 3

@@
 \subsection{Comparison with chain-of-states methods}
-\begin{figure*}[tb]
-  \includegraphics[width=\linewidth]{testsystems.pdf}
+\begin{figure}[tb]
+  \includegraphics{testsystems.pdf}
   \caption{\label{fig:testsystems}
-    Comparisons between BITSS, DNEB, and the string method in the distance from the transition state as a function of the number of calculations of the energy gradient.
-    Three test systems are used: (a) a Lennard-Jones seven-particle cluster, (b) cylindrical shell buckling, and (c) wetting of a chemically-striped surface.
+    The three systems used for comparison with chain-of-states methods.
+    These are: (a) a Lennard-Jones seven-particle cluster, (b) cylindrical shell buckling, and (c) wetting of a chemically-striped surface.
     The configurations shown correspond to the two minimum energy states and the transition state, marked by an asterisk.
-    The string method and DNEB are repeated with a differing number of images, as listed in the legend in (c).
   }
-\end{figure*}
+\end{figure}
 

### 2022-08-22 fig/make_testsystems/plot.py

@@ -13,7 +13,7 @@ lt.update_width('aip-single')
 def str_converter(instr):
     return np.fromstring(instr[1:-1],sep=' ')
 
-w = 3/5
+w = 4/5
 hi = [1/3, 1/3, 1/5] # height of axes relative to width
 hd = 0
 h = np.sum(hi) + 2*hd

### 2022-08-22 manuscript.tex
Added CINEB to table

@@
 \usepackage{multirow}
+\usepackage{booktabs}
+\newcommand{\tworow}[1]{\multirow{2}{*}[-0.5\dimexpr \aboverulesep + \belowrulesep + \cmidrulewidth]{#1}}
 
@@
 \subsection{Comparison with chain-of-states methods}
-\begin{figure}[tb]
+\begin{figure}[htb]
   \includegraphics{testsystems.pdf}
@@
 
-\begin{table}[ht]
+\begin{table*}[tb]
   \begin{ruledtabular}
-  \begin{tabular}{ccccccc}
-    \multirow{2}{*}{System} & \multirow{2}{*}{BITSS} &
-    \multirow{2}{*}{\begin{tabular}[c]{@{}c@{}}BITSS-\\HEVF\end{tabular}} &
-    \multicolumn{4}{c}{DNEB-HEVF} \\
-             &             &             & 3           & 5           & 10          & 20          \\
+  \begin{tabular}{c cc cccc cccc}
+    \tworow{System} & \tworow{BITSS} &
+      \tworow{\begin{tabular}[c]{@{}c@{}}BITSS-\\HEVF\end{tabular}} &
+      \multicolumn{4}{c}{DNEB-HEVF} & \multicolumn{4}{c}{CINEB} \\
+    \cmidrule(lr){4-7}\cmidrule(lr){8-11}
+             &             &             & 3           & 5           & 10          & 20          & 3   & 5          & 10          & 20          \\
     \hline
-    LJ-7     & 148         & 144         & 135         & 138         & 208         & 361         \\
-    Buckling & \num{12866} & \num{14446} & ---         & \num{7315}  & \num{6242}  & \num{12094} \\
-    Wetting  & \num{12100} & \num{17262} & \num{17840} & \num{17721} & \num{20221} & \num{48286} \\
+    LJ-7     & 148         & 144         & 135         & 138         & 208         & 361         & 30  & 153        & 2000        & 1692        \\
+    Buckling & \num{12866} & \num{14446} & ---         & \num{7315}  & \num{6242}  & \num{12094} & --- & \num{8352} & \num{19360} & \num{77904} \\
+    Wetting  & \num{12100} & \num{17262} & \num{17840} & \num{17721} & \num{20221} & \num{48286} & --- & ---        & ---         & ---         \\
   \end{tabular}
@@
     Number of potential gradient calculations required to reach the transition state for the three comparison examples.
-    The approach combining DNEB and hybrid eigenvector-following (HEVF) has been run for different numbers of images.
-    Convergence is determined as when the root-mean-square of the gradient is less than $10^{-4}$.
+    The climbing-image nudged-elastic-band (CINEB) and DNEB with hybrid eigenvector-following (HEVF) methods have been run for different numbers of images.
+    Convergence is determined to be when the root-mean-square of the gradient at the estimate for the transition state is less than $10^{-4}$.
+    The fields left blank indicate that the method has not converged to the correct transition state.
   }
-\end{table}
+\end{table*}
 

### 2022-08-22 manuscript.tex
Added parameters for toy2d potential

@@
     Trajectories of the bracketing methods on a hooked potential with a single saddle point.
-    The equation for this potential is provided in \cref{sec:bracketingpotential}.
+    The equation for this potential is provided in \cref{sec:2dpotentials}.
     The minimum energy pathway is shown by the dashed line.
@@
 \section{Energy and gradient expressions for the example systems}
-\subsection{Hook potential equation}\label{sec:bracketingpotential}
-The 2D potential used for the comparison of bracketing methods in \cref{fig:bracketing} uses a sum of Gaussian potentials, \cref{eq:bracketingparams}, the parameters for which are provided in \cref{tab:bracketingparams}.
+\subsection{2D potentials}\label{sec:2dpotentials}
+The 2D potentials in \cref{fig:toy2d,fig:bracketing} use a sum of Gaussian potentials, \cref{eq:gaussianpeaks}, the parameters for which are provided in \cref{tab:toy2dparams,tab:bracketingparams}.
 \begin{equation}
-  E(x,y) = \sum_i a_i \exp\!\left( \frac{(x-b_{x,i})^2}{c_{x,i}} + \frac{(y-b_{y,i})^2}{c_{y,i}} \right)
-  \label{eq:bracketingparams}
+  E(x,y) = \sum_i a_i \exp\!\left( - \frac{(x-b_{x,i})^2}{c_{x,i}} - \frac{(y-b_{y,i})^2}{c_{y,i}} \right)
+  \label{eq:gaussianpeaks}
 \end{equation}
+
 \begin{table}[ht]
@@
   \begin{tabular}{ccccc}
-    $a$  & $b_x$ & $b_x$ & $c_x$ & $c_y$ \\
+    $a$ & $b_x$ & $b_y$ & $c_x$ & $c_y$ \\
+    \hline
+    -3  & -1.4  &   0   &   1   &   1   \\
+    -2  &  1.4  &   0   &   1   &   1   \\
+    -1  &  0.07 &   1   &   1   &   1   \\
+  \end{tabular}
+  \end{ruledtabular}
+  \caption{\label{tab:toy2dparams}
+    Parameters for the Gaussians to produce the potential used in \cref{fig:toy2d}.
+  }
+\end{table}
+
+\begin{table}[ht]
+  \begin{ruledtabular}
+  \begin{tabular}{ccccc}
+    $a$  & $b_x$ & $b_y$ & $c_x$ & $c_y$ \\
     \hline

### 2022-08-28 manuscript.tex
Rewritten CoS section to remove base methods comparison

@@
 This process is completed once a suitable convergence criterion is reached.
-This can either be based upon the separation between the states, or the size of gradient at the midpoint between them.
+This can either be based upon the separation between the states, the size of gradient at the midpoint between them, or the change in the position of the midpoint.
 
@@
 \subsection{Comparison with chain-of-states methods}
-\begin{figure}[htb]
+In contrast to BITSS, chain-of-states methods do not typically find transition states within a reasonable accuracy.
+Instead, they are used to find the full pathway (or an approximation thereof), and a secondary method can then be used to refine to the transition state.
+Because these methods can identify multiple transition state candidates, they are advantageous for pathways with many intermediate minima.
+However, for systems with few or just a single transition state along the pathways, BITSS offers the possibility for improved efficiency and reduced memory requirements, since just two states are being optimised.
+This is particularly likely to be true for complex, non-linear pathways which can need a large number of states to accurately approximate the pathway.
+Also, a complicated initial interpolation may be necessary for these pathways, whereas BITSS requires no such initialisation.
+
+Here we compare the speeds of convergence of BITSS to two often-used chain-of-states methods for finding transition states: climbing-image nudged elastic band (CINEB) \cite{Henkelman2000a}, and DNEB with hybrid eigenvector following (DNEB-HEVF) \cite{Cerjan1981}.
+It is also possible to use hybrid methods based upon the string method, although the results are expected to be similar.
+Further, here we aim to observe how the BITSS method behaves for different systems, rather than providing a comprehensive comparison of the available methods.
+
+The core of these methods involves minimising the total energy of a chain of states, connected by elastic springs to keep them equally spaced along the transition pathway.
+CINEB modifies this by altering the behaviour of the state with the highest energy.
+The direction of minimisation on this state is inverted in the along pathway direction, effectively converting the saddle point into a local minimum.
+Alternatively, DNEB-HEVF involves first minimising the chain of states until a criterion is met, for which we use the root-mean-square of the total energy gradient of the chain. 
+At this point eigenvector-following is performed from the highest energy state, moving uphill along the smallest eigenvector of the Hessian until it reaches the transition state.
+
+It is also possible to combine eigenvector-following with BITSS, which we also include in the comparison for comleteness.
+For this, the switch from BITSS to eigenvector-following is chosen to occur when the average of the two states changes by less than a tenth of the reduction in the distance given by \cref{eq:diteration}.
+
+\begin{figure}[tb]
   \includegraphics{testsystems.pdf}
@@
 \end{figure}
-
-Although reliable, chain-of-states approaches may need to use a large number of states in cases where the transition pathway is highly complex or non-linear.
-Since the BITSS method uses just two states, it has the potential to be more efficient in these cases.
-This is analysed here in two ways.
-First, we measure how quickly BITSS reduces the distance to the transition state, compared to the string method \cite{E2007} and DNEB \cite{Trygubenko2004} using 5, 10, and 20 images (including the endpoints, which are fixed in place at the minima).
-Second, these methods are often used in conjunction with another method to accurately find the transition state.
-Here we compare the number of potential gradient calculations required to reach the transition state for BITSS, BITSS in combination with hybrid eigenvector-following, and DNEB in combination with hybrid eigenvector-following.
 
@@
 The pathway for this example is highly non-linear in the coordinate space because each degree of freedom only varies when it is at the interface of the droplet.
-As a result, the initial pathway for the chain of states methods cannot be a simple linear interpolation.
+As a result, the initial pathway for the chain-of-states methods cannot be a simple linear interpolation.
 Instead, the position of a semi-circular droplet is interpolated between the two final positions.
-In contrast, it is unnecessary to assume any initial interpolation for the BITSS method.
-
-{\Cref{fig:testsystems}} shows the comparison between BITSS, DNEB and the string method.
-Here, the $x$-axis corresponds to the number of calculations of the potential gradient.
-The measure in the $y$-axis is the distance from the true transition state.
-For BITSS, the average of the two states is used for this, whereas for the chain-of-states methods, the closest point on a cubic spline interpolation is used.
-The parameters used in the chain-of-states methods are chosen such that they optimise the speed of convergence.
-For the string method, this is the number of downhill iterations before the images are redistributed.
-The optimal values are found to be 2, 50, and 20 for the particle cluster, cylindrical buckling, and striped wetting examples, respectively.
-In the case of DNEB, the spring constant between the images is optimised instead.
-The spring constants that have been used are $0.1$, $0.01$, and $10^{-4}$ for the three respective systems.
-
-In \cref{fig:testsystems}, for each system, BITSS quickly converges to the transition state.
-In contrast, DNEB and the string method converge quickly to an approximation of the minimum energy pathway.
-However, as the images are spaced along the chain of states, it is unlikely that they closely approach the transition state.
-It is interesting to note that for the high-dimensional, non-linear pathways of wetting example shown in \cref{fig:testsystems}c, DNEB and the string method do not substantially reduce the distance to the transition state compared to the initial interpolation.
-
-To accurately obtain the transition state, the chain-of-states methods are often used in conjunction with another refinement method.
-One common set of methods are the climbing image hybrid methods \cite{Henkelman2000a,E2007}, but if the pathway is non-linear these can require a large number of images.
-For example, in the wetting example of \cref{fig:testsystems}c, we find even an 100-image initial double-ended search is not sufficient for the climbing image method to then successfully refine the transition state.
-Hybrid eigenvector-following (HEVF) methods \cite{Cerjan1981} are another commonly used approach, starting from the state with the highest energy on the chain.
-In this approach the eigenvector with the smallest eigenvalue of the Hessian is found, along which direction the state is then moved uphill until eventually it reaches the transition state.
-For completeness, we also use a hybrid method combining eigenvector-following with BITSS.
-For this, the criterion for switching to the eigenvector-following is when the change in the average of the two states is less than a tenth of the distance reduction during a BITSS step.
 
@@
     LJ-7     & 148         & 144         & 135         & 138         & 208         & 361         & 30  & 153        & 2000        & 1692        \\
-    Buckling & \num{12866} & \num{14446} & ---         & \num{7315}  & \num{6242}  & \num{12094} & --- & \num{8352} & \num{19360} & \num{77904} \\
+    Buckling & \num{12866} & \num{14446} & \num{73694} & \num{7315}  & \num{6242}  & \num{12094} & --- & \num{8352} & \num{19360} & \num{77904} \\
     Wetting  & \num{12100} & \num{17262} & \num{17840} & \num{17721} & \num{20221} & \num{48286} & --- & ---        & ---         & ---         \\
@@
     Number of potential gradient calculations required to reach the transition state for the three comparison examples.
-    The climbing-image nudged-elastic-band (CINEB) and DNEB with hybrid eigenvector-following (HEVF) methods have been run for different numbers of images.
+    The climbing-image nudged-elastic-band (CINEB) and DNEB with hybrid eigenvector-following (DNEB-HEVF) methods have been run for different numbers of images.
     Convergence is determined to be when the root-mean-square of the gradient at the estimate for the transition state is less than $10^{-4}$.
@@
 
-In \cref{tab:speed}, we compare the speed of convergence to the transition state for BITSS, BITSS with hybrid eigenvector-following, and DNEB with hybrid eigenvector-following.
-We do not carry out systematic calculations combining the string method with hybrid eigenvector-following because the results are essentially similar to those for DNEB with hybrid eigenvector-following.
-We see that, for the examples in \cref{tab:speed}, the speed of BITSS with hybrid eigenvector-following does not significantly improve upon the speed of BITSS alone.
-Indeed, for the wetting example it is considerably slower.
-Secondly, when the pathways are near-linear, the combination of DNEB and HEVF leads to the fastest convergence.
-For the Lennard-Jones cluster, a small number of images is the most efficient, while an intermediate number of images is optimal for the buckling problem because it will not converge to the correct transition state if there are too few images.
-Despite the large number of degrees of freedom, this buckling mode in \cref{fig:testsystems}c is known to exhibit a linear pathway close to the transition state, being controlled simply by the dimple depth increasing\cite{Panter2019}.
-On the other hand, for the droplet wetting example, DNEB-HEVF is considerably slower, even with a small number of images.
-This is in agreement with our expectation that BITSS offers an efficiency advantage for complex, non-linear pathways.
+The results for the three systems are shown in \cref{tab:speed}.
+The first thing to note is that using hybrid eigenvector-following does not significantly improve the speed of BITSS.
+Indeed, for the wetting example it is actually considerably faster to use BITSS alone.
+Next, we see that the chain-of-states methods can be faster than BITSS for the systems with more linear pathways, particularly when using few images.
+Although, if too few images are used both CINEB and DNEB-HEVF can struggle, as seen for the cylindrical buckling with three images.
+Meanwhile, for the wetting example, CINEB does not converge to the transition state because the estimated tangent vector is highly inaccurate due to the non-linearity of the pathway.
+A large number of images would have to be used for it to converge.
+Furthermore, we find that BITSS is quite a bit faster than DNEB-HEVF in this case, in line with the prediction that BITSS is advantageous for complex, non-linear pathways.
+
+Overall, while BITSS does not realise the significant improvements in speed that were hypothesised, it is at least comparable with other popular methods, and appears faster for highly non-linear pathways.
+It also benefits from lower computational memory demand and not requiring an initial interpolation.
 

### 2022-08-28 manuscript.tex
Citations for hybrid string methods and studies comparing double ended methods.

@@
 Here we compare the speeds of convergence of BITSS to two often-used chain-of-states methods for finding transition states: climbing-image nudged elastic band (CINEB) \cite{Henkelman2000a}, and DNEB with hybrid eigenvector following (DNEB-HEVF) \cite{Cerjan1981}.
-It is also possible to use hybrid methods based upon the string method, although the results are expected to be similar.
-Further, here we aim to observe how the BITSS method behaves for different systems, rather than providing a comprehensive comparison of the available methods.
+It is also possible to use hybrid methods based upon the string method \cite{E2007,Zimmerman2013}, although the results are expected to be similar.
+Also, we primarily aim to observe how the BITSS method behaves for different systems, rather than providing a comprehensive comparison of the available methods, which has been performed in other works \cite{Koslover2007,Sheppard2008}.
 

### 2022-08-28 manuscript.tex
Add mark-up

@@
 \Crefname{figure}{Fig.}{Figs.}
+
+% Temporary
+\usepackage{soul}
+\soulregister\cite7
+\soulregister\cref7
+\soulregister\num7
+\soulregister\multicolumn7
+% \renewcommand{\hl}[1]{#1} % Uncomment to remove mark-up
 
@@
 \subsection{Comparison with chain-of-states methods}
+\hl{%
 In contrast to BITSS, chain-of-states methods do not typically find transition states within a reasonable accuracy.
@@
 It is also possible to use hybrid methods based upon the string method \cite{E2007,Zimmerman2013}, although the results are expected to be similar.
-Also, we primarily aim to observe how the BITSS method behaves for different systems, rather than providing a comprehensive comparison of the available methods, which has been performed in other works \cite{Koslover2007,Sheppard2008}.
+Also, primarily, we aim to observe how the BITSS method behaves for different systems, rather than providing a comprehensive comparison of the available methods, which has been performed in other works \cite{Koslover2007,Sheppard2008}.
 
@@
 For this, the switch from BITSS to eigenvector-following is chosen to occur when the average of the two states changes by less than a tenth of the reduction in the distance given by \cref{eq:diteration}.
+}
 
@@
   \caption{\label{fig:testsystems}
-    The three systems used for comparison with chain-of-states methods.
-    These are: (a) a Lennard-Jones seven-particle cluster, (b) cylindrical shell buckling, and (c) wetting of a chemically-striped surface.
+    \hl{The three systems used for comparison with chain-of-states methods.
+    These are: (a) a Lennard-Jones seven-particle cluster, (b) cylindrical shell buckling, and (c) wetting of a chemically-striped surface.}
     The configurations shown correspond to the two minimum energy states and the transition state, marked by an asterisk.
@@
 
+\hl{%
 Three diverse systems are used for this comparison, exhibiting a broad range of energy landscapes.
@@
 This transition is essential to capture to predict mechanical failure under strain \cite{Panter2019,Virot2017}.
+}
 
+\begin{table*}[tb]
+  \begin{ruledtabular}
+  \begin{tabular}{c cc cccc cccc}
+    \tworow{System} & \tworow{BITSS} &
+      \tworow{\begin{tabular}[c]{@{}c@{}}BITSS-\\HEVF\end{tabular}} &
+        \multicolumn{4}{c}{DNEB-HEVF} & \multicolumn{4}{c}{\hl{CINEB}} \\
+    \cmidrule(lr){4-7}\cmidrule(lr){8-11}
+             &             &             & 3           & 5           & 10          & 20          & \hl{3  } & \hl{5         } & \hl{10         } & \hl{20         } \\
+    \hline                                                                                                                                             
+    LJ-7     & 148         & 144         & 135         & 138         & 208         & 361         & \hl{30 } & \hl{153       } & \hl{2000       } & \hl{1692       } \\
+    Buckling & \num{12866} & \num{14446} & \num{73694} & \num{7315}  & \num{6242}  & \num{12094} & \hl{---} & \hl{\num{8352}} & \hl{\num{19360}} & \hl{\num{77904}} \\
+    Wetting  & \num{12100} & \num{17262} & \num{17840} & \num{17721} & \num{20221} & \num{48286} & \hl{---} & \hl{---       } & \hl{---        } & \hl{---        } \\
+  \end{tabular}
+  \end{ruledtabular}
+  \caption{\label{tab:speed}
+    Number of potential gradient calculations required to reach the transition state for the three comparison examples.
+    \hl{The climbing-image nudged-elastic-band (CINEB) and DNEB with hybrid eigenvector-following (DNEB-HEVF) methods have been run for different numbers of images.
+    Convergence is determined to be when the root-mean-square of the gradient at the estimate for the transition state is less than $10^{-4}$.
+    The fields left blank indicate that the method has not converged to the correct transition state.
+    }
+  }
+\end{table*}
+
+\hl{%
 The final system involves a droplet situated on a chemically striped surface with both hydrophilic and hydrophobic regions.
@@
 Instead, the position of a semi-circular droplet is interpolated between the two final positions.
+}
 
-\begin{table*}[tb]
-  \begin{ruledtabular}
-  \begin{tabular}{c cc cccc cccc}
-    \tworow{System} & \tworow{BITSS} &
-      \tworow{\begin{tabular}[c]{@{}c@{}}BITSS-\\HEVF\end{tabular}} &
-      \multicolumn{4}{c}{DNEB-HEVF} & \multicolumn{4}{c}{CINEB} \\
-    \cmidrule(lr){4-7}\cmidrule(lr){8-11}
-             &             &             & 3           & 5           & 10          & 20          & 3   & 5          & 10          & 20          \\
-    \hline
-    LJ-7     & 148         & 144         & 135         & 138         & 208         & 361         & 30  & 153        & 2000        & 1692        \\
-    Buckling & \num{12866} & \num{14446} & \num{73694} & \num{7315}  & \num{6242}  & \num{12094} & --- & \num{8352} & \num{19360} & \num{77904} \\
-    Wetting  & \num{12100} & \num{17262} & \num{17840} & \num{17721} & \num{20221} & \num{48286} & --- & ---        & ---         & ---         \\
-  \end{tabular}
-  \end{ruledtabular}
-  \caption{\label{tab:speed}
-    Number of potential gradient calculations required to reach the transition state for the three comparison examples.
-    The climbing-image nudged-elastic-band (CINEB) and DNEB with hybrid eigenvector-following (DNEB-HEVF) methods have been run for different numbers of images.
-    Convergence is determined to be when the root-mean-square of the gradient at the estimate for the transition state is less than $10^{-4}$.
-    The fields left blank indicate that the method has not converged to the correct transition state.
-  }
-\end{table*}
-
+\hl{%
 The results for the three systems are shown in \cref{tab:speed}.
@@
 It also benefits from lower computational memory demand and not requiring an initial interpolation.
+}
 
@@
   \caption{\label{tab:toy2dparams}
-    Parameters for the Gaussians to produce the potential used in \cref{fig:toy2d}.
+    \hl{Parameters for the Gaussians to produce the potential used in \cref{fig:toy2d}.}
   }
@@
   \begin{tabular}{ccccc}
-    $a$  & $b_x$ & $b_y$ & $c_x$ & $c_y$ \\
+    $a$  & $b_x$ & \hl{$b_y$} & $c_x$ & $c_y$ \\
     \hline

### 2022-08-30 manuscript.tex
Jack and Halim's changes to CoS section

@@
 % Temporary
+\usepackage{xcolor}
 \usepackage{soul}
@@
 \hl{%
-In contrast to BITSS, chain-of-states methods do not typically find transition states within a reasonable accuracy.
-Instead, they are used to find the full pathway (or an approximation thereof), and a secondary method can then be used to refine to the transition state.
-Because these methods can identify multiple transition state candidates, they are advantageous for pathways with many intermediate minima.
-However, for systems with few or just a single transition state along the pathways, BITSS offers the possibility for improved efficiency and reduced memory requirements, since just two states are being optimised.
-This is particularly likely to be true for complex, non-linear pathways which can need a large number of states to accurately approximate the pathway.
-Also, a complicated initial interpolation may be necessary for these pathways, whereas BITSS requires no such initialisation.
+In contrast to BITSS, chain-of-states methods do not typically find transition states directly.
+Instead, they are designed to find the full pathway (or an approximation thereof), and a secondary method can then be used to refine to the transition state.
+As we will demonstrate, this strategy is successful for simple, linear pathways, but faces two key challenges when the pathway is highly non-linear.
+Firstly, for such complex pathways, a large number of states are required to sufficiently approximate the minimum energy pathway.
+The second is that choosing a suitable initial interpolation can be problematic to achieve.
+BITSS is advantageous in both these regards, as only two states are evolved, regardless of the pathway complexity, and no initial interpolation is required.
+For these advantages to be of practical use, BITSS must demonstrate at least a comparable speed of convergence to the transition states, relative to these hybrid chain-of-states methods, which we now investigate.
 
-Here we compare the speeds of convergence of BITSS to two often-used chain-of-states methods for finding transition states: climbing-image nudged elastic band (CINEB) \cite{Henkelman2000a}, and DNEB with hybrid eigenvector following (DNEB-HEVF) \cite{Cerjan1981}.
-It is also possible to use hybrid methods based upon the string method \cite{E2007,Zimmerman2013}, although the results are expected to be similar.
-Also, primarily, we aim to observe how the BITSS method behaves for different systems, rather than providing a comprehensive comparison of the available methods, which has been performed in other works \cite{Koslover2007,Sheppard2008}.
-
+Here we compare the speeds of convergence of BITSS to two widely used approaches for finding transition states that employ chain-of-states methods: climbing-image nudged elastic band (CINEB) \cite{Henkelman2000a}, and DNEB with hybrid eigenvector following (DNEB-HEVF) \cite{Cerjan1981}.
+}{\color{blue}
+It is also possible to use the string method with a climbing image \cite{E2007} or eigenvector following \cite{Zimmerman2013}; although, in this case, the results are expected to be similar to the nudged-elastic-band methods.
+}\hl{%
 The core of these methods involves minimising the total energy of a chain of states, connected by elastic springs to keep them equally spaced along the transition pathway.
 CINEB modifies this by altering the behaviour of the state with the highest energy.
-The direction of minimisation on this state is inverted in the along pathway direction, effectively converting the saddle point into a local minimum.
+The direction of minimisation on this state is inverted along the pathway direction, effectively converting the saddle point into a local minimum.
 Alternatively, DNEB-HEVF involves first minimising the chain of states until a criterion is met, for which we use the root-mean-square of the total energy gradient of the chain.
 At this point eigenvector-following is performed from the highest energy state, moving uphill along the smallest eigenvector of the Hessian until it reaches the transition state.
-
-It is also possible to combine eigenvector-following with BITSS, which we also include in the comparison for comleteness.
-For this, the switch from BITSS to eigenvector-following is chosen to occur when the average of the two states changes by less than a tenth of the reduction in the distance given by \cref{eq:diteration}.
+It is also possible to combine eigenvector-following with BITSS, which we also include in the comparison for completeness.
+}{\color{red}
+Move this to methods: For this, the switch from BITSS to eigenvector-following is chosen to occur when the average of the two states changes by less than a tenth of the reduction in the distance given by \cref{eq:diteration}.
+}\hl{%
+We note that our aim in this section is to observe how the BITSS method behaves for different systems, rather than providing a comprehensive comparison of the currently available methods, which has been performed in other works \cite{Koslover2007,Sheppard2008}.
 }
@@
 The results for the three systems are shown in \cref{tab:speed}.
-The first thing to note is that using hybrid eigenvector-following does not significantly improve the speed of BITSS.
-Indeed, for the wetting example it is actually considerably faster to use BITSS alone.
-Next, we see that the chain-of-states methods can be faster than BITSS for the systems with more linear pathways, particularly when using few images.
-Although, if too few images are used both CINEB and DNEB-HEVF can struggle, as seen for the cylindrical buckling with three images.
-Meanwhile, for the wetting example, CINEB does not converge to the transition state because the estimated tangent vector is highly inaccurate due to the non-linearity of the pathway.
-A large number of images would have to be used for it to converge.
-Furthermore, we find that BITSS is quite a bit faster than DNEB-HEVF in this case, in line with the prediction that BITSS is advantageous for complex, non-linear pathways.
+First, we note that for all three systems, using hybrid eigenvector-following does not significantly improve the speed of BITSS.
+Indeed, for buckling and especially wetting, HEVF is detrimental to performance.
+Next, it is interesting to compare each method's performance between simple and complex pathways.
+In contrast to the wetting transition's highly non-linear pathway, the pathways of the LJ-7 rearrangement and the buckling system can be simply tracked following a gradual variation in the order parameters.
+For LJ-7, this is the translation of atoms 5 and 6, and for buckling, this is the radial displacement of the centre of the dimple \cite{Panter2019}.
+For the simpler pathways, BITSS is generally slower, but for the complex pathways, BITSS is faster.
+Moreover, we see that for the wetting example, CINEB does not converge to the transition state because the estimated tangent vector is highly inaccurate due to the non-linearity of the pathway.
 
-Overall, while BITSS does not realise the significant improvements in speed that were hypothesised, it is at least comparable with other popular methods, and appears faster for highly non-linear pathways.
-It also benefits from lower computational memory demand and not requiring an initial interpolation.
+For situations where memory is limited, it is important to minimise the number of images used.
+As is shown for cylindrical buckling with three images, efficiently finding the TS is challenging for both CINEB and DNEB-HEVF.
+BITSS however converges using only two images.
+
+However, if too few images are used (the minimum number of which is system dependant), both CINEB and DNEB-HEVF can struggle, as observed for the cylindrical buckling with three images.
 }
@@
 \end{align}
-where index $k$ denotes neighboring nodes at which the evaluation of the gradient uses $\phi_i$.
+where index $k$ denotes neighbouring nodes at which the evaluation of the gradient uses $\phi_i$.
+
+{\color{red}
+\section{Implementation of the hybrid methods, CINEB, DENB-HEVF, and BITSS-HEVF}
+JRP - Sam can you fill out this section to briefly detail the method parameters?
+Also, say that HEVF was performed using the program OPTIM, with the reference http://www-wales.ch.cam.ac.uk/software.html.
+}
 

### 2022-08-31 manuscript.tex
HEVF appendix and fixed endpoints

@@
 \soulregister\multicolumn7
-% \renewcommand{\hl}[1]{#1} % Uncomment to remove mark-up
+\renewcommand{\hl}[1]{#1} % Uncomment to remove mark-up
 
@@
 Here we compare the speeds of convergence of BITSS to two widely used approaches for finding transition states that employ chain-of-states methods: climbing-image nudged elastic band (CINEB) \cite{Henkelman2000a}, and DNEB with hybrid eigenvector following (DNEB-HEVF) \cite{Cerjan1981}.
+The core of these methods involves minimising the total energy of a chain of states, connected by elastic springs to keep them equally spaced along the transition pathway.
 }{\color{blue}
+We fix the two end-points at the minima, so the number of states that are minimised is two fewer than the number of states in the chain.
+}\hl{%
+CINEB modifies the method by altering the behaviour of the state with the highest energy.
+The direction of minimisation on this state is inverted along the pathway direction, effectively converting the saddle point into a local minimum.
+Alternatively, DNEB-HEVF involves first minimising the chain of states until a criterion is met, and then performing eigenvector-following from the highest energy state, moving uphill along the smallest eigenvector of the Hessian until it reaches the transition state.
+It is also possible to combine eigenvector-following with BITSS, which we also include in the comparison for completeness.
+}{\color{blue}
+Additional implementation details for these methods are included in \cref{sec:HEVFdetails}.
+
 It is also possible to use the string method with a climbing image \cite{E2007} or eigenvector following \cite{Zimmerman2013}; although, in this case, the results are expected to be similar to the nudged-elastic-band methods.
-}\hl{%
-The core of these methods involves minimising the total energy of a chain of states, connected by elastic springs to keep them equally spaced along the transition pathway.
-CINEB modifies this by altering the behaviour of the state with the highest energy.
-The direction of minimisation on this state is inverted along the pathway direction, effectively converting the saddle point into a local minimum.
-Alternatively, DNEB-HEVF involves first minimising the chain of states until a criterion is met, for which we use the root-mean-square of the total energy gradient of the chain.
-At this point eigenvector-following is performed from the highest energy state, moving uphill along the smallest eigenvector of the Hessian until it reaches the transition state.
-It is also possible to combine eigenvector-following with BITSS, which we also include in the comparison for completeness.
-}{\color{red}
-Move this to methods: For this, the switch from BITSS to eigenvector-following is chosen to occur when the average of the two states changes by less than a tenth of the reduction in the distance given by \cref{eq:diteration}.
 }\hl{%
@@
 For situations where memory is limited, it is important to minimise the number of images used.
-As is shown for cylindrical buckling with three images, efficiently finding the TS is challenging for both CINEB and DNEB-HEVF.
-BITSS however converges using only two images.
-
-However, if too few images are used (the minimum number of which is system dependant), both CINEB and DNEB-HEVF can struggle, as observed for the cylindrical buckling with three images.
+}{\color{blue}
+However, efficiently finding the TS is challenging for both CINEB and DNEB-HEVF if too few images are used, as observed for the cylindrical buckling with three images.
+BITSS, on the other hand, converges using only two images.
 }
@@
 
-{\color{red}
-\section{Implementation of the hybrid methods, CINEB, DENB-HEVF, and BITSS-HEVF}
-JRP - Sam can you fill out this section to briefly detail the method parameters?
-Also, say that HEVF was performed using the program OPTIM, with the reference http://www-wales.ch.cam.ac.uk/software.html.
+{\color{blue}
+\section{Implementation details for the DNEB-HEVF and BITSS-HEVF methods}\label{sec:HEVFdetails}
+In the hybrid eigenvector-following methods, criteria are used to determine when the initial method has converged sufficiently, at which point the eigenvector following begins.
+For BITSS, the criterion is when the average of the two states changes during a BITSS step by less than a tenth of the reduction in the separation given by \cref{eq:diteration}.
+As for DNEB, the root-mean-square of the total energy gradient of the chain of states is used with a convergence criterion of $10^{-3}$ for the particle cluster and cylindrical buckling systems, or $10^{-5}$ for the striped wetting.
+The eigenvector-following method itself was performed using the program OPTIM \cite{OPTIM}.
 }

### 2022-08-31 manuscript.tex
Spring constants

@@
 {\color{blue}
-\section{Implementation details for the DNEB-HEVF and BITSS-HEVF methods}\label{sec:HEVFdetails}
+\section{Implementation details for the CINEB, DNEB-HEVF, and BITSS-HEVF methods}\label{sec:HEVFdetails}
+The spring constants connecting the states in CINEB and DNEB are system dependent such that they keep the states equidistant without overwhelming the single state forces.
+The parameters chosen for this are $10^{-1}$ for the particle cluster, $10^{-2}$ for cylindrical buckling, and $10^{-6}$ for the striped wetting.
+
 In the hybrid eigenvector-following methods, criteria are used to determine when the initial method has converged sufficiently, at which point the eigenvector following begins.

### 2022-09-01 manuscript.tex
Halim's changes, consistent hyphons, removed blue

--- 2022-08-31 manuscript.tex
@@
 \soulregister\multicolumn7
-\renewcommand{\hl}[1]{#1} % Uncomment to remove mark-up
+% \renewcommand{\hl}[1]{#1} % Uncomment to remove mark-up
 
@@
 The second is that choosing a suitable initial interpolation can be problematic to achieve.
-BITSS is advantageous in both these regards, as only two states are evolved, regardless of the pathway complexity, and no initial interpolation is required.
-For these advantages to be of practical use, BITSS must demonstrate at least a comparable speed of convergence to the transition states, relative to these hybrid chain-of-states methods, which we now investigate.
+BITSS can be advantageous in both these regards, as only two states are evolved, regardless of the pathway complexity, and no initial interpolation is required.
 
-Here we compare the speeds of convergence of BITSS to two widely used approaches for finding transition states that employ chain-of-states methods: climbing-image nudged elastic band (CINEB) \cite{Henkelman2000a}, and DNEB with hybrid eigenvector following (DNEB-HEVF) \cite{Cerjan1981}.
+Here we compare the speeds of convergence of BITSS to two widely used approaches for finding transition states that employ chain-of-states methods: climbing image nudged elastic band (CINEB) \cite{Henkelman2000a}, and DNEB with hybrid eigenvector following (DNEB-HEVF) \cite{Cerjan1981}.
 The core of these methods involves minimising the total energy of a chain of states, connected by elastic springs to keep them equally spaced along the transition pathway.
-}{\color{blue}
 We fix the two end-points at the minima, so the number of states that are minimised is two fewer than the number of states in the chain.
-}\hl{%
 CINEB modifies the method by altering the behaviour of the state with the highest energy.
 The direction of minimisation on this state is inverted along the pathway direction, effectively converting the saddle point into a local minimum.
-Alternatively, DNEB-HEVF involves first minimising the chain of states until a criterion is met, and then performing eigenvector-following from the highest energy state, moving uphill along the smallest eigenvector of the Hessian until it reaches the transition state.
-It is also possible to combine eigenvector-following with BITSS, which we also include in the comparison for completeness.
-}{\color{blue}
+Alternatively, DNEB-HEVF involves first minimising the chain of states until a convergence criterion is met, and then performing hybrid eigenvector following from the highest energy state, moving uphill along the smallest eigenvector of the Hessian until it reaches the transition state.
+For completeness, we also combine hybrid eigenvector following with BITSS and include the results in the convergence comparison.
 Additional implementation details for these methods are included in \cref{sec:HEVFdetails}.
 
-It is also possible to use the string method with a climbing image \cite{E2007} or eigenvector following \cite{Zimmerman2013}; although, in this case, the results are expected to be similar to the nudged-elastic-band methods.
-}\hl{%
+It is also possible to use the string method with a climbing image \cite{E2007} or eigenvector following \cite{Zimmerman2013}; although, in this case, the results are expected to be similar to the nudged elastic band methods.
 We note that our aim in this section is to observe how the BITSS method behaves for different systems, rather than providing a comprehensive comparison of the currently available methods, which has been performed in other works \cite{Koslover2007,Sheppard2008}.
@@
     Number of potential gradient calculations required to reach the transition state for the three comparison examples.
-    \hl{The climbing-image nudged-elastic-band (CINEB) and DNEB with hybrid eigenvector-following (DNEB-HEVF) methods have been run for different numbers of images.
+    \hl{The climbing image nudged elastic band (CINEB) and DNEB with hybrid eigenvector following (DNEB-HEVF) methods have been run for different numbers of images.
     Convergence is determined to be when the root-mean-square of the gradient at the estimate for the transition state is less than $10^{-4}$.
@@
 The results for the three systems are shown in \cref{tab:speed}.
-First, we note that for all three systems, using hybrid eigenvector-following does not significantly improve the speed of BITSS.
+First, we note that for all three systems, using hybrid eigenvector following does not significantly improve the speed of BITSS.
 Indeed, for buckling and especially wetting, HEVF is detrimental to performance.
@@
 For situations where memory is limited, it is important to minimise the number of images used.
-}{\color{blue}
 However, efficiently finding the TS is challenging for both CINEB and DNEB-HEVF if too few images are used, as observed for the cylindrical buckling with three images.
@@
 
-{\color{blue}
-\section{Implementation details for the DNEB-HEVF and BITSS-HEVF methods}\label{sec:HEVFdetails}
-In the hybrid eigenvector-following methods, criteria are used to determine when the initial method has converged sufficiently, at which point the eigenvector following begins.
-For BITSS, the criterion is when the average of the two states changes during a BITSS step by less than a tenth of the reduction in the separation given by \cref{eq:diteration}.
-As for DNEB, the root-mean-square of the total energy gradient of the chain of states is used with a convergence criterion of $10^{-3}$ for the particle cluster and cylindrical buckling systems, or $10^{-5}$ for the striped wetting.
-The eigenvector-following method itself was performed using the program OPTIM \cite{OPTIM}.
+\hl{%
+\section{Implementation details for the CINEB, DNEB-HEVF, and BITSS-HEVF methods}\label{sec:HEVFdetails}
+The spring constants used to connect the states in the CINEB and DNEB methods are system dependent.
+They are chosen such that they keep the states equidistant without overwhelming the gradients arising from the potential energy landscapes under consideration.
+We employ $10^{-1}$ for the Lennard-Jones particle cluster, $10^{-2}$ for the cylindrical buckling example, and $10^{-6}$ for the striped wetting system.
+
+When hybrid eigenvector following is combined with BITSS or DNEB, we need to set out criteria to determine when the double-ended method has sufficiently converged, at which point the hybrid eigenvector following method begins.
+For BITSS, the criterion is when the average of the two states changes by less than a tenth of the reduction in the separation given by \cref{eq:diteration} during a BITSS step.
+For DNEB, the root-mean-square of the total energy gradient of the chain of states is used with a convergence criterion of $10^{-3}$ for the particle cluster and cylindrical buckling systems, and $10^{-5}$ for the striped wetting.
+We employ the hybrid eigenvector following method implemented in the program OPTIM \cite{OPTIM}.
 }

### 2022-09-01 manuscript.tex
Minor changes

@@
 The characteristic transition in \cref{fig:testsystems}b shows the formation of a stable dimple from an initially unbuckled cylinder.
-This transition is essential to capture to predict mechanical failure under strain \cite{Panter2019,Virot2017}.
+This transition is essential to capture and predict mechanical failure under strain \cite{Panter2019,Virot2017}.
 }
@@
 Moreover, we see that for the wetting example, CINEB does not converge to the transition state because the estimated tangent vector is highly inaccurate due to the non-linearity of the pathway.
+}
 
+\hl{%
 For situations where memory is limited, it is important to minimise the number of images used.
@@
 
+\section{Implementation details for the CINEB, DNEB-HEVF, and BITSS-HEVF methods}\label{sec:HEVFdetails}
 \hl{%
-\section{Implementation details for the CINEB, DNEB-HEVF, and BITSS-HEVF methods}\label{sec:HEVFdetails}
 The spring constants used to connect the states in the CINEB and DNEB methods are system dependent.

### 2022-09-01 manuscript.tex
Remove markup

--- 2022-09-01 manuscript.tex
@@
 \Crefname{figure}{Fig.}{Figs.}
-
-% Temporary
-\usepackage{xcolor}
-\usepackage{soul}
-\soulregister\cite7
-\soulregister\cref7
-\soulregister\num7
-\soulregister\multicolumn7
-% \renewcommand{\hl}[1]{#1} % Uncomment to remove mark-up
 
@@
 \subsection{Comparison with chain-of-states methods}
-\hl{%
 In contrast to BITSS, chain-of-states methods do not typically find transition states directly.
@@
 We note that our aim in this section is to observe how the BITSS method behaves for different systems, rather than providing a comprehensive comparison of the currently available methods, which has been performed in other works \cite{Koslover2007,Sheppard2008}.
-}
 
@@
   \caption{\label{fig:testsystems}
-    \hl{The three systems used for comparison with chain-of-states methods.
-    These are: (a) a Lennard-Jones seven-particle cluster, (b) cylindrical shell buckling, and (c) wetting of a chemically-striped surface.}
+    The three systems used for comparison with chain-of-states methods.
+    These are: (a) a Lennard-Jones seven-particle cluster, (b) cylindrical shell buckling, and (c) wetting of a chemically-striped surface.
     The configurations shown correspond to the two minimum energy states and the transition state, marked by an asterisk.
@@
 
-\hl{%
 Three diverse systems are used for this comparison, exhibiting a broad range of energy landscapes.
@@
 The characteristic transition in \cref{fig:testsystems}b shows the formation of a stable dimple from an initially unbuckled cylinder.
-This transition is essential to capture to predict mechanical failure under strain \cite{Panter2019,Virot2017}.
-}
+This transition is essential to capture and predict mechanical failure under strain \cite{Panter2019,Virot2017}.
 
@@
       \tworow{\begin{tabular}[c]{@{}c@{}}BITSS-\\HEVF\end{tabular}} &
-        \multicolumn{4}{c}{DNEB-HEVF} & \multicolumn{4}{c}{\hl{CINEB}} \\
+        \multicolumn{4}{c}{DNEB-HEVF} & \multicolumn{4}{c}{CINEB} \\
     \cmidrule(lr){4-7}\cmidrule(lr){8-11}
-             &             &             & 3           & 5           & 10          & 20          & \hl{3  } & \hl{5         } & \hl{10         } & \hl{20         } \\
+             &             &             & 3           & 5           & 10          & 20          & 3   & 5          & 10          & 20          \\
     \hline                                                                                                                                             
-    LJ-7     & 148         & 144         & 135         & 138         & 208         & 361         & \hl{30 } & \hl{153       } & \hl{2000       } & \hl{1692       } \\
-    Buckling & \num{12866} & \num{14446} & \num{73694} & \num{7315}  & \num{6242}  & \num{12094} & \hl{---} & \hl{\num{8352}} & \hl{\num{19360}} & \hl{\num{77904}} \\
-    Wetting  & \num{12100} & \num{17262} & \num{17840} & \num{17721} & \num{20221} & \num{48286} & \hl{---} & \hl{---       } & \hl{---        } & \hl{---        } \\
+    LJ-7     & 148         & 144         & 135         & 138         & 208         & 361         & 30  & 153        & 2000        & 1692        \\
+    Buckling & \num{12866} & \num{14446} & \num{73694} & \num{7315}  & \num{6242}  & \num{12094} & --- & \num{8352} & \num{19360} & \num{77904} \\
+    Wetting  & \num{12100} & \num{17262} & \num{17840} & \num{17721} & \num{20221} & \num{48286} & --- & ---        & ---         & ---         \\
   \end{tabular}
@@
     Number of potential gradient calculations required to reach the transition state for the three comparison examples.
-    \hl{The climbing image nudged elastic band (CINEB) and DNEB with hybrid eigenvector following (DNEB-HEVF) methods have been run for different numbers of images.
+    The climbing image nudged elastic band (CINEB) and DNEB with hybrid eigenvector following (DNEB-HEVF) methods have been run for different numbers of images.
     Convergence is determined to be when the root-mean-square of the gradient at the estimate for the transition state is less than $10^{-4}$.
@@
   }
-  }
 \end{table*}
 
-\hl{%
 The final system involves a droplet situated on a chemically striped surface with both hydrophilic and hydrophobic regions.
@@
 Instead, the position of a semi-circular droplet is interpolated between the two final positions.
-}
 
-\hl{%
 The results for the three systems are shown in \cref{tab:speed}.
@@
 BITSS, on the other hand, converges using only two images.
-}
 
@@
   \caption{\label{tab:toy2dparams}
-    \hl{Parameters for the Gaussians to produce the potential used in \cref{fig:toy2d}.}
+    Parameters for the Gaussians to produce the potential used in \cref{fig:toy2d}.
   }
@@
   \begin{tabular}{ccccc}
-    $a$  & $b_x$ & \hl{$b_y$} & $c_x$ & $c_y$ \\
+    $a$  & $b_x$ & $b_y$ & $c_x$ & $c_y$ \\
     \hline
@@
 
-\hl{%
 \section{Implementation details for the CINEB, DNEB-HEVF, and BITSS-HEVF methods}\label{sec:HEVFdetails}
@@
 We employ the hybrid eigenvector following method implemented in the program OPTIM \cite{OPTIM}.
-}
 
